### 2024-01-22 ms.qmd
Updates

---
docx: 
bibliography: "./bib/refs.bib"
csl: "./bib/animal-cognition.csl"
reference-doc: "./bib/tmpl.docx"
execute:
  echo: false
  error: false
  cache: false
  warning: false
link-citations: true
crossref:  
  fig-title: Fig    # (default is "Figure")
  title-delim: —     # (default is ":")
  fig-prefix: Fig.   # (default is "Figure")
  tbl-prefix: Table  # (default is "Table")
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: setup
pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
```

## Introduction

Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making [@shettleworth]. These cognitive processes underpin several aspects of animals' ecology such as foraging, mate choice, antipredatory strategies, and/or social behaviours, that are crucial for the survival and reproduction of animals [@dukas_evolutionary_2004]. Particularly, learning - the acquisition of neuronal representations of new information [@dukas_evolutionary_2004] - is seen as fundamental for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013]. However, in nature, there is individual variation in the capacity to acquire new information, influenced by factors like age, sex, gut microbiota, or the environment where they develop [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning]. In particular, early life conditions can play a pivotal role since the brain is especially susceptible to environmental influences during early stages of development [@zhu_prenatal_2004]. Therefore, investigating the effects of the developmental environment on learning can be essential to understand how individual variation in learning is shaped, and, in consequence, to predict animals' responses towards environmental change.  
In this sense, prenatal Glucocorticoids (GCs) - hormones related to organisms' response to stress [@sapolsky_how_2000] - and prenatal thermal environment are known to influence learning abilities in different taxa [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020]. For instance, some studies have demonstrated that prenatal stress and high prenatal GC levels impair learning [@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn], while others showed diverse effects depending on factors like subjects' sex or the nature of the learning task [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016]. Similarly, some experiments have shown significant impacts of prenatal temperature on learning in ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @abayarathna_effects_2020]. For example, high incubation temperatures have been linked with faster learning rates in skinks [@amiel_hotter_2012; @amiel_egg_2014], while velvet geckos incubated at temperatures over their natural range learn slower than those incubated within the natural thermal limits [@abayarathna_effects_2020]. In this vein, the effect of prenatal temperature appears to be linked to alterations in neural structure and metabolic activity [@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017; @beltran_are_2021] that share some similarities with those resulting from prenatal increased stress or GC levels [@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009]. This suggests that prenatal GCs and temperature can act on the same physiological mechanisms and, thus, both could interact to shape individual variation in learning abilities [@noble_developmental_2018]. Furthermore, GCs can play an pivotal role in determining vertebrate responses to elevated temperatures [@Crino_2023] potentially fostering natural interactions between temperature and GCs. However, despite the proximate similarities of prenatal GCs and temperature effects, and the potential role of GCs in vertebrates' response to elevated temperatures, our understanding of how these two factors interact remains incomplete.  
In this study, our objective is to explore the interactive effects between prenatal Glucocorticoids (GCs) and the prenatal thermal environment on learning. We utilized two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_), as model species. We experimentally increased Corticosterone (CORT) - the main GC in birds, reptiles, amphibians, and rodents [@Crino_2023] - levels in the eggs of these two species of skinks and then incubated them at two different temperatures in a 2X2 factorial design. Post-incubation, the juveniles were subjectd to a colour-associative and a reversal task to assess their learning abilities. Our hypothesis posits that changes in CORT levels and temperature during early development will induce sustained effects on brain's physiology that will ultimately impact learning skills. We predict that individuals exposed to high levels of CORT and/or low temperatures will perform less proficiently in both learning tasks compared to control individuals or those exposed to high temperatures. Additionally, we anticipate that incubation at high temperatures will mitigate the impact of CORT on skink performance, while cold incubation temperatures are expected to enhance the detrimental effects of CORT on learning. We also expect the treatments to affect both tasks equally, with those individuals exposed to high levels of CORT and/or low temperatures performing less proficiently in both tasks compared to control individuals or those exposed to high temperatures. Finally, we expect that the effects of the treatments will be similar in both species, as both species share similar life history traits and are closely related [@chapple_know_2011; @chapple_biology_2014], and other cognitive studies have not found any difference between species when tested in an associative learning task [@bezzina2014does].

## Methods

#### Subjects  
_L. guichenoti_ and _L. delicata_ are small (∼35--55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia [@chapple_know_2011]. Both species have similar breeding periods, but with some differences in reproductive output: while *L. delicata* lays 1 to 6 eggs in only one clutch per season, *L. guichenoti* clutches are smaller (1-5 eggs per clutch) but they usually lay two clutches per season [@chapple_know_2011; @chapple_biology_2014]. Also, some sudies have found some behavioural divergence between the two skinks [@chapple_know_2011]. _L. delicata_ is more exploratory and bolder than _L. guichenoti_ [@chapple_know_2011] which was related to the former's success as an invassive species [@chapple_know_2011; @bezzina2014does], but not with their ability to learn in an associatve learning task [@bezzina2014does].

#### Husbandry  
*Breeding colony* -- We tested juveniles coming from a breeding colony established in the lab since 2019. There is a total of 270 and 180 adults of *L. delicata* and *L. guichenoti* respectively, housed in big containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure. Enclosures are provided with non-stick matting, shelter, and several small water dishes. Water is given daily, and they are fed approx. 40 mid-size crickets (*Acheta domestica*) per enclosure three days a week. Crickets are dusted with calcium weekly and multivitamin and calcium biweekly. To ensure a temperature gradient, we employ a heat chord and a heat lamp following a 12 h light:12 h dark cycle. Room temperatures are set to 22-24 Celsius, and warm side of enclosures is usually at 32 Celsius.  
*Eggs collection and incubation* -- Between mid-October 2022 to the end of February 2023, we provided females with a place to lay the eggs by means of small boxes (12.5 L x 8.3 W x 5 H cm) with moist vermiculite inside, that were placed in one extreme of the communal enclosures (see above). We checked for the presence of eggs in the boxes three days a week. After collection, we measured length and width of eggs with a digital caliper to the nearest 0.1 mm and weight them with a (OHAUS, Model spx123) digital scale ± 0.001g error. Then eggs were treated with CORT or vehicle (see CORT and Temperature manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite). The cups were covered with cling wrap to retain moisture and left in LATWIT 2X5D-R1160 incubators at two different temperatures (see CORT and Temperature manipulation below) until hatching.  
*Hatchlings* -- Eggs in the incubator were checked three times a week for hatchlings. After hatchling, we measured juveniles' SVL and Tail Length (TL) with a rule to the nearest mm and weighted them with a (OHAUS, Model spx123) digital scale ± 0.001g error. We then placed hatchlings in individual enclosures (18.7L x 13.2W x 6.3H cm) and provided them with non-stick matting and a small water dish. During this period, they were sprayed water every day and received 3-6 small *A. domestica* crickets three times a week. All care otherwise follows similar protocols to adults (see above).  
Two weeks before we started the training phase (see below), lizards were moved to the experimental arena for acclimatation. The arenas were individual medium size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the extremes and a water dish on the other. These new enclosures were placed in two rooms in 7 different racks associated to 7 different CCTV systems (device model DVR-HP210475) that allowed us to record their behaviour during the experiment (see details below). The number of lizards per species and treatment in each rack was counterbalanced to control for any effect of the room or the position of the lizard in the rack. During acclimatation and all the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin (see protocol below), and water was supplied *ad libitum*. We provided a temperature gradient by means of a heat cord and heat lamps in a 12 h light: 12 h dark cycle. The rooms temperature was set to between 22-24 Celsius.

#### CORT and Temperature manipulation  
To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A). We first allocated eggs to one of two different treatments: CORT treatment, where eggs were topically supplied with 5µL of CORT dissolved in 70% Ethanol and 30% DMSO (vehicle) at a final (10 pg CORT/mL) concentration (CORT treatment); and a Control treatment, where eggs received an equal volume of the vehicle. CORT concentration employed in the CORT treatment represents 2 standard deviations above the mean natural concentration obtained in eggs from both species (non-published data). Then, eggs were incubated in one of the two previously mentioned temperature regimes ('Cold' or 'Hot') until hatching. The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.

#### Learning  
To estimate learning skills, we tested skinks' ability to locate a food reward in a series of behavioural tasks (@fig-Methods B) [see @leal_behavioural_2012; @clark_colour_2014]. First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical to the ones from the experiment except for the colour (see below). We divided this training phase into three stages: in the first stage, lizards had to eat a small, frozen cricket (*A. domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure (@fig-Methods B, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods B, Stage 2); and finally, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp in the third and last stage (Fig. @fig-Methods B, Stage 3). Every trial began when we left the feeding block (petri dish, ramp, or both) inside the enclosure and finished one hour later when we took it away. At the end of each trial, we recorded whether the cricket had been consumed or not. Trial was considered successful if the lizard could locate and consume the reward, while completion of each stage required the lizards to eat the crickets in at least 5 out of 6 trials. This phase lasted 38 days until all the lizards were able to eat from the ramp; only in one case we decided not to use the lizard because its behaviour was not consistent over the course of the training phase.  
In the next phase, we trained lizards to associate between colour and a food reward (Associative task in Fig. @fig-Methods B). The test was like the third stage of the training phase, but here lizards were presented with three feeders that differed in the colour. We placed the food reward (small, frozen, *A. domestica* crickets) inside the wells of the three feeders, covering two of the crickets with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp. The food reward was placed in all three wells to avoid lizard using prey chemical cues, and the lids had a series of small holes on the top to allow the release of those chemicals. The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision]. To control for potential colour preference that could bias our results (see Supplementary Material), we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with the non-covered frozen cricket) was the blue one during the associative task and red in the reversal, while for the other group we assigned red as correct for the associative and blue for the reversal. In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association. Lizards were tested in this task once a day for 35 days.  
After the colour association phase, we performed a choice reversal task (Reversal task in @fig-Methods B). This task was like the colour association test, except that the attainability of prey was indicated by a different colour, requiring the lizards to form a novel association between the new colour and the food reward. This test was done once a day for 40 days.  
The full experiment was done daily between the 6^th^ of March until the 26^th^ of June 2023, between 11 to 12 am, when the lizards were active. Trials in the learning phases (colour associative task and reversal tasks) were recorded with different CCTV systems always using the same camera per individual. Videos were analysed manually using a standard video player (IINA) by PR, who recorded whether the first choice made by each subject was the correct feeder or not. A choice was considered to be made if the head of the lizard was inside the well of one of the ramps. PR was blinded to the treatments of the lizards during the analyses of the video. We considered a trial failed if there was no choice in one hour of recording and those trials were considered as 'non data' in the analyses. We excluded from our analyses those individuals with more than 15 trials failed (i.e. they did not make a choice), and we considered the first trial to be the first one where the individual made a choice.

```{r, fig-Methods}
#| label: fig-Methods
#| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."

knitr::include_graphics("./Others/LEARN_FIG_1.svg")

```

#### Statistical analyses  
We performed the analyses with species (_L. delicata_ or _L. guichenoti_) and task ('Associative' or 'Reversal') separately. We also saw a significant effect of the colour assigned in the preliminary analises, so we decided to split the data by colour ('Blue' or 'Red') as well. As such, we run a total of different 8 models employing Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022). Each model consisted of four parallel chains of 3000 iterations, with a warm up interval of 1000 iterations.'Choice', i.e. whether the individual chose correct (1) or not (0) was used as the response variable. The fixed effects of the model included a triple interaction between: trial ('Associative trial' or 'Reversal trial') as a numeric variable, and hormone treatmet ('CORT' versus 'Control') and the temperature at which eggs were incubated ('Cold' versus 'Hot') as factors. For the random effects, we employed lizard identity as a random intercept, and as a random slope we included the variable trial ('Associative' or 'Reversal') within each level of lizard identity.  
We used the resulting posterior of these models to evaluate learning differences between treatments within and between species and colour assigned. More specifically, we calculated learning slopes by using the estimates of the trial variable per each level of the hormone-temperature interaction ('Treatments'); values bigger from zero were considered as evidence of learning, while those less or equal to zero not. We used the pmcmc method to test whether those slopes or the comparissons between 'Treatments' (e.g. slope for 'CORT-Cold' lizards minus 'CORT-Hot' lizards) were different from zero (two-tailed tests). We considered statistical significance if p-value < 0.05.

## Results
```{r, cleaning}
#| label: cleaning
source(here("R", "1_data_process.R"))
# Once we run this code, the result will be two different dataframes, one for the Associative learning task (data_asso) and the other for the Reversal learning task (data_rev).
write.csv(data_asso, file= "./output/databases_clean/data_asso.csv")
write.csv(data_rev, file= "./output/databases_clean/data_rev.csv")
```

```{r, sampleSize}
#| label: sampleSize
# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
source(here("R", "func.R"))
#
specie <- c("delicata", "guichenoti")
groups <- c("Red", "Blue")
hormone <- c("CORT", "Control")
temperature <- c("Cold", "Hot")
#
n_list <- list()
#
for(i in 1:length(specie)){
  for(j in 1:length(groups)){
    for(k in 1:length(hormone)){
      for(l in 1:length(temperature)){
        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(specie[i], groups[j], hormone[k], temperature[l])
      }
    }
  }
}
```

Originally, we started with 96 lizards, 48 per species and 12 per treatment per species. However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3; see above), we ended up with a total of 81 lizards. Final sample sizes per treatment and species are disclosed on @tbl-data.  
```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# A) Associative task. Model formula: FC_associative ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id)
## A.1) L. delicata
deli_asso_red <- fit_m("asso", "deli", "red", refit = FALSE)
write.csv(deli_asso_red, file= "./output/Checking/deli_asso_red.csv")
deli_asso_blue <- fit_m("asso", "deli", "blue", refit = FALSE)
write.csv(deli_asso_blue, file= "./output/Checking/deli_asso_blue.csv")
## A.2) L. guichenoti
guich_asso_red <- fit_m("asso", "guich", "red", refit = FALSE)
write.csv(guich_asso_red, file= "./output/Checking/guich_asso_red.csv")
guich_asso_blue <- fit_m("asso", "guich", "blue", refit = FALSE)
write.csv(guich_asso_blue, file= "./output/Checking/guich_asso_blue.csv")
# B) Reversal task. Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
## B.1) L. delicata
deli_rev_red <- fit_m("rev", "deli", "red", refit = FALSE)
write.csv(deli_rev_red, file= "./output/Checking/deli_rev_red.csv")
deli_rev_blue <- fit_m("rev", "deli", "blue", refit = FALSE)
write.csv(deli_rev_blue, file= "./output/Checking/deli_rev_blue.csv")
## B.2) L. guichenoti
guich_rev_red <- fit_m("rev", "guich", "red", refit = FALSE)
write.csv(guich_rev_red, file= "./output/Checking/guich_rev_red.csv")
guich_rev_blue <- fit_m("rev", "guich", "blue", refit = FALSE)
write.csv(guich_rev_blue, file= "./output/Checking/guich_rev_blue.csv")
```

```{r, resultsAsso}
# Rename some of the posteriors and obtain estimates for the "learning rate" for each group and treatment in the Associative task. This "learning rate" consists on the slope of the posterior of the Associative_Trial parameter. The slope is the rate at which the probability of choosing the correct feeder increases with each trial. The slope is obtained by adding the posterior of the Associative_Trial parameter to the posterior of the interaction between Associative_Trial and the treatment (cort and temp). 
## 1) L. delicata
### Group = red
dar_CORTCold <- deli_asso_red$b_Associative_Trial #Slope for treatment CORT-Cold for L. delicata, red as the right choice
dar_ControlCold <- (deli_asso_red$'b_Associative_Trial:cortControl' + deli_asso_red$b_Associative_Trial)
dar_CORTHot <- (deli_asso_red$'b_Associative_Trial:tempHot' + deli_asso_red$b_Associative_Trial)
dar_ControlHot <- (deli_asso_red$'b_Associative_Trial:cortControl:tempHot' + deli_asso_red$b_Associative_Trial+ deli_asso_red$'b_Associative_Trial:cortControl' + deli_asso_red$'b_Associative_Trial:tempHot')
### Group = blue
dab_CORTCold <- deli_asso_blue$b_Associative_Trial
dab_ControlCold <- (deli_asso_blue$'b_Associative_Trial:cortControl' + deli_asso_blue$b_Associative_Trial)
dab_CORTHot <- (deli_asso_blue$'b_Associative_Trial:tempHot' + deli_asso_blue$b_Associative_Trial)
dab_ControlHot <- (deli_asso_blue$'b_Associative_Trial:cortControl:tempHot' + deli_asso_blue$b_Associative_Trial + deli_asso_blue$'b_Associative_Trial:cortControl' + deli_asso_blue$'b_Associative_Trial:tempHot')
## 2) L. guichenoti
### Group = red
gar_CORTCold <- guich_asso_red$b_Associative_Trial
gar_ControlCold <- (guich_asso_red$'b_Associative_Trial:cortControl' + guich_asso_red$b_Associative_Trial)
gar_CORTHot <- (guich_asso_red$'b_Associative_Trial:tempHot' + guich_asso_red$b_Associative_Trial)
gar_ControlHot <- (guich_asso_red$'b_Associative_Trial:cortControl:tempHot' + guich_asso_red$b_Associative_Trial + guich_asso_red$'b_Associative_Trial:cortControl' + guich_asso_red$'b_Associative_Trial:tempHot')
### Group = blue
gab_CORTCold <- guich_asso_blue$b_Associative_Trial
gab_ControlCold <- (guich_asso_blue$'b_Associative_Trial:cortControl' + guich_asso_blue$b_Associative_Trial)
gab_CORTHot <- (guich_asso_blue$'b_Associative_Trial:tempHot' + guich_asso_blue$b_Associative_Trial)
gab_ControlHot <- (guich_asso_blue$'b_Associative_Trial:cortControl:tempHot' + guich_asso_blue$b_Associative_Trial + guich_asso_blue$'b_Associative_Trial:cortControl' + guich_asso_blue$'b_Associative_Trial:tempHot')
```

```{r, resultsRev}
# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task doing the same thing we did in the chunk above.
## 1) L. delicata
### Group = red
drr_CORTCold <- deli_rev_red$b_trial_reversal
drr_ControlCold <- (deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$b_trial_reversal)
drr_CORTHot <- (deli_rev_red$'b_trial_reversal:tempHot' + deli_rev_red$b_trial_reversal)
drr_ControlHot <- (deli_rev_red$'b_trial_reversal:cortControl:tempHot' + deli_rev_red$b_trial_reversal + deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$'b_trial_reversal:tempHot')
### Group = blue
drb_CORTCold <- deli_rev_blue$b_trial_reversal
drb_ControlCold <- (deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$b_trial_reversal)
drb_CORTHot <- (deli_rev_blue$'b_trial_reversal:tempHot' + deli_rev_blue$b_trial_reversal)
drb_ControlHot <- (deli_rev_blue$'b_trial_reversal:cortControl:tempHot' + deli_rev_blue$b_trial_reversal + deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$'b_trial_reversal:tempHot')
## 2) L. guichenoti
### Group = red
grr_CORTCold <- guich_rev_red$b_trial_reversal
grr_ControlCold <- (guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$b_trial_reversal)
grr_CORTHot <- (guich_rev_red$'b_trial_reversal:tempHot' + guich_rev_red$b_trial_reversal)
grr_ControlHot <- (guich_rev_red$'b_trial_reversal:cortControl:tempHot' + guich_rev_red$b_trial_reversal + guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$'b_trial_reversal:tempHot')
### Group = blue
grb_CORTCold <- guich_rev_blue$b_trial_reversal
grb_ControlCold <- (guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$b_trial_reversal)
grb_CORTHot <- (guich_rev_blue$'b_trial_reversal:tempHot' + guich_rev_blue$b_trial_reversal)
grb_ControlHot <- (guich_rev_blue$'b_trial_reversal:cortControl:tempHot' + guich_rev_blue$b_trial_reversal + guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$'b_trial_reversal:tempHot')
```

```{r, tbl-data}
#| label: tbl-data
#| tbl-cap: "Estimates of Associative learning slope for all the different treatments per each task, species and group. Mean shows the aritmetic mean of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean. All p-values were obtained using pmcmc and test the hypothesis that the mean is equal to zero. In bold, those values that are significant (p-value <0.05)"
source(here("R", "func.R"))
#
############################## CREATING BIG DF FOR TABLE ##############################
# Building the vectors for titles of rows and columns
specie <- c("L. delicata", "L. guichenoti")
groups <- c("Red", "Blue")
test <- c("Associative", "Reversal")
treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
values <- c("Mean", "95% CI", "p-value")
# Building the vectors for estimated means, co.intervals(95%), and p-values for the slopes obtained from posteriors. p-values are obtained using pmcmc function (see func.R), assuming a two-tailed test that testes the hypothesis that the value (slopes in this case) is 0.
#First get estimates for both tasks
estimates_asso <- list(
  dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot, 
  dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot, 
  gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot, 
  gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot
)
#
estimates_rev <- list(
  drr_CORTCold, drr_ControlCold, drr_CORTHot, drr_ControlHot, 
  drb_CORTCold, drb_ControlCold, drb_CORTHot, drb_ControlHot, 
  grr_CORTCold, grr_ControlCold, grr_CORTHot, grr_ControlHot, 
  grb_CORTCold, grb_ControlCold, grb_CORTHot, grb_ControlHot
)
# Then get the mean, co.intervals(95%), and p-values
asso_mean <- format_dec(sapply(estimates_asso, mean), 3)
asso_interval_025 <- format_dec(sapply(estimates_asso, function(x) quantile(x,0.025)), 3)
asso_interval_975 <- format_dec(sapply(estimates_asso, function(x) quantile(x,0.975)), 3)
asso_intervals <- paste(asso_interval_025, asso_interval_975, sep = " , ")
asso_pvalue <- format_dec(sapply(estimates_asso, pmcmc), 3)
#
rev_mean <- format_dec(sapply(estimates_rev, mean), 3)
rev_interval_025 <- format_dec(sapply(estimates_rev, function(x) quantile(x,0.025)), 3)
rev_interval_975 <- format_dec(sapply(estimates_rev, function(x) quantile(x,0.975)), 3)
rev_intervals <- paste(rev_interval_025, rev_interval_975, sep = " , ")
rev_pvalue <- format_dec(sapply(estimates_rev, pmcmc), 3)
#
# Building the df for the associative
asso_df <- data.frame(
  Specie = rep(specie, each = length(groups) * length(treatments)),
  Group = rep(rep(groups, each = length(treatments)), times = length(specie)),
  Treatment = rep(rep(treatments, each = 1), times = length(groups) * length(specie)),
  Mean = rep(asso_mean, each = 1),
  CI = rep(asso_intervals, each = 1),
  PValue = rep(asso_pvalue, each = 1),
  Task = rep("Associative", length(asso_mean))
)
# Building the df for the reversal
rev_df <- data.frame(
  Specie = rep(specie, each = length(groups) * length(treatments)),
  Group = rep(rep(groups, each = length(treatments)), times = length(specie)),
  Treatment = rep(rep(treatments, each = 1), times = length(groups) * length(specie)),
  Mean = rep(rev_mean, each = 1),
  CI = rep(rev_intervals, each = 1),
  PValue = rep(rev_pvalue, each = 1),
  Task = rep("Reversal", length(rev_mean))
)
# Joining both dfs
table_data <- rbind(asso_df, rev_df)
table_data[, sapply(table_data, is.numeric)] <- lapply(table_data[, sapply(table_data, is.numeric)], function(x) format(x, scientific = FALSE))
#
############################## ADDING SAMPLE SIZE TO DF FOR TABLE ##############################
# Make n_list into a df
n_df <- as.data.frame(do.call(rbind, n_list)) %>%
  rename("n" = V1) %>%
  rownames_to_column("model") %>%
  separate(model, into = c("Specie", "Group", "cort", "temp"), sep = "_") %>%
  unite("Treatment", c("cort", "temp"), sep = "-") %>%
  mutate(Specie = factor(Specie,
                  labels = c(delicata = "L. delicata", guichenoti = "L. guichenoti")),
        Treatment = factor(Treatment,
                   levels = c("CORT-Cold", "Control-Cold", "CORT-Hot","Control-Hot")))
# Merge both dfs, put sample size together with the treatment, and organize the new df to make it look like the table
new_table_data <- merge(table_data, n_df) %>%
  rename('p-value' = 'PValue', '95% CI' = 'CI') %>% #Change the names of the columns for the table
  pivot_wider(names_from = Task, values_from = c(Mean, `95% CI`, `p-value`)) %>% # to split between Asociative and Reversal
  select(Specie, Group, Treatment, Mean_Associative, `95% CI_Associative`, `p-value_Associative`, Mean_Reversal, `95% CI_Reversal`, `p-value_Reversal`, n) %>% #To order the columns in the way I want for the table
  mutate(Specie = factor(Specie,
                  levels = c("L. delicata", "L. guichenoti")),
        Group = factor(Group,
                  levels = c("Red", "Blue")),
        Treatment = factor(Treatment, 
                  levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")))%>%
  arrange(Specie, Group, Treatment) %>% # To arrange the rows the way I want
  unite("Treatment", c("Treatment", "n"), sep = " (n = ") %>%
  mutate(Treatment = paste0(Treatment, ")"))
write.csv(new_table_data, file= "./output/Checking/new_table_data.csv")
#
############################## MAKING THE TABLE ##############################
## Table format
set_flextable_defaults(
 font.family = "Times New Roman",
 fint.size = 10)
# Split the table_data df by task
real_table <- flextable(new_table_data) %>%
    bold(~ `p-value_Associative` < 0.05, ~ `p-value_Associative` + Mean_Associative + `95% CI_Associative`) %>%
    bold(~ `p-value_Reversal` < 0.05, ~ `p-value_Reversal` + Mean_Reversal + `95% CI_Reversal`) %>%
    set_table_properties(width = 1) %>%
    align(align="center", part="all") %>% 
    add_header_row(values = c("", "Associative task", "Reversal task"), colwidths = c(3, 3, 3)) %>%
    set_header_labels(Mean_Associative = "Mean",
                      `95% CI_Associative` = "95% CI",
                      `p-value_Associative` = "p-value",
                      Mean_Reversal = "Mean",
                      `95% CI_Reversal` = "95% CI",
                      `p-value_Reversal` = "p-value") %>%
    italic(j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
    flextable::compose(i = c(2:8,10:16), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
    flextable::compose(i = c(2:4,6:8,10:12,14:16), j = 2, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the second column
    hline(i = c(4,12), j = c(2:9), part = "body") %>% # To make some horizontal lines
    hline(i = c(8), j = c(1:9), part = "body") %>% # To make some horizontal lines
    vline(i = (1:16), j = c(3,6), part = "body") %>% # To make some vertical lines on body
    vline(j=c(3,6), part = "header") %>% # To make some vertical lines on header
    autofit() 
real_table
```

Results of the associative task are summarized in @tbl-data and figures @Figdeli, @Figguich. On average, we found that the estimated learning slopes were lower when the blue feeders were the correct choice compared to those assigned to the group 'Red'  for _L. delicata_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot)), 3)`, p = `r format_dec(pmcmc((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot)), 3)`), but not for _L. guichenoti_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)), 3)`, p = `r format_dec(pmcmc((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)),3)`). However, further analyses using the first trial indicated a potential bias towards 'Blue' in the initial choice (see Supplementary Material and Figs. @Figdeli, @Figguich); and in consequence, we only used those individuals assigned to 'Red' to compare between-treatment performance in the associative learning task. In this regard, we did not find any significant differences between treatments for _L. delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dar_ControlCold - dar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(dar_ControlCold - dar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dar_ControlHot- dar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(dar_ControlHot - dar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dar_ControlHot - dar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(dar_ControlHot - dar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dar_CORTHot - dar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(dar_CORTHot - dar_CORTCold), 3)`) (see @Figdeli), or _L. guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gar_ControlCold - gar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(gar_ControlCold - gar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gar_ControlHot- gar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(gar_ControlHot - gar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gar_ControlHot - gar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(gar_ControlHot - gar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gar_CORTHot - gar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(gar_CORTHot - gar_CORTCold), 3)`) (see @Figguich). When groups were pooled by incubation temperature or hormonal treatment, there was not significant differences in the estimated slopes caused by temperature (_L. delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`, p-value = `r format_dec(pmcmc((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`; _L. guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`, p-value = `r format_dec(pmcmc((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`) or the hormone (_L. delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)` ; _L. guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`). We also did not find any significant differences when we compared the estimated slopes between species for the associative task (_L. delicata_ - _L. guichenoti_ = `r format_dec(mean((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`).  
In the reversal tesk, we decided to pool both groups 'Blue' and 'Red' to make the between-treatment comparisons for two reasons. First, we did not find any significant differences caused group on the learning slopes (_L. delicata_: 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean((drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drr_CORTCold + drr_ControlHot)), 3)`, p = `r format_dec(pmcmc((drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drr_CORTCold + drr_ControlHot)), 3)`; _L. guichenoti_: 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean((grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTCold + grr_ControlHot)), 3)`, p = `r format_dec(pmcmc((grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTCold + grr_ControlHot)), 3)`). Second, we were expecting an acquired bias towards the colour assigned in the associative task as part of the design. Nonetheless, we did not find any significant differences between treatments in _L. delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean((drr_ControlCold + drb_ControlCold) - (drr_CORTCold + drb_CORTCold)), 3)`, p- value = `r format_dec(pmcmc((drr_ControlCold + drb_ControlCold) - (drr_CORTCold + drb_CORTCold)), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((drr_ControlHot + drb_ControlHot) - (drr_CORTHot + drb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((drr_ControlHot + drb_ControlHot) - (drr_CORTHot + drb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((drr_ControlHot + drb_ControlHot) - (drr_ControlCold + drb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((drr_ControlHot + drb_ControlHot) - (drr_ControlCold + drb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((drr_CORTHot + drb_CORTHot) - (drr_CORTCold + drb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((drr_CORTHot + drb_CORTHot) - (drr_CORTCold + drb_CORTCold)), 3)`) (see @Figdeli) or _L. guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean((grr_ControlCold + grb_ControlCold) - (grr_CORTCold + grb_CORTCold)), 3)`, p- value = `r format_dec(pmcmc((grr_ControlCold + grb_ControlCold) - (grr_CORTCold + grb_CORTCold)), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((grr_ControlHot + grb_ControlHot) - (grr_CORTHot + grb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((grr_ControlHot + grb_ControlHot) - (grr_CORTHot + grb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((grr_ControlHot + grb_ControlHot) - (grr_ControlCold + grb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((grr_ControlHot + grb_ControlHot) - (grr_ControlCold + grb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((grr_CORTHot + grb_CORTHot) - (grr_CORTCold + grb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((grr_CORTHot + grb_CORTHot) - (grr_CORTCold + grb_CORTCold)), 3)`) (see @Figguich). We did not find any effect of incubation temperature (_L. delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((drr_CORTHot + drr_ControlHot + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drb_CORTCold + drb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((drr_CORTHot + drr_ControlHot + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drb_CORTCold + drb_ControlCold)),3)`; _L. guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((grr_CORTHot + grr_ControlHot + grb_CORTHot + grb_ControlHot) -(grr_CORTCold + grr_ControlCold + grb_CORTCold + grb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((grr_CORTHot + grr_ControlHot + grb_CORTHot + grb_ControlHot) -(grr_CORTCold + grr_ControlCold + grb_CORTCold + grb_ControlCold)),3)`) or the hormone (_L. delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((drr_ControlCold + drr_ControlHot + drb_ControlCold + drb_ControlHot) - (drr_CORTCold + drr_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((drr_ControlCold + drr_ControlHot + drb_ControlCold + drb_ControlHot) - (drr_CORTCold + drr_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`;_L. guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((grr_ControlCold + grr_ControlHot + grb_ControlCold + grb_ControlHot)-(grr_CORTCold + grr_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((grr_ControlCold + grr_ControlHot + grb_ControlCold + grb_ControlHot)-(grr_CORTCold + grr_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`) when groups were pooled. Finally, we did not find any significant differences when we compared the estimated slopes between species for the reversal task (_L. delicata_ - _L. guichenoti_ = `r format_dec(mean((drr_CORTCold + drr_ControlCold + drr_CORTHot + drr_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTHot + grr_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((drr_CORTCold + drr_ControlCold + drr_CORTHot + drr_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTHot + grr_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`).

```{r, figdeli}
#| label: figdeli
#| fig.cap: "Deli"
# First step, create the Intercepts for all models
## 1) Associative task
### Group = red
int_dar_CORTCold <- deli_asso_red$b_Intercept
int_dar_ControlCold <- (deli_asso_red$b_cortControl + deli_asso_red$b_Intercept)
int_dar_CORTHot <- (deli_asso_red$b_tempHot + deli_asso_red$b_Intercept)
int_dar_ControlHot <- (deli_asso_red$'b_cortControl:tempHot' + deli_asso_red$b_cortControl + deli_asso_red$b_tempHot + deli_asso_red$b_Intercept)
### Group = blue
int_dab_CORTCold <- deli_asso_blue$b_Intercept
int_dab_ControlCold <- (deli_asso_blue$b_cortControl + deli_asso_blue$b_Intercept)
int_dab_CORTHot <- (deli_asso_blue$b_tempHot + deli_asso_blue$b_Intercept)
int_dab_ControlHot <- (deli_asso_blue$'b_cortControl:tempHot' + deli_asso_blue$b_cortControl + deli_asso_blue$b_tempHot + deli_asso_blue$b_Intercept)
## 2) Reversal task
### Group = red
int_drr_CORTCold <- deli_rev_red$b_Intercept
int_drr_ControlCold <- (deli_rev_red$b_cortControl + deli_rev_red$b_Intercept)
int_drr_CORTHot <- (deli_rev_red$b_tempHot + deli_rev_red$b_Intercept)
int_drr_ControlHot <- (deli_rev_red$'b_cortControl:tempHot' + deli_rev_red$b_cortControl + deli_rev_red$b_tempHot + deli_rev_red$b_Intercept)
### Group = blue
int_drb_CORTCold <- deli_rev_blue$b_Intercept
int_drb_ControlCold <- (deli_rev_blue$b_cortControl + deli_rev_blue$b_Intercept)
int_drb_CORTHot <- (deli_rev_blue$b_tempHot + deli_rev_blue$b_Intercept)
int_drb_ControlHot <- (deli_rev_blue$'b_cortControl:tempHot' + deli_rev_blue$b_cortControl + deli_rev_blue$b_tempHot + deli_rev_blue$b_Intercept)
# Second step, create the df for each model with trials as columns and the predicted probability of choosing right as rows under equation: Prob = 1/(1+e^-(Intercept + Slope*trial))??
## 1) Associative task
### Group = red
#### CORT-Cold

```

```{r, figguich}
#| label: Figguich
#| fig.cap: "Guich"
```

## Discussion

## References
<div id="refs"></div>

```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

# Suplementary Material

#### Colour preference in the Associative task
To test if lizards were biased towards the assigned colour as our preliminary analyses suggested, we employed the intercepts  from our posterior distributions. We first estimated the predicted probability of choosing the correct feeder first in the first trial, by using the formula: 
$$\text{Probability} = \frac{1}{1 + e^{-Intercept}}$$

Second, we tested the hypothesis that the estimated probability was higher than 0.33 (the probability expected by chance of choosing the correct feeder) using pmcmc. If the estimated probability is above 0.33. we consider it as an indication that there was a preference towards that colour that could be affecting learning slopes. The results per treatment are summarized in @tbl-bias. 
```{r, tbl-bias}
#| label: tbl-bias
#| tbl-cap: "Probability of choosing the correct feeder in the first trial when the correct feeder was blue (Prob Blue) or red (Prob Red) for each species and each treatment. p-values were obtained using pmcmc and test the hypothesis that the probability is >0.33. In bold, those values that are significant (p-value <0.05)"
source(here("R", "func.R"))
# First we estimate the probability of choosing right in the first trial using the intercepts from the posteriors
## 1) L. delicata
### Group = red
probright_drCORTCold <- 1/(1+exp(-deli_asso_red$b_Intercept))
probright_drControlCold <- 1/(1+exp(-(deli_asso_red$b_cortControl + deli_asso_red$b_Intercept)))
probright_drCORTHot <- 1/(1+exp(-(deli_asso_red$b_tempHot + deli_asso_red$b_Intercept)))
probright_drControlHot <- 1/(1+exp(-(deli_asso_red$'b_cortControl:tempHot' + deli_asso_red$b_cortControl + deli_asso_red$b_tempHot + deli_asso_red$b_Intercept)))
### Group = blue
probright_dbCORTCold <- 1/(1+exp(-(deli_asso_blue$b_Intercept)))
probright_dbControlCold <- 1/(1+exp(-(deli_asso_blue$b_cortControl + deli_asso_blue$b_Intercept)))
probright_dbCORTHot <- 1/(1+exp(-(deli_asso_blue$b_tempHot + deli_asso_blue$b_Intercept)))
probright_dbControlHot <- 1/(1+exp(-(deli_asso_blue$'b_cortControl:tempHot' + deli_asso_blue$b_cortControl + deli_asso_blue$b_tempHot + deli_asso_blue$b_Intercept)))
## 2) L. guichenoti
### Group = red
probright_grCORTCold <- 1/(1+exp(-guich_asso_red$b_Intercept))
probright_grControlCold <- 1/(1+exp(-(guich_asso_red$b_cortControl + guich_asso_red$b_Intercept)))
probright_grCORTHot <- 1/(1+exp(-(guich_asso_red$b_tempHot + guich_asso_red$b_Intercept)))
probright_grControlHot <- 1/(1+exp(-(guich_asso_red$'b_cortControl:tempHot' + guich_asso_red$b_cortControl + guich_asso_red$b_tempHot + guich_asso_red$b_Intercept)))
### Group = blue
probright_gbCORTCold <- 1/(1+exp(-guich_asso_blue$b_Intercept))
probright_gbControlCold <- 1/(1+exp(-(guich_asso_blue$b_cortControl + guich_asso_blue$b_Intercept)))
probright_gbCORTHot <- 1/(1+exp(-(guich_asso_blue$b_tempHot + guich_asso_blue$b_Intercept)))
probright_gbControlHot <- 1/(1+exp(-(guich_asso_blue$'b_cortControl:tempHot' + guich_asso_blue$b_cortControl + guich_asso_blue$b_tempHot + guich_asso_blue$b_Intercept)))
# Second we build a df with all the mean probabilities of choosing right in the first trial for each treatment and species
prob_df <- data.frame(
  probright_drCORTCold_t = format_dec(mean(probright_drCORTCold), 3),
  probright_drControlCold_t = format_dec(mean(probright_drControlCold), 3),
  probright_drCORTHot_t = format_dec(mean(probright_drCORTHot), 3),
  probright_drControlHot_t = format_dec(mean(probright_drControlHot), 3),
  probright_dbCORTCold_t = format_dec(mean(probright_dbCORTCold), 3),
  probright_dbControlCold_t = format_dec(mean(probright_dbControlCold), 3),
  probright_dbCORTHot_t = format_dec(mean(probright_dbCORTHot), 3),
  probright_dbControlHot_t = format_dec(mean(probright_dbControlHot), 3),
  probright_grCORTCold_t = format_dec(mean(probright_grCORTCold), 3),
  probright_grControlCold_t = format_dec(mean(probright_grControlCold), 3),
  probright_grCORTHot_t = format_dec(mean(probright_grCORTHot), 3),
  probright_grControlHot_t = format_dec(mean(probright_grControlHot), 3),
  probright_gbCORTCold_t = format_dec(mean(probright_gbCORTCold), 3),
  probright_gbControlCold_t = format_dec(mean(probright_gbControlCold), 3),
  probright_gbCORTHot_t = format_dec(mean(probright_gbCORTHot), 3),
  probright_gbControlHot_t = format_dec(mean(probright_gbControlHot), 3)) %>%
gather(key = "column", value = "value", .) %>%
rename("prob_choice" = "value") %>%
data.frame()
write.csv(prob_df, file= "./output/Checking/prob_df.csv")
# Then we build a df with the statistical test (one-tailed pmcmc) that the probability is >0.33 (the probability of choosing right by chance)
comp_pval <- data.frame(
  probright_drCORTCold_t = format_dec(pmcmc(probright_drCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_drControlCold_t = format_dec(pmcmc(probright_drControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_drCORTHot_t = format_dec(pmcmc(probright_drCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_drControlHot_t = format_dec(pmcmc(probright_drControlHot, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_dbCORTCold_t = format_dec(pmcmc(probright_dbCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_dbControlCold_t = format_dec(pmcmc(probright_dbControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_dbCORTHot_t = format_dec(pmcmc(probright_dbCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_dbControlHot_t = format_dec(pmcmc(probright_dbControlHot, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_grCORTCold_t = format_dec(pmcmc(probright_grCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_grControlCold_t = format_dec(pmcmc(probright_grControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_grCORTHot_t = format_dec(pmcmc(probright_grCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_grControlHot_t = format_dec(pmcmc(probright_grControlHot, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_gbCORTCold_t = format_dec(pmcmc(probright_gbCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_gbControlCold_t = format_dec(pmcmc(probright_gbControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_gbCORTHot_t = format_dec(pmcmc(probright_gbCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
  probright_gbControlHot_t = format_dec(pmcmc(probright_gbControlHot, null = 0.33, twotail = FALSE, dir=">"), 3)) %>%
gather(key = "column", value = "value", .) %>%
rename("p_value" = "value") %>%
data.frame()
write.csv(comp_pval, file= "./output/Checking/comp_pval.csv")
# Now we merge them and organise them to have the final dt for the table
table_df <- merge(prob_df, comp_pval, by ="column") %>%
  mutate(Specie = gsub(".*_(d|g).*", "\\1",column)) %>%
  mutate(Group = gsub(".*_(dr|db|gr|gb).*", "\\1",column)) %>%
  mutate(Treatment = gsub(".*(CORTCold|ControlCold|CORTHot|ControlHot).*", "\\1",column)) %>% #Last three commands used to get the species, group and treatment from the column names
  mutate(Treatment = factor(Treatment, 
                    levels = c("CORTCold", "ControlCold", "CORTHot", "ControlHot"),
                    labels = c("CORTCold" = "CORT-Cold", "ControlCold" = "Control-Cold", "CORTHot" = "CORT-Hot", "ControlHot" = "Control-Hot"))) %>%
  mutate(Specie = factor(Specie,
                levels = c("d", "g"),
                labels = c("d" = "L. delicata", "g" = "L. guichenoti"))) %>%
  mutate(Group = recode(Group, "dr" = "Red", "db" = "Blue", "gr" = "Red", "gb" = "Blue")) %>%
  select(-column) %>%
  pivot_wider(names_from = Group, values_from = c(prob_choice, p_value)) %>% #To split the df in Red and Blue
  select(Specie, Treatment, prob_choice_Blue, p_value_Blue, prob_choice_Red, p_value_Red) %>%
  arrange(Specie, Treatment) %>% # To arrange the rows the way I wantdata.frame()
data.frame()
write.csv(table_df, file= "./output/Checking/table_df.csv")
#################
colour_table <- flextable(table_df) %>%
  bold(~ `p_value_Blue` < 0.05, ~ `p_value_Blue` + prob_choice_Blue) %>%
  bold(~ `p_value_Red` < 0.05, ~ `p_value_Red` + prob_choice_Red) %>%
  set_table_properties(width = 1) %>%
  align(align="center", part="all") %>% 
  set_header_labels(prob_choice_Blue = "Prob Blue", 
                    p_value_Blue = "p-value Blue", 
                    prob_choice_Red = "Prob Red", 
                    p_value_Red = "p-value Red") %>%
  italic(j = 1, italic = TRUE, part = "body") %>% # To have names of species in italics
  flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
  hline(i = c(4), j = c(1:6), part = "body") %>% # To make some horizontal lines
  vline(j = c(2,4), part = "all") %>% # To make some vertical lines on body
autofit()
colour_table
```

On average, we found that, for both species, the proportion of correct choices in the first trial was significantly above chance when the correct feeder was blue (_L. delicata_: mean Prob choice = `r format_dec(mean((probright_dbCORTCold + probright_dbControlCold + probright_dbCORTHot + probright_dbControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_dbCORTCold + probright_dbControlCold + probright_dbCORTHot + probright_dbControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L. guichenoti_: mean Prob choice = `r format_dec(mean((probright_gbCORTCold + probright_gbControlCold + probright_gbCORTHot + probright_gbControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_gbCORTCold + probright_gbControlCold + probright_gbCORTHot + probright_gbControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`), but not when it was red (_L. delicata_: mean Prob choice = `r format_dec(mean((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L. guichenoti_: mean Prob choice = `r format_dec(mean((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`).

```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

#### Checking the models plots  
```{r, residuals}
# Chunk for calling all the models and making the residuals
# Associative task
## L. delicata
### Red
mod_dar <- readRDS(here("output/models/asso_deli_red.rds"))
resid_dar <- residuals(mod_dar)
### Blue
mod_dab <- readRDS(here("output/models/asso_deli_blue.rds"))
resid_dab <- residuals(mod_dab)
## L. guichenoti
### Red
mod_gar <- readRDS(here("output/models/asso_guich_red.rds"))
resid_gar <- residuals(mod_gar)
### Blue
mod_gab <- readRDS(here("output/models/asso_guich_blue.rds"))
resid_gab <- residuals(mod_gab)
# Reversal task
## L. delicata
### Red
mod_drr <- readRDS(here("output/models/rev_deli_red.rds"))
resid_drr <- residuals(mod_drr)
### Blue
mod_drb <- readRDS(here("output/models/rev_deli_blue.rds"))
resid_drb <- residuals(mod_drb)
## L. guichenoti
### Red
mod_grr <- readRDS(here("output/models/rev_guich_red.rds"))
resid_grr <- residuals(mod_grr)
### Blue
mod_grb <- readRDS(here("output/models/rev_guich_blue.rds"))
resid_grb <- residuals(mod_grb)
```

Model formula for the associative task is:  
Choice  ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id)  
Plots for the different models of the associative task:  
1.- _L. delicata_  
  1.a.- Red  
```{r , plotmod_dar, out.width="70%", fig.align="center"}
plot(mod_dar)
```
```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

  1.b.- Blue  
```{r , plotmod_dab, out.width="70%", fig.align="center"}
plot(mod_dab)
```

```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

2.- _L. guichenoti_  
  2.a.- Red  
```{r , plotmod_gar, out.width="70%", fig.align="center"}
plot(mod_gar)
```
```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

  2.b.- Blue  
```{r , plotmod_gab, out.width="70%", fig.align="center"}
plot(mod_gab)
```

```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

Model formula for the reversal task is:  
Choice  ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)  
Plots for the different models of the associative task:  
1.- _L. delicata_  
  1.a.- Red  
```{r , plotmod_drr, out.width="70%", fig.align="center"}
plot(mod_drr)
```

```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

  1.b.- Blue  
```{r , plotmod_drb, out.width="70%", fig.align="center"}  
plot(mod_drb)
```

```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

2.- _L. guichenoti_  
  2.a.- Red  
```{r , plotmod_grr, out.width="70%", fig.align="center"}
plot(mod_grr)
```

```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

  2.b.- Blue  
```{r , plotmod_grb, out.width="70%", fig.align="center"}
plot(mod_grb)
```

### 2024-01-22 R/1_data_process.R

@@ -1,0 +1,55 @@
+####################################
+# 1_data_process
+####################################
+
+# Packages
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, forcats)
+
+# Load data
+data  <-  read.csv("./data/Learning.csv")
+
+# Remove individuals who did not participate (more than 15 NAs), remove trials [36-40] (Only in associative) and split treatment into Temp and Cort
+data_asso <- data %>%
+  group_by(lizard_id) %>%
+    filter(sum(is.na(FC_associative)) <= 15) %>%
+    filter(trial_associative <= 35) %>%
+  ungroup()  %>%
+    mutate(group = factor(group,
+     levels = c("R_B", "B_R"),
+     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
+    mutate(temp = gsub("[AB]_", "", trt),
+          cort = gsub("_[2][38]", "", trt))  %>%
+    mutate(temp = factor(temp,
+      levels = c("23", "28"),
+      labels = c("23" = "Cold", "28" = "Hot"))) %>%
+    mutate(cort = factor(cort,
+      levels = c("B", "A"),
+      labels = c("B" = "CORT", "A" = "Control"))) %>%
+    mutate( # Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)
+      first_non_na = min(which(!is.na(FC_associative))),
+      Associative_Trial = ifelse(!is.na(first_non_na),trial_associative - first_non_na + 1, trial_associative))%>% 
+      filter(Associative_Trial >= 1) %>%
+  ungroup() %>% 
+data.frame()
+
+
+data_rev <- data %>%
+  group_by(lizard_id) %>%
+    filter(sum(is.na(FC_associative)) <= 15) %>%
+    filter(sum(is.na(FC_reversal)) <= 15) %>%
+   ungroup()  %>%
+    mutate(group = factor(group,
+     levels = c("R_B", "B_R"),
+     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
+    mutate(temp = gsub("[AB]_", "", trt),
+          cort = gsub("_[2][38]", "", trt))  %>%
+    mutate(temp = factor(temp,
+      levels = c("23", "28"),
+      labels = c("23" = "Cold", "28" = "Hot"))) %>%
+    mutate(cort = factor(cort,
[…]

### 2024-01-22 R/func.r

@@ -1,0 +1,156 @@
+#################### 
+####################
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
+#
+####################
+####################
+# Extract sample size per group
+#' @title sample
+#' @description Estract sample size per group
+#' @param sp To select the species of interest ("deli"/"guich")
+#' @param bias To select group depending on the colour assigned as correct for each task ("blue"/"red")
+#' @param corti To select cort treatment ("CORT"/"Control")
+#' @param therm To select temp treatment ("Cold"/"Hot")
+sample <- function(sp, bias, corti, therm){
+  #Specify database
+  data <- data_asso
+  # Count sample
+  sample_size <- data %>%
+                filter(species == sp, group == bias, cort == corti, temp == therm, Associative_Trial == 1) %>%
+                group_by(lizard_id) %>%
+                summarise(n = n()) %>%
+                summarise(total_count = sum(n)) %>%
+                pull(total_count)
+  return(sample_size)
+}
+####################
+####################
+# Fit models and extract posteriors both per each treatment:
+#' @title fit_m Function
+#' @description Fit brm models for different the associative task
+#' @param type To define if we are analysing the associative ("asso) or the reversal ("rev")
+#' @param sp To select the species of interest ("deli"/"guich")
+#' @param bias To select group depending on the colour assigned as correct for each task ("blue"/"red")
+#' @param refir To choose whether to refit the models (TRUE, default) or use the ones already made (FALSE)
+#' @return Raw posteriors of fitted brm model for each treatment, species, and group (df)
+fit_m <- function(type, sp, bias, refit = TRUE) {
+  #Specify the type
+  if (type == "asso"){
+    data <- data_asso
+    formula <- FC_associative ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id)
+  }else{
+    if(type == "rev"){
+      data <- data_rev
+      formula <- FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
+    } else {
+      stop("Type not valid")
+      return(NULL)  # Return NULL in case of an invalid option
+    }
+  }
+  #Specify species
+    if (sp == "deli"){
+      sp_data <- data %>%
+            group_by(lizard_id) %>%
[…]

### 2024-01-22 ms.qmd
Updates

@@
 bibliography: "./bib/refs.bib"
-csl: "./bib/animal-cognition.csl"
+csl: "./bib/biology-letters.csl"
 reference-doc: "./bib/tmpl.docx"
@@
 ## Methods  
-
-#### Subjects  
-_L.
-guichenoti_ and _L.
-delicata_ are small (∼35--55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia [@chapple_know_2011].
-Both species have similar breeding periods, but with some differences in reproductive output: while *L.
-delicata* lays 1 to 6 eggs in only one clutch per season, *L.
-guichenoti* clutches are smaller (1-5 eggs per clutch) but they usually lay two clutches per season [@chapple_know_2011; @chapple_biology_2014].
-Also, some sudies have found some behavioural divergence between the two skinks [@chapple_know_2011].
-_L.
-delicata_ is more exploratory and bolder than _L.
-guichenoti_ [@chapple_know_2011] which was related to the former's success as an invassive species [@chapple_know_2011; @bezzina2014does], but not with their ability to learn in an associatve learning task [@bezzina2014does].
-
-#### Husbandry  
-*Breeding colony* -- We tested juveniles coming from a breeding colony established in the lab since 2019.
-There is a total of 270 and 180 adults of *L.
-delicata* and *L.
-guichenoti* respectively, housed in big containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure.
-Enclosures are provided with non-stick matting, shelter, and several small water dishes.
-Water is given daily, and they are fed approx.
-40 mid-size crickets (*Acheta domestica*) per enclosure three days a week.
-Crickets are dusted with calcium weekly and multivitamin and calcium biweekly.
-To ensure a temperature gradient, we employ a heat chord and a heat lamp following a 12 h light:12 h dark cycle.
-Room temperatures are set to 22-24 Celsius, and warm side of enclosures is usually at 32 Celsius.
-*Eggs collection and incubation* -- Between mid-October 2022 to the end of February 2023, we provided females with a place to lay the eggs by means of small boxes (12.5 L x 8.3 W x 5 H cm) with moist vermiculite inside, that were placed in one extreme of the communal enclosures (see above).
-We checked for the presence of eggs in the boxes three days a week.
-After collection, we measured length and width of eggs with a digital caliper to the nearest 0.1 mm and weight them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
-Then eggs were treated with CORT or vehicle (see CORT and Temperature manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite).
-The cups were covered with cling wrap to retain moisture and left in LATWIT 2X5D-R1160 incubators at two different temperatures (see CORT and Temperature manipulation below) until hatching.
-*Hatchlings* -- Eggs in the incubator were checked three times a week for hatchlings.
-After hatchling, we measured juveniles' SVL and Tail Length (TL) with a rule to the nearest mm and weighted them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
-We then placed hatchlings in individual enclosures (18.7L x 13.2W x 6.3H cm) and provided them with non-stick matting and a small water dish.
-During this period, they were sprayed water every day and received 3-6 small *A.
-domestica* crickets three times a week.
-All care otherwise follows similar protocols to adults (see above).
-Two weeks before we started the training phase (see below), lizards were moved to the experimental arena for acclimatation.
-The arenas were individual medium size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the extremes and a water dish on the other.
-These new enclosures were placed in two rooms in 7 different racks associated to 7 different CCTV systems (device model DVR-HP210475) that allowed us to record their behaviour during the experiment (see details below).
-The number of lizards per species and treatment in each rack was counterbalanced to control for any effect of the room or the position of the lizard in the rack.
-During acclimatation and all the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin (see protocol below), and water was supplied *ad libitum*.
-We provided a temperature gradient by means of a heat cord and heat lamps in a 12 h light: 12 h dark cycle.
-The rooms temperature was set to between 22-24 Celsius.
-
-#### CORT and Temperature manipulation  
-To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
-We first allocated eggs to one of two different treatments: CORT treatment, where eggs were topically supplied with 5µL of CORT dissolved in 70% Ethanol and 30% DMSO (vehicle) at a final (10 pg CORT/mL) concentration (CORT treatment); and a Control treatment, where eggs received an equal volume of the vehicle.
-CORT concentration employed in the CORT treatment represents 2 standard deviations above the mean natural concentration obtained in eggs from both species (non-published data).
-Then, eggs were incubated in one of the two previously mentioned temperature regimes ('Cold' or 'Hot') until hatching.
-The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.
-
-#### Learning  
-To estimate learning skills, we tested skinks' ability to locate a food reward in a series of behavioural tasks (@fig-Methods B) [see @leal_behavioural_2012; @clark_colour_2014].
-First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical to the ones from the experiment except for the colour (see below).
-We divided this training phase into three stages: in the first stage, lizards had to eat a small, frozen cricket (*A.
-domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure (@fig-Methods B, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods B, Stage 2); and finally, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp in the third and last stage (Fig.
+We employed juveniles of both species, _L.
+delicata_ and _L.
+guichenoti_ that came from a breeding colony kept in the lab (details of breeding colony and husbandry in Supplementary Material).
+Those individuals were treated with prenatal CORT or vehicle, and incubated at different temperatures (see Supplementary Material), but previous data demonstrated that there was no differences in learning skills caused by these treatments (**REF**).
+To estimate behavioural flexibility, we examined lizards' performance in a learning task and its reversal (**REF**) using colour as the main conditioned stimulus and food as a reward (see @fig-Methods).
+There was first a habituation phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm); then a second phase where lizards had to associate the attainability of food with one colour; and finally a reversal task where the colour associated with attainable food was changed (@fig-Methods B).
+We evaluated the correlation between performance in the associative and reversal task as the main estimate of behavioural flexibility.
+The habituation phase was divided into three stages: in the first stage, the reward, a small, frozen cricket (*A.
+domestica*) was placed in an opaque petri dish (3D x 1.6H cm) (@fig-Methods B, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods B, Stage 2); and in the third stage, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp (Fig.
 @fig-Methods B, Stage 3).
-Every trial began when we left the feeding block (petri dish, ramp, or both) inside the enclosure and finished one hour later when we took it away.
-At the end of each trial, we recorded whether the cricket had been consumed or not.
-Trial was considered successful if the lizard could locate and consume the reward, while completion of each stage required the lizards to eat the crickets in at least 5 out of 6 trials.
-This phase lasted 38 days until all the lizards were able to eat from the ramp; only in one case we decided not to use the lizard because its behaviour was not consistent over the course of the training phase.
-In the next phase, we trained lizards to associate between colour and a food reward (Associative task in Fig.
+Trials in every stage lasted one hour, begining when the feeding block (petri dish, ramp, or both) was placed inside the enclosure and finished when we took the feeding block away.
+We recorded whether the cricket had been consumed or not and we considered an stage as completed if the lizards ate the crickets in at least 5 out of 6 trials.
+This phase lasted 38 days, and only in one case we decided not to use the lizard in the next phases because its behaviour was not consistent.
+In the associative phase, we used three ramps that were identical in shape and size but differ in the colour (Associative task in Fig.
 @fig-Methods B).
-The test was like the third stage of the training phase, but here lizards were presented with three feeders that differed in the colour.
-We placed the food reward (small, frozen, *A.
-domestica* crickets) inside the wells of the three feeders, covering two of the crickets with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp.
-The food reward was placed in all three wells to avoid lizard using prey chemical cues, and the lids had a series of small holes on the top to allow the release of those chemicals.
+As in the last stage of the habituation phase, we placed the cricket inside the wells of the ramps, but then two of them were covered with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp.
+The food reward was placed in all three wells to avoid lizard using prey chemical cues, that were released in the closed wells thanks to a series of small holes on the top of the lids.
 The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
-To control for potential colour preference that could bias our results (see Supplementary Material), we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with the non-covered frozen cricket) was the blue one during the associative task and red in the reversal, while for the other group we assigned red as correct for the associative and blue for the reversal.
+However, we decided to split the lizards in two groups to control for potential colour preference that could bias our results.
+One group of lizards was assigned the blue ramp as the correct choice (i.e., the ramp with the non-covered frozen cricket) in the associative task and the red ramp in the reversal, while the other group was assigned red as correct for the associative and blue for the reversal.
 In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
@@
 After the colour association phase, we performed a choice reversal task (Reversal task in @fig-Methods B).
-This task was like the colour association test, except that the attainability of prey was indicated by a different colour, requiring the lizards to form a novel association between the new colour and the food reward.
+Here, the attainability of prey was indicated by a different colour from the reversal, requiring the lizards to form a novel association between the new colour and the food reward.
 This test was done once a day for 40 days.
-The full experiment was done daily between the 6^th^ of March until the 26^th^ of June 2023, between 11 to 12 am, when the lizards were active.
+We performed the full experiment was between the 6^th^ of March until the 26^th^ of June 2023, between 11 to 12 am, when the lizards were active.
 Trials in the learning phases (colour associative task and reversal tasks) were recorded with different CCTV systems always using the same camera per individual.
@@
 A choice was considered to be made if the head of the lizard was inside the well of one of the ramps.
-PR was blinded to the treatments of the lizards during the analyses of the video.
 We considered a trial failed if there was no choice in one hour of recording and those trials were considered as 'non data' in the analyses.
@@
 they did not make a choice), and we considered the first trial to be the first one where the individual made a choice.
+We also considered individuals to be reinforced if the cricket was eaten after the test independently of whether their initial choice was correct or not.
 
@@
 #### Statistical analyses
-We performed the analyses with species (_L.
-delicata_ or _L.
-guichenoti_) and task ('Associative' or 'Reversal') separately.
-We also saw a significant effect of the colour assigned in the preliminary analises, so we decided to split the data by colour ('Blue' or 'Red') as well.
-As such, we run a total of different 8 models employing Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022).
+
+**As such, we run a total of different 8 models employing Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022).
 Each model consisted of four parallel chains of 3000 iterations, with a warm up interval of 1000 iterations.'Choice', i.e.
@@
 slope for 'CORT-Cold' lizards minus 'CORT-Hot' lizards) were different from zero (two-tailed tests).
-We considered statistical significance if p-value < 0.05.
+We considered statistical significance if p-value < 0.05.**
 
 ## Results
-```{r, cleaning}
-#| label: cleaning
-source(here("R", "1_data_process.R"))
-# Once we run this code, the result will be two different dataframes, one for the Associative learning task (data_asso) and the other for the Reversal learning task (data_rev).
-write.csv(data_asso, file= "./output/databases_clean/data_asso.csv")
-write.csv(data_rev, file= "./output/databases_clean/data_rev.csv")
-```
-
-```{r, sampleSize}
-#| label: sampleSize
-# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task.
-We used function sample (see func.R) to estimate the sample size per treatment and species.
-source(here("R", "func.R"))
-#
-specie <- c("delicata", "guichenoti")
-groups <- c("Red", "Blue")
-hormone <- c("CORT", "Control")
-temperature <- c("Cold", "Hot")
-#
-n_list <- list()
-#
-for(i in 1:length(specie)){
-  for(j in 1:length(groups)){
-    for(k in 1:length(hormone)){
-      for(l in 1:length(temperature)){
-        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(specie[i], groups[j], hormone[k], temperature[l])
-      }
-    }
-  }
-}
-```
-
-Originally, we started with 96 lizards, 48 per species and 12 per treatment per species.
-However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3; see above), we ended up with a total of 81 lizards.
-Final sample sizes per treatment and species are disclosed on @tbl-data.
-```{r, models}
-#| label: models
-# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder).
-The result everytime the function is used is a df with the posteriors of the model.
-The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
-source(here("R", "func.R"))
-# A) Associative task. Model formula: FC_associative ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id)
-## A.1) L. delicata
-deli_asso_red <- fit_m("asso", "deli", "red", refit = FALSE)
-write.csv(deli_asso_red, file= "./output/Checking/deli_asso_red.csv")
-deli_asso_blue <- fit_m("asso", "deli", "blue", refit = FALSE)
-write.csv(deli_asso_blue, file= "./output/Checking/deli_asso_blue.csv")
-## A.2) L. guichenoti
-guich_asso_red <- fit_m("asso", "guich", "red", refit = FALSE)
-write.csv(guich_asso_red, file= "./output/Checking/guich_asso_red.csv")
-guich_asso_blue <- fit_m("asso", "guich", "blue", refit = FALSE)
-write.csv(guich_asso_blue, file= "./output/Checking/guich_asso_blue.csv")
-# B) Reversal task. Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
-## B.1) L. delicata
-deli_rev_red <- fit_m("rev", "deli", "red", refit = FALSE)
-write.csv(deli_rev_red, file= "./output/Checking/deli_rev_red.csv")
-deli_rev_blue <- fit_m("rev", "deli", "blue", refit = FALSE)
-write.csv(deli_rev_blue, file= "./output/Checking/deli_rev_blue.csv")
-## B.2) L. guichenoti
-guich_rev_red <- fit_m("rev", "guich", "red", refit = FALSE)
-write.csv(guich_rev_red, file= "./output/Checking/guich_rev_red.csv")
-guich_rev_blue <- fit_m("rev", "guich", "blue", refit = FALSE)
-write.csv(guich_rev_blue, file= "./output/Checking/guich_rev_blue.csv")
-```
-
-```{r, resultsAsso}
-# Rename some of the posteriors and obtain estimates for the "learning rate" for each group and treatment in the Associative task.
-This "learning rate" consists on the slope of the posterior of the Associative_Trial parameter.
-The slope is the rate at which the probability of choosing the correct feeder increases with each trial.
-The slope is obtained by adding the posterior of the Associative_Trial parameter to the posterior of the interaction between Associative_Trial and the treatment (cort and temp).
-## 1) L. delicata
-### Group = red
-dar_CORTCold <- deli_asso_red$b_Associative_Trial #Slope for treatment CORT-Cold for L. delicata, red as the right choice
-dar_ControlCold <- (deli_asso_red$'b_Associative_Trial:cortControl' + deli_asso_red$b_Associative_Trial)
-dar_CORTHot <- (deli_asso_red$'b_Associative_Trial:tempHot' + deli_asso_red$b_Associative_Trial)
-dar_ControlHot <- (deli_asso_red$'b_Associative_Trial:cortControl:tempHot' + deli_asso_red$b_Associative_Trial+ deli_asso_red$'b_Associative_Trial:cortControl' + deli_asso_red$'b_Associative_Trial:tempHot')
-### Group = blue
-dab_CORTCold <- deli_asso_blue$b_Associative_Trial
-dab_ControlCold <- (deli_asso_blue$'b_Associative_Trial:cortControl' + deli_asso_blue$b_Associative_Trial)
-dab_CORTHot <- (deli_asso_blue$'b_Associative_Trial:tempHot' + deli_asso_blue$b_Associative_Trial)
-dab_ControlHot <- (deli_asso_blue$'b_Associative_Trial:cortControl:tempHot' + deli_asso_blue$b_Associative_Trial + deli_asso_blue$'b_Associative_Trial:cortControl' + deli_asso_blue$'b_Associative_Trial:tempHot')
-## 2) L. guichenoti
-### Group = red
-gar_CORTCold <- guich_asso_red$b_Associative_Trial
-gar_ControlCold <- (guich_asso_red$'b_Associative_Trial:cortControl' + guich_asso_red$b_Associative_Trial)
-gar_CORTHot <- (guich_asso_red$'b_Associative_Trial:tempHot' + guich_asso_red$b_Associative_Trial)
-gar_ControlHot <- (guich_asso_red$'b_Associative_Trial:cortControl:tempHot' + guich_asso_red$b_Associative_Trial + guich_asso_red$'b_Associative_Trial:cortControl' + guich_asso_red$'b_Associative_Trial:tempHot')
-### Group = blue
-gab_CORTCold <- guich_asso_blue$b_Associative_Trial
-gab_ControlCold <- (guich_asso_blue$'b_Associative_Trial:cortControl' + guich_asso_blue$b_Associative_Trial)
-gab_CORTHot <- (guich_asso_blue$'b_Associative_Trial:tempHot' + guich_asso_blue$b_Associative_Trial)
-gab_ControlHot <- (guich_asso_blue$'b_Associative_Trial:cortControl:tempHot' + guich_asso_blue$b_Associative_Trial + guich_asso_blue$'b_Associative_Trial:cortControl' + guich_asso_blue$'b_Associative_Trial:tempHot')
-```
-
-```{r, resultsRev}
-# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task doing the same thing we did in the chunk above.
-## 1) L. delicata
-### Group = red
-drr_CORTCold <- deli_rev_red$b_trial_reversal
-drr_ControlCold <- (deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$b_trial_reversal)
-drr_CORTHot <- (deli_rev_red$'b_trial_reversal:tempHot' + deli_rev_red$b_trial_reversal)
-drr_ControlHot <- (deli_rev_red$'b_trial_reversal:cortControl:tempHot' + deli_rev_red$b_trial_reversal + deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$'b_trial_reversal:tempHot')
-### Group = blue
-drb_CORTCold <- deli_rev_blue$b_trial_reversal
-drb_ControlCold <- (deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$b_trial_reversal)
-drb_CORTHot <- (deli_rev_blue$'b_trial_reversal:tempHot' + deli_rev_blue$b_trial_reversal)
-drb_ControlHot <- (deli_rev_blue$'b_trial_reversal:cortControl:tempHot' + deli_rev_blue$b_trial_reversal + deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$'b_trial_reversal:tempHot')
-## 2) L. guichenoti
-### Group = red
-grr_CORTCold <- guich_rev_red$b_trial_reversal
-grr_ControlCold <- (guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$b_trial_reversal)
-grr_CORTHot <- (guich_rev_red$'b_trial_reversal:tempHot' + guich_rev_red$b_trial_reversal)
-grr_ControlHot <- (guich_rev_red$'b_trial_reversal:cortControl:tempHot' + guich_rev_red$b_trial_reversal + guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$'b_trial_reversal:tempHot')
-### Group = blue
-grb_CORTCold <- guich_rev_blue$b_trial_reversal
-grb_ControlCold <- (guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$b_trial_reversal)
-grb_CORTHot <- (guich_rev_blue$'b_trial_reversal:tempHot' + guich_rev_blue$b_trial_reversal)
-grb_ControlHot <- (guich_rev_blue$'b_trial_reversal:cortControl:tempHot' + guich_rev_blue$b_trial_reversal + guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$'b_trial_reversal:tempHot')
-```
-
-```{r, tbl-data}
-#| label: tbl-data
-#| tbl-cap: "Estimates of Associative learning slope for all the different treatments per each task, species and group.
-Mean shows the aritmetic mean of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
-All p-values were obtained using pmcmc and test the hypothesis that the mean is equal to zero.
-In bold, those values that are significant (p-value <0.05)"
-source(here("R", "func.R"))
-#
-############################## CREATING BIG DF FOR TABLE ##############################
-# Building the vectors for titles of rows and columns
-specie <- c("L. delicata", "L. guichenoti")
-groups <- c("Red", "Blue")
-test <- c("Associative", "Reversal")
-treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
-values <- c("Mean", "95% CI", "p-value")
-# Building the vectors for estimated means, co.intervals(95%), and p-values for the slopes obtained from posteriors.
-p-values are obtained using pmcmc function (see func.R), assuming a two-tailed test that testes the hypothesis that the value (slopes in this case) is 0.
-#First get estimates for both tasks
-estimates_asso <- list(
-  dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot, 
-  dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot, 
-  gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot, 
-  gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot
-)
-#
-estimates_rev <- list(
-  drr_CORTCold, drr_ControlCold, drr_CORTHot, drr_ControlHot, 
-  drb_CORTCold, drb_ControlCold, drb_CORTHot, drb_ControlHot, 
-  grr_CORTCold, grr_ControlCold, grr_CORTHot, grr_ControlHot, 
-  grb_CORTCold, grb_ControlCold, grb_CORTHot, grb_ControlHot
-)
-# Then get the mean, co.intervals(95%), and p-values
-asso_mean <- format_dec(sapply(estimates_asso, mean), 3)
-asso_interval_025 <- format_dec(sapply(estimates_asso, function(x) quantile(x,0.025)), 3)
-asso_interval_975 <- format_dec(sapply(estimates_asso, function(x) quantile(x,0.975)), 3)
-asso_intervals <- paste(asso_interval_025, asso_interval_975, sep = " , ")
-asso_pvalue <- format_dec(sapply(estimates_asso, pmcmc), 3)
-#
-rev_mean <- format_dec(sapply(estimates_rev, mean), 3)
-rev_interval_025 <- format_dec(sapply(estimates_rev, function(x) quantile(x,0.025)), 3)
-rev_interval_975 <- format_dec(sapply(estimates_rev, function(x) quantile(x,0.975)), 3)
-rev_intervals <- paste(rev_interval_025, rev_interval_975, sep = " , ")
-rev_pvalue <- format_dec(sapply(estimates_rev, pmcmc), 3)
-#
-# Building the df for the associative
-asso_df <- data.frame(
-  Specie = rep(specie, each = length(groups) * length(treatments)),
-  Group = rep(rep(groups, each = length(treatments)), times = length(specie)),
-  Treatment = rep(rep(treatments, each = 1), times = length(groups) * length(specie)),
-  Mean = rep(asso_mean, each = 1),
-  CI = rep(asso_intervals, each = 1),
-  PValue = rep(asso_pvalue, each = 1),
-  Task = rep("Associative", length(asso_mean))
-)
-# Building the df for the reversal
-rev_df <- data.frame(
-  Specie = rep(specie, each = length(groups) * length(treatments)),
-  Group = rep(rep(groups, each = length(treatments)), times = length(specie)),
-  Treatment = rep(rep(treatments, each = 1), times = length(groups) * length(specie)),
-  Mean = rep(rev_mean, each = 1),
-  CI = rep(rev_intervals, each = 1),
-  PValue = rep(rev_pvalue, each = 1),
-  Task = rep("Reversal", length(rev_mean))
-)
-# Joining both dfs
-table_data <- rbind(asso_df, rev_df)
-table_data[, sapply(table_data, is.numeric)] <- lapply(table_data[, sapply(table_data, is.numeric)], function(x) format(x, scientific = FALSE))
-#
-############################## ADDING SAMPLE SIZE TO DF FOR TABLE ##############################
-# Make n_list into a df
-n_df <- as.data.frame(do.call(rbind, n_list)) %>%
-  rename("n" = V1) %>%
-  rownames_to_column("model") %>%
-  separate(model, into = c("Specie", "Group", "cort", "temp"), sep = "_") %>%
-  unite("Treatment", c("cort", "temp"), sep = "-") %>%
-  mutate(Specie = factor(Specie,
-                  labels = c(delicata = "L. delicata", guichenoti = "L. guichenoti")),
-        Treatment = factor(Treatment,
-                   levels = c("CORT-Cold", "Control-Cold", "CORT-Hot","Control-Hot")))
-# Merge both dfs, put sample size together with the treatment, and organize the new df to make it look like the table
-new_table_data <- merge(table_data, n_df) %>%
-  rename('p-value' = 'PValue', '95% CI' = 'CI') %>% #Change the names of the columns for the table
-  pivot_wider(names_from = Task, values_from = c(Mean, `95% CI`, `p-value`)) %>% # to split between Asociative and Reversal
-  select(Specie, Group, Treatment, Mean_Associative, `95% CI_Associative`, `p-value_Associative`, Mean_Reversal, `95% CI_Reversal`, `p-value_Reversal`, n) %>% #To order the columns in the way I want for the table
-  mutate(Specie = factor(Specie,
-                  levels = c("L. delicata", "L. guichenoti")),
-        Group = factor(Group,
-                  levels = c("Red", "Blue")),
-        Treatment = factor(Treatment, 
-                  levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")))%>%
-  arrange(Specie, Group, Treatment) %>% # To arrange the rows the way I want
-  unite("Treatment", c("Treatment", "n"), sep = " (n = ") %>%
-  mutate(Treatment = paste0(Treatment, ")"))
-write.csv(new_table_data, file= "./output/Checking/new_table_data.csv")
-#
-############################## MAKING THE TABLE ##############################
-## Table format
-set_flextable_defaults(
- font.family = "Times New Roman",
- fint.size = 10)
-# Split the table_data df by task
-real_table <- flextable(new_table_data) %>%
-    bold(~ `p-value_Associative` < 0.05, ~ `p-value_Associative` + Mean_Associative + `95% CI_Associative`) %>%
-    bold(~ `p-value_Reversal` < 0.05, ~ `p-value_Reversal` + Mean_Reversal + `95% CI_Reversal`) %>%
-    set_table_properties(width = 1) %>%
-    align(align="center", part="all") %>% 
-    add_header_row(values = c("", "Associative task", "Reversal task"), colwidths = c(3, 3, 3)) %>%
-    set_header_labels(Mean_Associative = "Mean",
-                      `95% CI_Associative` = "95% CI",
-                      `p-value_Associative` = "p-value",
-                      Mean_Reversal = "Mean",
-                      `95% CI_Reversal` = "95% CI",
-                      `p-value_Reversal` = "p-value") %>%
-    italic(j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
-    flextable::compose(i = c(2:8,10:16), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
-    flextable::compose(i = c(2:4,6:8,10:12,14:16), j = 2, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the second column
-    hline(i = c(4,12), j = c(2:9), part = "body") %>% # To make some horizontal lines
-    hline(i = c(8), j = c(1:9), part = "body") %>% # To make some horizontal lines
-    vline(i = (1:16), j = c(3,6), part = "body") %>% # To make some vertical lines on body
-    vline(j=c(3,6), part = "header") %>% # To make some vertical lines on header
-    autofit() 
-real_table
-```
-
-Results of the associative task are summarized in @tbl-data and figures @Figdeli, @Figguich.
-On average, we found that the estimated learning slopes were lower when the blue feeders were the correct choice compared to those assigned to the group 'Red'  for _L.
-delicata_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot)), 3)`, p = `r format_dec(pmcmc((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot)), 3)`), but not for _L.
-guichenoti_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)), 3)`, p = `r format_dec(pmcmc((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)),3)`).
-However, further analyses using the first trial indicated a potential bias towards 'Blue' in the initial choice (see Supplementary Material and Figs.
-@Figdeli, @Figguich); and in consequence, we only used those individuals assigned to 'Red' to compare between-treatment performance in the associative learning task.
-In this regard, we did not find any significant differences between treatments for _L.
-delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dar_ControlCold - dar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(dar_ControlCold - dar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dar_ControlHot- dar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(dar_ControlHot - dar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dar_ControlHot - dar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(dar_ControlHot - dar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dar_CORTHot - dar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(dar_CORTHot - dar_CORTCold), 3)`) (see @Figdeli), or _L.
-guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gar_ControlCold - gar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(gar_ControlCold - gar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gar_ControlHot- gar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(gar_ControlHot - gar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gar_ControlHot - gar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(gar_ControlHot - gar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gar_CORTHot - gar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(gar_CORTHot - gar_CORTCold), 3)`) (see @Figguich).
-When groups were pooled by incubation temperature or hormonal treatment, there was not significant differences in the estimated slopes caused by temperature (_L.
-delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`, p-value = `r format_dec(pmcmc((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`; _L.
-guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`, p-value = `r format_dec(pmcmc((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`) or the hormone (_L.
-delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)` ; _L.
-guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`).
-We also did not find any significant differences when we compared the estimated slopes between species for the associative task (_L.
-delicata_ - _L.
-guichenoti_ = `r format_dec(mean((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`).
-In the reversal tesk, we decided to pool both groups 'Blue' and 'Red' to make the between-treatment comparisons for two reasons.
-First, we did not find any significant differences caused group on the learning slopes (_L.
-delicata_: 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean((drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drr_CORTCold + drr_ControlHot)), 3)`, p = `r format_dec(pmcmc((drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drr_CORTCold + drr_ControlHot)), 3)`; _L.
-guichenoti_: 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean((grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTCold + grr_ControlHot)), 3)`, p = `r format_dec(pmcmc((grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTCold + grr_ControlHot)), 3)`).
-Second, we were expecting an acquired bias towards the colour assigned in the associative task as part of the design.
-Nonetheless, we did not find any significant differences between treatments in _L.
-delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean((drr_ControlCold + drb_ControlCold) - (drr_CORTCold + drb_CORTCold)), 3)`, p- value = `r format_dec(pmcmc((drr_ControlCold + drb_ControlCold) - (drr_CORTCold + drb_CORTCold)), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((drr_ControlHot + drb_ControlHot) - (drr_CORTHot + drb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((drr_ControlHot + drb_ControlHot) - (drr_CORTHot + drb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((drr_ControlHot + drb_ControlHot) - (drr_ControlCold + drb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((drr_ControlHot + drb_ControlHot) - (drr_ControlCold + drb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((drr_CORTHot + drb_CORTHot) - (drr_CORTCold + drb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((drr_CORTHot + drb_CORTHot) - (drr_CORTCold + drb_CORTCold)), 3)`) (see @Figdeli) or _L.
-guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean((grr_ControlCold + grb_ControlCold) - (grr_CORTCold + grb_CORTCold)), 3)`, p- value = `r format_dec(pmcmc((grr_ControlCold + grb_ControlCold) - (grr_CORTCold + grb_CORTCold)), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((grr_ControlHot + grb_ControlHot) - (grr_CORTHot + grb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((grr_ControlHot + grb_ControlHot) - (grr_CORTHot + grb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((grr_ControlHot + grb_ControlHot) - (grr_ControlCold + grb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((grr_ControlHot + grb_ControlHot) - (grr_ControlCold + grb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((grr_CORTHot + grb_CORTHot) - (grr_CORTCold + grb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((grr_CORTHot + grb_CORTHot) - (grr_CORTCold + grb_CORTCold)), 3)`) (see @Figguich).
-We did not find any effect of incubation temperature (_L.
-delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((drr_CORTHot + drr_ControlHot + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drb_CORTCold + drb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((drr_CORTHot + drr_ControlHot + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drb_CORTCold + drb_ControlCold)),3)`; _L.
-guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((grr_CORTHot + grr_ControlHot + grb_CORTHot + grb_ControlHot) -(grr_CORTCold + grr_ControlCold + grb_CORTCold + grb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((grr_CORTHot + grr_ControlHot + grb_CORTHot + grb_ControlHot) -(grr_CORTCold + grr_ControlCold + grb_CORTCold + grb_ControlCold)),3)`) or the hormone (_L.
-delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((drr_ControlCold + drr_ControlHot + drb_ControlCold + drb_ControlHot) - (drr_CORTCold + drr_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((drr_ControlCold + drr_ControlHot + drb_ControlCold + drb_ControlHot) - (drr_CORTCold + drr_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`;_L.
-guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((grr_ControlCold + grr_ControlHot + grb_ControlCold + grb_ControlHot)-(grr_CORTCold + grr_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((grr_ControlCold + grr_ControlHot + grb_ControlCold + grb_ControlHot)-(grr_CORTCold + grr_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`) when groups were pooled.
-Finally, we did not find any significant differences when we compared the estimated slopes between species for the reversal task (_L.
-delicata_ - _L.
-guichenoti_ = `r format_dec(mean((drr_CORTCold + drr_ControlCold + drr_CORTHot + drr_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTHot + grr_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((drr_CORTCold + drr_ControlCold + drr_CORTHot + drr_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTHot + grr_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`).
-
-```{r, figdeli}
-#| label: figdeli
-#| fig.cap: "Deli"
-# First step, create the Intercepts for all models
-## 1) Associative task
-### Group = red
-int_dar_CORTCold <- deli_asso_red$b_Intercept
-int_dar_ControlCold <- (deli_asso_red$b_cortControl + deli_asso_red$b_Intercept)
-int_dar_CORTHot <- (deli_asso_red$b_tempHot + deli_asso_red$b_Intercept)
-int_dar_ControlHot <- (deli_asso_red$'b_cortControl:tempHot' + deli_asso_red$b_cortControl + deli_asso_red$b_tempHot + deli_asso_red$b_Intercept)
-### Group = blue
-int_dab_CORTCold <- deli_asso_blue$b_Intercept
-int_dab_ControlCold <- (deli_asso_blue$b_cortControl + deli_asso_blue$b_Intercept)
-int_dab_CORTHot <- (deli_asso_blue$b_tempHot + deli_asso_blue$b_Intercept)
-int_dab_ControlHot <- (deli_asso_blue$'b_cortControl:tempHot' + deli_asso_blue$b_cortControl + deli_asso_blue$b_tempHot + deli_asso_blue$b_Intercept)
-## 2) Reversal task
-### Group = red
-int_drr_CORTCold <- deli_rev_red$b_Intercept
-int_drr_ControlCold <- (deli_rev_red$b_cortControl + deli_rev_red$b_Intercept)
-int_drr_CORTHot <- (deli_rev_red$b_tempHot + deli_rev_red$b_Intercept)
-int_drr_ControlHot <- (deli_rev_red$'b_cortControl:tempHot' + deli_rev_red$b_cortControl + deli_rev_red$b_tempHot + deli_rev_red$b_Intercept)
-### Group = blue
-int_drb_CORTCold <- deli_rev_blue$b_Intercept
-int_drb_ControlCold <- (deli_rev_blue$b_cortControl + deli_rev_blue$b_Intercept)
-int_drb_CORTHot <- (deli_rev_blue$b_tempHot + deli_rev_blue$b_Intercept)
-int_drb_ControlHot <- (deli_rev_blue$'b_cortControl:tempHot' + deli_rev_blue$b_cortControl + deli_rev_blue$b_tempHot + deli_rev_blue$b_Intercept)
-# Second step, create the df for each model with trials as columns and the predicted probability of choosing right as rows under equation: Prob = 1/(1+e^-(Intercept + Slope*trial))??
-## 1) Associative task
-### Group = red
-#### CORT-Cold
-
-```
-
-```{r, figguich}
-#| label: Figguich
-#| fig.cap: "Guich"
-```
 
@@
 
-#### Checking the models plots  
-```{r, residuals}
-# Chunk for calling all the models and making the residuals
-# Associative task
-## L. delicata
-### Red
-mod_dar <- readRDS(here("output/models/asso_deli_red.rds"))
-resid_dar <- residuals(mod_dar)
-### Blue
-mod_dab <- readRDS(here("output/models/asso_deli_blue.rds"))
-resid_dab <- residuals(mod_dab)
-## L. guichenoti
-### Red
-mod_gar <- readRDS(here("output/models/asso_guich_red.rds"))
-resid_gar <- residuals(mod_gar)
-### Blue
-mod_gab <- readRDS(here("output/models/asso_guich_blue.rds"))
-resid_gab <- residuals(mod_gab)
-# Reversal task
-## L. delicata
-### Red
-mod_drr <- readRDS(here("output/models/rev_deli_red.rds"))
-resid_drr <- residuals(mod_drr)
-### Blue
-mod_drb <- readRDS(here("output/models/rev_deli_blue.rds"))
-resid_drb <- residuals(mod_drb)
-## L. guichenoti
-### Red
-mod_grr <- readRDS(here("output/models/rev_guich_red.rds"))
-resid_grr <- residuals(mod_grr)
-### Blue
-mod_grb <- readRDS(here("output/models/rev_guich_blue.rds"))
-resid_grb <- residuals(mod_grb)
-```
+#### Husbandry  
+*Breeding colony* -- We tested juveniles coming from a breeding colony established in the lab since 2019.
+There is a total of 270 and 180 adults of *L.
+delicata* and *L.
+guichenoti* respectively, housed in big containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure.
+Enclosures are provided with non-stick matting, shelter, and several small water dishes.
+Water is given daily, and they are fed approx.
+40 mid-size crickets (*Acheta domestica*) per enclosure three days a week.
+Crickets are dusted with calcium weekly and multivitamin and calcium biweekly.
+To ensure a temperature gradient, we employ a heat chord and a heat lamp following a 12 h light:12 h dark cycle.
+Room temperatures are set to 22-24 Celsius, and warm side of enclosures is usually at 32 Celsius.
+*Eggs collection and incubation* -- Between mid-October 2022 to the end of February 2023, we provided females with a place to lay the eggs by means of small boxes (12.5 L x 8.3 W x 5 H cm) with moist vermiculite inside, that were placed in one extreme of the communal enclosures (see above).
+We checked for the presence of eggs in the boxes three days a week.
+After collection, we measured length and width of eggs with a digital caliper to the nearest 0.1 mm and weight them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
+Then eggs were treated with CORT or vehicle (see CORT and Temperature manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite).
+The cups were covered with cling wrap to retain moisture and left in LATWIT 2X5D-R1160 incubators at two different temperatures (see CORT and Temperature manipulation below) until hatching.
+*Hatchlings* -- Eggs in the incubator were checked three times a week for hatchlings.
+After hatchling, we measured juveniles' SVL and Tail Length (TL) with a rule to the nearest mm and weighted them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
+We then placed hatchlings in individual enclosures (18.7L x 13.2W x 6.3H cm) and provided them with non-stick matting and a small water dish.
+During this period, they were sprayed water every day and received 3-6 small *A.
+domestica* crickets three times a week.
+All care otherwise follows similar protocols to adults (see above).
+Two weeks before we started the training phase (see below), lizards were moved to the experimental arena for acclimatation.
+The arenas were individual medium size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the extremes and a water dish on the other.
+These new enclosures were placed in two rooms in 7 different racks associated to 7 different CCTV systems (device model DVR-HP210475) that allowed us to record their behaviour during the experiment (see details below).
+The number of lizards per species and treatment in each rack was counterbalanced to control for any effect of the room or the position of the lizard in the rack.
+During acclimatation and all the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin (see protocol below), and water was supplied *ad libitum*.
+We provided a temperature gradient by means of a heat cord and heat lamps in a 12 h light: 12 h dark cycle.
+The rooms temperature was set to between 22-24 Celsius.
 
-Model formula for the associative task is:  
-Choice  ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id)  
-Plots for the different models of the associative task:  
-1.- _L. delicata_  
-  1.a.- Red  
-```{r , plotmod_dar, out.width="70%", fig.align="center"}
-plot(mod_dar)
-```
-```{r, results='asis', echo=FALSE}
-cat("\\newpage")
-```
-
-  1.b.- Blue  
-```{r , plotmod_dab, out.width="70%", fig.align="center"}
-plot(mod_dab)
-```
+#### CORT and Temperature manipulation  
+To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
+We first allocated eggs to one of two different treatments: CORT treatment, where eggs were topically supplied with 5µL of CORT dissolved in 70% Ethanol and 30% DMSO (vehicle) at a final (10 pg CORT/mL) concentration (CORT treatment); and a Control treatment, where eggs received an equal volume of the vehicle.
+CORT concentration employed in the CORT treatment represents 2 standard deviations above the mean natural concentration obtained in eggs from both species (non-published data).
+Then, eggs were incubated in one of the two previously mentioned temperature regimes ('Cold' or 'Hot') until hatching.
+The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.
 
@@
 ```
-
-2.- _L. guichenoti_  
-  2.a.- Red  
-```{r , plotmod_gar, out.width="70%", fig.align="center"}
-plot(mod_gar)
-```
-```{r, results='asis', echo=FALSE}
-cat("\\newpage")
-```
-
-  2.b.- Blue  
-```{r , plotmod_gab, out.width="70%", fig.align="center"}
-plot(mod_gab)
-```
-
-```{r, results='asis', echo=FALSE}
-cat("\\newpage")
-```
-
-Model formula for the reversal task is:  
-Choice  ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)  
-Plots for the different models of the associative task:  
-1.- _L. delicata_  
-  1.a.- Red  
-```{r , plotmod_drr, out.width="70%", fig.align="center"}
-plot(mod_drr)
-```
-
-```{r, results='asis', echo=FALSE}
-cat("\\newpage")
-```
-
-  1.b.- Blue  
-```{r , plotmod_drb, out.width="70%", fig.align="center"}  
-plot(mod_drb)
-```
-
-```{r, results='asis', echo=FALSE}
-cat("\\newpage")
-```
-
-2.- _L. guichenoti_  
-  2.a.- Red  
-```{r , plotmod_grr, out.width="70%", fig.align="center"}
-plot(mod_grr)
-```
-
-```{r, results='asis', echo=FALSE}
-cat("\\newpage")
-```
-
-  2.b.- Blue  
-```{r , plotmod_grb, out.width="70%", fig.align="center"}
-plot(mod_grb)
-```

### 2024-01-26 ms.qmd
Updates

@@
 ## Results
+```{r, sampleSize}
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task.
+We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+groups <- c("Red", "Blue")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(j in 1:length(groups)){
+    for(k in 1:length(hormone)){
+      for(l in 1:length(temperature)){
+        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(specie[i], groups[j], hormone[k], temperature[l])
+      }
+    }
+  }
+}
+```
+
+Originally, we started with 96 lizards, 48 per species and 12 per treatment per species.
+However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3; see above), we ended up with a total of 81 lizards.
+Final sample sizes per treatment and species are disclosed on @tbl-data.
+
+```{r, models}
+#| label: models
+# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder).
+The result everytime the function is used is a df with the posteriors of the model.
+The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
+source(here("R", "func.R"))
+# A) Associative task. Model formula: FC_associative ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id)
+## A.1) L. delicata
+deli_asso_red <- fit_m("asso", "deli", "red", refit = FALSE)
+write.csv(deli_asso_red, file= "./output/Checking/deli_asso_red.csv")
+deli_asso_blue <- fit_m("asso", "deli", "blue", refit = FALSE)
+write.csv(deli_asso_blue, file= "./output/Checking/deli_asso_blue.csv")
+## A.2) L. guichenoti
+guich_asso_red <- fit_m("asso", "guich", "red", refit = FALSE)
+write.csv(guich_asso_red, file= "./output/Checking/guich_asso_red.csv")
+guich_asso_blue <- fit_m("asso", "guich", "blue", refit = FALSE)
+write.csv(guich_asso_blue, file= "./output/Checking/guich_asso_blue.csv")
+# B) Reversal task. Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
+## B.1) L. delicata
+deli_rev_red <- fit_m("rev", "deli", "red", refit = FALSE)
+write.csv(deli_rev_red, file= "./output/Checking/deli_rev_red.csv")
+deli_rev_blue <- fit_m("rev", "deli", "blue", refit = FALSE)
+write.csv(deli_rev_blue, file= "./output/Checking/deli_rev_blue.csv")
+## B.2) L. guichenoti
+guich_rev_red <- fit_m("rev", "guich", "red", refit = FALSE)
+write.csv(guich_rev_red, file= "./output/Checking/guich_rev_red.csv")
+guich_rev_blue <- fit_m("rev", "guich", "blue", refit = FALSE)
+write.csv(guich_rev_blue, file= "./output/Checking/guich_rev_blue.csv")
+```
+
+```{r, resultsRev}
+# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task doing the same thing we did in the chunk above.
+## 1) L. delicata
+### Group = red
+drr_CORTCold <- deli_rev_red$b_trial_reversal
+drr_ControlCold <- (deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$b_trial_reversal)
+drr_CORTHot <- (deli_rev_red$'b_trial_reversal:tempHot' + deli_rev_red$b_trial_reversal)
+drr_ControlHot <- (deli_rev_red$'b_trial_reversal:cortControl:tempHot' + deli_rev_red$b_trial_reversal + deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$'b_trial_reversal:tempHot')
+### Group = blue
+drb_CORTCold <- deli_rev_blue$b_trial_reversal
+drb_ControlCold <- (deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$b_trial_reversal)
+drb_CORTHot <- (deli_rev_blue$'b_trial_reversal:tempHot' + deli_rev_blue$b_trial_reversal)
+drb_ControlHot <- (deli_rev_blue$'b_trial_reversal:cortControl:tempHot' + deli_rev_blue$b_trial_reversal + deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$'b_trial_reversal:tempHot')
+## 2) L. guichenoti
+### Group = red
+grr_CORTCold <- guich_rev_red$b_trial_reversal
+grr_ControlCold <- (guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$b_trial_reversal)
+grr_CORTHot <- (guich_rev_red$'b_trial_reversal:tempHot' + guich_rev_red$b_trial_reversal)
+grr_ControlHot <- (guich_rev_red$'b_trial_reversal:cortControl:tempHot' + guich_rev_red$b_trial_reversal + guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$'b_trial_reversal:tempHot')
+### Group = blue
+grb_CORTCold <- guich_rev_blue$b_trial_reversal
+grb_ControlCold <- (guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$b_trial_reversal)
+grb_CORTHot <- (guich_rev_blue$'b_trial_reversal:tempHot' + guich_rev_blue$b_trial_reversal)
+grb_ControlHot <- (guich_rev_blue$'b_trial_reversal:cortControl:tempHot' + guich_rev_blue$b_trial_reversal + guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$'b_trial_reversal:tempHot')
+```
+
+```{r, tbl-data}
+#| label: tbl-data
+#| tbl-cap: "Estimates of Associative learning slope for all the different treatments per each task, species and group.
+Mean shows the aritmetic mean of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
+All p-values were obtained using pmcmc and test the hypothesis that the mean is equal to zero.
+In bold, those values that are significant (p-value <0.05)"
+source(here("R", "func.R"))
+#
+############################## CREATING BIG DF FOR TABLE ##############################
+# Building the vectors for titles of rows and columns
+specie <- c("L. delicata", "L. guichenoti")
+groups <- c("Red", "Blue")
+test <- c("Associative", "Reversal")
+treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
+values <- c("Mean", "95% CI", "p-value")
+# Building the vectors for estimated means, co.intervals(95%), and p-values for the slopes obtained from posteriors.
+p-values are obtained using pmcmc function (see func.R), assuming a two-tailed test that testes the hypothesis that the value (slopes in this case) is 0.
+#First get estimates for both tasks
+estimates_asso <- list(
+  dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot, 
+  dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot, 
+  gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot, 
+  gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot
+)
+#
+estimates_rev <- list(
+  drr_CORTCold, drr_ControlCold, drr_CORTHot, drr_ControlHot, 
+  drb_CORTCold, drb_ControlCold, drb_CORTHot, drb_ControlHot, 
+  grr_CORTCold, grr_ControlCold, grr_CORTHot, grr_ControlHot, 
+  grb_CORTCold, grb_ControlCold, grb_CORTHot, grb_ControlHot
+)
+# Then get the mean, co.intervals(95%), and p-values
+asso_mean <- format_dec(sapply(estimates_asso, mean), 3)
+asso_interval_025 <- format_dec(sapply(estimates_asso, function(x) quantile(x,0.025)), 3)
+asso_interval_975 <- format_dec(sapply(estimates_asso, function(x) quantile(x,0.975)), 3)
+asso_intervals <- paste(asso_interval_025, asso_interval_975, sep = " , ")
+asso_pvalue <- format_dec(sapply(estimates_asso, pmcmc), 3)
+#
+rev_mean <- format_dec(sapply(estimates_rev, mean), 3)
+rev_interval_025 <- format_dec(sapply(estimates_rev, function(x) quantile(x,0.025)), 3)
+rev_interval_975 <- format_dec(sapply(estimates_rev, function(x) quantile(x,0.975)), 3)
+rev_intervals <- paste(rev_interval_025, rev_interval_975, sep = " , ")
+rev_pvalue <- format_dec(sapply(estimates_rev, pmcmc), 3)
+#
+# Building the df for the associative
+asso_df <- data.frame(
+  Specie = rep(specie, each = length(groups) * length(treatments)),
+  Group = rep(rep(groups, each = length(treatments)), times = length(specie)),
+  Treatment = rep(rep(treatments, each = 1), times = length(groups) * length(specie)),
+  Mean = rep(asso_mean, each = 1),
+  CI = rep(asso_intervals, each = 1),
+  PValue = rep(asso_pvalue, each = 1),
+  Task = rep("Associative", length(asso_mean))
+)
+# Building the df for the reversal
+rev_df <- data.frame(
+  Specie = rep(specie, each = length(groups) * length(treatments)),
+  Group = rep(rep(groups, each = length(treatments)), times = length(specie)),
+  Treatment = rep(rep(treatments, each = 1), times = length(groups) * length(specie)),
+  Mean = rep(rev_mean, each = 1),
+  CI = rep(rev_intervals, each = 1),
+  PValue = rep(rev_pvalue, each = 1),
+  Task = rep("Reversal", length(rev_mean))
+)
+# Joining both dfs
+table_data <- rbind(asso_df, rev_df)
+table_data[, sapply(table_data, is.numeric)] <- lapply(table_data[, sapply(table_data, is.numeric)], function(x) format(x, scientific = FALSE))
+#
+############################## ADDING SAMPLE SIZE TO DF FOR TABLE ##############################
+# Make n_list into a df
+n_df <- as.data.frame(do.call(rbind, n_list)) %>%
+  rename("n" = V1) %>%
+  rownames_to_column("model") %>%
+  separate(model, into = c("Specie", "Group", "cort", "temp"), sep = "_") %>%
+  unite("Treatment", c("cort", "temp"), sep = "-") %>%
+  mutate(Specie = factor(Specie,
+                  labels = c(delicata = "L. delicata", guichenoti = "L. guichenoti")),
+        Treatment = factor(Treatment,
+                   levels = c("CORT-Cold", "Control-Cold", "CORT-Hot","Control-Hot")))
+# Merge both dfs, put sample size together with the treatment, and organize the new df to make it look like the table
+new_table_data <- merge(table_data, n_df) %>%
+  rename('p-value' = 'PValue', '95% CI' = 'CI') %>% #Change the names of the columns for the table
+  pivot_wider(names_from = Task, values_from = c(Mean, `95% CI`, `p-value`)) %>% # to split between Asociative and Reversal
+  select(Specie, Group, Treatment, Mean_Associative, `95% CI_Associative`, `p-value_Associative`, Mean_Reversal, `95% CI_Reversal`, `p-value_Reversal`, n) %>% #To order the columns in the way I want for the table
+  mutate(Specie = factor(Specie,
+                  levels = c("L. delicata", "L. guichenoti")),
+        Group = factor(Group,
+                  levels = c("Red", "Blue")),
+        Treatment = factor(Treatment, 
+                  levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")))%>%
+  arrange(Specie, Group, Treatment) %>% # To arrange the rows the way I want
+  unite("Treatment", c("Treatment", "n"), sep = " (n = ") %>%
+  mutate(Treatment = paste0(Treatment, ")"))
+write.csv(new_table_data, file= "./output/Checking/new_table_data.csv")
+#
+############################## MAKING THE TABLE ##############################
+## Table format
+set_flextable_defaults(
+ font.family = "Times New Roman",
+ fint.size = 10)
+# Split the table_data df by task
+real_table <- flextable(new_table_data) %>%
+    bold(~ `p-value_Associative` < 0.05, ~ `p-value_Associative` + Mean_Associative + `95% CI_Associative`) %>%
+    bold(~ `p-value_Reversal` < 0.05, ~ `p-value_Reversal` + Mean_Reversal + `95% CI_Reversal`) %>%
+    set_table_properties(width = 1) %>%
+    align(align="center", part="all") %>% 
+    add_header_row(values = c("", "Associative task", "Reversal task"), colwidths = c(3, 3, 3)) %>%
+    set_header_labels(Mean_Associative = "Mean",
+                      `95% CI_Associative` = "95% CI",
+                      `p-value_Associative` = "p-value",
+                      Mean_Reversal = "Mean",
+                      `95% CI_Reversal` = "95% CI",
+                      `p-value_Reversal` = "p-value") %>%
+    italic(j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
+    flextable::compose(i = c(2:8,10:16), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
+    flextable::compose(i = c(2:4,6:8,10:12,14:16), j = 2, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the second column
+    hline(i = c(4,12), j = c(2:9), part = "body") %>% # To make some horizontal lines
+    hline(i = c(8), j = c(1:9), part = "body") %>% # To make some horizontal lines
+    vline(i = (1:16), j = c(3,6), part = "body") %>% # To make some vertical lines on body
+    vline(j=c(3,6), part = "header") %>% # To make some vertical lines on header
+    autofit() 
+real_table
+```
+
+In the reversal tesk, we decided to pool both groups 'Blue' and 'Red' to make the between-treatment comparisons for two reasons.
+First, we did not find any significant differences caused group on the learning slopes (_L.
+delicata_: 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean((drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drr_CORTCold + drr_ControlHot)), 3)`, p = `r format_dec(pmcmc((drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drr_CORTCold + drr_ControlHot)), 3)`; _L.
+guichenoti_: 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean((grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTCold + grr_ControlHot)), 3)`, p = `r format_dec(pmcmc((grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTCold + grr_ControlHot)), 3)`).
+Second, we were expecting an acquired bias towards the colour assigned in the associative task as part of the design.
+Nonetheless, we did not find any significant differences between treatments in _L.
+delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean((drr_ControlCold + drb_ControlCold) - (drr_CORTCold + drb_CORTCold)), 3)`, p- value = `r format_dec(pmcmc((drr_ControlCold + drb_ControlCold) - (drr_CORTCold + drb_CORTCold)), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((drr_ControlHot + drb_ControlHot) - (drr_CORTHot + drb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((drr_ControlHot + drb_ControlHot) - (drr_CORTHot + drb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((drr_ControlHot + drb_ControlHot) - (drr_ControlCold + drb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((drr_ControlHot + drb_ControlHot) - (drr_ControlCold + drb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((drr_CORTHot + drb_CORTHot) - (drr_CORTCold + drb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((drr_CORTHot + drb_CORTHot) - (drr_CORTCold + drb_CORTCold)), 3)`) (see @Figdeli) or _L.
+guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean((grr_ControlCold + grb_ControlCold) - (grr_CORTCold + grb_CORTCold)), 3)`, p- value = `r format_dec(pmcmc((grr_ControlCold + grb_ControlCold) - (grr_CORTCold + grb_CORTCold)), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((grr_ControlHot + grb_ControlHot) - (grr_CORTHot + grb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((grr_ControlHot + grb_ControlHot) - (grr_CORTHot + grb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((grr_ControlHot + grb_ControlHot) - (grr_ControlCold + grb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((grr_ControlHot + grb_ControlHot) - (grr_ControlCold + grb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((grr_CORTHot + grb_CORTHot) - (grr_CORTCold + grb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((grr_CORTHot + grb_CORTHot) - (grr_CORTCold + grb_CORTCold)), 3)`) (see @Figguich).
+We did not find any effect of incubation temperature (_L.
+delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((drr_CORTHot + drr_ControlHot + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drb_CORTCold + drb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((drr_CORTHot + drr_ControlHot + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drb_CORTCold + drb_ControlCold)),3)`; _L.
+guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((grr_CORTHot + grr_ControlHot + grb_CORTHot + grb_ControlHot) -(grr_CORTCold + grr_ControlCold + grb_CORTCold + grb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((grr_CORTHot + grr_ControlHot + grb_CORTHot + grb_ControlHot) -(grr_CORTCold + grr_ControlCold + grb_CORTCold + grb_ControlCold)),3)`) or the hormone (_L.
+delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((drr_ControlCold + drr_ControlHot + drb_ControlCold + drb_ControlHot) - (drr_CORTCold + drr_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((drr_ControlCold + drr_ControlHot + drb_ControlCold + drb_ControlHot) - (drr_CORTCold + drr_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`;_L.
+guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((grr_ControlCold + grr_ControlHot + grb_ControlCold + grb_ControlHot)-(grr_CORTCold + grr_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((grr_ControlCold + grr_ControlHot + grb_ControlCold + grb_ControlHot)-(grr_CORTCold + grr_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`) when groups were pooled.
+Finally, we did not find any significant differences when we compared the estimated slopes between species for the reversal task (_L.
+delicata_ - _L.
+guichenoti_ = `r format_dec(mean((drr_CORTCold + drr_ControlCold + drr_CORTHot + drr_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTHot + grr_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((drr_CORTCold + drr_ControlCold + drr_CORTHot + drr_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTHot + grr_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`).
 
@@
 ```
+
+#### Checking the models plots  
+```{r, residuals}
+# Chunk for calling all the models and making the residuals
+# Associative task
+## L. delicata
+### Red
+mod_dar <- readRDS(here("output/models/asso_deli_red.rds"))
+resid_dar <- residuals(mod_dar)
+### Blue
+mod_dab <- readRDS(here("output/models/asso_deli_blue.rds"))
+resid_dab <- residuals(mod_dab)
+## L. guichenoti
+### Red
+mod_gar <- readRDS(here("output/models/asso_guich_red.rds"))
+resid_gar <- residuals(mod_gar)
+### Blue
+mod_gab <- readRDS(here("output/models/asso_guich_blue.rds"))
+resid_gab <- residuals(mod_gab)
+# Reversal task
+## L. delicata
+### Red
+mod_drr <- readRDS(here("output/models/rev_deli_red.rds"))
+resid_drr <- residuals(mod_drr)
+### Blue
+mod_drb <- readRDS(here("output/models/rev_deli_blue.rds"))
+resid_drb <- residuals(mod_drb)
+## L. guichenoti
+### Red
+mod_grr <- readRDS(here("output/models/rev_guich_red.rds"))
+resid_grr <- residuals(mod_grr)
+### Blue
+mod_grb <- readRDS(here("output/models/rev_guich_blue.rds"))
+resid_grb <- residuals(mod_grb)
+```
+
+Model formula for the reversal task is:  
+Choice  ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)  
+Plots for the different models of the associative task:  
+1.- _L. delicata_  
+  1.a.- Red  
+```{r , plotmod_drr, out.width="70%", fig.align="center"}
+plot(mod_drr)
+```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+  1.b.- Blue  
+```{r , plotmod_drb, out.width="70%", fig.align="center"}  
+plot(mod_drb)
+```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+2.- _L. guichenoti_  
+  2.a.- Red  
+```{r , plotmod_grr, out.width="70%", fig.align="center"}
+plot(mod_grr)
+```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+  2.b.- Blue  
+```{r , plotmod_grb, out.width="70%", fig.align="center"}
+plot(mod_grb)
+```

### 2024-01-31 ms.qmd
Updates

@@
 
-```{r}
-#| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
-```
+## Introduction
+Behavioural flexibility, **the ability to adapt behaviour to changing environments** (**REFS**), is considered crucial for invasion success [@sol2002behavioural].
+In general, species with higher behavioural flexibility are more likely to survive and establish in new habitats (**REFS**) as behaving flexibly enhances their capacity to exploit new resources and face new challenges (**REFS**).
 
-## Introduction
+adaptive flexibility hypothesis says that flexibility may be relevant in early and late stages of invassion (Wright et al 2010).
+But at the same time behavioural flexibility  it is related to relative brain size (Sol et al 2002, 2008), that may be more fixed than we thought (controversy with Wright et al??).
+In contrast, other hyoptheses predict this is constant, or there is individual variation in beh flexibility (Wright et al 2010).
+Since some aspects of early environment can play a prominent role in shaping neural substrate, we hypothesize that beh flexibility may be affected by early environment.
+Also, since beh flexibility is advantageous at different stages of colonization (**REFS**), invassive species may be able to maintain this behavioral flexibility through generations.
+In other words, there may be some mechanisms in invassive species to avoid early developmental constraints.
+CORT can be essential in this process as it is associated to vertebrates response to environmental changes, and it is known to impact brain development (Zhu et al 2004).
+Also, temperature may be relevant, since it affects brain development in ectotherms, it can be one of the main environmental changes to face by animals, andvertebrates reponse to changes in temeprature is also associated with the production of CORT (Crino et al 2023).
 
-Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making [@shettleworth].
-These cognitive processes underpin several aspects of animals' ecology such as foraging, mate choice, antipredatory strategies, and/or social behaviours, that are crucial for the survival and reproduction of animals [@dukas_evolutionary_2004].
-Particularly, learning - the acquisition of neuronal representations of new information [@dukas_evolutionary_2004] - is seen as fundamental for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013].
-However, in nature, there is individual variation in the capacity to acquire new information, influenced by factors like age, sex, gut microbiota, or the environment where they develop [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning].
-In particular, early life conditions can play a pivotal role since the brain is especially susceptible to environmental influences during early stages of development [@zhu_prenatal_2004].
-Therefore, investigating the effects of the developmental environment on learning can be essential to understand how individual variation in learning is shaped, and, in consequence, to predict animals' responses towards environmental change.
-In this sense, prenatal Glucocorticoids (GCs) - hormones related to organisms' response to stress [@sapolsky_how_2000] - and prenatal thermal environment are known to influence learning abilities in different taxa [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020].
-For instance, some studies have demonstrated that prenatal stress and high prenatal GC levels impair learning [@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn], while others showed diverse effects depending on factors like subjects' sex or the nature of the learning task [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016].
-Similarly, some experiments have shown significant impacts of prenatal temperature on learning in ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @abayarathna_effects_2020].
-For example, high incubation temperatures have been linked with faster learning rates in skinks [@amiel_hotter_2012; @amiel_egg_2014], while velvet geckos incubated at temperatures over their natural range learn slower than those incubated within the natural thermal limits [@abayarathna_effects_2020].
-In this vein, the effect of prenatal temperature appears to be linked to alterations in neural structure and metabolic activity [@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017; @beltran_are_2021] that share some similarities with those resulting from prenatal increased stress or GC levels [@lemaire_prenatal_2000; @zhu_prenatal_2004; @du_dynamic_2009].
-This suggests that prenatal GCs and temperature can act on the same physiological mechanisms and, thus, both could interact to shape individual variation in learning abilities [@noble_developmental_2018].
-Furthermore, GCs can play an pivotal role in determining vertebrate responses to elevated temperatures [@Crino_2023] potentially fostering natural interactions between temperature and GCs.
-However, despite the proximate similarities of prenatal GCs and temperature effects, and the potential role of GCs in vertebrates' response to elevated temperatures, our understanding of how these two factors interact remains incomplete.
-In this study, our objective is to explore the interactive effects between prenatal Glucocorticoids (GCs) and the prenatal thermal environment on learning.
-We utilized two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
-guichenoti_), as model species.
-We experimentally increased Corticosterone (CORT) - the main GC in birds, reptiles, amphibians, and rodents [@Crino_2023] - levels in the eggs of these two species of skinks and then incubated them at two different temperatures in a 2X2 factorial design.
-Post-incubation, the juveniles were subjectd to a colour-associative and a reversal task to assess their learning abilities.
-Our hypothesis posits that changes in CORT levels and temperature during early development will induce sustained effects on brain's physiology that will ultimately impact learning skills.
-We predict that individuals exposed to high levels of CORT and/or low temperatures will perform less proficiently in both learning tasks compared to control individuals or those exposed to high temperatures.
-Additionally, we anticipate that incubation at high temperatures will mitigate the impact of CORT on skink performance, while cold incubation temperatures are expected to enhance the detrimental effects of CORT on learning.
-We also expect the treatments to affect both tasks equally, with those individuals exposed to high levels of CORT and/or low temperatures performing less proficiently in both tasks compared to control individuals or those exposed to high temperatures.
-Finally, we expect that the effects of the treatments will be similar in both species, as both species share similar life history traits and are closely related [@chapple_know_2011; @chapple_biology_2014], and other cognitive studies have not found any difference between species when tested in an associative learning task [@bezzina2014does].
+Here, we aim to study the effects of prenatal environment on behavioural flexibility in the invassion ecology context.
+To do so, we employed as our model species the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+guichenoti_).
+These two species are closely related and share similar life history traits [@chapple_know_2011; @chapple_biology_2014], but only _L.
+delicata_ has been succesful in colonising different areas around the globe (**REFS**).
+Some studies have shown differences in personality traits between these two species that can be related to higher behavioural flexibility in _L.
+delicata_ (**REFS**), and are likely key for its invassive success (**REFS**).
+Our goal in this study was to investigate if behavioural flexibility is affected by the prenatal environment and the species specific response to it.
+Particularly, we were interested in the interactive effects of prenatal temperature and Corticosterone (CORT) - the main type of GC in reptiles [@Crino_2023] - because CORT is usually associated to vertebrates response to changes in temeprature [@Crino_2023], and both factors are known to impact brain development [@coomber_independent_1997; @zhu_prenatal_2004].
+We hypothesized that, since behavioural flexibility is advantageous at different stages of colonization (**REFS**), invassive species may be able to maintain this behavioral flexibility through generations.
+In other words, there may be some mechanisms in invassive species to avoid early
 
 ## Methods
+
+#### Experimental design
 We employed juveniles of both species, _L.
@@
 guichenoti_ that came from a breeding colony kept in the lab (details of breeding colony and husbandry in Supplementary Material).
-Those individuals were treated with prenatal CORT or vehicle, and incubated at different temperatures (see Supplementary Material), but previous data demonstrated that there was no differences in learning skills caused by these treatments (**REF**).
-To estimate behavioural flexibility, we examined lizards' performance in a learning task and its reversal (**REF**) using colour as the main conditioned stimulus and food as a reward (see @fig-Methods).
-There was first a habituation phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm); then a second phase where lizards had to associate the attainability of food with one colour; and finally a reversal task where the colour associated with attainable food was changed (@fig-Methods B).
-We evaluated the correlation between performance in the associative and reversal task as the main estimate of behavioural flexibility.
-The habituation phase was divided into three stages: in the first stage, the reward, a small, frozen cricket (*A.
-domestica*) was placed in an opaque petri dish (3D x 1.6H cm) (@fig-Methods B, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods B, Stage 2); and in the third stage, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp (Fig.
-@fig-Methods B, Stage 3).
-Trials in every stage lasted one hour, begining when the feeding block (petri dish, ramp, or both) was placed inside the enclosure and finished when we took the feeding block away.
-We recorded whether the cricket had been consumed or not and we considered an stage as completed if the lizards ate the crickets in at least 5 out of 6 trials.
-This phase lasted 38 days, and only in one case we decided not to use the lizard in the next phases because its behaviour was not consistent.
-In the associative phase, we used three ramps that were identical in shape and size but differ in the colour (Associative task in Fig.
-@fig-Methods B).
-As in the last stage of the habituation phase, we placed the cricket inside the wells of the ramps, but then two of them were covered with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp.
-The food reward was placed in all three wells to avoid lizard using prey chemical cues, that were released in the closed wells thanks to a series of small holes on the top of the lids.
-The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
-However, we decided to split the lizards in two groups to control for potential colour preference that could bias our results.
-One group of lizards was assigned the blue ramp as the correct choice (i.e., the ramp with the non-covered frozen cricket) in the associative task and the red ramp in the reversal, while the other group was assigned red as correct for the associative and blue for the reversal.
+To see the effect of prenatal CORT and temperature, eggs were topically supplied with 5µL of CORT dissolved in 70% Ethanol and 30% DMSO ('CORT' treatment) or the same volume of the vehicle ('Control'), and were then incubated at different temperatures ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) until hatching.
+To estimate behavioural flexibility, we examined lizards' performance in a reversal learning task using colour as the main conditioned stimulus and food (frozen small *A.
+domestica*) as a reward (see @fig-Methods).
+The learning test was divided in three main phases: there was first a habituation phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm); then a second phase where lizards had to associate the attainability of food with one colour; and finally the reversal task where the colour associated with the attainable food was changed (@fig-Methods B).
+In associative and reversal tasks we used  using three different ramps that were identical in size and shape to the ones for the habituation phase.
+The colours of the ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
+To control for potential colour biases, we assigned one group of lizards to associate the blue ramp with the attainable food in the associative task and the red ramp in the reversal, while the other group was assigned red as correct for the associative and blue for the reversal.
 In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
-Lizards were tested in this task once a day for 35 days.
-After the colour association phase, we performed a choice reversal task (Reversal task in @fig-Methods B).
-Here, the attainability of prey was indicated by a different colour from the reversal, requiring the lizards to form a novel association between the new colour and the food reward.
-This test was done once a day for 40 days.
-We performed the full experiment was between the 6^th^ of March until the 26^th^ of June 2023, between 11 to 12 am, when the lizards were active.
-Trials in the learning phases (colour associative task and reversal tasks) were recorded with different CCTV systems always using the same camera per individual.
-Videos were analysed manually using a standard video player (IINA) by PR, who recorded whether the first choice made by each subject was the correct feeder or not.
-A choice was considered to be made if the head of the lizard was inside the well of one of the ramps.
+To avoid the use of chemical cues, we placed the food reward in all three ramps, but in two of them the cricket was covered by small white lids with holes on the top.
+Lizards were tested once daily between 11 to 12 am, when lizards are active.
+The training phase lasted 38 days, the Associaive learning task 35, and the Reversal learning task 40 days.
+We recorded and analysed manually all trials form the learning phases using a standard video player (IINA).
+PR was the main researcher analysing the data, and was blinded to the lizards' treatment until the end of the analyses.
+We used as the main variable whether the animal chose the correct ramp first or not.
+We considered that a choice was made if the head of the lizard was inside the well of one of the ramps.
 We considered a trial failed if there was no choice in one hour of recording and those trials were considered as 'non data' in the analyses.
-We excluded from our analyses those individuals with more than 15 trials failed (i.e.
-they did not make a choice), and we considered the first trial to be the first one where the individual made a choice.
-We also considered individuals to be reinforced if the cricket was eaten after the test independently of whether their initial choice was correct or not.
+Here, we analysed the data of the reversal as a measure of behavioural flexibility.
+As such, we only included in our analyses those individuals who passed a learning criterion of 80% correct choices in the last 10 trials of the associative task.
 
@@
 
-knitr::include_graphics("./Others/LEARN_FIG_1.svg")
+knitr::include_graphics("./Others/BEHFLEX_FIG_1.svg")
 
@@
 
+We also considered individuals to be reinforced if the cricket was eaten after the test independently of whether their initial choice was correct or not.  
 **As such, we run a total of different 8 models employing Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022).
@@
 
+### Learning task
+The habituation phase was divided into three stages: in the first stage, the reward, a small, frozen cricket (*A.
+domestica*) was placed in an opaque petri dish (3D x 1.6H cm) (@fig-Methods B, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods B, Stage 2); and in the third stage, the cricket was left inside a well (3D x 1.75H cm) on top of the ramp (Fig.
+@fig-Methods B, Stage 3).
+Trials in every stage lasted one hour, begining when the feeding block (petri dish, ramp, or both) was placed inside the enclosure and finished when we took the feeding block away.
+We recorded whether the cricket had been consumed or not and we considered an stage as completed if the lizards ate the crickets in at least 5 out of 6 trials.
+This phase lasted 38 days, and only in one case we decided not to use the lizard in the next phases because its behaviour was not consistent.
+In the associative phase, we used three ramps that were identical in shape and size but differ in the colour (Associative task in Fig.
+@fig-Methods B).
+As in the last stage of the habituation phase, we placed the cricket inside the wells of the ramps, but then two of them were covered with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp.
+The food reward was placed in all three wells to avoid lizard using prey chemical cues, that were released in the closed wells thanks to a series of small holes on the top of the lids.
+The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
+However, we decided to split the lizards in two groups to control for potential colour preference that could bias our results.
+One group of lizards was assigned the blue ramp as the correct choice (i.e., the ramp with the non-covered frozen cricket) in the associative task and the red ramp in the reversal, while the other group was assigned red as correct for the associative and blue for the reversal.
+In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
+Lizards were tested in this task once a day for 35 days.
+After the colour association phase, we performed a choice reversal task (Reversal task in @fig-Methods B).
+Here, the attainability of prey was indicated by a different colour from the reversal, requiring the lizards to form a novel association between the new colour and the food reward.
+This test was done once a day for 40 days.
+We performed the full experiment was between the 6^th^ of March until the 26^th^ of June 2023, between 11 to 12 am, when the lizards were active.
+Trials in the learning phases (colour associative task and reversal tasks) were recorded with different CCTV systems always using the same camera per individual.
+Videos were analysed manually using a standard video player (IINA) by PR, who recorded whether the first choice made by each subject was the correct feeder or not.
+We considered a choice was made if the head of the lizard was inside the well of one of the ramps.
+We considered a trial failed if there was no choice in one hour of recording and those trials were considered as 'non data' in the analyses.
+We excluded from our analyses those individuals with more than 15 trials failed (i.e.
+they did not make a choice), and we considered the first trial to be the first one where the individual made a choice.
+We also considered individuals to be reinforced if the cricket was eaten after the test independently of whether their initial choice was correct or not.
+
 ```{r, results='asis', echo=FALSE}

### 2024-01-31 R/1_data_process.R

@@ -1,43 +1,25 @@
 ####################################
 # 1_data_process
 ####################################
-
 # Packages
 pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, forcats)
-
+#
 # Load data
 data  <-  read.csv("./data/Learning.csv")
-
-# Remove individuals who did not participate (more than 15 NAs), remove trials [36-40] (Only in associative) and split treatment into Temp and Cort
-data_asso <- data %>%
+###### Select individuals that pass the criterion of 80% of correct choices in the last 10 trials in the Associative
+#
+# Calculate the percentage of '1' values in FC_associative for the last 10 trials
+percentage_per_lizard <- data %>%
+  filter(trial_associative > 25 & trial_associative <= 35) %>%
   group_by(lizard_id) %>%
-    filter(sum(is.na(FC_associative)) <= 15) %>%
-    filter(trial_associative <= 35) %>%
-  ungroup()  %>%
-    mutate(group = factor(group,
-     levels = c("R_B", "B_R"),
-     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
-    mutate(temp = gsub("[AB]_", "", trt),
-          cort = gsub("_[2][38]", "", trt))  %>%
-    mutate(temp = factor(temp,
-      levels = c("23", "28"),
-      labels = c("23" = "Cold", "28" = "Hot"))) %>%
-    mutate(cort = factor(cort,
-      levels = c("B", "A"),
-      labels = c("B" = "CORT", "A" = "Control"))) %>%
-    mutate( # Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)
-      first_non_na = min(which(!is.na(FC_associative))),
-      Associative_Trial = ifelse(!is.na(first_non_na),trial_associative - first_non_na + 1, trial_associative))%>% 
-      filter(Associative_Trial >= 1) %>%
-  ungroup() %>% 
-data.frame()
-
-
-data_rev <- data %>%
-  group_by(lizard_id) %>%
-    filter(sum(is.na(FC_associative)) <= 15) %>%
-    filter(sum(is.na(FC_reversal)) <= 15) %>%
-   ungroup()  %>%
+  summarise(percentage = mean(FC_associative == 1))
+# Filter lizards where the percentage is at least 80%
[…]

### 2024-01-31 R/1_data_process.R
Updates

@@ -19,7 +19,7 @@ filtered_lizards <- percentage_per_lizard %>%
 # Subset the original dataset based on the filtered lizard IDs
 clean_df <- data %>%
   filter(lizard_id %in% filtered_lizards$lizard_id) %>%
-  filter(sum(is.na(FC_reversal)) <= 15) ungroup()  %>%
+  filter(sum(is.na(FC_reversal)) <= 15) %>%
     mutate(group = factor(group,
      levels = c("R_B", "B_R"),
      labels=c("R_B"="Red", "B_R"="Blue"))) %>%
@@ -33,6 +33,6 @@ clean_df <- data %>%
       labels = c("B" = "CORT", "A" = "Control"))) %>%
     mutate(trial_reversal=as.numeric(trial_reversal)) %>%
   data.frame()
-write.csv(filtered_df, "./output/databases_clean/clean_database.csv")
+write.csv(clean_df, "./output/databases_clean/clean_df.csv")
 
 

### 2024-01-31 R/func.r

@@ -7,16 +7,14 @@ pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4,
 # Extract sample size per group
 #' @title sample
 #' @description Estract sample size per group
+#' @param df To select the df
 #' @param sp To select the species of interest ("deli"/"guich")
 #' @param bias To select group depending on the colour assigned as correct for each task ("blue"/"red")
 #' @param corti To select cort treatment ("CORT"/"Control")
 #' @param therm To select temp treatment ("Cold"/"Hot")
-sample <- function(sp, bias, corti, therm){
-  #Specify database
-  data <- data_asso
-  # Count sample
-  sample_size <- data %>%
-                filter(species == sp, group == bias, cort == corti, temp == therm, Associative_Trial == 1) %>%
+sample <- function(df, sp, bias, corti, therm){
+  sample_size <- df %>%
+                filter(species == sp, group == bias, cort == corti, temp == therm, trial_reversal == 1) %>%
                 group_by(lizard_id) %>%
                 summarise(n = n()) %>%
                 summarise(total_count = sum(n)) %>%
@@ -28,35 +26,23 @@ sample <- function(sp, bias, corti, therm){
 # Fit models and extract posteriors both per each treatment:
 #' @title fit_m Function
 #' @description Fit brm models for different the associative task
-#' @param type To define if we are analysing the associative ("asso) or the reversal ("rev")
+#' @param df To select the df
 #' @param sp To select the species of interest ("deli"/"guich")
 #' @param bias To select group depending on the colour assigned as correct for each task ("blue"/"red")
 #' @param refir To choose whether to refit the models (TRUE, default) or use the ones already made (FALSE)
 #' @return Raw posteriors of fitted brm model for each treatment, species, and group (df)
-fit_m <- function(type, sp, bias, refit = TRUE) {
-  #Specify the type
-  if (type == "asso"){
-    data <- data_asso
-    formula <- FC_associative ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id)
-  }else{
-    if(type == "rev"){
-      data <- data_rev
-      formula <- FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
-    } else {
-      stop("Type not valid")
-      return(NULL)  # Return NULL in case of an invalid option
-    }
-  }
[…]

### 2024-01-31 ms.qmd
Updates

@@
 ---
+
+```{r}
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
+```
 
@@
 ## Results
+
+```{r, cleandata}
+#| label: cleandata
+# Obtain the main df using "./R/1_data_process.R"
+source(here("R", "1_data_process.R"))
+```
+
 ```{r, sampleSize}
@@
 specie <- c("delicata", "guichenoti")
-groups <- c("Red", "Blue")
 hormone <- c("CORT", "Control")
@@
       for(l in 1:length(temperature)){
-        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(specie[i], groups[j], hormone[k], temperature[l])
+        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], groups[j], hormone[k], temperature[l])
       }
@@
 source(here("R", "func.R"))
-# A) Associative task. Model formula: FC_associative ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id)
-## A.1) L. delicata
-deli_asso_red <- fit_m("asso", "deli", "red", refit = FALSE)
-write.csv(deli_asso_red, file= "./output/Checking/deli_asso_red.csv")
-deli_asso_blue <- fit_m("asso", "deli", "blue", refit = FALSE)
-write.csv(deli_asso_blue, file= "./output/Checking/deli_asso_blue.csv")
-## A.2) L. guichenoti
-guich_asso_red <- fit_m("asso", "guich", "red", refit = FALSE)
-write.csv(guich_asso_red, file= "./output/Checking/guich_asso_red.csv")
-guich_asso_blue <- fit_m("asso", "guich", "blue", refit = FALSE)
-write.csv(guich_asso_blue, file= "./output/Checking/guich_asso_blue.csv")
-# B) Reversal task. Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
-## B.1) L. delicata
-deli_rev_red <- fit_m("rev", "deli", "red", refit = FALSE)
-write.csv(deli_rev_red, file= "./output/Checking/deli_rev_red.csv")
-deli_rev_blue <- fit_m("rev", "deli", "blue", refit = FALSE)
-write.csv(deli_rev_blue, file= "./output/Checking/deli_rev_blue.csv")
-## B.2) L. guichenoti
-guich_rev_red <- fit_m("rev", "guich", "red", refit = FALSE)
-write.csv(guich_rev_red, file= "./output/Checking/guich_rev_red.csv")
-guich_rev_blue <- fit_m("rev", "guich", "blue", refit = FALSE)
-write.csv(guich_rev_blue, file= "./output/Checking/guich_rev_blue.csv")
+# Reversal task. Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
+## B) L. delicata
+deli_red <- fit_m(clean_df, "deli", "red", refit = TRUE)
+write.csv(deli_red, file= "./output/Checking/deli_red.csv")
+deli_blue <- fit_m(clean_df, "deli", "blue", refit = TRUE)
+write.csv(deli_blue, file= "./output/Checking/deli_blue.csv")
+## B) L. guichenoti
+guich_red <- fit_m(clean_df, "guich", "red", refit = TRUE)
+write.csv(guich_red, file= "./output/Checking/guich_red.csv")
+guich_blue <- fit_m(clean_df, "guich", "blue", refit = TRUE)
+write.csv(guich_blue, file= "./output/Checking/guich_blue.csv")
 ```
@@
 
-#### Colour preference in the Associative task
-To test if lizards were biased towards the assigned colour as our preliminary analyses suggested, we employed the intercepts  from our posterior distributions.
-We first estimated the predicted probability of choosing the correct feeder first in the first trial, by using the formula:
-$$\text{Probability} = \frac{1}{1 + e^{-Intercept}}$$
+#### Methods details
 
-Second, we tested the hypothesis that the estimated probability was higher than 0.33 (the probability expected by chance of choosing the correct feeder) using pmcmc.
-If the estimated probability is above 0.33.
-we consider it as an indication that there was a preference towards that colour that could be affecting learning slopes.
-The results per treatment are summarized in @tbl-bias.
-```{r, tbl-bias}
-#| label: tbl-bias
-#| tbl-cap: "Probability of choosing the correct feeder in the first trial when the correct feeder was blue (Prob Blue) or red (Prob Red) for each species and each treatment.
-p-values were obtained using pmcmc and test the hypothesis that the probability is >0.33.
-In bold, those values that are significant (p-value <0.05)"
-source(here("R", "func.R"))
-# First we estimate the probability of choosing right in the first trial using the intercepts from the posteriors
-## 1) L. delicata
-### Group = red
-probright_drCORTCold <- 1/(1+exp(-deli_asso_red$b_Intercept))
-probright_drControlCold <- 1/(1+exp(-(deli_asso_red$b_cortControl + deli_asso_red$b_Intercept)))
-probright_drCORTHot <- 1/(1+exp(-(deli_asso_red$b_tempHot + deli_asso_red$b_Intercept)))
-probright_drControlHot <- 1/(1+exp(-(deli_asso_red$'b_cortControl:tempHot' + deli_asso_red$b_cortControl + deli_asso_red$b_tempHot + deli_asso_red$b_Intercept)))
-### Group = blue
-probright_dbCORTCold <- 1/(1+exp(-(deli_asso_blue$b_Intercept)))
-probright_dbControlCold <- 1/(1+exp(-(deli_asso_blue$b_cortControl + deli_asso_blue$b_Intercept)))
-probright_dbCORTHot <- 1/(1+exp(-(deli_asso_blue$b_tempHot + deli_asso_blue$b_Intercept)))
-probright_dbControlHot <- 1/(1+exp(-(deli_asso_blue$'b_cortControl:tempHot' + deli_asso_blue$b_cortControl + deli_asso_blue$b_tempHot + deli_asso_blue$b_Intercept)))
-## 2) L. guichenoti
-### Group = red
-probright_grCORTCold <- 1/(1+exp(-guich_asso_red$b_Intercept))
-probright_grControlCold <- 1/(1+exp(-(guich_asso_red$b_cortControl + guich_asso_red$b_Intercept)))
-probright_grCORTHot <- 1/(1+exp(-(guich_asso_red$b_tempHot + guich_asso_red$b_Intercept)))
-probright_grControlHot <- 1/(1+exp(-(guich_asso_red$'b_cortControl:tempHot' + guich_asso_red$b_cortControl + guich_asso_red$b_tempHot + guich_asso_red$b_Intercept)))
-### Group = blue
-probright_gbCORTCold <- 1/(1+exp(-guich_asso_blue$b_Intercept))
-probright_gbControlCold <- 1/(1+exp(-(guich_asso_blue$b_cortControl + guich_asso_blue$b_Intercept)))
-probright_gbCORTHot <- 1/(1+exp(-(guich_asso_blue$b_tempHot + guich_asso_blue$b_Intercept)))
-probright_gbControlHot <- 1/(1+exp(-(guich_asso_blue$'b_cortControl:tempHot' + guich_asso_blue$b_cortControl + guich_asso_blue$b_tempHot + guich_asso_blue$b_Intercept)))
-# Second we build a df with all the mean probabilities of choosing right in the first trial for each treatment and species
-prob_df <- data.frame(
-  probright_drCORTCold_t = format_dec(mean(probright_drCORTCold), 3),
-  probright_drControlCold_t = format_dec(mean(probright_drControlCold), 3),
-  probright_drCORTHot_t = format_dec(mean(probright_drCORTHot), 3),
-  probright_drControlHot_t = format_dec(mean(probright_drControlHot), 3),
-  probright_dbCORTCold_t = format_dec(mean(probright_dbCORTCold), 3),
-  probright_dbControlCold_t = format_dec(mean(probright_dbControlCold), 3),
-  probright_dbCORTHot_t = format_dec(mean(probright_dbCORTHot), 3),
-  probright_dbControlHot_t = format_dec(mean(probright_dbControlHot), 3),
-  probright_grCORTCold_t = format_dec(mean(probright_grCORTCold), 3),
-  probright_grControlCold_t = format_dec(mean(probright_grControlCold), 3),
-  probright_grCORTHot_t = format_dec(mean(probright_grCORTHot), 3),
-  probright_grControlHot_t = format_dec(mean(probright_grControlHot), 3),
-  probright_gbCORTCold_t = format_dec(mean(probright_gbCORTCold), 3),
-  probright_gbControlCold_t = format_dec(mean(probright_gbControlCold), 3),
-  probright_gbCORTHot_t = format_dec(mean(probright_gbCORTHot), 3),
-  probright_gbControlHot_t = format_dec(mean(probright_gbControlHot), 3)) %>%
-gather(key = "column", value = "value", .) %>%
-rename("prob_choice" = "value") %>%
-data.frame()
-write.csv(prob_df, file= "./output/Checking/prob_df.csv")
-# Then we build a df with the statistical test (one-tailed pmcmc) that the probability is >0.33 (the probability of choosing right by chance)
-comp_pval <- data.frame(
-  probright_drCORTCold_t = format_dec(pmcmc(probright_drCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_drControlCold_t = format_dec(pmcmc(probright_drControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_drCORTHot_t = format_dec(pmcmc(probright_drCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_drControlHot_t = format_dec(pmcmc(probright_drControlHot, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_dbCORTCold_t = format_dec(pmcmc(probright_dbCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_dbControlCold_t = format_dec(pmcmc(probright_dbControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_dbCORTHot_t = format_dec(pmcmc(probright_dbCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_dbControlHot_t = format_dec(pmcmc(probright_dbControlHot, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_grCORTCold_t = format_dec(pmcmc(probright_grCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_grControlCold_t = format_dec(pmcmc(probright_grControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_grCORTHot_t = format_dec(pmcmc(probright_grCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_grControlHot_t = format_dec(pmcmc(probright_grControlHot, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_gbCORTCold_t = format_dec(pmcmc(probright_gbCORTCold, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_gbControlCold_t = format_dec(pmcmc(probright_gbControlCold, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_gbCORTHot_t = format_dec(pmcmc(probright_gbCORTHot, null = 0.33, twotail = FALSE, dir=">"), 3),
-  probright_gbControlHot_t = format_dec(pmcmc(probright_gbControlHot, null = 0.33, twotail = FALSE, dir=">"), 3)) %>%
-gather(key = "column", value = "value", .) %>%
-rename("p_value" = "value") %>%
-data.frame()
-write.csv(comp_pval, file= "./output/Checking/comp_pval.csv")
-# Now we merge them and organise them to have the final dt for the table
-table_df <- merge(prob_df, comp_pval, by ="column") %>%
-  mutate(Specie = gsub(".*_(d|g).*", "\\1",column)) %>%
-  mutate(Group = gsub(".*_(dr|db|gr|gb).*", "\\1",column)) %>%
-  mutate(Treatment = gsub(".*(CORTCold|ControlCold|CORTHot|ControlHot).*", "\\1",column)) %>% #Last three commands used to get the species, group and treatment from the column names
-  mutate(Treatment = factor(Treatment, 
-                    levels = c("CORTCold", "ControlCold", "CORTHot", "ControlHot"),
-                    labels = c("CORTCold" = "CORT-Cold", "ControlCold" = "Control-Cold", "CORTHot" = "CORT-Hot", "ControlHot" = "Control-Hot"))) %>%
-  mutate(Specie = factor(Specie,
-                levels = c("d", "g"),
-                labels = c("d" = "L. delicata", "g" = "L. guichenoti"))) %>%
-  mutate(Group = recode(Group, "dr" = "Red", "db" = "Blue", "gr" = "Red", "gb" = "Blue")) %>%
-  select(-column) %>%
-  pivot_wider(names_from = Group, values_from = c(prob_choice, p_value)) %>% #To split the df in Red and Blue
-  select(Specie, Treatment, prob_choice_Blue, p_value_Blue, prob_choice_Red, p_value_Red) %>%
-  arrange(Specie, Treatment) %>% # To arrange the rows the way I wantdata.frame()
-data.frame()
-write.csv(table_df, file= "./output/Checking/table_df.csv")
-#################
-colour_table <- flextable(table_df) %>%
-  bold(~ `p_value_Blue` < 0.05, ~ `p_value_Blue` + prob_choice_Blue) %>%
-  bold(~ `p_value_Red` < 0.05, ~ `p_value_Red` + prob_choice_Red) %>%
-  set_table_properties(width = 1) %>%
-  align(align="center", part="all") %>% 
-  set_header_labels(prob_choice_Blue = "Prob Blue", 
-                    p_value_Blue = "p-value Blue", 
-                    prob_choice_Red = "Prob Red", 
-                    p_value_Red = "p-value Red") %>%
-  italic(j = 1, italic = TRUE, part = "body") %>% # To have names of species in italics
-  flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
-  hline(i = c(4), j = c(1:6), part = "body") %>% # To make some horizontal lines
-  vline(j = c(2,4), part = "all") %>% # To make some vertical lines on body
-autofit()
-colour_table
-```
-
-On average, we found that, for both species, the proportion of correct choices in the first trial was significantly above chance when the correct feeder was blue (_L.
-delicata_: mean Prob choice = `r format_dec(mean((probright_dbCORTCold + probright_dbControlCold + probright_dbCORTHot + probright_dbControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_dbCORTCold + probright_dbControlCold + probright_dbCORTHot + probright_dbControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L.
-guichenoti_: mean Prob choice = `r format_dec(mean((probright_gbCORTCold + probright_gbControlCold + probright_gbCORTHot + probright_gbControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_gbCORTCold + probright_gbControlCold + probright_gbCORTHot + probright_gbControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`), but not when it was red (_L.
-delicata_: mean Prob choice = `r format_dec(mean((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L.
-guichenoti_: mean Prob choice = `r format_dec(mean((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), 3)`, p-value = `r format_dec(pmcmc(((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`).
-
-```{r, results='asis', echo=FALSE}
-cat("\\newpage")
-```
-
-#### Husbandry  
+###### Husbandry  
 *Breeding colony* -- We tested juveniles coming from a breeding colony established in the lab since 2019.
@@
 
-#### CORT and Temperature manipulation  
+###### CORT and Temperature manipulation  
 To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
@@
 
-### Learning task
+###### Learning task
 The habituation phase was divided into three stages: in the first stage, the reward, a small, frozen cricket (*A.
@@
 # Chunk for calling all the models and making the residuals
-# Associative task
 ## L. delicata
 ### Red
-mod_dar <- readRDS(here("output/models/asso_deli_red.rds"))
-resid_dar <- residuals(mod_dar)
+mod_dr <- readRDS(here("output/models/deli_red.rds"))
+resid_dr <- residuals(mod_dr)
 ### Blue
-mod_dab <- readRDS(here("output/models/asso_deli_blue.rds"))
-resid_dab <- residuals(mod_dab)
+mod_db <- readRDS(here("output/models/deli_blue.rds"))
+resid_db <- residuals(mod_db)
 ## L. guichenoti
 ### Red
-mod_gar <- readRDS(here("output/models/asso_guich_red.rds"))
-resid_gar <- residuals(mod_gar)
+mod_gr <- readRDS(here("output/models/guich_red.rds"))
+resid_gr <- residuals(mod_gr)
 ### Blue
-mod_gab <- readRDS(here("output/models/asso_guich_blue.rds"))
-resid_gab <- residuals(mod_gab)
-# Reversal task
-## L. delicata
-### Red
-mod_drr <- readRDS(here("output/models/rev_deli_red.rds"))
-resid_drr <- residuals(mod_drr)
-### Blue
-mod_drb <- readRDS(here("output/models/rev_deli_blue.rds"))
-resid_drb <- residuals(mod_drb)
-## L. guichenoti
-### Red
-mod_grr <- readRDS(here("output/models/rev_guich_red.rds"))
-resid_grr <- residuals(mod_grr)
-### Blue
-mod_grb <- readRDS(here("output/models/rev_guich_blue.rds"))
-resid_grb <- residuals(mod_grb)
+mod_gb <- readRDS(here("output/models/guich_blue.rds"))
+resid_gb <- residuals(mod_gb)
 ```

### 2024-01-31 .vdoc.r
Updates

@@ -1,0 +1,304 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/BEHFLEX_FIG_1.svg")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleandata
+# Obtain the main df using "./R/1_data_process.R"
+source(here("R", "1_data_process.R"))
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(k in 1:length(hormone)){
+    for(l in 1:length(temperature)){
+      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
+      }
+    }
+  }
+#
+#
+#
+#
+#
+#| label: models
+# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
+source(here("R", "func.R"))
[…]

### 2024-01-31 ms.qmd
Update ms.qmd

@@
 for(i in 1:length(specie)){
-  for(j in 1:length(groups)){
   for(k in 1:length(hormone)){
     for(l in 1:length(temperature)){
-        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], groups[j], hormone[k], temperature[l])
-      }
+      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
       }
@@
 source(here("R", "func.R"))
-# Reversal task. Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
-## B) L. delicata
-deli_red <- fit_m(clean_df, "deli", "red", refit = TRUE)
-write.csv(deli_red, file= "./output/Checking/deli_red.csv")
-deli_blue <- fit_m(clean_df, "deli", "blue", refit = TRUE)
-write.csv(deli_blue, file= "./output/Checking/deli_blue.csv")
+# Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
+## A) L. delicata
+deli <- fit_m(clean_df, "deli", refit = TRUE)
+write.csv(deli, file= "./output/Checking/deli.csv")
 ## B) L. guichenoti
-guich_red <- fit_m(clean_df, "guich", "red", refit = TRUE)
-write.csv(guich_red, file= "./output/Checking/guich_red.csv")
-guich_blue <- fit_m(clean_df, "guich", "blue", refit = TRUE)
-write.csv(guich_blue, file= "./output/Checking/guich_blue.csv")
+guich <- fit_m(clean_df, "guich", refit = TRUE)
+write.csv(guich, file= "./output/Checking/guich.csv")
 ```
@@
 ## 1) L. delicata
-### Group = red
-drr_CORTCold <- deli_rev_red$b_trial_reversal
-drr_ControlCold <- (deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$b_trial_reversal)
-drr_CORTHot <- (deli_rev_red$'b_trial_reversal:tempHot' + deli_rev_red$b_trial_reversal)
-drr_ControlHot <- (deli_rev_red$'b_trial_reversal:cortControl:tempHot' + deli_rev_red$b_trial_reversal + deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$'b_trial_reversal:tempHot')
-### Group = blue
-drb_CORTCold <- deli_rev_blue$b_trial_reversal
-drb_ControlCold <- (deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$b_trial_reversal)
-drb_CORTHot <- (deli_rev_blue$'b_trial_reversal:tempHot' + deli_rev_blue$b_trial_reversal)
-drb_ControlHot <- (deli_rev_blue$'b_trial_reversal:cortControl:tempHot' + deli_rev_blue$b_trial_reversal + deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$'b_trial_reversal:tempHot')
+deli_CORTCold <- deli$b_trial_reversal
+deli_ControlCold <- (deli$'b_trial_reversal:cortControl' + deli$b_trial_reversal)
+deli_CORTHot <- (deli$'b_trial_reversal:tempHot' + deli$b_trial_reversal)
+deli_ControlHot <- (deli$'b_trial_reversal:cortControl:tempHot' + deli$b_trial_reversal + deli$'b_trial_reversal:cortControl' + deli$'b_trial_reversal:tempHot')
 ## 2) L. guichenoti
-### Group = red
-grr_CORTCold <- guich_rev_red$b_trial_reversal
-grr_ControlCold <- (guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$b_trial_reversal)
-grr_CORTHot <- (guich_rev_red$'b_trial_reversal:tempHot' + guich_rev_red$b_trial_reversal)
-grr_ControlHot <- (guich_rev_red$'b_trial_reversal:cortControl:tempHot' + guich_rev_red$b_trial_reversal + guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$'b_trial_reversal:tempHot')
-### Group = blue
-grb_CORTCold <- guich_rev_blue$b_trial_reversal
-grb_ControlCold <- (guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$b_trial_reversal)
-grb_CORTHot <- (guich_rev_blue$'b_trial_reversal:tempHot' + guich_rev_blue$b_trial_reversal)
-grb_ControlHot <- (guich_rev_blue$'b_trial_reversal:cortControl:tempHot' + guich_rev_blue$b_trial_reversal + guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$'b_trial_reversal:tempHot')
+guich_CORTCold <- guich$b_trial_reversal
+guich_ControlCold <- (guich$'b_trial_reversal:cortControl' + guich$b_trial_reversal)
+guich_CORTHot <- (guich$'b_trial_reversal:tempHot' + guich$b_trial_reversal)
+guich_ControlHot <- (guich$'b_trial_reversal:cortControl:tempHot' + guich$b_trial_reversal + guich$'b_trial_reversal:cortControl' + guich$'b_trial_reversal:tempHot')
 ```
@@
 specie <- c("L. delicata", "L. guichenoti")
-groups <- c("Red", "Blue")
-test <- c("Associative", "Reversal")
 treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
@@
 #First get estimates for both tasks
-estimates_asso <- list(
-  dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot, 
-  dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot, 
-  gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot, 
-  gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot
+estimates <- list(
+  deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot, 
+  guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot
 )
 #
-estimates_rev <- list(
-  drr_CORTCold, drr_ControlCold, drr_CORTHot, drr_ControlHot, 
-  drb_CORTCold, drb_ControlCold, drb_CORTHot, drb_ControlHot, 
-  grr_CORTCold, grr_ControlCold, grr_CORTHot, grr_ControlHot, 
-  grb_CORTCold, grb_ControlCold, grb_CORTHot, grb_ControlHot
+# Then get the mean, co.intervals(95%), and p-values
+mean <- format_dec(sapply(estimates, mean), 3)
+interval_025 <- format_dec(sapply(estimates, function(x) quantile(x,0.025)), 3)
+interval_975 <- format_dec(sapply(estimates, function(x) quantile(x,0.975)), 3)
+intervals <- paste(interval_025, interval_975, sep = " , ")
+pvalue <- format_dec(sapply(estimates, pmcmc), 3)
+#
+# Building the df
+table_df <- data.frame(
+  Specie = rep(specie, each = length(treatments)),
+  Treatment = rep(rep(treatments, each = 1), times = length(specie)),
+  Mean = rep(mean, each = 1),
+  CI = rep(intervals, each = 1),
+  PValue = rep(pvalue, each = 1),
 )
-# Then get the mean, co.intervals(95%), and p-values
-asso_mean <- format_dec(sapply(estimates_asso, mean), 3)
-asso_interval_025 <- format_dec(sapply(estimates_asso, function(x) quantile(x,0.025)), 3)
-asso_interval_975 <- format_dec(sapply(estimates_asso, function(x) quantile(x,0.975)), 3)
-asso_intervals <- paste(asso_interval_025, asso_interval_975, sep = " , ")
-asso_pvalue <- format_dec(sapply(estimates_asso, pmcmc), 3)
-#
-rev_mean <- format_dec(sapply(estimates_rev, mean), 3)
-rev_interval_025 <- format_dec(sapply(estimates_rev, function(x) quantile(x,0.025)), 3)
-rev_interval_975 <- format_dec(sapply(estimates_rev, function(x) quantile(x,0.975)), 3)
-rev_intervals <- paste(rev_interval_025, rev_interval_975, sep = " , ")
-rev_pvalue <- format_dec(sapply(estimates_rev, pmcmc), 3)
-#
-# Building the df for the associative
-asso_df <- data.frame(
-  Specie = rep(specie, each = length(groups) * length(treatments)),
-  Group = rep(rep(groups, each = length(treatments)), times = length(specie)),
-  Treatment = rep(rep(treatments, each = 1), times = length(groups) * length(specie)),
-  Mean = rep(asso_mean, each = 1),
-  CI = rep(asso_intervals, each = 1),
-  PValue = rep(asso_pvalue, each = 1),
-  Task = rep("Associative", length(asso_mean))
-)
-# Building the df for the reversal
-rev_df <- data.frame(
-  Specie = rep(specie, each = length(groups) * length(treatments)),
-  Group = rep(rep(groups, each = length(treatments)), times = length(specie)),
-  Treatment = rep(rep(treatments, each = 1), times = length(groups) * length(specie)),
-  Mean = rep(rev_mean, each = 1),
-  CI = rep(rev_intervals, each = 1),
-  PValue = rep(rev_pvalue, each = 1),
-  Task = rep("Reversal", length(rev_mean))
-)
-# Joining both dfs
-table_data <- rbind(asso_df, rev_df)
-table_data[, sapply(table_data, is.numeric)] <- lapply(table_data[, sapply(table_data, is.numeric)], function(x) format(x, scientific = FALSE))
 #
@@
   rownames_to_column("model") %>%
-  separate(model, into = c("Specie", "Group", "cort", "temp"), sep = "_") %>%
+  separate(model, into = c("Specie", "cort", "temp"), sep = "_") %>%
   unite("Treatment", c("cort", "temp"), sep = "-") %>%
@@
 # Merge both dfs, put sample size together with the treatment, and organize the new df to make it look like the table
-new_table_data <- merge(table_data, n_df) %>%
+new_table_df <- merge(table_df, n_df) %>%
   rename('p-value' = 'PValue', '95% CI' = 'CI') %>% #Change the names of the columns for the table
   pivot_wider(names_from = Task, values_from = c(Mean, `95% CI`, `p-value`)) %>% # to split between Asociative and Reversal
-  select(Specie, Group, Treatment, Mean_Associative, `95% CI_Associative`, `p-value_Associative`, Mean_Reversal, `95% CI_Reversal`, `p-value_Reversal`, n) %>% #To order the columns in the way I want for the table
+  select(Specie, Treatment, Mean, `95% CI`, `p-value`, n) %>% #To order the columns in the way I want for the table
   mutate(Specie = factor(Specie,
                   levels = c("L. delicata", "L. guichenoti")),
-        Group = factor(Group,
-                  levels = c("Red", "Blue")),
         Treatment = factor(Treatment, 
                   levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")))%>%
-  arrange(Specie, Group, Treatment) %>% # To arrange the rows the way I want
+  arrange(Specie, Treatment) %>% # To arrange the rows the way I want
   unite("Treatment", c("Treatment", "n"), sep = " (n = ") %>%
@@
 
-In the reversal tesk, we decided to pool both groups 'Blue' and 'Red' to make the between-treatment comparisons for two reasons.
-First, we did not find any significant differences caused group on the learning slopes (_L.
-delicata_: 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean((drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drr_CORTCold + drr_ControlHot)), 3)`, p = `r format_dec(pmcmc((drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drr_CORTCold + drr_ControlHot)), 3)`; _L.
-guichenoti_: 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean((grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTCold + grr_ControlHot)), 3)`, p = `r format_dec(pmcmc((grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTCold + grr_ControlHot)), 3)`).
-Second, we were expecting an acquired bias towards the colour assigned in the associative task as part of the design.
-Nonetheless, we did not find any significant differences between treatments in _L.
-delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean((drr_ControlCold + drb_ControlCold) - (drr_CORTCold + drb_CORTCold)), 3)`, p- value = `r format_dec(pmcmc((drr_ControlCold + drb_ControlCold) - (drr_CORTCold + drb_CORTCold)), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((drr_ControlHot + drb_ControlHot) - (drr_CORTHot + drb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((drr_ControlHot + drb_ControlHot) - (drr_CORTHot + drb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((drr_ControlHot + drb_ControlHot) - (drr_ControlCold + drb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((drr_ControlHot + drb_ControlHot) - (drr_ControlCold + drb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((drr_CORTHot + drb_CORTHot) - (drr_CORTCold + drb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((drr_CORTHot + drb_CORTHot) - (drr_CORTCold + drb_CORTCold)), 3)`) (see @Figdeli) or _L.
-guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean((grr_ControlCold + grb_ControlCold) - (grr_CORTCold + grb_CORTCold)), 3)`, p- value = `r format_dec(pmcmc((grr_ControlCold + grb_ControlCold) - (grr_CORTCold + grb_CORTCold)), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((grr_ControlHot + grb_ControlHot) - (grr_CORTHot + grb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((grr_ControlHot + grb_ControlHot) - (grr_CORTHot + grb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((grr_ControlHot + grb_ControlHot) - (grr_ControlCold + grb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((grr_ControlHot + grb_ControlHot) - (grr_ControlCold + grb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((grr_CORTHot + grb_CORTHot) - (grr_CORTCold + grb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((grr_CORTHot + grb_CORTHot) - (grr_CORTCold + grb_CORTCold)), 3)`) (see @Figguich).
+We did not find any significant differences between treatments in _L.
+delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(deli_ControlCold - deli_CORTCold), 3)`, p- value = `r format_dec(pmcmc(deli_ControlCold - deli_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((deli_ControlHot + drb_ControlHot) - (deli_CORTHot + drb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((deli_ControlHot + drb_ControlHot) - (deli_CORTHot + drb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((deli_ControlHot + drb_ControlHot) - (deli_ControlCold + drb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlHot + drb_ControlHot) - (deli_ControlCold + drb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((deli_CORTHot + drb_CORTHot) - (deli_CORTCold + drb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((deli_CORTHot + drb_CORTHot) - (deli_CORTCold + drb_CORTCold)), 3)`) (see @Figdeli) or _L.
+guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean((guich_ControlCold + grb_ControlCold) - (guich_CORTCold + grb_CORTCold)), 3)`, p- value = `r format_dec(pmcmc((guich_ControlCold + grb_ControlCold) - (guich_CORTCold + grb_CORTCold)), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((guich_ControlHot + grb_ControlHot) - (guich_CORTHot + grb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((guich_ControlHot + grb_ControlHot) - (guich_CORTHot + grb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((guich_ControlHot + grb_ControlHot) - (guich_ControlCold + grb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlHot + grb_ControlHot) - (guich_ControlCold + grb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((guich_CORTHot + grb_CORTHot) - (guich_CORTCold + grb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((guich_CORTHot + grb_CORTHot) - (guich_CORTCold + grb_CORTCold)), 3)`) (see @Figguich).
 We did not find any effect of incubation temperature (_L.
-delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((drr_CORTHot + drr_ControlHot + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drb_CORTCold + drb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((drr_CORTHot + drr_ControlHot + drb_CORTHot + drb_ControlHot) - (drr_CORTCold + drr_ControlCold + drb_CORTCold + drb_ControlCold)),3)`; _L.
-guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((grr_CORTHot + grr_ControlHot + grb_CORTHot + grb_ControlHot) -(grr_CORTCold + grr_ControlCold + grb_CORTCold + grb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((grr_CORTHot + grr_ControlHot + grb_CORTHot + grb_ControlHot) -(grr_CORTCold + grr_ControlCold + grb_CORTCold + grb_ControlCold)),3)`) or the hormone (_L.
-delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((drr_ControlCold + drr_ControlHot + drb_ControlCold + drb_ControlHot) - (drr_CORTCold + drr_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((drr_ControlCold + drr_ControlHot + drb_ControlCold + drb_ControlHot) - (drr_CORTCold + drr_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`;_L.
-guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((grr_ControlCold + grr_ControlHot + grb_ControlCold + grb_ControlHot)-(grr_CORTCold + grr_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((grr_ControlCold + grr_ControlHot + grb_ControlCold + grb_ControlHot)-(grr_CORTCold + grr_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`) when groups were pooled.
+delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((deli_CORTHot + deli_ControlHot + drb_CORTHot + drb_ControlHot) - (deli_CORTCold + deli_ControlCold + drb_CORTCold + drb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((deli_CORTHot + deli_ControlHot + drb_CORTHot + drb_ControlHot) - (deli_CORTCold + deli_ControlCold + drb_CORTCold + drb_ControlCold)),3)`; _L.
+guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((guich_CORTHot + guich_ControlHot + grb_CORTHot + grb_ControlHot) -(guich_CORTCold + guich_ControlCold + grb_CORTCold + grb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((guich_CORTHot + guich_ControlHot + grb_CORTHot + grb_ControlHot) -(guich_CORTCold + guich_ControlCold + grb_CORTCold + grb_ControlCold)),3)`) or the hormone (_L.
+delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot + drb_ControlCold + drb_ControlHot) - (deli_CORTCold + deli_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlCold + deli_ControlHot + drb_ControlCold + drb_ControlHot) - (deli_CORTCold + deli_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`;_L.
+guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot + grb_ControlCold + grb_ControlHot)-(guich_CORTCold + guich_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlCold + guich_ControlHot + grb_ControlCold + grb_ControlHot)-(guich_CORTCold + guich_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`) when groups were pooled.
 Finally, we did not find any significant differences when we compared the estimated slopes between species for the reversal task (_L.
 delicata_ - _L.
-guichenoti_ = `r format_dec(mean((drr_CORTCold + drr_ControlCold + drr_CORTHot + drr_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTHot + grr_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((drr_CORTCold + drr_ControlCold + drr_CORTHot + drr_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (grr_CORTCold + grr_ControlCold + grr_CORTHot + grr_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`).
+guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`).
 

### 2024-01-31 R/1_data_process.R
Create guich.rds

@@ -20,9 +20,6 @@ filtered_lizards <- percentage_per_lizard %>%
 clean_df <- data %>%
   filter(lizard_id %in% filtered_lizards$lizard_id) %>%
   filter(sum(is.na(FC_reversal)) <= 15) %>%
-    mutate(group = factor(group,
-     levels = c("R_B", "B_R"),
-     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
     mutate(temp = gsub("[AB]_", "", trt),
           cort = gsub("_[2][38]", "", trt))  %>%
     mutate(temp = factor(temp,

### 2024-01-31 R/func.r

@@ -9,12 +9,11 @@ pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4,
 #' @description Estract sample size per group
 #' @param df To select the df
 #' @param sp To select the species of interest ("deli"/"guich")
-#' @param bias To select group depending on the colour assigned as correct for each task ("blue"/"red")
 #' @param corti To select cort treatment ("CORT"/"Control")
 #' @param therm To select temp treatment ("Cold"/"Hot")
-sample <- function(df, sp, bias, corti, therm){
+sample <- function(df, sp, corti, therm){
   sample_size <- df %>%
-                filter(species == sp, group == bias, cort == corti, temp == therm, trial_reversal == 1) %>%
+                filter(species == sp, cort == corti, temp == therm, trial_reversal == 1) %>%
                 group_by(lizard_id) %>%
                 summarise(n = n()) %>%
                 summarise(total_count = sum(n)) %>%
@@ -28,10 +27,9 @@ sample <- function(df, sp, bias, corti, therm){
 #' @description Fit brm models for different the associative task
 #' @param df To select the df
 #' @param sp To select the species of interest ("deli"/"guich")
-#' @param bias To select group depending on the colour assigned as correct for each task ("blue"/"red")
-#' @param refir To choose whether to refit the models (TRUE, default) or use the ones already made (FALSE)
+#' @param refit To choose whether to refit the models (TRUE, default) or use the ones already made (FALSE)
 #' @return Raw posteriors of fitted brm model for each treatment, species, and group (df)
-fit_m <- function(df, sp, bias, refit = TRUE) {
+fit_m <- function(df, sp, refit = TRUE) {
   formula <- (FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)) 
   #Specify species
     if (sp == "deli"){
@@ -51,36 +49,18 @@ fit_m <- function(df, sp, bias, refit = TRUE) {
         stop("Species not valid")
       }
     }
-  #Specify bias/group
-    if (bias == "blue"){
-      sub_data <- sp_data %>%
-            group_by(lizard_id) %>%
-            filter(group == "Blue") %>%
-            ungroup() %>%
-      data.frame() 
-    } else {
-      if(bias == "red"){
-        sub_data <- sp_data %>%
-              group_by(lizard_id) %>%
-              filter(group == "Red") %>%
-              ungroup() %>%
-        data.frame()
[…]

### 2024-01-31 ms.qmd
Updates

@@
 ## A) L. delicata
-deli <- fit_m(clean_df, "deli", refit = TRUE)
+deli <- fit_m(clean_df, "deli", refit = FALSE)
 write.csv(deli, file= "./output/Checking/deli.csv")
 ## B) L. guichenoti
-guich <- fit_m(clean_df, "guich", refit = TRUE)
+guich <- fit_m(clean_df, "guich", refit = FALSE)
 write.csv(guich, file= "./output/Checking/guich.csv")
@@
   CI = rep(intervals, each = 1),
-  PValue = rep(pvalue, each = 1),
+  PValue = rep(pvalue, each = 1)
 )
+#
+write.csv(table_df, file= "./output/Checking/df.csv")
 #
@@
   rename('p-value' = 'PValue', '95% CI' = 'CI') %>% #Change the names of the columns for the table
-  pivot_wider(names_from = Task, values_from = c(Mean, `95% CI`, `p-value`)) %>% # to split between Asociative and Reversal
   select(Specie, Treatment, Mean, `95% CI`, `p-value`, n) %>% #To order the columns in the way I want for the table
@@
   mutate(Treatment = paste0(Treatment, ")"))
-write.csv(new_table_data, file= "./output/Checking/new_table_data.csv")
+write.csv(new_table_df, file= "./output/Checking/new_table_data.csv")
 #
@@
 # Split the table_data df by task
-real_table <- flextable(new_table_data) %>%
-    bold(~ `p-value_Associative` < 0.05, ~ `p-value_Associative` + Mean_Associative + `95% CI_Associative`) %>%
-    bold(~ `p-value_Reversal` < 0.05, ~ `p-value_Reversal` + Mean_Reversal + `95% CI_Reversal`) %>%
+real_table <- flextable(new_table_df) %>%
+    bold(~ `p-value` < 0.05, ~ `p-value` + Mean + `95% CI`) %>%
     set_table_properties(width = 1) %>%
     align(align="center", part="all") %>% 
-    add_header_row(values = c("", "Associative task", "Reversal task"), colwidths = c(3, 3, 3)) %>%
-    set_header_labels(Mean_Associative = "Mean",
-                      `95% CI_Associative` = "95% CI",
-                      `p-value_Associative` = "p-value",
-                      Mean_Reversal = "Mean",
-                      `95% CI_Reversal` = "95% CI",
-                      `p-value_Reversal` = "p-value") %>%
+    set_header_labels(Mean = "Mean",
+                      `95% CI` = "95% CI",
+                      `p-value` = "p-value") %>%
     italic(j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
-    flextable::compose(i = c(2:8,10:16), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
-    flextable::compose(i = c(2:4,6:8,10:12,14:16), j = 2, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the second column
-    hline(i = c(4,12), j = c(2:9), part = "body") %>% # To make some horizontal lines
-    hline(i = c(8), j = c(1:9), part = "body") %>% # To make some horizontal lines
-    vline(i = (1:16), j = c(3,6), part = "body") %>% # To make some vertical lines on body
-    vline(j=c(3,6), part = "header") %>% # To make some vertical lines on header
+    flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
+    hline(i = 4, j = c(1:5), part = "body") %>% # To make some horizontal lines
     autofit() 
@@
 We did not find any significant differences between treatments in _L.
-delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(deli_ControlCold - deli_CORTCold), 3)`, p- value = `r format_dec(pmcmc(deli_ControlCold - deli_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((deli_ControlHot + drb_ControlHot) - (deli_CORTHot + drb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((deli_ControlHot + drb_ControlHot) - (deli_CORTHot + drb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((deli_ControlHot + drb_ControlHot) - (deli_ControlCold + drb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlHot + drb_ControlHot) - (deli_ControlCold + drb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((deli_CORTHot + drb_CORTHot) - (deli_CORTCold + drb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((deli_CORTHot + drb_CORTHot) - (deli_CORTCold + drb_CORTCold)), 3)`) (see @Figdeli) or _L.
-guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean((guich_ControlCold + grb_ControlCold) - (guich_CORTCold + grb_CORTCold)), 3)`, p- value = `r format_dec(pmcmc((guich_ControlCold + grb_ControlCold) - (guich_CORTCold + grb_CORTCold)), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((guich_ControlHot + grb_ControlHot) - (guich_CORTHot + grb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((guich_ControlHot + grb_ControlHot) - (guich_CORTHot + grb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((guich_ControlHot + grb_ControlHot) - (guich_ControlCold + grb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlHot + grb_ControlHot) - (guich_ControlCold + grb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((guich_CORTHot + grb_CORTHot) - (guich_CORTCold + grb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((guich_CORTHot + grb_CORTHot) - (guich_CORTCold + grb_CORTCold)), 3)`) (see @Figguich).
+delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(deli_ControlCold - deli_CORTCold), 3)`, p- value = `r format_dec(pmcmc(deli_ControlCold - deli_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(deli_ControlHot - deli_CORTHot), 3)`, p- value = `r format_dec(pmcmc(deli_ControlHot - deli_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(deli_ControlHot - deli_ControlCold), 3)`, p-value = `r format_dec(pmcmc(deli_ControlHot - deli_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(deli_CORTHot - deli_CORTCold), 3)`, p-value = `r format_dec(pmcmc(deli_CORTHot - deli_CORTCold), 3)`) (see @fig-results) or _L.
+guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(guich_ControlCold - guich_CORTCold), 3)`, p- value = `r format_dec(pmcmc(guich_ControlCold - guich_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(guich_ControlHot - guich_CORTHot), 3)`, p- value = `r format_dec(pmcmc(guich_ControlHot - guich_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(guich_ControlHot - guich_ControlCold), 3)`, p-value = `r format_dec(pmcmc(guich_ControlHot - guich_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(guich_CORTHot - guich_CORTCold), 3)`, p-value = `r format_dec(pmcmc(guich_CORTHot - guich_CORTCold), 3)`) (see @fig-results).
 We did not find any effect of incubation temperature (_L.
-delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((deli_CORTHot + deli_ControlHot + drb_CORTHot + drb_ControlHot) - (deli_CORTCold + deli_ControlCold + drb_CORTCold + drb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((deli_CORTHot + deli_ControlHot + drb_CORTHot + drb_ControlHot) - (deli_CORTCold + deli_ControlCold + drb_CORTCold + drb_ControlCold)),3)`; _L.
-guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((guich_CORTHot + guich_ControlHot + grb_CORTHot + grb_ControlHot) -(guich_CORTCold + guich_ControlCold + grb_CORTCold + grb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((guich_CORTHot + guich_ControlHot + grb_CORTHot + grb_ControlHot) -(guich_CORTCold + guich_ControlCold + grb_CORTCold + grb_ControlCold)),3)`) or the hormone (_L.
-delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot + drb_ControlCold + drb_ControlHot) - (deli_CORTCold + deli_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlCold + deli_ControlHot + drb_ControlCold + drb_ControlHot) - (deli_CORTCold + deli_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`;_L.
-guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot + grb_ControlCold + grb_ControlHot)-(guich_CORTCold + guich_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlCold + guich_ControlHot + grb_ControlCold + grb_ControlHot)-(guich_CORTCold + guich_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`) when groups were pooled.
+delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_dec(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`; _L.
+guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_dec(pmcmc((guich_CORTHot + guich_ControlHot) -(guich_CORTCold + guich_ControlCold)),3)`) or the hormone (_L.
+delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`;_L.
+guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`) when groups were pooled.
 Finally, we did not find any significant differences when we compared the estimated slopes between species for the reversal task (_L.
 delicata_ - _L.
-guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`).
+guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`).
 
@@
 ```{r , plotmod_drr, out.width="70%", fig.align="center"}
-plot(mod_drr)
-```
-
-```{r, results='asis', echo=FALSE}
-cat("\\newpage")
-```
-
-  1.b.- Blue  
-```{r , plotmod_drb, out.width="70%", fig.align="center"}  
-plot(mod_drb)
+plot(mod_deli)
 ```
@@
 2.- _L. guichenoti_  
-  2.a.- Red  
 ```{r , plotmod_grr, out.width="70%", fig.align="center"}
-plot(mod_grr)
+plot(mod_guich)
 ```
-
-```{r, results='asis', echo=FALSE}
-cat("\\newpage")
-```
-
-  2.b.- Blue  
-```{r , plotmod_grb, out.width="70%", fig.align="center"}
-plot(mod_grb)
-```

### 2024-01-31 .vdoc.r

@@ -1,304 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: fig-Methods
-#| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
-
-knitr::include_graphics("./Others/BEHFLEX_FIG_1.svg")
-
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: cleandata
-# Obtain the main df using "./R/1_data_process.R"
-source(here("R", "1_data_process.R"))
-#
-#
-#
-#| label: sampleSize
-# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
-source(here("R", "func.R"))
-#
-specie <- c("delicata", "guichenoti")
-hormone <- c("CORT", "Control")
-temperature <- c("Cold", "Hot")
-#
-n_list <- list()
-#
-for(i in 1:length(specie)){
-  for(k in 1:length(hormone)){
-    for(l in 1:length(temperature)){
-      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
-      }
-    }
-  }
-#
-#
-#
-#
-#
-#| label: models
-# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
-source(here("R", "func.R"))
[…]

### 2024-01-31 ms.qmd
Updates

@@
 ## L. delicata
-### Red
-mod_dr <- readRDS(here("output/models/deli_red.rds"))
-resid_dr <- residuals(mod_dr)
-### Blue
-mod_db <- readRDS(here("output/models/deli_blue.rds"))
-resid_db <- residuals(mod_db)
+mod_deli <- readRDS(here("output/models/deli.rds"))
+resid_deli <- residuals(mod_deli)
 ## L. guichenoti
-### Red
-mod_gr <- readRDS(here("output/models/guich_red.rds"))
-resid_gr <- residuals(mod_gr)
-### Blue
-mod_gb <- readRDS(here("output/models/guich_blue.rds"))
-resid_gb <- residuals(mod_gb)
+mod_guich <- readRDS(here("output/models/guich.rds"))
+resid_guich <- residuals(mod_guich)
 ```

### 2024-01-31 .vdoc.r
Updates

@@ -1,0 +1,292 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
+
+knitr::include_graphics("./Others/BEHFLEX_FIG_1.svg")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleandata
+# Obtain the main df using "./R/1_data_process.R"
+source(here("R", "1_data_process.R"))
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(k in 1:length(hormone)){
+    for(l in 1:length(temperature)){
+      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
+      }
+    }
+  }
+#
+#
+#
+#
+#
+#| label: models
+# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
+source(here("R", "func.R"))
+# Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
+## A) L. delicata
[…]

### 2024-01-31 R/func.r

@@ -1,6 +1,6 @@
 #################### 
 ####################
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
 #
 ####################
 ####################
@@ -119,4 +119,76 @@ pmcmc <- function(x, null = 0, twotail = TRUE, dir){
 format_dec <- function(x, n) {
   z <- sprintf(paste0("%.",n,"f"), x)
   return(as.numeric(z))
+}
+####################
+####################
+# Function to create each df for the figure
+#' @title df_fig
+#' @param df to select the df
+#' @param specie to add data of the specie
+df_fig <- function(df, specie){
+  # Create a vector with treatments
+  treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
+  # Create new matrix and new dfs
+  treat_matrix <- matrix(NA, nrow = 8000, ncol = 40)
+  fig_df <- data.frame()
+  # Loop through treatments
+  for(t in treatments){
+    if(t == "CORT-Cold"){
+      m <- df$b_trial_reversal
+      u <- df$b_Intercept
+    } else if(t == "Control-Cold"){
+        m <- (df$'b_trial_reversal:cortControl' + df$b_trial_reversal)
+        u <- (df$b_cortControl + df$b_Intercept)
+    } else if(t == "CORT-Hot"){
+        m <- (df$'b_trial_reversal:tempHot' + df$b_trial_reversal)
+        u <- (df$b_tempHot + df$b_Intercept)
+    } else if(t == "Control-Hot"){
+        m <- (df$'b_trial_reversal:cortControl:tempHot' + df$b_trial_reversal+ df$'b_trial_reversal:cortControl' + df$'b_trial_reversal:tempHot')
+        u <- (df$'b_cortControl:tempHot' + df$b_cortControl + df$b_tempHot + df$b_Intercept)
+    } else {
+    stop("loop wrong")
+    }
+    # Loop per treatment
+    for(x in 0:40){
+      for(j in 1:8000){
+        value <- exp(u[j] + m[j] * x) / (1 + exp(u[j] + m[j] * x))
+        treat_matrix[j, x] <- value
+      }
+    }
+    treat_df <- as.data.frame(treat_matrix)
[…]

### 2024-01-31 ms.qmd
Updates

@@
 guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(guich_ControlCold - guich_CORTCold), 3)`, p- value = `r format_dec(pmcmc(guich_ControlCold - guich_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(guich_ControlHot - guich_CORTHot), 3)`, p- value = `r format_dec(pmcmc(guich_ControlHot - guich_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(guich_ControlHot - guich_ControlCold), 3)`, p-value = `r format_dec(pmcmc(guich_ControlHot - guich_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(guich_CORTHot - guich_CORTCold), 3)`, p-value = `r format_dec(pmcmc(guich_CORTHot - guich_CORTCold), 3)`) (see @fig-results).
-We did not find any effect of incubation temperature (_L.
+When pooled together, we did not find any effect of incubation temperature (_L.
 delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_dec(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`; _L.
@@
 guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`).
+
+```{r, fig-results}
+#| label: fig-results
+#| fig.cap: "Predicted probability of choosing the correct feeder first over trials.
+The lines represent the mean predicted probability of choosing the correct feeder first, and the shaded areas represent the standard deviation of the mean; both obtained by using the slope and intercept estimates from the posterior distributions.
+The different colours represent the different treatments."
+source(here("R", "func.R"))
+# First step, create the dfs for all models
+## 1) L. delicata
+df_deli <- df_fig(as.data.frame(deli), "L. delicata")
+## 2) L. guichenoti
+df_guich <- df_fig(as.data.frame(guich), "L. guichenoti")
+#
+# Second step, merge the df into a big Fig_df
+Fig_df <- rbind(df_deli, df_guich) %>%
+  mutate(Trial = gsub("X", "", Trial)) %>%
+  mutate(Trial = as.numeric(Trial)) %>%
+  group_by(Trial, Treatment, Species) %>%
+  summarize(
+    Mean_Predicted_prob = mean(Value),
+    SE_Predicted_prob = sd(Value)
+    ) %>%
+  ungroup() %>%
+  mutate(
+    Treatment = factor(Treatment,
+                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
+    ) %>%
+data.frame()
+write.csv(Fig_df, file= "./output/Checking/Fig_df.csv")
+# Make the plot
+figure_results <- plotting(Fig_df)
+ggsave("./output/figures/figure_results.png", plot=figure_results, width = 18, height = 20, units = "cm", dpi = 3000)
+knitr::include_graphics("./output/figures/figure_results.png")
+```
 
@@
 1.- _L. delicata_    
-  1.a.- Red  
 ```{r , plotmod_drr, out.width="70%", fig.align="center"}
+bayes_R2(mod_deli)
 plot(mod_deli)
@@
 ```{r , plotmod_grr, out.width="70%", fig.align="center"}
+bayes_R2(mod_guich)
 plot(mod_guich)

### 2024-01-31 .vdoc.r

@@ -1,292 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: fig-Methods
-#| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**). Stages 1-3 indicate the different phases of the habituation process. In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
-
-knitr::include_graphics("./Others/BEHFLEX_FIG_1.svg")
-
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: cleandata
-# Obtain the main df using "./R/1_data_process.R"
-source(here("R", "1_data_process.R"))
-#
-#
-#
-#| label: sampleSize
-# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
-source(here("R", "func.R"))
-#
-specie <- c("delicata", "guichenoti")
-hormone <- c("CORT", "Control")
-temperature <- c("Cold", "Hot")
-#
-n_list <- list()
-#
-for(i in 1:length(specie)){
-  for(k in 1:length(hormone)){
-    for(l in 1:length(temperature)){
-      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
-      }
-    }
-  }
-#
-#
-#
-#
-#
-#| label: models
-# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
-source(here("R", "func.R"))
-# Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
-## A) L. delicata
[…]

### 2024-01-31 R/func.r

@@ -178,17 +178,17 @@ plotting <- function(df){
   geom_ribbon(aes(ymin = Mean_Predicted_prob - SE_Predicted_prob, ymax = Mean_Predicted_prob + SE_Predicted_prob, fill = Treatment), color = NA, alpha = 0.075) + 
   scale_fill_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="cyan", "CORT-Hot"="black", "Control-Hot"="#616161")) +
   theme_classic() +
-  facet_grid2(Species, scale = "free_x", space = "free_x", axes = "all") +
-  theme(strip.placement = "outside") +  
+  facet_wrap(Species ~ ., scale = "free_x", ncol= 1, strip.position = "right") +
+  theme(strip.placement = "outside") +
   theme(strip.background = element_blank()) +
   labs(y = "Predicted probability of correct choice", x = "Trial") +
-  theme(plot.margin = margin(5.5, 5.5, 5.5, 5.5, "mm")) + 
+  theme(plot.margin = margin(5.5, 5.5, 5.5, 5.5, "mm")) +
   theme(
-    axis.title = element_text(size = 15, family = "Times New Roman"),
-    axis.text = element_text(size = 10, family = "Times New Roman"),
-    legend.title = element_text(size = 12, family = "Times New Roman"),
-    legend.text = element_text(size = 10, family = "Times New Roman"),
-    strip.text = element_text(size = 13, family = "Times New Roman")
+    axis.title = element_text(size = 15, family = "Times"),
+    axis.text = element_text(size = 10, family = "Times"),
+    legend.title = element_text(size = 12, family = "Times"),
+    legend.text = element_text(size = 10, family = "Times"),
+    strip.text = element_text(size = 14, family = "Times", face = "italic")
   )  
   return(plot)
 }

### 2024-02-02 R/1_data_process.R
Updates

@@ -6,19 +6,10 @@ pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4,
 #
 # Load data
 data  <-  read.csv("./data/Learning.csv")
-###### Select individuals that pass the criterion of 80% of correct choices in the last 10 trials in the Associative
 #
-# Calculate the percentage of '1' values in FC_associative for the last 10 trials
-percentage_per_lizard <- data %>%
-  filter(trial_associative > 25 & trial_associative <= 35) %>%
-  group_by(lizard_id) %>%
-  summarise(percentage = mean(FC_associative == 1))
-# Filter lizards where the percentage is at least 80%
-filtered_lizards <- percentage_per_lizard %>%
-  filter(percentage >= 0.8)
 # Subset the original dataset based on the filtered lizard IDs
 clean_df <- data %>%
-  filter(lizard_id %in% filtered_lizards$lizard_id) %>%
+  group_by(lizard_id) %>%
   filter(sum(is.na(FC_reversal)) <= 15) %>%
     mutate(temp = gsub("[AB]_", "", trt),
           cort = gsub("_[2][38]", "", trt))  %>%
@@ -31,5 +22,4 @@ clean_df <- data %>%
     mutate(trial_reversal=as.numeric(trial_reversal)) %>%
   data.frame()
 write.csv(clean_df, "./output/databases_clean/clean_df.csv")
-
 

### 2024-02-02 R/func.r

@@ -30,7 +30,7 @@ sample <- function(df, sp, corti, therm){
 #' @param refit To choose whether to refit the models (TRUE, default) or use the ones already made (FALSE)
 #' @return Raw posteriors of fitted brm model for each treatment, species, and group (df)
 fit_m <- function(df, sp, refit = TRUE) {
-  formula <- (FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)) 
+  formula <- (FC_reversal ~ 1 + (1 + trial_reversal|lizard_id)) 
   #Specify species
     if (sp == "deli"){
       sp_data <- df %>%
@@ -66,27 +66,10 @@ fit_m <- function(df, sp, refit = TRUE) {
   posteriors <- as_draws_df(model)
   return(posteriors)
 }
-###################
-###################
-# Tidy estimates from fit_m
-#' @title tidy_post
-#' @description The df obtained by fit_m contains the estimates of the Intercept and fixed effects of "Choice ~ trial (1 + lizard)"
-#' for each treatment, species, and group,but it extracts the estimates of the four chains, each chain in a column, here we want to
-#' tidy up to two columns (Intercept and trial), plus the ones indicating species, group, tand treatment
-#' @param df Dataframe used
-#' @return Same df but tidy
-tidy_post <- function(df) {
-  # Select data
-  data <- df
-  # Split original df into four by chain, and give the columns a common name
-  res1 <- data%>%select(matches("^X1.b_"),treatment_level, species_level,bias_level)%>%rename_all(~sub("^X1.b_", "", .))
-  res2 <- data%>%select(matches("^X2.b_"),treatment_level, species_level,bias_level)%>%rename_all(~sub("^X2.b_", "", .))
-  res3 <- data%>%select(matches("^X3.b_"),treatment_level, species_level,bias_level)%>%rename_all(~sub("^X3.b_", "", .))
-  res4 <- data%>%select(matches("^X4.b_"),treatment_level, species_level,bias_level)%>%rename_all(~sub("^X4.b_", "", .))
-  # Bind data again
-  new_df <- bind_rows(res1, res2,res3,res4)
-return(new_df) 
-}
+####################
+####################
+# Function to estimate the intercepts or slope per individual and sd
+
 ####################
 ####################
 # Estimate p-values using pmcm

### 2024-02-02 R/1_data_process.R
Revert "Updates"
This reverts commit bddaebdbe72f540e8f35fd4b0c58314dc6de608d.

@@ -6,10 +6,19 @@ pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4,
 #
 # Load data
 data  <-  read.csv("./data/Learning.csv")
+###### Select individuals that pass the criterion of 80% of correct choices in the last 10 trials in the Associative
 #
+# Calculate the percentage of '1' values in FC_associative for the last 10 trials
+percentage_per_lizard <- data %>%
+  filter(trial_associative > 25 & trial_associative <= 35) %>%
+  group_by(lizard_id) %>%
+  summarise(percentage = mean(FC_associative == 1))
+# Filter lizards where the percentage is at least 80%
+filtered_lizards <- percentage_per_lizard %>%
+  filter(percentage >= 0.8)
 # Subset the original dataset based on the filtered lizard IDs
 clean_df <- data %>%
-  group_by(lizard_id) %>%
+  filter(lizard_id %in% filtered_lizards$lizard_id) %>%
   filter(sum(is.na(FC_reversal)) <= 15) %>%
     mutate(temp = gsub("[AB]_", "", trt),
           cort = gsub("_[2][38]", "", trt))  %>%
@@ -22,4 +31,5 @@ clean_df <- data %>%
     mutate(trial_reversal=as.numeric(trial_reversal)) %>%
   data.frame()
 write.csv(clean_df, "./output/databases_clean/clean_df.csv")
+
 

### 2024-02-02 R/func.r

@@ -30,7 +30,7 @@ sample <- function(df, sp, corti, therm){
 #' @param refit To choose whether to refit the models (TRUE, default) or use the ones already made (FALSE)
 #' @return Raw posteriors of fitted brm model for each treatment, species, and group (df)
 fit_m <- function(df, sp, refit = TRUE) {
-  formula <- (FC_reversal ~ 1 + (1 + trial_reversal|lizard_id)) 
+  formula <- (FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)) 
   #Specify species
     if (sp == "deli"){
       sp_data <- df %>%
@@ -66,10 +66,27 @@ fit_m <- function(df, sp, refit = TRUE) {
   posteriors <- as_draws_df(model)
   return(posteriors)
 }
-####################
-####################
-# Function to estimate the intercepts or slope per individual and sd
-
+###################
+###################
+# Tidy estimates from fit_m
+#' @title tidy_post
+#' @description The df obtained by fit_m contains the estimates of the Intercept and fixed effects of "Choice ~ trial (1 + lizard)"
+#' for each treatment, species, and group,but it extracts the estimates of the four chains, each chain in a column, here we want to
+#' tidy up to two columns (Intercept and trial), plus the ones indicating species, group, tand treatment
+#' @param df Dataframe used
+#' @return Same df but tidy
+tidy_post <- function(df) {
+  # Select data
+  data <- df
+  # Split original df into four by chain, and give the columns a common name
+  res1 <- data%>%select(matches("^X1.b_"),treatment_level, species_level,bias_level)%>%rename_all(~sub("^X1.b_", "", .))
+  res2 <- data%>%select(matches("^X2.b_"),treatment_level, species_level,bias_level)%>%rename_all(~sub("^X2.b_", "", .))
+  res3 <- data%>%select(matches("^X3.b_"),treatment_level, species_level,bias_level)%>%rename_all(~sub("^X3.b_", "", .))
+  res4 <- data%>%select(matches("^X4.b_"),treatment_level, species_level,bias_level)%>%rename_all(~sub("^X4.b_", "", .))
+  # Bind data again
+  new_df <- bind_rows(res1, res2,res3,res4)
+return(new_df) 
+}
 ####################
 ####################
 # Estimate p-values using pmcm

### 2024-02-02 ms.qmd
Updates

@@
 ## A) L. delicata
-deli <- fit_m(clean_df, "deli", refit = FALSE)
+deli <- fit_m(clean_df, "deli", "complete",  refit = FALSE)
 write.csv(deli, file= "./output/Checking/deli.csv")
 ## B) L. guichenoti
-guich <- fit_m(clean_df, "guich", refit = FALSE)
+guich <- fit_m(clean_df, "guich", "complete", refit = FALSE)
 write.csv(guich, file= "./output/Checking/guich.csv")
@@
 intervals <- paste(interval_025, interval_975, sep = " , ")
-pvalue <- format_dec(sapply(estimates, pmcmc), 3)
+pvalue <- format_dec(sapply(estimates, pmcmc), 4)
 #
@@
 ## L. delicata
-mod_deli <- readRDS(here("output/models/deli.rds"))
+mod_deli <- readRDS(here("output/models/delicomplete.rds"))
 resid_deli <- residuals(mod_deli)
 ## L. guichenoti
-mod_guich <- readRDS(here("output/models/guich.rds"))
+mod_guich <- readRDS(here("output/models/guichcomplete.rds"))
 resid_guich <- residuals(mod_guich)
@@
 ```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+#### Results employing only those individuals that passed a learning criterion of 80% correct choices in the last 10 trials of the associative task
+
+```{r, cleandata2}
+#| label: cleandata2
+# Cleaning the data to select only those individuals that passed a learning criterion of 80% correct choices in the last 10 trials of the associative task.
+data <- read.csv(here("data/Learning.csv"))
+percentage_per_lizard <- data %>%
+  filter(trial_associative > 25 & trial_associative <= 35) %>%
+  group_by(lizard_id) %>%
+  summarise(percentage = mean(FC_associative == 1))
+# Filter lizards where the percentage is at least 80%
+filtered_lizards <- percentage_per_lizard %>%
+  filter(percentage >= 0.8)
+# Subset the original dataset based on the filtered lizard IDs
+clean_df_2 <- data %>%
+  filter(lizard_id %in% filtered_lizards$lizard_id) %>%
+  filter(sum(is.na(FC_reversal)) <= 15) %>%
+    mutate(temp = gsub("[AB]_", "", trt),
+          cort = gsub("_[2][38]", "", trt))  %>%
+    mutate(temp = factor(temp,
+      levels = c("23", "28"),
+      labels = c("23" = "Cold", "28" = "Hot"))) %>%
+    mutate(cort = factor(cort,
+      levels = c("B", "A"),
+      labels = c("B" = "CORT", "A" = "Control"))) %>%
+    mutate(trial_reversal=as.numeric(trial_reversal)) %>%
+  data.frame()
+```
+
+```{r, sampleSize2}
+#| label: sampleSize2
+# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task.
+We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list_2 <- list()
+for(i in 1:length(specie)){
+  for(k in 1:length(hormone)){
+    for(l in 1:length(temperature)){
+      n_list_2[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df_2, specie[i], hormone[k], temperature[l])
+      }
+    }
+  }
+```
+
+```{r, models2}
+#| label: models2
+# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder).
+The result everytime the function is used is a df with the posteriors of the model.
+The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
+source(here("R", "func.R"))
+# Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
+## A) L. delicata
+deli_2 <- fit_m(clean_df_2, "deli", "suppl", refit = FALSE)
+write.csv(deli_2, file= "./output/Checking/deli.csv")
+## B) L. guichenoti
+guich_2 <- fit_m(clean_df_2, "guich", "suppl", refit = FALSE)
+write.csv(guich_2, file= "./output/Checking/guich.csv")
+```
+
+```{r, resultsRev2}
+# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task doing the same thing we did in the chunk above.
+## 1) L. delicata
+deli_CORTCold_2 <- deli_2$b_trial_reversal
+deli_ControlCold_2 <- (deli_2$'b_trial_reversal:cortControl' + deli_2$b_trial_reversal)
+deli_CORTHot_2 <- (deli_2$'b_trial_reversal:tempHot' + deli_2$b_trial_reversal)
+deli_ControlHot_2 <- (deli_2$'b_trial_reversal:cortControl:tempHot' + deli_2$b_trial_reversal + deli_2$'b_trial_reversal:cortControl' + deli_2$'b_trial_reversal:tempHot')
+## 2) L. guichenoti
+guich_CORTCold_2 <- guich_2$b_trial_reversal
+guich_ControlCold_2 <- (guich_2$'b_trial_reversal:cortControl' + guich_2$b_trial_reversal)
+guich_CORTHot_2 <- (guich_2$'b_trial_reversal:tempHot' + guich_2$b_trial_reversal)
+guich_ControlHot_2 <- (guich_2$'b_trial_reversal:cortControl:tempHot' + guich_2$b_trial_reversal + guich_2$'b_trial_reversal:cortControl' + guich_2$'b_trial_reversal:tempHot')
+```
+
+```{r, tbl-data_2}
+#| label: tbl-data
+#| tbl-cap: "Estimates of Associative learning slope for all the different treatments per each task, species and group.
+Mean shows the aritmetic mean of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
+All p-values were obtained using pmcmc and test the hypothesis that the mean is equal to zero.
+In bold, those values that are significant (p-value <0.05)"
+source(here("R", "func.R"))
+#
+############################## CREATING BIG DF FOR TABLE ##############################
+# Building the vectors for titles of rows and columns
+specie <- c("L. delicata", "L. guichenoti")
+treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
+values <- c("Mean", "95% CI", "p-value")
+# Building the vectors for estimated means, co.intervals(95%), and p-values for the slopes obtained from posteriors.
+p-values are obtained using pmcmc function (see func.R), assuming a two-tailed test that testes the hypothesis that the value (slopes in this case) is 0.
+#First get estimates for both tasks
+estimates_2 <- list(
+  deli_CORTCold_2, deli_ControlCold_2, deli_CORTHot_2, deli_ControlHot_2, 
+  guich_CORTCold_2, guich_ControlCold_2, guich_CORTHot_2, guich_ControlHot_2
+)
+#
+# Then get the mean, co.intervals(95%), and p-values
+mean_2 <- format_dec(sapply(estimates_2, mean), 3)
+interval_025_2 <- format_dec(sapply(estimates_2, function(x) quantile(x,0.025)), 3)
+interval_975_2 <- format_dec(sapply(estimates_2, function(x) quantile(x,0.975)), 3)
+intervals_2 <- paste(interval_025_2, interval_975_2, sep = " , ")
+pvalue_2 <- format_dec(sapply(estimates_2, pmcmc), 4)
+#
+# Building the df
+table_df_2 <- data.frame(
+  Specie = rep(specie, each = length(treatments)),
+  Treatment = rep(rep(treatments, each = 1), times = length(specie)),
+  Mean = rep(mean_2, each = 1),
+  CI = rep(intervals_2, each = 1),
+  PValue = rep(pvalue_2, each = 1)
+)
+#
+write.csv(table_df, file= "./output/Checking/df.csv")
+#
+############################## ADDING SAMPLE SIZE TO DF FOR TABLE ##############################
+# Make n_list into a df
+n_df_2 <- as.data.frame(do.call(rbind, n_list_2)) %>%
+  rename("n" = V1) %>%
+  rownames_to_column("model") %>%
+  separate(model, into = c("Specie", "cort", "temp"), sep = "_") %>%
+  unite("Treatment", c("cort", "temp"), sep = "-") %>%
+  mutate(Specie = factor(Specie,
+                  labels = c(delicata = "L. delicata", guichenoti = "L. guichenoti")),
+        Treatment = factor(Treatment,
+                   levels = c("CORT-Cold", "Control-Cold", "CORT-Hot","Control-Hot")))
+# Merge both dfs, put sample size together with the treatment, and organize the new df to make it look like the table
+new_table_df_2 <- merge(table_df_2, n_df_2) %>%
+  rename('p-value' = 'PValue', '95% CI' = 'CI') %>% #Change the names of the columns for the table
+  select(Specie, Treatment, Mean, `95% CI`, `p-value`, n) %>% #To order the columns in the way I want for the table
+  mutate(Specie = factor(Specie,
+                  levels = c("L. delicata", "L. guichenoti")),
+        Treatment = factor(Treatment, 
+                  levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")))%>%
+  arrange(Specie, Treatment) %>% # To arrange the rows the way I want
+  unite("Treatment", c("Treatment", "n"), sep = " (n = ") %>%
+  mutate(Treatment = paste0(Treatment, ")"))
+write.csv(new_table_df, file= "./output/Checking/new_table_data.csv")
+#
+############################## MAKING THE TABLE ##############################
+## Table format
+set_flextable_defaults(
+ font.family = "Times New Roman",
+ fint.size = 10)
+# Split the table_data df by task
+real_table_2 <- flextable(new_table_df_2) %>%
+    bold(~ `p-value` < 0.05, ~ `p-value` + Mean + `95% CI`) %>%
+    set_table_properties(width = 1) %>%
+    align(align="center", part="all") %>% 
+    set_header_labels(Mean = "Mean",
+                      `95% CI` = "95% CI",
+                      `p-value` = "p-value") %>%
+    italic(j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
+    flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
+    hline(i = 4, j = c(1:5), part = "body") %>% # To make some horizontal lines
+    autofit() 
+real_table_2
+```

### 2024-02-02 R/1_data_process.R

@@ -6,19 +6,9 @@ pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4,
 #
 # Load data
 data  <-  read.csv("./data/Learning.csv")
-###### Select individuals that pass the criterion of 80% of correct choices in the last 10 trials in the Associative
 #
-# Calculate the percentage of '1' values in FC_associative for the last 10 trials
-percentage_per_lizard <- data %>%
-  filter(trial_associative > 25 & trial_associative <= 35) %>%
-  group_by(lizard_id) %>%
-  summarise(percentage = mean(FC_associative == 1))
-# Filter lizards where the percentage is at least 80%
-filtered_lizards <- percentage_per_lizard %>%
-  filter(percentage >= 0.8)
-# Subset the original dataset based on the filtered lizard IDs
 clean_df <- data %>%
-  filter(lizard_id %in% filtered_lizards$lizard_id) %>%
+  group_by(lizard_id) %>%
   filter(sum(is.na(FC_reversal)) <= 15) %>%
     mutate(temp = gsub("[AB]_", "", trt),
           cort = gsub("_[2][38]", "", trt))  %>%

### 2024-02-02 R/func.r

@@ -27,9 +27,11 @@ sample <- function(df, sp, corti, therm){
 #' @description Fit brm models for different the associative task
 #' @param df To select the df
 #' @param sp To select the species of interest ("deli"/"guich")
+#' @param com To select whether the analyses are done for the full dataset ("complete") or for only those lizards 
+# that met the learning criterion ("suppl")
 #' @param refit To choose whether to refit the models (TRUE, default) or use the ones already made (FALSE)
 #' @return Raw posteriors of fitted brm model for each treatment, species, and group (df)
-fit_m <- function(df, sp, refit = TRUE) {
+fit_m <- function(df, sp, com, refit = TRUE) {
   formula <- (FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)) 
   #Specify species
     if (sp == "deli"){
@@ -57,10 +59,10 @@ fit_m <- function(df, sp, refit = TRUE) {
                 family = bernoulli(link = "logit"),
                 chains = 4, cores = 4, iter = 3000, warmup = 1000, control = list(adapt_delta = 0.99))
     # Write the model to a file
-    saveRDS(model, file = paste0(here("output/models/"), sp, ".rds"))
+    saveRDS(model, file = paste0(here("output/models/"), sp, com, ".rds"))
   } else {
       # Read the model from a file
-      model <- readRDS(file = paste0(here("output/models/"), sp, ".rds"))
+      model <- readRDS(file = paste0(here("output/models/"), sp, com, ".rds"))
   } 
   # Extract posteriors
   posteriors <- as_draws_df(model)

### 2024-02-03 ms.qmd
Update ms.qmd
Updates

@@
 ## Introduction
-Behavioural flexibility, **the ability to adapt behaviour to changing environments** (**REFS**), is considered crucial for invasion success [@sol2002behavioural].
-In general, species with higher behavioural flexibility are more likely to survive and establish in new habitats (**REFS**) as behaving flexibly enhances their capacity to exploit new resources and face new challenges (**REFS**).
+Behavioural flexibility, the ability to adjust the behaviour in response to internal or external changes in an adaptive way by, e.g., problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral], is considered crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can].
+In general, species with higher behavioural flexibility are more likely to survive and establish in new habitats, as behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can].
+Indeed, when closely related species of birds were compared, successful invaders showed a higher frequency of foraging innovations [@sol2000behavioural].
+According to the adaptive flexibility hypothesis, behavioural flexibility can be more relevant during introduction, establishment, and spread of the population [@wright2010behavioral; @chapple2012can; @szabo2020can], stages that, nonetheless, can involve more than one generation [**REFS**].
+Since behavioural flexibility can be affected by early environment [@jonson1976effect; @lui2017chronic], it is possible that the new prenatal environment faced by establishing populations can affect the behavioural flexibility of the new generations, with a consequent impact on invasion success.
+Therefore, we consider important to investigate the effect of developmental conditions on behavioural flexibility and whether their susceptibility to the early environment can predict the success of invasive species.
+Here, we are particularly interested in the interactive contribution of prenatal temperature and Glucocorticoids (GCs).
+There are several reasons why we believe these two aspects are salient for studying behavioural flexibility in the context of invasion ecology.
+First, GCs are the main group of hormones related to animals’ response towards alterations in homeostasis [@sapolsky_how_2000] that may become relevant when facing new environments.
+Furthermore, Gcs are one of the mechanisms mediating vertebrates’ response to changes in temperature that, at the same time, can have direct effects on animals' physiology and behaviour [@Crino_2023].
+Secondly, there is evidence that both developmental GCs and thermal environment can impact cognition in different taxa [@jonson1976effect; @zhu_prenatal_2004; @amiel_hotter_2012; @lui2017chronic].
+For instance, young Sprague-Dawley rats treated with Corticosterone (CORT) - the principal GC in rodents, birds, and reptiles [@Crino_2023] - performed worse than controls in a reversal learning task [@lui2017chronic], while exposure of pregnant guinea pigs to higher temperatures resulted in significant impariments with offspring behavoural flexibility [@jonson1976effect].
+In addition, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004], an aspect that is considered essential in succesful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
 
-adaptive flexibility hypothesis says that flexibility may be relevant in early and late stages of invassion (Wright et al 2010).
-But at the same time behavioural flexibility  it is related to relative brain size (Sol et al 2002, 2008), that may be more fixed than we thought (controversy with Wright et al??).
-In contrast, other hyoptheses predict this is constant, or there is individual variation in beh flexibility (Wright et al 2010).
-Since some aspects of early environment can play a prominent role in shaping neural substrate, we hypothesize that beh flexibility may be affected by early environment.
-Also, since beh flexibility is advantageous at different stages of colonization (**REFS**), invassive species may be able to maintain this behavioral flexibility through generations.
-In other words, there may be some mechanisms in invassive species to avoid early developmental constraints.
-CORT can be essential in this process as it is associated to vertebrates response to environmental changes, and it is known to impact brain development (Zhu et al 2004).
-Also, temperature may be relevant, since it affects brain development in ectotherms, it can be one of the main environmental changes to face by animals, andvertebrates reponse to changes in temeprature is also associated with the production of CORT (Crino et al 2023).
-
-Here, we aim to study the effects of prenatal environment on behavioural flexibility in the invassion ecology context.
+MODEL SPECIES AND POPULATIONS
 To do so, we employed as our model species the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
@@
 delicata_ (**REFS**), and are likely key for its invassive success (**REFS**).
-Our goal in this study was to investigate if behavioural flexibility is affected by the prenatal environment and the species specific response to it.
-Particularly, we were interested in the interactive effects of prenatal temperature and Corticosterone (CORT) - the main type of GC in reptiles [@Crino_2023] - because CORT is usually associated to vertebrates response to changes in temeprature [@Crino_2023], and both factors are known to impact brain development [@coomber_independent_1997; @zhu_prenatal_2004].
-We hypothesized that, since behavioural flexibility is advantageous at different stages of colonization (**REFS**), invassive species may be able to maintain this behavioral flexibility through generations.
-In other words, there may be some mechanisms in invassive species to avoid early
+
+HYPOTHESES
+Here, we aim to study the effects of prenatal environment on behavioural flexibility in the invassion ecology context.
 
@@
 We considered a trial failed if there was no choice in one hour of recording and those trials were considered as 'non data' in the analyses.
-Here, we analysed the data of the reversal as a measure of behavioural flexibility.
-As such, we only included in our analyses those individuals who passed a learning criterion of 80% correct choices in the last 10 trials of the associative task.
+Here, we analysed the data of the reversal as an index of behavioural flexibility [@brown2010behavioral].
 
@@
 
-We also considered individuals to be reinforced if the cricket was eaten after the test independently of whether their initial choice was correct or not.  
-**As such, we run a total of different 8 models employing Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022).
-Each model consisted of four parallel chains of 3000 iterations, with a warm up interval of 1000 iterations.'Choice', i.e.
-whether the individual chose correct (1) or not (0) was used as the response variable.
-The fixed effects of the model included a triple interaction between: trial ('Associative trial' or 'Reversal trial') as a numeric variable, and hormone treatmet ('CORT' versus 'Control') and the temperature at which eggs were incubated ('Cold' versus 'Hot') as factors.
-For the random effects, we employed lizard identity as a random intercept, and as a random slope we included the variable trial ('Associative' or 'Reversal') within each level of lizard identity.
-We used the resulting posterior of these models to evaluate learning differences between treatments within and between species and colour assigned.
-More specifically, we calculated learning slopes by using the estimates of the trial variable per each level of the hormone-temperature interaction ('Treatments'); values bigger from zero were considered as evidence of learning, while those less or equal to zero not.
-We used the pmcmc method to test whether those slopes or the comparissons between 'Treatments' (e.g.
-slope for 'CORT-Cold' lizards minus 'CORT-Hot' lizards) were different from zero (two-tailed tests).
-We considered statistical significance if p-value < 0.05.**
+We performed the analyses for both species separately.
+As such, we fitted a total of two different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022).
+We had per each model four parallel chains of 3000 iterations, with a warm up interval of 1000 iterations.
+We used 'Choice' - whether the individual chose correct (1) or not (0) - as the response variable, and trial, hormone ('CORT' versus 'Control'), incubation temperature ('Cold' versus 'Hot'), and their interaction as fixed factors.
+Lizard identity was employed as a random intercept, and as a random slope we included the trial within each level of lizard identity.
+We used the posterior distributions of these models to evaluate differences in learning rate between treatments and species.
+Learning slopes were obtained using the estimates of the variable trial per each level of the hormone-temperature interaction ('Treatments'); values bigger from zero were considered as evidence of learning, while those less or equal to zero not.
+We used the pmcmc method to test whether those slopes or the comparissons between treatments (e.g.
+slope for 'CORT-Cold' lizards minus 'CORT-Hot' lizards) or species were different from zero (two-tailed tests).
+We considered statistical significance if p-value < 0.05.
 
@@
 ```{r, tbl-data_2}
-#| label: tbl-data
+#| label: tbl-data_2
 #| tbl-cap: "Estimates of Associative learning slope for all the different treatments per each task, species and group.

### 2024-02-05 ms.qmd
Update ms.qmd

@@
 According to the adaptive flexibility hypothesis, behavioural flexibility can be more relevant during introduction, establishment, and spread of the population [@wright2010behavioral; @chapple2012can; @szabo2020can], stages that, nonetheless, can involve more than one generation [**REFS**].
-Since behavioural flexibility can be affected by early environment [@jonson1976effect; @lui2017chronic], it is possible that the new prenatal environment faced by establishing populations can affect the behavioural flexibility of the new generations, with a consequent impact on invasion success.
+**[Add a sentence here about how invassive species phenotype is advantageous when is plastic, but also mention that be plastic is not always fantastic if the environment constrain the development of adaptive phenotypes]**
+Relative brain size, e.g., is a good predictor of behavioural plasticity and invasive success in mammals [@sol2008brain], birds [@sol2000behavioural; @sol2002behavioural], and reptiles and amphibians [@amiel_effects_2017].
+Since the brain is especially snesitive during the early stages of development [@zhu_prenatal_2004] it is possible that the new prenatal environment faced by establishing populations can affect the behavioural flexibility of the new generations [see @jonson1976effect; @lui2017chronic], with a consequent impact on invasion success.
 Therefore, we consider important to investigate the effect of developmental conditions on behavioural flexibility and whether their susceptibility to the early environment can predict the success of invasive species.

### 2024-02-05 ms.qmd
Updates

--- 2024-02-03 ms.qmd
@@
 ## Introduction
-Behavioural flexibility, the ability to adjust the behaviour in response to internal or external changes in an adaptive way by, e.g., problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral], is considered crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can].
+Behavioural flexibility, the ability to adjust the behaviour adaptively in response to internal or external by, e.g., problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral], is considered crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can].
 In general, species with higher behavioural flexibility are more likely to survive and establish in new habitats, as behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can].
 Indeed, when closely related species of birds were compared, successful invaders showed a higher frequency of foraging innovations [@sol2000behavioural].
-According to the adaptive flexibility hypothesis, behavioural flexibility can be more relevant during introduction, establishment, and spread of the population [@wright2010behavioral; @chapple2012can; @szabo2020can], stages that, nonetheless, can involve more than one generation [**REFS**].
-Since behavioural flexibility can be affected by early environment [@jonson1976effect; @lui2017chronic], it is possible that the new prenatal environment faced by establishing populations can affect the behavioural flexibility of the new generations, with a consequent impact on invasion success.
+According to the adaptive flexibility hypothesis, behavioural flexibility can be more relevant during introduction, establishment, and spread of the population [@wright2010behavioral; @chapple2012can; @szabo2020can], stages that, nonetheless, can involve more than one generation.
+If behavioural flexibility is adaptive in these different stages, both this trait and the underlining mechanisms are expected to persist through generations in succesful invaders.
+For example, relative brain size is a good predictor of behavioural flexibility and invasive success in mammals [@sol2008brain], birds [@sol2000behavioural; @sol2002behavioural], reptiles, and amphibians [@amiel_effects_2017].
+Since the brain is especially sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004] it is possible that the new prenatal environment faced by establishing populations can affect the behavioural flexibility of the new generations [see @jonson1976effect; @lui2017chronic], with a consequent impact on invasion success.
 Therefore, we consider important to investigate the effect of developmental conditions on behavioural flexibility and whether their susceptibility to the early environment can predict the success of invasive species.
-Here, we are particularly interested in the interactive contribution of prenatal temperature and Glucocorticoids (GCs).
-There are several reasons why we believe these two aspects are salient for studying behavioural flexibility in the context of invasion ecology.
+In this scenario, we consider prenatal GCs and thermal environment to be salient factors in the study of behavioural flexibility within the context of invasion biology for several reasons.
 First, GCs are the main group of hormones related to animals’ response towards alterations in homeostasis [@sapolsky_how_2000] that may become relevant when facing new environments.
@@
 In addition, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004], an aspect that is considered essential in succesful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
-
-MODEL SPECIES AND POPULATIONS
-To do so, we employed as our model species the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+Here, we studied the interactive contribution of prenatal temperature and Glucocorticoids (GCs) on behavioural flexibility in two species that exhibit distinct outcomes in their roles as invasive species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_).
 These two species are closely related and share similar life history traits [@chapple_know_2011; @chapple_biology_2014], but only _L.
-delicata_ has been succesful in colonising different areas around the globe (**REFS**).
+delicata_ has been succesful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI].
 Some studies have shown differences in personality traits between these two species that can be related to higher behavioural flexibility in _L.
-delicata_ (**REFS**), and are likely key for its invassive success (**REFS**).
-
-HYPOTHESES
-Here, we aim to study the effects of prenatal environment on behavioural flexibility in the invassion ecology context.
+delicata_, and are likely key for its invassive success [@chapple_know_2011; @chapple2012can; @bezzina2014does].
+However, differences between species in behavioural flexibility and how this trait is affected by the prenatal environment remains unknown.
+To investigate these effects, we first manipulated CORT levels and incubation temperature in eggs from both species, and then subjected the juveniles to a reversal learning task as a measure of behavioural flexibility [@brown2010behavioral; @szabo2020can].
+We predicted that _L.
+delicata_ would, on average, perform more proficiently in the task that _L.
+guichenoti_.
+We also anticipated prenatal CORT and temperature to affect the behavioural flexibility of both species, and that _L.
+guichenoti_ would be more impacted by the prenatal environment than _L.
+delicata_.
+Regarding the directionality of the treatments, high prenatal temperatures are considered to improve performance in cognitive tasks in ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014], so we expected those incubated at higher temperatures to perform better in the reversal task.
+On the other hand, we expected that prenatal CORT would impair the performance of the lizards in the task, as it has been shown in other species [@lemaire_prenatal_2000; @zhu_prenatal_2004; @lui2017chronic].
 
@@
 ## Discussion
+
+**Our results suggest that prenatal CORT and temperature do not affect the behavioural flexibility of _L.
+delicata_ and _L.
+guichenoti_.
+We did not find any significant differences between treatments in the reversal task, and when we compared the estimated slopes between species.
+This is in contrast with our predictions, as we expected that _L.
+guichenoti_ would be more impacted by the prenatal environment than _L.
+delicata_.
+We also expected that prenatal CORT would impair the performance of the lizards in the task, and that higher temperatures would improve it.
+However, we did not find any evidence of this.
+
+They learn on average, as shown by positive slopes that do not vary when only those "superperformers" are employed in the analyses.
+
+Why no effect of treatment? 
+    What is expected from CORT?
+Other studeis showing no effects or the opposite: @szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016.
+Multiple factors may affect this results, including the dose of CORT, the time of exposure, and the species.
+Reversal??
+Check @lui2017chronic and @jonson1976effect.
+
+    What is expected from temperature?
+Other studies showing no effects or the opposite: @abayarathna_effects_2020; @dayananda.
+But these studies are in other species and with temperatures above the natural range.
+None of them reversal??
+Only reversal done with criterion, so cold were not tested
+
+    Selective sieve? No effects because is too simple?
+
+Why no differences between species?
+    Other papers finding no effects in learning: @bezzina2014does. Here they did not learn at all, too complex? Related with absence of treatment effects?
+
+    No differences in treatment effects
+
+Conclusions (sum up the discussion)**
 

### 2024-02-06 ms.qmd
Updates

@@
 ## Introduction
-Behavioural flexibility, the ability to adjust the behaviour adaptively in response to internal or external by, e.g., problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral], is considered crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can].
+Behavioural flexibility, i.e.
+the ability to adjust the behaviour adaptively in response to internal or external changes by problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral], is considered crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can].
 In general, species with higher behavioural flexibility are more likely to survive and establish in new habitats, as behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can].
-Indeed, when closely related species of birds were compared, successful invaders showed a higher frequency of foraging innovations [@sol2000behavioural].
+For instance, when closely related species of birds were compared, successful invaders showed a higher frequency of foraging innovations [@sol2000behavioural].
 According to the adaptive flexibility hypothesis, behavioural flexibility can be more relevant during introduction, establishment, and spread of the population [@wright2010behavioral; @chapple2012can; @szabo2020can], stages that, nonetheless, can involve more than one generation.
 If behavioural flexibility is adaptive in these different stages, both this trait and the underlining mechanisms are expected to persist through generations in succesful invaders.
-For example, relative brain size is a good predictor of behavioural flexibility and invasive success in mammals [@sol2008brain], birds [@sol2000behavioural; @sol2002behavioural], reptiles, and amphibians [@amiel_effects_2017].
+For example, in mammals, birds, reptiles and amphibians, relative brain size is a good predictor of behavioural flexibility and invasive success [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_effects_2017].
 Since the brain is especially sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004] it is possible that the new prenatal environment faced by establishing populations can affect the behavioural flexibility of the new generations [see @jonson1976effect; @lui2017chronic], with a consequent impact on invasion success.
-Therefore, we consider important to investigate the effect of developmental conditions on behavioural flexibility and whether their susceptibility to the early environment can predict the success of invasive species.
-In this scenario, we consider prenatal GCs and thermal environment to be salient factors in the study of behavioural flexibility within the context of invasion biology for several reasons.
-First, GCs are the main group of hormones related to animals’ response towards alterations in homeostasis [@sapolsky_how_2000] that may become relevant when facing new environments.
-Furthermore, Gcs are one of the mechanisms mediating vertebrates’ response to changes in temperature that, at the same time, can have direct effects on animals' physiology and behaviour [@Crino_2023].
+Therefore, we consider important to investigate the effect of developmental conditions on behavioural flexibility and if it can predict the success of invasive species.
+In this scenario, we consider prenatal Glucocorticoids (GCs) and thermal environment to be salient factors in the study of behavioural flexibility within the context of invasion biology for several reasons.
+First, GCs are the main group of hormones related to animals’ response towards alterations in homeostasis [@sapolsky_how_2000] that may become relevant when facing new environments and their new thermal conditions [@Crino_2023].
 Secondly, there is evidence that both developmental GCs and thermal environment can impact cognition in different taxa [@jonson1976effect; @zhu_prenatal_2004; @amiel_hotter_2012; @lui2017chronic].
 For instance, young Sprague-Dawley rats treated with Corticosterone (CORT) - the principal GC in rodents, birds, and reptiles [@Crino_2023] - performed worse than controls in a reversal learning task [@lui2017chronic], while exposure of pregnant guinea pigs to higher temperatures resulted in significant impariments with offspring behavoural flexibility [@jonson1976effect].
-In addition, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004], an aspect that is considered essential in succesful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
-Here, we studied the interactive contribution of prenatal temperature and Glucocorticoids (GCs) on behavioural flexibility in two species that exhibit distinct outcomes in their roles as invasive species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+In addition, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017], an aspect that is considered essential in succesful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_effects_2017].
+Here, we studied the interactive contribution of prenatal temperature and CORT on behavioural flexibility in two species that exhibit distinct outcomes in their roles as invasive species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_).
@@
 On the other hand, we expected that prenatal CORT would impair the performance of the lizards in the task, as it has been shown in other species [@lemaire_prenatal_2000; @zhu_prenatal_2004; @lui2017chronic].
+Finally, we expected an interaction between both treatments, with high temperatures mitigating the negative effects of prenatal CORT on the performance of the lizards in the task.
 
@@
 We performed the analyses for both species separately.
-As such, we fitted a total of two different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022).
+We fitted a total of two different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022).
 We had per each model four parallel chains of 3000 iterations, with a warm up interval of 1000 iterations.
@@
 
-**Our results suggest that prenatal CORT and temperature do not affect the behavioural flexibility of _L.
-delicata_ and _L.
-guichenoti_.
-We did not find any significant differences between treatments in the reversal task, and when we compared the estimated slopes between species.
-This is in contrast with our predictions, as we expected that _L.
-guichenoti_ would be more impacted by the prenatal environment than _L.
-delicata_.
-We also expected that prenatal CORT would impair the performance of the lizards in the task, and that higher temperatures would improve it.
-However, we did not find any evidence of this.
-
-They learn on average, as shown by positive slopes that do not vary when only those "superperformers" are employed in the analyses.
-
-Why no effect of treatment? 
-    What is expected from CORT?
-Other studeis showing no effects or the opposite: @szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016.
-Multiple factors may affect this results, including the dose of CORT, the time of exposure, and the species.
-Reversal??
-Check @lui2017chronic and @jonson1976effect.
-
-    What is expected from temperature?
-Other studies showing no effects or the opposite: @abayarathna_effects_2020; @dayananda.
-But these studies are in other species and with temperatures above the natural range.
-None of them reversal??
-Only reversal done with criterion, so cold were not tested
-
-    Selective sieve? No effects because is too simple?
-
-Why no differences between species?
-    Other papers finding no effects in learning: @bezzina2014does. Here they did not learn at all, too complex? Related with absence of treatment effects?
-
-    No differences in treatment effects
-
-Conclusions (sum up the discussion)**
+The study embarked on unraveling the interactive effects of prenatal temperature and Glucocorticoids (GCs) on behavioral flexibility in two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+guichenoti_).
+Despite sharing life history traits, only _L.
+delicata_ has proven successful in colonizing various global regions, and we hypothesized this may be related with higher behavioural flexibility.
+Furthermore, we expected behavioural flexibility in this species to be less susceptible to the effect of early environment since this trait can be adaptive in several stages of invasion that can involve more than one generation.
+Nevertheless, we did not find any significant differences between treatments or species when we compared their performance in a reversal task.
+We found that, on average, all the lizards from the four treatments and the two species learned the reversal task - indicated by estimated slopes that are significantly different from cero - and that they learn, on average, at the same rate.
+Furthermore, these results were consistent when only those individuals that performed better in the previous associative task were included (see Supplementary material).
+Previous studies have shown that _L.
+delicata_ is more explorative than _L.
+guichenoti_, which can be advantageous in some facets of the colonization of new environments [@chapple_know_2011].
+However, @bezzina2014does found no differences in learning between the two skinks in an associative learning task.
+Our results are consistent with this study, and suggest that behavioural flexibility does not differ in these species.
+In addition, we did not find any effect of the treatments on both species.
+Both results contrast our original predictions, and may indicate that other aspects of their biology are more relevant for _L.
+delicata_ success as invaders than behavioural flexibility.
+For instance, the mentioned differences in exploratory behaviour can be the key factor explaining why _L.
+delicata_ and not _L.
+guichenoti_ is better at colonising new areas, since exploring more can enhance the ability to effectively locate novel resources in _L.
+delicata_ [@chapple_know_2011].
+Our early environment manipulation did not affect the performance of the lizards in the task.
+We expected CORT to decrease reversal learning abilities and high temperatures to minimize these effects.
+However, our results show no significant differences between treatments in both species.
+These results contrast with previous studies that show impairments of high GCs levels in different types of learning tests [@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn], but align with other experiments where GCs increased or did not impact learning abilities [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016].
+More striking is the absence of effect of incubation temperature, since most of the studies in reptiles reported better performance when incubated at higher temperatures in different associative learning and motor tasks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014]; and those studies that reported cold-incubated lizards to learn faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temepratures far beyond the natural range in the hot treatment.
+It could be arguable whether our results are caused by a low sample size or treatments (especially hormone) are not properly applied, but we find these possibilities unlikely for two main reasons.
+First, we have seen the effect of the treatments in other traits of the lizards (data non published), and second, both effects are still non significant when the data is pooled.
+In contrast, we find more plausible that the effects of the early environment can be task-dependent, as some studies show that the effects of prenatal GCs and temeprature vary depending on the region of the brain [@coomber_independent_1997; @sakata_neural_2000; @lemaire_prenatal_2000].
+However, this is a speculation that needs to be tested in future studies that examine both the performance in different cognitive tasks as well as the neurophysiological effects.
+In conculsion, our results showed that lizards performed the reversal learning task - as measurement of behavioural flexibility - at a similar level, with no differences between treatments or species.
+These results contrast our original predictions, and may indicate that other aspects of their biology are more relevant for _L.
+delicata_ success as invaders than behavioural flexibility and the effects of developmental environment on this trait.
+However, we cannot discard that the effects of the early environment can be task-dependent, and future studies should examine both the performance in different cognitive tasks as well as the effect of both treatments in the brain.
 

### 2024-02-06 ms.qmd
Update ms.qmd

@@
 If behavioural flexibility is adaptive in these different stages, both this trait and the underlining mechanisms are expected to persist through generations in succesful invaders.
-For example, in mammals, birds, reptiles and amphibians, relative brain size is a good predictor of behavioural flexibility and invasive success [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_effects_2017].
+For example, in mammals, birds, reptiles and amphibians, relative brain size is a good predictor of behavioural flexibility and invasive success [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
 Since the brain is especially sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004] it is possible that the new prenatal environment faced by establishing populations can affect the behavioural flexibility of the new generations [see @jonson1976effect; @lui2017chronic], with a consequent impact on invasion success.
@@
 For instance, young Sprague-Dawley rats treated with Corticosterone (CORT) - the principal GC in rodents, birds, and reptiles [@Crino_2023] - performed worse than controls in a reversal learning task [@lui2017chronic], while exposure of pregnant guinea pigs to higher temperatures resulted in significant impariments with offspring behavoural flexibility [@jonson1976effect].
-In addition, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017], an aspect that is considered essential in succesful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_effects_2017].
+In addition, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017], an aspect that is considered essential in succesful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
 Here, we studied the interactive contribution of prenatal temperature and CORT on behavioural flexibility in two species that exhibit distinct outcomes in their roles as invasive species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.

### 2024-02-08 ms.qmd
Updates

@@
 Since the brain is especially sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004] it is possible that the new prenatal environment faced by establishing populations can affect the behavioural flexibility of the new generations [see @jonson1976effect; @lui2017chronic], with a consequent impact on invasion success.
-Therefore, we consider important to investigate the effect of developmental conditions on behavioural flexibility and if it can predict the success of invasive species.
-In this scenario, we consider prenatal Glucocorticoids (GCs) and thermal environment to be salient factors in the study of behavioural flexibility within the context of invasion biology for several reasons.
-First, GCs are the main group of hormones related to animals’ response towards alterations in homeostasis [@sapolsky_how_2000] that may become relevant when facing new environments and their new thermal conditions [@Crino_2023].
-Secondly, there is evidence that both developmental GCs and thermal environment can impact cognition in different taxa [@jonson1976effect; @zhu_prenatal_2004; @amiel_hotter_2012; @lui2017chronic].
+As such, we find that studying the effect of developmental conditions on behavioural flexibility can be key to understand and predict the success of invasive species.
+In this scenario, prenatal Glucocorticoids (GCs) and thermal environment can be salient factors in the study of behavioural flexibility within the context of invasion biology.
+On one hand, GCs are the main group of hormones related to animals’ response towards alterations in homeostasis [@sapolsky_how_2000] that may become relevant when facing new environments and their new thermal conditions [@Crino_2023].
+On the other hand, there is evidence that both developmental GCs and thermal environment can impact cognition in different taxa [@jonson1976effect; @zhu_prenatal_2004; @amiel_hotter_2012; @lui2017chronic].
 For instance, young Sprague-Dawley rats treated with Corticosterone (CORT) - the principal GC in rodents, birds, and reptiles [@Crino_2023] - performed worse than controls in a reversal learning task [@lui2017chronic], while exposure of pregnant guinea pigs to higher temperatures resulted in significant impariments with offspring behavoural flexibility [@jonson1976effect].
@@
 delicata_ and _L.
-guichenoti_ that came from a breeding colony kept in the lab (details of breeding colony and husbandry in Supplementary Material).
+guichenoti_ that came from a breeding colony kept in the lab.
+This colony, established in 2019, originates from animals collected in Sydney, likely from similar populations that have become invasive on Lord Howe Island [@chapple2016origin] (details of breeding colony and husbandry in Supplementary Material).
 To see the effect of prenatal CORT and temperature, eggs were topically supplied with 5µL of CORT dissolved in 70% Ethanol and 30% DMSO ('CORT' treatment) or the same volume of the vehicle ('Control'), and were then incubated at different temperatures ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) until hatching.
@@
 domestica*) as a reward (see @fig-Methods).
-The learning test was divided in three main phases: there was first a habituation phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm); then a second phase where lizards had to associate the attainability of food with one colour; and finally the reversal task where the colour associated with the attainable food was changed (@fig-Methods B).
-In associative and reversal tasks we used  using three different ramps that were identical in size and shape to the ones for the habituation phase.
+The learning test was divided in three main phases: there was first a habituation phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm); then a second step where lizards had to associate the attainability of food with one colour (@fig-Methods Associative task); and finally the reversal task where the colour associated with the attainable food was changed (@fig-Methods Reversal task).
+In associative and reversal tasks we used three different ramps that were identical in size and shape to the ones for the habituation phase.
 The colours of the ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
@@
 #| label: fig-Methods
-#| fig.cap: "Experimental design of early environment manipulation (**A**) and learning tasks (**B**).
-Stages 1-3 indicate the different phases of the habituation process.
+#| fig.cap: "Experimental design of early environment manipulation and learning tasks.
+Stages 1-3 indicate the different phases of the habituation phase.
 In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
@@
 We had per each model four parallel chains of 3000 iterations, with a warm up interval of 1000 iterations.
-We used 'Choice' - whether the individual chose correct (1) or not (0) - as the response variable, and trial, hormone ('CORT' versus 'Control'), incubation temperature ('Cold' versus 'Hot'), and their interaction as fixed factors.
+We used 'Choice' - whether the individual chose correct (1) or not (0) - as the response variable; and trial, hormone ('CORT' versus 'Control'), incubation temperature ('Cold' versus 'Hot'), and their interaction as fixed factors.
 Lizard identity was employed as a random intercept, and as a random slope we included the trial within each level of lizard identity.
@@
 
-```{r, tbl-data}
+```{r, tbl-data, results='asis'}
 #| label: tbl-data
@@
     autofit() 
-real_table
+knitr::knit_print(real_table)
 ```
@@
 delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`;_L.
-guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`) when groups were pooled.
+guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`).
 Finally, we did not find any significant differences when we compared the estimated slopes between species for the reversal task (_L.
@@
 Nevertheless, we did not find any significant differences between treatments or species when we compared their performance in a reversal task.
-We found that, on average, all the lizards from the four treatments and the two species learned the reversal task - indicated by estimated slopes that are significantly different from cero - and that they learn, on average, at the same rate.
+We found that, on average, all the lizards from the four treatments and the two species learned the reversal task - indicated by estimated slopes that are significantly different from zero - and that they learn, on average, at the same rate.
 Furthermore, these results were consistent when only those individuals that performed better in the previous associative task were included (see Supplementary material).
@@
 However, @bezzina2014does found no differences in learning between the two skinks in an associative learning task.
-Our results are consistent with this study, and suggest that behavioural flexibility does not differ in these species.
+Our results align with the latter study, and suggest that behavioural flexibility does not differ in these species.
 In addition, we did not find any effect of the treatments on both species.
@@
 delicata_ and not _L.
-guichenoti_ is better at colonising new areas, since exploring more can enhance the ability to effectively locate novel resources in _L.
+guichenoti_ is better at colonising new areas, since exploring more can also enhance the ability to effectively locate novel resources in _L.
 delicata_ [@chapple_know_2011].
@@
 However, our results show no significant differences between treatments in both species.
-These results contrast with previous studies that show impairments of high GCs levels in different types of learning tests [@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn], but align with other experiments where GCs increased or did not impact learning abilities [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016].
-More striking is the absence of effect of incubation temperature, since most of the studies in reptiles reported better performance when incubated at higher temperatures in different associative learning and motor tasks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014]; and those studies that reported cold-incubated lizards to learn faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temepratures far beyond the natural range in the hot treatment.
-It could be arguable whether our results are caused by a low sample size or treatments (especially hormone) are not properly applied, but we find these possibilities unlikely for two main reasons.
-First, we have seen the effect of the treatments in other traits of the lizards (data non published), and second, both effects are still non significant when the data is pooled.
-In contrast, we find more plausible that the effects of the early environment can be task-dependent, as some studies show that the effects of prenatal GCs and temeprature vary depending on the region of the brain [@coomber_independent_1997; @sakata_neural_2000; @lemaire_prenatal_2000].
-However, this is a speculation that needs to be tested in future studies that examine both the performance in different cognitive tasks as well as the neurophysiological effects.
-In conculsion, our results showed that lizards performed the reversal learning task - as measurement of behavioural flexibility - at a similar level, with no differences between treatments or species.
-These results contrast our original predictions, and may indicate that other aspects of their biology are more relevant for _L.
-delicata_ success as invaders than behavioural flexibility and the effects of developmental environment on this trait.
-However, we cannot discard that the effects of the early environment can be task-dependent, and future studies should examine both the performance in different cognitive tasks as well as the effect of both treatments in the brain.
+Our outcome contrast with previous studies that show impairments of high GCs levels in different types of learning tests [@lemaire_prenatal_2000; @zhu_prenatal_2004;  @farrell_developmental_2016], but they are consistent with other experiments where GCs increased or did not impact learning abilities [@szuran_water_1994; @bebus_associative_2016].
+More striking is the absence of effect of incubation temperature, since most of the studies in reptiles reported better performance when incubated at higher temperatures in different associative learning and motor tasks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014]; and those studies that reported cold-incubated lizards to learn faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temperatures far beyond the natural range in the hot treatment.
+It could be argued whether our results stem from an insufficient manipulation of the prenatal environment, particularly regarding CORT as it is known to have hermetic effects on learning and neural structure [@du_dynamic_2009; @mcewen_brain_2012].
+However, we find these possibilities unlikely for two primary reasons.
+First, we have observed the effects of the treatments on other traits of the lizards (unpublished data).
+Conversely, we find more plausible that the effects of the early environment may vary depending on the cognitive task, as evidenced by studies showing variations in the impact of prenatal GCs and temperature on different brain regions [@coomber_independent_1997; @sakata_neural_2000; @lemaire_prenatal_2000].
+However, this hypothesis requires further testing, involving assessments of performance in various cognitive tasks together with the neurophysiological effects on different brain nuclei.
+In conclusion, our results indicate that lizards performed the reversal learning task, a measure of behavioral flexibility, at similar rates, with no discernible differences between treatments or species.
+These findings contrast our initial predictions and suggest that other aspects of _L.
+delicata_ biology may be more influential for their success as invaders than behavioral flexibility alone.
+The present study also indicates that prenatal CORT and temeprature do not affect learning abilities in these species.
+Nevertheless, it remains possible that the effects of the early environment are task-dependent, and future studies should explore performance across different cognitive tasks, as well as the effects of both treatments on brain function.
 

### 2024-02-22 ms.qmd
Update ms.qmd

@@
 For instance, when closely related species of birds were compared, successful invaders showed a higher frequency of foraging innovations [@sol2000behavioural].
-According to the adaptive flexibility hypothesis, behavioural flexibility can be more relevant during introduction, establishment, and spread of the population [@wright2010behavioral; @chapple2012can; @szabo2020can], stages that, nonetheless, can involve more than one generation.
-If behavioural flexibility is adaptive in these different stages, both this trait and the underlining mechanisms are expected to persist through generations in succesful invaders.
+According to the adaptive flexibility hypothesis, behavioural flexibility is particularly relevant during introduction, establishment, and spread of the population [@wright2010behavioral; @chapple2012can; @szabo2020can], stages that can involve more than one generation.
+If behavioural flexibility is adaptive in these different phases, both this trait and the underlining mechanisms are expected to persist through generations in successful invaders.
 For example, in mammals, birds, reptiles and amphibians, relative brain size is a good predictor of behavioural flexibility and invasive success [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
@@
 As such, we find that studying the effect of developmental conditions on behavioural flexibility can be key to understand and predict the success of invasive species.
-In this scenario, prenatal Glucocorticoids (GCs) and thermal environment can be salient factors in the study of behavioural flexibility within the context of invasion biology.
-On one hand, GCs are the main group of hormones related to animals’ response towards alterations in homeostasis [@sapolsky_how_2000] that may become relevant when facing new environments and their new thermal conditions [@Crino_2023].
-On the other hand, there is evidence that both developmental GCs and thermal environment can impact cognition in different taxa [@jonson1976effect; @zhu_prenatal_2004; @amiel_hotter_2012; @lui2017chronic].
-For instance, young Sprague-Dawley rats treated with Corticosterone (CORT) - the principal GC in rodents, birds, and reptiles [@Crino_2023] - performed worse than controls in a reversal learning task [@lui2017chronic], while exposure of pregnant guinea pigs to higher temperatures resulted in significant impariments with offspring behavoural flexibility [@jonson1976effect].
-In addition, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017], an aspect that is considered essential in succesful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
+**BETTER LINK**In this scenario, prenatal glucocorticoids (GCs) and thermal environment can be salient factors in the study of behavioural flexibility within the context of invasion biology.
+GCs are the main group of hormones related to animals’ response towards alterations in homeostasis [@sapolsky_how_2000] that may become relevant when facing new environments and their new thermal conditions [@Crino_2023].
+Furthermore, there is evidence that both developmental GCs and thermal environment can impact cognition in different taxa [@jonson1976effect; @zhu_prenatal_2004; @amiel_hotter_2012; @lui2017chronic].
+For instance, young Sprague-Dawley rats treated with corticosterone (CORT) - the principal GC in rodents, birds, and reptiles [@Crino_2023] - performed worse than controls in a reversal learning task [@lui2017chronic], while exposure of pregnant guinea pigs to higher temperatures resulted in significant impairments with offspring behavioural flexibility [@jonson1976effect].
+In addition, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017], an aspect that is considered essential in successful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
 Here, we studied the interactive contribution of prenatal temperature and CORT on behavioural flexibility in two species that exhibit distinct outcomes in their roles as invasive species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
@@
 These two species are closely related and share similar life history traits [@chapple_know_2011; @chapple_biology_2014], but only _L.
-delicata_ has been succesful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI].
+delicata_ has been successful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI].
 Some studies have shown differences in personality traits between these two species that can be related to higher behavioural flexibility in _L.
-delicata_, and are likely key for its invassive success [@chapple_know_2011; @chapple2012can; @bezzina2014does].
+delicata_, and are likely key for its invasive success [@chapple_know_2011; @chapple2012can; @bezzina2014does].
 However, differences between species in behavioural flexibility and how this trait is affected by the prenatal environment remains unknown.
@@
 guichenoti_.
-We also anticipated prenatal CORT and temperature to affect the behavioural flexibility of both species, and that _L.
-guichenoti_ would be more impacted by the prenatal environment than _L.
+We also predicted that prenatal CORT and temperature would affect the behavioural flexibility of both species, but that _L.
+guichenoti_ would be more impacted by the prenatal treatments than _L.
 delicata_.
-Regarding the directionality of the treatments, high prenatal temperatures are considered to improve performance in cognitive tasks in ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014], so we expected those incubated at higher temperatures to perform better in the reversal task.
-On the other hand, we expected that prenatal CORT would impair the performance of the lizards in the task, as it has been shown in other species [@lemaire_prenatal_2000; @zhu_prenatal_2004; @lui2017chronic].
+High prenatal temperatures are considered to improve performance in cognitive tasks in some ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+For this reason, we predicted that lizardss incubated at higher temperatures would perform better in the learning reversal task.
+Conversely, we predicted that prenatal CORT would impair learning [@lemaire_prenatal_2000; @zhu_prenatal_2004; @lui2017chronic].
 Finally, we expected an interaction between both treatments, with high temperatures mitigating the negative effects of prenatal CORT on the performance of the lizards in the task.

### 2024-02-23 ms.qmd
Updates

@@
 the ability to adjust the behaviour adaptively in response to internal or external changes by problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral], is considered crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can].
-In general, species with higher behavioural flexibility are more likely to survive and establish in new habitats, as behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can].
+In general, species with higher behavioural flexibility are more likely to survive and establish in new habitats because behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can].
 For instance, when closely related species of birds were compared, successful invaders showed a higher frequency of foraging innovations [@sol2000behavioural].
@@
 GCs are the main group of hormones related to animals’ response towards alterations in homeostasis [@sapolsky_how_2000] that may become relevant when facing new environments and their new thermal conditions [@Crino_2023].
-Furthermore, there is evidence that both developmental GCs and thermal environment can impact cognition in different taxa [@jonson1976effect; @zhu_prenatal_2004; @amiel_hotter_2012; @lui2017chronic].
-For instance, young Sprague-Dawley rats treated with corticosterone (CORT) - the principal GC in rodents, birds, and reptiles [@Crino_2023] - performed worse than controls in a reversal learning task [@lui2017chronic], while exposure of pregnant guinea pigs to higher temperatures resulted in significant impairments with offspring behavioural flexibility [@jonson1976effect].
-In addition, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017], an aspect that is considered essential in successful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
+In addition, there is evidence that both developmental GCs and thermal environment can impact cognition in different taxa [@jonson1976effect; @zhu_prenatal_2004; @amiel_hotter_2012; @lui2017chronic].
+For instance, young Sprague-Dawley rats treated with corticosterone (CORT) - the principal GC in rodents, birds, and reptiles [@Crino_2023] - performed worse than controls in a reversal learning task [@lui2017chronic], while cold incubation temperatures in the eastern three-lined skink resulted in significant impairments with behavioural flexibility [@clark_colour_2014].
+Moreover, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017], an aspect that is considered essential in successful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
 Here, we studied the interactive contribution of prenatal temperature and CORT on behavioural flexibility in two species that exhibit distinct outcomes in their roles as invasive species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
@@
 High prenatal temperatures are considered to improve performance in cognitive tasks in some ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-For this reason, we predicted that lizardss incubated at higher temperatures would perform better in the learning reversal task.
-Conversely, we predicted that prenatal CORT would impair learning [@lemaire_prenatal_2000; @zhu_prenatal_2004; @lui2017chronic].
+For this reason, we predicted that lizards incubated at higher temperatures would perform better in the learning reversal task.
+Conversely, we predicted that prenatal CORT would impair learning [as seen previously in @lemaire_prenatal_2000; @zhu_prenatal_2004; @lui2017chronic].
 Finally, we expected an interaction between both treatments, with high temperatures mitigating the negative effects of prenatal CORT on the performance of the lizards in the task.
+This may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004]; and second, the elevated metabolic rate associated with higher temperatures accelerates the metabolism of CORT, resulting in embryos being exposed to CORT for a shorter time.
 
@@
 #### Experimental design
-We employed juveniles of both species, _L.
+For this study, we used juveniles of _L.
 delicata_ and _L.
@@
 This colony, established in 2019, originates from animals collected in Sydney, likely from similar populations that have become invasive on Lord Howe Island [@chapple2016origin] (details of breeding colony and husbandry in Supplementary Material).
-To see the effect of prenatal CORT and temperature, eggs were topically supplied with 5µL of CORT dissolved in 70% Ethanol and 30% DMSO ('CORT' treatment) or the same volume of the vehicle ('Control'), and were then incubated at different temperatures ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) until hatching.
+To see the effect of prenatal CORT and temperature, eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol ('CORT' treatment) or the same volume of the vehicle ('Control'), and were then incubated at different temperatures ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) until hatching.
 To estimate behavioural flexibility, we examined lizards' performance in a reversal learning task using colour as the main conditioned stimulus and food (frozen small *A.
 domestica*) as a reward (see @fig-Methods).
-The learning test was divided in three main phases: there was first a habituation phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm); then a second step where lizards had to associate the attainability of food with one colour (@fig-Methods Associative task); and finally the reversal task where the colour associated with the attainable food was changed (@fig-Methods Reversal task).
-In associative and reversal tasks we used three different ramps that were identical in size and shape to the ones for the habituation phase.
+The learning test was divided in three main phases: (1) _habituation_ -  lizards were conditioned to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm); (2) _association_ - lizards were conditioned to associate food with one colour (Fig.
+1 Associative task); and (3) _reversal_ - the colour associated with the food was changed (Fig.
+1 Reversal task).
+For the associative and reversal phases we used three different ramps that were identical in size and shape to the ones for the habituation phase.
 The colours of the ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
-To control for potential colour biases, we assigned one group of lizards to associate the blue ramp with the attainable food in the associative task and the red ramp in the reversal, while the other group was assigned red as correct for the associative and blue for the reversal.
+To control for potential colour biases, we assigned one group of lizards to associate the blue ramp with the accessible food in the associative task and the red ramp in the reversal, while the other group was assigned red as correct for the associative and blue for the reversal.
 In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
@@
 Lizards were tested once daily between 11 to 12 am, when lizards are active.
-The training phase lasted 38 days, the Associaive learning task 35, and the Reversal learning task 40 days.
-We recorded and analysed manually all trials form the learning phases using a standard video player (IINA).
-PR was the main researcher analysing the data, and was blinded to the lizards' treatment until the end of the analyses.
+The habituation phase lasted 38 days, the association phase 35, and the reversal phase 40 days.
+We recorded and analysed manually all trials form the association and reversal phases using a standard video player (IINA).
+Videos were analysed by one person (P.R.) who was blind to the treatment groups.
 We used as the main variable whether the animal chose the correct ramp first or not.
 We considered that a choice was made if the head of the lizard was inside the well of one of the ramps.
-We considered a trial failed if there was no choice in one hour of recording and those trials were considered as 'non data' in the analyses.
+Lizards were considered to make a correct choice if they chose the ramp with the accessible food first.
+We scored lizards that chose ramps with inaccessible foods first to have made an incorrect choice.
+We considered a trial failed if there was no choice in one hour of recording and those trials were considered as ‘non data’ in the analyses.
 Here, we analysed the data of the reversal as an index of behavioural flexibility [@brown2010behavioral].
@@
 Stages 1-3 indicate the different phases of the habituation phase.
-In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."
+In the associative and reversal tasks, white lids show the ramps where the food reward was not accessible."
 
@@
 We fitted a total of two different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022).
-We had per each model four parallel chains of 3000 iterations, with a warm up interval of 1000 iterations.
+We had per each model four parallel chains of 3000 iterations, with a warmup interval of 1000 iterations.
 We used 'Choice' - whether the individual chose correct (1) or not (0) - as the response variable; and trial, hormone ('CORT' versus 'Control'), incubation temperature ('Cold' versus 'Hot'), and their interaction as fixed factors.
@@
 Learning slopes were obtained using the estimates of the variable trial per each level of the hormone-temperature interaction ('Treatments'); values bigger from zero were considered as evidence of learning, while those less or equal to zero not.
-We used the pmcmc method to test whether those slopes or the comparissons between treatments (e.g.
+We used the pmcmc method to test whether those slopes or the comparisons between treatments (e.g.
 slope for 'CORT-Cold' lizards minus 'CORT-Hot' lizards) or species were different from zero (two-tailed tests).
@@
 Originally, we started with 96 lizards, 48 per species and 12 per treatment per species.
-However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3; see above), we ended up with a total of 81 lizards.
-Final sample sizes per treatment and species are disclosed on @tbl-data.
+However, our final sample size was 81 due to natural mortality (n = 11), failure to complete the training stage (n = 1), or if the number of failed tasks (see above) was higher than 15 (n = 3).
+Final sample sizes per treatment and species are listed in @tbl-data.
 
@@
 #| label: tbl-data
-#| tbl-cap: "Estimates of Associative learning slope for all the different treatments per each task, species and group.
-Mean shows the aritmetic mean of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
+#| tbl-cap: "Estimates of Reversal learning slope for all the different treatments per each task, species, and group.
+Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
 All p-values were obtained using pmcmc and test the hypothesis that the mean is equal to zero.
@@
 
-We did not find any significant differences between treatments in _L.
+We found that the learning slopes for all treatments and species were higher from zero, but we did not find any difference between treatments or species.
+There were not significant differences between treatments in _L.
 delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(deli_ControlCold - deli_CORTCold), 3)`, p- value = `r format_dec(pmcmc(deli_ControlCold - deli_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(deli_ControlHot - deli_CORTHot), 3)`, p- value = `r format_dec(pmcmc(deli_ControlHot - deli_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(deli_ControlHot - deli_ControlCold), 3)`, p-value = `r format_dec(pmcmc(deli_ControlHot - deli_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(deli_CORTHot - deli_CORTCold), 3)`, p-value = `r format_dec(pmcmc(deli_CORTHot - deli_CORTCold), 3)`) (see @fig-results) or _L.
 guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(guich_ControlCold - guich_CORTCold), 3)`, p- value = `r format_dec(pmcmc(guich_ControlCold - guich_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(guich_ControlHot - guich_CORTHot), 3)`, p- value = `r format_dec(pmcmc(guich_ControlHot - guich_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(guich_ControlHot - guich_ControlCold), 3)`, p-value = `r format_dec(pmcmc(guich_ControlHot - guich_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(guich_CORTHot - guich_CORTCold), 3)`, p-value = `r format_dec(pmcmc(guich_CORTHot - guich_CORTCold), 3)`) (see @fig-results).
-When pooled together, we did not find any effect of incubation temperature (_L.
+When pooled together, we did not find any significant effect of incubation temperature (_L.
 delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_dec(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`; _L.
 guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_dec(pmcmc((guich_CORTHot + guich_ControlHot) -(guich_CORTCold + guich_ControlCold)),3)`) or the hormone (_L.
-delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`;_L.
+delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`; _L.
 guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`).
-Finally, we did not find any significant differences when we compared the estimated slopes between species for the reversal task (_L.
+Finally, there were not significant differences when we compared the estimated slopes between species (_L.
 delicata_ - _L.
@@
 
-The study embarked on unraveling the interactive effects of prenatal temperature and Glucocorticoids (GCs) on behavioral flexibility in two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+The study embarked on unravelling the interactive effects of prenatal temperature and Glucocorticoids (GCs) on behavioral flexibility in two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_).
@@
 Previous studies have shown that _L.
-delicata_ is more explorative than _L.
-guichenoti_, which can be advantageous in some facets of the colonization of new environments [@chapple_know_2011].
-However, @bezzina2014does found no differences in learning between the two skinks in an associative learning task.
-Our results align with the latter study, and suggest that behavioural flexibility does not differ in these species.
+delicata_ more readily explores novel environments than _L.
+guichenoti_, which can be advantageous during colonization [@chapple_know_2011].
+However, Bezzina et al.
+[@bezzina2014does] found no differences in learning between the two skinks in an associative learning task.
+Our results align with the latter study and suggest that behavioural flexibility does not differ between these species.
 In addition, we did not find any effect of the treatments on both species.
-Both results contrast our original predictions, and may indicate that other aspects of their biology are more relevant for _L.
+Both results contrast our original predictions and may indicate that other aspects of their biology are more relevant for _L.
 delicata_ success as invaders than behavioural flexibility.
@@
 Our early environment manipulation did not affect the performance of the lizards in the task.
-We expected CORT to decrease reversal learning abilities and high temperatures to minimize these effects.
+We predicted that prenatal CORT treatment would decrease reversal learning abilities and that high temperatures would minimize these effects.
 However, our results show no significant differences between treatments in both species.
 Our outcome contrast with previous studies that show impairments of high GCs levels in different types of learning tests [@lemaire_prenatal_2000; @zhu_prenatal_2004;  @farrell_developmental_2016], but they are consistent with other experiments where GCs increased or did not impact learning abilities [@szuran_water_1994; @bebus_associative_2016].
-More striking is the absence of effect of incubation temperature, since most of the studies in reptiles reported better performance when incubated at higher temperatures in different associative learning and motor tasks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014]; and those studies that reported cold-incubated lizards to learn faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temperatures far beyond the natural range in the hot treatment.
-It could be argued whether our results stem from an insufficient manipulation of the prenatal environment, particularly regarding CORT as it is known to have hermetic effects on learning and neural structure [@du_dynamic_2009; @mcewen_brain_2012].
-However, we find these possibilities unlikely for two primary reasons.
-First, we have observed the effects of the treatments on other traits of the lizards (unpublished data).
+More striking is the absence of effect of incubation temperature, since most of the studies in reptiles reported better performance when incubated at higher temperatures in different associative learning and motor tasks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+Furthermore, those studies that reported cold-incubated lizards learn faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temperatures far beyond the natural range in the hot treatment.
+In some systems, exposure to CORT during development has hermetic effects on  learning and neural structures [@du_dynamic_2009; @mcewen_brain_2012].
+For example, in Sprague–Dawley rats, exposure to high doses of CORT, but not low doses, reduced density of immature neurons and cell proliferation and in the dentate gyrus [@DOSEneurobrummelte2010chronic].
+We know that prenatal CORT treatment affects  other traits in both species of lizards used in this experiment (unpublished data).
+However, it is possible that prenatal CORT treatment affects tissues differently.
 Conversely, we find more plausible that the effects of the early environment may vary depending on the cognitive task, as evidenced by studies showing variations in the impact of prenatal GCs and temperature on different brain regions [@coomber_independent_1997; @sakata_neural_2000; @lemaire_prenatal_2000].
-However, this hypothesis requires further testing, involving assessments of performance in various cognitive tasks together with the neurophysiological effects on different brain nuclei.
+These hypotheses are not mutually exclusive and could be tested in future experiments using multiple doses of prenatal CORT treatment, assessing learning using multiple cognitive tasks, and by measuring the neurophysiological effects on different brain nuclei.
 In conclusion, our results indicate that lizards performed the reversal learning task, a measure of behavioral flexibility, at similar rates, with no discernible differences between treatments or species.
@@
 delicata_ biology may be more influential for their success as invaders than behavioral flexibility alone.
-The present study also indicates that prenatal CORT and temeprature do not affect learning abilities in these species.
+The present study also indicates that prenatal CORT and temperature do not affect learning abilities in these species.
 Nevertheless, it remains possible that the effects of the early environment are task-dependent, and future studies should explore performance across different cognitive tasks, as well as the effects of both treatments on brain function.
@@
 #| label: tbl-data_2
-#| tbl-cap: "Estimates of Associative learning slope for all the different treatments per each task, species and group.
-Mean shows the aritmetic mean of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
+#| tbl-cap: "Estimates of Reversal learning slope for all the different treatments per each task, species, and group.
+Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
 All p-values were obtained using pmcmc and test the hypothesis that the mean is equal to zero.

### 2024-02-23 ms.qmd
Update ms.qmd

@@
 ## Introduction
-Behavioural flexibility, i.e.
-the ability to adjust the behaviour adaptively in response to internal or external changes by problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral], is considered crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can].
-In general, species with higher behavioural flexibility are more likely to survive and establish in new habitats because behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can].
+Behavioural flexibility describes the ability to adjust behaviour adaptively in response to internal or external changes by problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral], is considered crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can].
+Generally, species with higher behavioural flexibility are more likely to survive and establish in new habitats because behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can].
 For instance, when closely related species of birds were compared, successful invaders showed a higher frequency of foraging innovations [@sol2000behavioural].
-According to the adaptive flexibility hypothesis, behavioural flexibility is particularly relevant during introduction, establishment, and spread of the population [@wright2010behavioral; @chapple2012can; @szabo2020can], stages that can involve more than one generation.
-If behavioural flexibility is adaptive in these different phases, both this trait and the underlining mechanisms are expected to persist through generations in successful invaders.
-For example, in mammals, birds, reptiles and amphibians, relative brain size is a good predictor of behavioural flexibility and invasive success [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
-Since the brain is especially sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004] it is possible that the new prenatal environment faced by establishing populations can affect the behavioural flexibility of the new generations [see @jonson1976effect; @lui2017chronic], with a consequent impact on invasion success.
-As such, we find that studying the effect of developmental conditions on behavioural flexibility can be key to understand and predict the success of invasive species.
-**BETTER LINK**In this scenario, prenatal glucocorticoids (GCs) and thermal environment can be salient factors in the study of behavioural flexibility within the context of invasion biology.
+According to the adaptive flexibility hypothesis, behavioural flexibility is most relevant during introduction, establishment, and spreading stages of the population into new habitats [@wright2010behavioral; @chapple2012can; @szabo2020can].
+These stages can involve more than one generation, so selection may act on behavioural flexibility and the underlying mechanisms in successful invaders to ensure the persistence of behavioural flexibility through generations.
+In mammals, birds, reptiles and amphibians, relative brain size is a good predictor of behavioural flexibility and invasive success [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
+Since the brain is especially sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004] it is possible that the new prenatal environment faced by establishing populations can affect the behavioural flexibility of future generations [see @jonson1976effect; @lui2017chronic], with a consequent impact on invasion success.
+As such, we find that studying the effect of developmental conditions on behavioural flexibility can be key to understanding and predicting invasive species' success.
+**BETTER LINK**In this scenario, prenatal glucocorticoids (GCs) and the thermal environment can be salient factors in the study of behavioural flexibility within invasion biology.
 GCs are the main group of hormones related to animals’ response towards alterations in homeostasis [@sapolsky_how_2000] that may become relevant when facing new environments and their new thermal conditions [@Crino_2023].
-In addition, there is evidence that both developmental GCs and thermal environment can impact cognition in different taxa [@jonson1976effect; @zhu_prenatal_2004; @amiel_hotter_2012; @lui2017chronic].
-For instance, young Sprague-Dawley rats treated with corticosterone (CORT) - the principal GC in rodents, birds, and reptiles [@Crino_2023] - performed worse than controls in a reversal learning task [@lui2017chronic], while cold incubation temperatures in the eastern three-lined skink resulted in significant impairments with behavioural flexibility [@clark_colour_2014].
-Moreover, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017], an aspect that is considered essential in successful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
+In addition, there is evidence that developmental GCs and thermal environment can impact cognition in different taxa [@jonson1976effect; @zhu_prenatal_2004; @amiel_hotter_2012; @lui2017chronic].
+For instance, young Sprague-Dawley rats treated with corticosterone (CORT) - the principal GC in rodents, birds, and reptiles [@Crino_2023] - performed worse than controls in a reversal learning task [@lui2017chronic], while cold incubation temperatures in the eastern three-lined skink resulted in significant impairments with associative and reversal learning [@clark_colour_2014].
+Moreover, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017], an aspect considered essential in successful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
 Here, we studied the interactive contribution of prenatal temperature and CORT on behavioural flexibility in two species that exhibit distinct outcomes in their roles as invasive species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
@@
 These two species are closely related and share similar life history traits [@chapple_know_2011; @chapple_biology_2014], but only _L.
-delicata_ has been successful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI].
+delicata_ has successfully colonised different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI].
 Some studies have shown differences in personality traits between these two species that can be related to higher behavioural flexibility in _L.
-delicata_, and are likely key for its invasive success [@chapple_know_2011; @chapple2012can; @bezzina2014does].
-However, differences between species in behavioural flexibility and how this trait is affected by the prenatal environment remains unknown.
-To investigate these effects, we first manipulated CORT levels and incubation temperature in eggs from both species, and then subjected the juveniles to a reversal learning task as a measure of behavioural flexibility [@brown2010behavioral; @szabo2020can].
+delicata_, and are likely key to its invasive success [@chapple_know_2011; @chapple2012can; @bezzina2014does].
+However, differences between species in behavioural flexibility and how this trait is affected by the prenatal environment remain unknown.
+To investigate these effects, we first manipulated CORT levels and incubation temperature in eggs from both species, then subjected the juveniles to a reversal learning task to measure behavioural flexibility [@brown2010behavioral; @szabo2020can].
 We predicted that _L.
-delicata_ would, on average, perform more proficiently in the task that _L.
+delicata_ would, on average, perform more proficiently in the task than _L.
 guichenoti_.
-We also predicted that prenatal CORT and temperature would affect the behavioural flexibility of both species, but that _L.
+We also predicted that prenatal CORT and temperature would affect the behavioural flexibility of both species and that _L.
 guichenoti_ would be more impacted by the prenatal treatments than _L.
 delicata_.
-High prenatal temperatures are considered to improve performance in cognitive tasks in some ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-For this reason, we predicted that lizards incubated at higher temperatures would perform better in the learning reversal task.
-Conversely, we predicted that prenatal CORT would impair learning [as seen previously in @lemaire_prenatal_2000; @zhu_prenatal_2004; @lui2017chronic].
+**The rationale behind this prediction is that behavioural flexibility is expected to be preserved through generations in invassive species, and as such, less impacted by early environment.** Further, we predicted those incubated at higher temperatures to perform better in the reversal task because high prenatal temperatures often improve performance in cognitive tasks in ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+Conversely, we predicted that prenatal CORT would impair learning as shown in other species [@lemaire_prenatal_2000; @zhu_prenatal_2004; @lui2017chronic].
 Finally, we expected an interaction between both treatments, with high temperatures mitigating the negative effects of prenatal CORT on the performance of the lizards in the task.
@@
 delicata_ and _L.
-guichenoti_ that came from a breeding colony kept in the lab.
-This colony, established in 2019, originates from animals collected in Sydney, likely from similar populations that have become invasive on Lord Howe Island [@chapple2016origin] (details of breeding colony and husbandry in Supplementary Material).
-To see the effect of prenatal CORT and temperature, eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol ('CORT' treatment) or the same volume of the vehicle ('Control'), and were then incubated at different temperatures ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) until hatching.
-To estimate behavioural flexibility, we examined lizards' performance in a reversal learning task using colour as the main conditioned stimulus and food (frozen small *A.
+guichenoti_ from a breeding colony kept in the lab.
+Established in 2019, this colony originates from animals collected in Sydney, likely from similar populations that have become invasive on Lord Howe Island [@chapple2016origin] (details of breeding colony and husbandry in Supplementary Material).
+To test the effect of prenatal CORT and temperature, eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (CORT treatment) or the same volume of the vehicle (Control), and were then incubated at different temperatures (Cold -- 23ºC ± 3ºC or Hot -- 30ºC ± 3ºC) until hatching.
+To estimate behavioural flexibility, we examined lizards' performance in a reversal learning task using colour as the primary conditioned stimulus and food (frozen small *A.
 domestica*) as a reward (see @fig-Methods).
-The learning test was divided in three main phases: (1) _habituation_ -  lizards were conditioned to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm); (2) _association_ - lizards were conditioned to associate food with one colour (Fig.
+The learning test was divided into three main phases: (1) _habituation_ -  lizards were conditioned to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm); (2) _association_ - lizards were conditioned to associate food with one colour (Fig.
 1 Associative task); and (3) _reversal_ - the colour associated with the food was changed (Fig.
@@
 In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
-To avoid the use of chemical cues, we placed the food reward in all three ramps, but in two of them the cricket was covered by small white lids with holes on the top.
+To avoid the influence of chemical cues, we placed the food reward in the wells of all three ramps, but in two of the wells the cricket was covered by immovable small white lids with holes on the top.
 Lizards were tested once daily between 11 to 12 am, when lizards are active.
@@
 
-We performed the analyses for both species separately.
+We performed the analyses for each species separately.
 We fitted a total of two different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022).
-We had per each model four parallel chains of 3000 iterations, with a warmup interval of 1000 iterations.
-We used 'Choice' - whether the individual chose correct (1) or not (0) - as the response variable; and trial, hormone ('CORT' versus 'Control'), incubation temperature ('Cold' versus 'Hot'), and their interaction as fixed factors.
-Lizard identity was employed as a random intercept, and as a random slope we included the trial within each level of lizard identity.
+We had per each model four parallel chains of 3000 iterations, with a warm-up interval of 1000 iterations.
+We used Choice - whether the individual chose correct (1) or not (0) - as the response variable, and trial, hormone (CORT versus Control), incubation temperature (Cold versus Hot), and their interaction as fixed factors.
+Lizard identity was employed as a random intercept, and as a random slope, we included the trial within each level of lizard identity.
 We used the posterior distributions of these models to evaluate differences in learning rate between treatments and species.
-Learning slopes were obtained using the estimates of the variable trial per each level of the hormone-temperature interaction ('Treatments'); values bigger from zero were considered as evidence of learning, while those less or equal to zero not.
+Learning slopes were obtained using the estimates of the variable trial per each level of the hormone-temperature interaction (Treatments); values greater than zero were considered as evidence of learning, while those less or equal to zero were not.
 We used the pmcmc method to test whether those slopes or the comparisons between treatments (e.g.
-slope for 'CORT-Cold' lizards minus 'CORT-Hot' lizards) or species were different from zero (two-tailed tests).
+slope for CORT-Cold lizards minus CORT-Hot lizards) or species differed from zero (two-tailed tests).
 We considered statistical significance if p-value < 0.05.
@@
 Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
-All p-values were obtained using pmcmc and test the hypothesis that the mean is equal to zero.
+All p-values were obtained using pmcmc and tested the hypothesis that the mean equals zero.
 In bold, those values that are significant (p-value <0.05)"
@@
 
-We found that the learning slopes for all treatments and species were higher from zero, but we did not find any difference between treatments or species.
+**Change RESULTS????** We found that the learning slopes for all treatments and species were higher from zero, but we did not find any difference between treatments or species.
 There were not significant differences between treatments in _L.
-delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(deli_ControlCold - deli_CORTCold), 3)`, p- value = `r format_dec(pmcmc(deli_ControlCold - deli_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(deli_ControlHot - deli_CORTHot), 3)`, p- value = `r format_dec(pmcmc(deli_ControlHot - deli_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(deli_ControlHot - deli_ControlCold), 3)`, p-value = `r format_dec(pmcmc(deli_ControlHot - deli_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(deli_CORTHot - deli_CORTCold), 3)`, p-value = `r format_dec(pmcmc(deli_CORTHot - deli_CORTCold), 3)`) (see @fig-results) or _L.
-guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(guich_ControlCold - guich_CORTCold), 3)`, p- value = `r format_dec(pmcmc(guich_ControlCold - guich_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(guich_ControlHot - guich_CORTHot), 3)`, p- value = `r format_dec(pmcmc(guich_ControlHot - guich_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(guich_ControlHot - guich_ControlCold), 3)`, p-value = `r format_dec(pmcmc(guich_ControlHot - guich_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(guich_CORTHot - guich_CORTCold), 3)`, p-value = `r format_dec(pmcmc(guich_CORTHot - guich_CORTCold), 3)`) (see @fig-results).
+delicata_ (Control-Cold - CORT-Cold = `r format_dec(mean(deli_ControlCold - deli_CORTCold), 3)`, p- value = `r format_dec(pmcmc(deli_ControlCold - deli_CORTCold), 3)`; Control-Hot - CORT-Hot = `r format_dec(mean(deli_ControlHot - deli_CORTHot), 3)`, p- value = `r format_dec(pmcmc(deli_ControlHot - deli_CORTHot), 3)`; Control-Hot - Control-Cold = `r format_dec(mean(deli_ControlHot - deli_ControlCold), 3)`, p-value = `r format_dec(pmcmc(deli_ControlHot - deli_ControlCold), 3)`; CORT-Hot - CORT-Cold = `r format_dec(mean(deli_CORTHot - deli_CORTCold), 3)`, p-value = `r format_dec(pmcmc(deli_CORTHot - deli_CORTCold), 3)`) (see @fig-results) or _L.
+guichenoti_ (Control-Cold - CORT-Cold = `r format_dec(mean(guich_ControlCold - guich_CORTCold), 3)`, p- value = `r format_dec(pmcmc(guich_ControlCold - guich_CORTCold), 3)`; Control-Hot - CORT-Hot = `r format_dec(mean(guich_ControlHot - guich_CORTHot), 3)`, p- value = `r format_dec(pmcmc(guich_ControlHot - guich_CORTHot), 3)`; Control-Hot - Control-Cold = `r format_dec(mean(guich_ControlHot - guich_ControlCold), 3)`, p-value = `r format_dec(pmcmc(guich_ControlHot - guich_ControlCold), 3)`; CORT-Hot - CORT-Cold = `r format_dec(mean(guich_CORTHot - guich_CORTCold), 3)`, p-value = `r format_dec(pmcmc(guich_CORTHot - guich_CORTCold), 3)`) (see @fig-results).
 When pooled together, we did not find any significant effect of incubation temperature (_L.
-delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_dec(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`; _L.
-guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_dec(pmcmc((guich_CORTHot + guich_ControlHot) -(guich_CORTCold + guich_ControlCold)),3)`) or the hormone (_L.
-delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`; _L.
-guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`).
+delicata_: Hot learning slope - Cold learning slope = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_dec(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`; _L.
+guichenoti_: Hot learning slope - Cold learning slope = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_dec(pmcmc((guich_CORTHot + guich_ControlHot) -(guich_CORTCold + guich_ControlCold)),3)`) or the hormone (_L.
+delicata_: Control learning slope - CORT learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`; _L.
+guichenoti_: Control learning slope - CORT learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`).
 Finally, there were not significant differences when we compared the estimated slopes between species (_L.
@@
 
-The study embarked on unravelling the interactive effects of prenatal temperature and Glucocorticoids (GCs) on behavioral flexibility in two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+The study embarked on unravelling the interactive effects of prenatal temperature and GCs on behavioural flexibility in two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_).
 Despite sharing life history traits, only _L.
-delicata_ has proven successful in colonizing various global regions, and we hypothesized this may be related with higher behavioural flexibility.
-Furthermore, we expected behavioural flexibility in this species to be less susceptible to the effect of early environment since this trait can be adaptive in several stages of invasion that can involve more than one generation.
-Nevertheless, we did not find any significant differences between treatments or species when we compared their performance in a reversal task.
+delicata_ has proven successful in colonising various global regions, and we hypothesised this may be related to higher behavioural flexibility.
+Furthermore, we expected behavioural flexibility in this species to be less susceptible to the effect of early environment since this trait can be adaptive in several stages of invasion involving more than one generation.
+Nevertheless, we did not find significant differences between treatments or species when we compared their performance in a reversal task.
 We found that, on average, all the lizards from the four treatments and the two species learned the reversal task - indicated by estimated slopes that are significantly different from zero - and that they learn, on average, at the same rate.
@@
 delicata_ more readily explores novel environments than _L.
-guichenoti_, which can be advantageous during colonization [@chapple_know_2011].
+guichenoti_, which can be advantageous during colonisation [@chapple_know_2011].
 However, Bezzina et al.
@@
 Our results align with the latter study and suggest that behavioural flexibility does not differ between these species.
-In addition, we did not find any effect of the treatments on both species.
+In addition, we did not find any effect of the treatments on either species.
 Both results contrast our original predictions and may indicate that other aspects of their biology are more relevant for _L.
-delicata_ success as invaders than behavioural flexibility.
+delicata_'s success as invaders than behavioural flexibility.
 For instance, the mentioned differences in exploratory behaviour can be the key factor explaining why _L.
@@
 delicata_ [@chapple_know_2011].
-Our early environment manipulation did not affect the performance of the lizards in the task.
-We predicted that prenatal CORT treatment would decrease reversal learning abilities and that high temperatures would minimize these effects.
+Our early environment manipulation did not affect the lizards' performance in the task.
+We predicted that prenatal CORT treatment would decrease reversal learning abilities and that high temperatures would minimise these effects.
 However, our results show no significant differences between treatments in both species.
-Our outcome contrast with previous studies that show impairments of high GCs levels in different types of learning tests [@lemaire_prenatal_2000; @zhu_prenatal_2004;  @farrell_developmental_2016], but they are consistent with other experiments where GCs increased or did not impact learning abilities [@szuran_water_1994; @bebus_associative_2016].
-More striking is the absence of effect of incubation temperature, since most of the studies in reptiles reported better performance when incubated at higher temperatures in different associative learning and motor tasks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+Our outcome contrasts with previous studies that show impairments of high GCs levels in different types of learning tests [@lemaire_prenatal_2000; @zhu_prenatal_2004;  @farrell_developmental_2016], but they are consistent with other experiments where GCs increased or did not impact learning abilities [@szuran_water_1994; @bebus_associative_2016].
+More striking is the absence of an effect of incubation temperature since most of the studies in reptiles reported better performance when incubated at higher temperatures in different associative learning and motor tasks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
 Furthermore, those studies that reported cold-incubated lizards learn faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temperatures far beyond the natural range in the hot treatment.
-In some systems, exposure to CORT during development has hermetic effects on  learning and neural structures [@du_dynamic_2009; @mcewen_brain_2012].
+In some systems, exposure to CORT during development has hormetic effects on  learning and neural structures [@du_dynamic_2009; @mcewen_brain_2012].
 For example, in Sprague–Dawley rats, exposure to high doses of CORT, but not low doses, reduced density of immature neurons and cell proliferation and in the dentate gyrus [@DOSEneurobrummelte2010chronic].
@@
 However, it is possible that prenatal CORT treatment affects tissues differently.
-Conversely, we find more plausible that the effects of the early environment may vary depending on the cognitive task, as evidenced by studies showing variations in the impact of prenatal GCs and temperature on different brain regions [@coomber_independent_1997; @sakata_neural_2000; @lemaire_prenatal_2000].
+Conversely, it is likely that the effects of the early environment may vary depending on the cognitive task, as evidenced by studies showing variations in the impact of prenatal GCs and temperature on different brain regions [@coomber_independent_1997; @sakata_neural_2000; @lemaire_prenatal_2000].
 These hypotheses are not mutually exclusive and could be tested in future experiments using multiple doses of prenatal CORT treatment, assessing learning using multiple cognitive tasks, and by measuring the neurophysiological effects on different brain nuclei.
-In conclusion, our results indicate that lizards performed the reversal learning task, a measure of behavioral flexibility, at similar rates, with no discernible differences between treatments or species.
+In conclusion, our results indicate that lizards performed the reversal learning task, a measure of behavioural flexibility, at similar rates, with no discernible differences between treatments or species.
 These findings contrast our initial predictions and suggest that other aspects of _L.
-delicata_ biology may be more influential for their success as invaders than behavioral flexibility alone.
+delicata_ biology may be more influential for their success as invaders than behavioural flexibility alone.
 The present study also indicates that prenatal CORT and temperature do not affect learning abilities in these species.
-Nevertheless, it remains possible that the effects of the early environment are task-dependent, and future studies should explore performance across different cognitive tasks, as well as the effects of both treatments on brain function.
+Nevertheless, it remains possible that the effects of the early environment are task-dependent, and future studies should explore performance across different cognitive tasks and the effects of both treatments on brain function.
 
@@
 ###### Husbandry  
-*Breeding colony* -- We tested juveniles coming from a breeding colony established in the lab since 2019.
+*Breeding colony* -- We tested juveniles originating from a breeding colony established in the lab since 2019.
 There is a total of 270 and 180 adults of *L.
@@
 We checked for the presence of eggs in the boxes three days a week.
-After collection, we measured length and width of eggs with a digital caliper to the nearest 0.1 mm and weight them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
+After collection, we measured length and width of eggs with a digital caliper to the nearest 0.1 mm and weighed them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
 Then eggs were treated with CORT or vehicle (see CORT and Temperature manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite).
@@
 *Hatchlings* -- Eggs in the incubator were checked three times a week for hatchlings.
-After hatchling, we measured juveniles' SVL and Tail Length (TL) with a rule to the nearest mm and weighted them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
+After hatchling, we measured juveniles' SVL and Tail Length (TL) with a ruler to the nearest mm and weighed them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
 We then placed hatchlings in individual enclosures (18.7L x 13.2W x 6.3H cm) and provided them with non-stick matting and a small water dish.
@@
 The number of lizards per species and treatment in each rack was counterbalanced to control for any effect of the room or the position of the lizard in the rack.
-During acclimatation and all the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin (see protocol below), and water was supplied *ad libitum*.
+During acclimatation and throughout the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin (see protocol below), and water was supplied *ad libitum*.
 We provided a temperature gradient by means of a heat cord and heat lamps in a 12 h light: 12 h dark cycle.
-The rooms temperature was set to between 22-24 Celsius.
+The temperature of both rooms was set to between 22-24 Celsius.
 
 ###### CORT and Temperature manipulation  
-To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
-We first allocated eggs to one of two different treatments: CORT treatment, where eggs were topically supplied with 5µL of CORT dissolved in 70% Ethanol and 30% DMSO (vehicle) at a final (10 pg CORT/mL) concentration (CORT treatment); and a Control treatment, where eggs received an equal volume of the vehicle.
+To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (Cold -- 23ºC ± 3ºC or Hot -- 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
+We first allocated eggs to one of two different treatments: CORT treatment, where eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (vehicle) at a final (10 pg CORT/mL) concentration (CORT treatment); and a Control treatment, where eggs received an equal volume of the vehicle.
 CORT concentration employed in the CORT treatment represents 2 standard deviations above the mean natural concentration obtained in eggs from both species (non-published data).
-Then, eggs were incubated in one of the two previously mentioned temperature regimes ('Cold' or 'Hot') until hatching.
+Then, eggs were incubated in one of the two previously mentioned temperature regimes (Cold or Hot) until hatching.
 The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.
@@
 Trials in every stage lasted one hour, begining when the feeding block (petri dish, ramp, or both) was placed inside the enclosure and finished when we took the feeding block away.
-We recorded whether the cricket had been consumed or not and we considered an stage as completed if the lizards ate the crickets in at least 5 out of 6 trials.
+We recorded whether the cricket had been consumed or not and we considered a stage as completed if the lizards ate the crickets in at least 5 out of 6 trials.
 This phase lasted 38 days, and only in one case we decided not to use the lizard in the next phases because its behaviour was not consistent.
@@
 As in the last stage of the habituation phase, we placed the cricket inside the wells of the ramps, but then two of them were covered with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp.
-The food reward was placed in all three wells to avoid lizard using prey chemical cues, that were released in the closed wells thanks to a series of small holes on the top of the lids.
+The food reward was placed in all three wells to avoid lizards using prey chemical cues, that were released in the closed wells through a series of small holes on the top of the lids.
 The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
@@
 This test was done once a day for 40 days.
-We performed the full experiment was between the 6^th^ of March until the 26^th^ of June 2023, between 11 to 12 am, when the lizards were active.
+We performed the full experiment between the 6^th^ of March until the 26^th^ of June 2023, between 11 to 12 am, when the lizards were active.
 Trials in the learning phases (colour associative task and reversal tasks) were recorded with different CCTV systems always using the same camera per individual.

### 2024-02-23 ms.qmd
Updates

@@
 ## Introduction
-Behavioural flexibility describes the ability to adjust behaviour adaptively in response to internal or external changes by problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral], is considered crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can].
-Generally, species with higher behavioural flexibility are more likely to survive and establish in new habitats because behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can].
-For instance, when closely related species of birds were compared, successful invaders showed a higher frequency of foraging innovations [@sol2000behavioural].
-According to the adaptive flexibility hypothesis, behavioural flexibility is most relevant during introduction, establishment, and spreading stages of the population into new habitats [@wright2010behavioral; @chapple2012can; @szabo2020can].
-These stages can involve more than one generation, so selection may act on behavioural flexibility and the underlying mechanisms in successful invaders to ensure the persistence of behavioural flexibility through generations.
-In mammals, birds, reptiles and amphibians, relative brain size is a good predictor of behavioural flexibility and invasive success [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
-Since the brain is especially sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004] it is possible that the new prenatal environment faced by establishing populations can affect the behavioural flexibility of future generations [see @jonson1976effect; @lui2017chronic], with a consequent impact on invasion success.
-As such, we find that studying the effect of developmental conditions on behavioural flexibility can be key to understanding and predicting invasive species' success.
+Behavioural flexibility describes the ability of individuals to adjust behaviour adaptively in response to internal or external changes in the environment [@brown2010behavioral].
+It comprises a suite of behavioural aspects like problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral]; and it is predicted to be crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can].
+Generally, species with greater behavioural flexibility are more likely to survive and establish in new habitats because behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can].
+For instance, in closely related bird species successful invaders show a higher frequency of foraging innovations [@sol2000behavioural].
+According to the 'adaptive flexibility hypothesis', behavioural flexibility is most relevant during introduction, establishment, and spread of an invasive population [@wright2010behavioral; @chapple2012can; @szabo2020can].
+In mammals, birds, reptiles and amphibians, relative brain size has been shown to be a good predictor of behavioural flexibility and invasive success [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
+However, the brain is also sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004] creating uncertainty about how environmental insults faced by early invaders might impact behavioural flexibility and thus the probability of invasion success.
 **BETTER LINK**In this scenario, prenatal glucocorticoids (GCs) and the thermal environment can be salient factors in the study of behavioural flexibility within invasion biology.
@@
 
-#### Experimental design
-For this study, we used juveniles of _L.
+#### Manipulating Early Thermal and CORT Environments  
+To manipulate early thermal environment and CORT, we collected eggs of _L.
 delicata_ and _L.
-guichenoti_ from a breeding colony kept in the lab.
-Established in 2019, this colony originates from animals collected in Sydney, likely from similar populations that have become invasive on Lord Howe Island [@chapple2016origin] (details of breeding colony and husbandry in Supplementary Material).
-To test the effect of prenatal CORT and temperature, eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (CORT treatment) or the same volume of the vehicle (Control), and were then incubated at different temperatures (Cold -- 23ºC ± 3ºC or Hot -- 30ºC ± 3ºC) until hatching.
-To estimate behavioural flexibility, we examined lizards' performance in a reversal learning task using colour as the primary conditioned stimulus and food (frozen small *A.
-domestica*) as a reward (see @fig-Methods).
-The learning test was divided into three main phases: (1) _habituation_ -  lizards were conditioned to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm); (2) _association_ - lizards were conditioned to associate food with one colour (Fig.
-1 Associative task); and (3) _reversal_ - the colour associated with the food was changed (Fig.
-1 Reversal task).
-For the associative and reversal phases we used three different ramps that were identical in size and shape to the ones for the habituation phase.
+guichenoti_ from a lab breeding colony that was established from a Sydney population in 2019.
+The Sydney population is thought to be the source population for invasive populations established on Lord Howe Island [@chapple2016origin].
+Eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (CORT treatment) or the same volume of the vehicle (Control) and were then incubated at different temperatures (Cold – 23ºC ± 3ºC or Hot – 30ºC ± 3ºC) until hatching in a fully factorial design.
+For full details of breeding colony and husbandry see Supplementary Material.
+
+#### Quantifying Behavioural Flexibility  
+Briefly, the learning test was divided in three main phases: a habituation phase where lizards had to learn to eat a frozen-thawed cricket from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm).
+The habituation phase lasted 38 days.
+This was followed by a colour association task where lizards had to associate the food reward with one of two colours (red or blue) (@fig-Methods Associative task).
+The associative learning task lasted 35 days.
+Finally, to quantify behavioural flexibility, we reversed the previously trained colour (red or blue) so that they needed to learn to associate the food with the opposite colour (@fig-Methods Reversal task).
+The reversal learning task lasted a total of 40 days.
+Lizards were tested once daily between 11 to 12 am when they were most active.
+In associative and reversal tasks we used three different ramps that were identical in size and shape to the ones for the habituation phase.
 The colours of the ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
-To control for potential colour biases, we assigned one group of lizards to associate the blue ramp with the accessible food in the associative task and the red ramp in the reversal, while the other group was assigned red as correct for the associative and blue for the reversal.
+To avoid the influence of chemical cues, we placed the food reward in all three ramps, but in two of them the cricket was covered by immovable small lids with holes on the top.
+To control for potential colour biases, we assigned one group of lizards within each treatment to associate food in the blue ramp followed by the red ramp in the reversal, while in the other group the order was reversed.
 In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
-To avoid the influence of chemical cues, we placed the food reward in the wells of all three ramps, but in two of the wells the cricket was covered by immovable small white lids with holes on the top.
-Lizards were tested once daily between 11 to 12 am, when lizards are active.
-The habituation phase lasted 38 days, the association phase 35, and the reversal phase 40 days.
-We recorded and analysed manually all trials form the association and reversal phases using a standard video player (IINA).
-Videos were analysed by one person (P.R.) who was blind to the treatment groups.
-We used as the main variable whether the animal chose the correct ramp first or not.
+We recorded whether the animal chose the correct ramp first or not.
 We considered that a choice was made if the head of the lizard was inside the well of one of the ramps.
-Lizards were considered to make a correct choice if they chose the ramp with the accessible food first.
-We scored lizards that chose ramps with inaccessible foods first to have made an incorrect choice.
-We considered a trial failed if there was no choice in one hour of recording and those trials were considered as ‘non data’ in the analyses.
-Here, we analysed the data of the reversal as an index of behavioural flexibility [@brown2010behavioral].
+We considered a trial failed if there was no choice in one hour of recording and those trials.
+Here, we analysed the data of the reversal task as a measure of behavioural flexibility [@brown2010behavioral].
 
@@
 #### Statistical analyses  
-
 We performed the analyses for each species separately.
-We fitted a total of two different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022).
-We had per each model four parallel chains of 3000 iterations, with a warm-up interval of 1000 iterations.
+We fitted a total of two different Bayesian multilevel models using the brm function from the _brms_ package [@burkner2017brms] using the R extension (version 2.8.2) [@R] for Visual Studio Code.
+We run four parallel MCMC chains of 3000 iterations for each model, with a warmup period of 1000 iterations.
 We used Choice - whether the individual chose correct (1) or not (0) - as the response variable, and trial, hormone (CORT versus Control), incubation temperature (Cold versus Hot), and their interaction as fixed factors.
-Lizard identity was employed as a random intercept, and as a random slope, we included the trial within each level of lizard identity.
-We used the posterior distributions of these models to evaluate differences in learning rate between treatments and species.
+We included a random intercept and slope (trial) for each lizard in our models.
+We used the posterior distributions of parameters from these models to test for differences in learning rate between treatments and species.
 Learning slopes were obtained using the estimates of the variable trial per each level of the hormone-temperature interaction (Treatments); values greater than zero were considered as evidence of learning, while those less or equal to zero were not.
@@
 intervals <- paste(interval_025, interval_975, sep = " , ")
-pvalue <- format_dec(sapply(estimates, pmcmc), 4)
+pvalue <- format_p(sapply(estimates, pmcmc), 4)
 #
@@
 
-**Change RESULTS????** We found that the learning slopes for all treatments and species were higher from zero, but we did not find any difference between treatments or species.
+ We found that the learning slopes for all treatments and species were higher from zero (@tbl-data), but we did not find any difference between treatments or species in the learning rate (@fig-results).
 There were not significant differences between treatments in _L.
-delicata_ (Control-Cold - CORT-Cold = `r format_dec(mean(deli_ControlCold - deli_CORTCold), 3)`, p- value = `r format_dec(pmcmc(deli_ControlCold - deli_CORTCold), 3)`; Control-Hot - CORT-Hot = `r format_dec(mean(deli_ControlHot - deli_CORTHot), 3)`, p- value = `r format_dec(pmcmc(deli_ControlHot - deli_CORTHot), 3)`; Control-Hot - Control-Cold = `r format_dec(mean(deli_ControlHot - deli_ControlCold), 3)`, p-value = `r format_dec(pmcmc(deli_ControlHot - deli_ControlCold), 3)`; CORT-Hot - CORT-Cold = `r format_dec(mean(deli_CORTHot - deli_CORTCold), 3)`, p-value = `r format_dec(pmcmc(deli_CORTHot - deli_CORTCold), 3)`) (see @fig-results) or _L.
-guichenoti_ (Control-Cold - CORT-Cold = `r format_dec(mean(guich_ControlCold - guich_CORTCold), 3)`, p- value = `r format_dec(pmcmc(guich_ControlCold - guich_CORTCold), 3)`; Control-Hot - CORT-Hot = `r format_dec(mean(guich_ControlHot - guich_CORTHot), 3)`, p- value = `r format_dec(pmcmc(guich_ControlHot - guich_CORTHot), 3)`; Control-Hot - Control-Cold = `r format_dec(mean(guich_ControlHot - guich_ControlCold), 3)`, p-value = `r format_dec(pmcmc(guich_ControlHot - guich_ControlCold), 3)`; CORT-Hot - CORT-Cold = `r format_dec(mean(guich_CORTHot - guich_CORTCold), 3)`, p-value = `r format_dec(pmcmc(guich_CORTHot - guich_CORTCold), 3)`) (see @fig-results).
-When pooled together, we did not find any significant effect of incubation temperature (_L.
-delicata_: Hot learning slope - Cold learning slope = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_dec(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`; _L.
-guichenoti_: Hot learning slope - Cold learning slope = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_dec(pmcmc((guich_CORTHot + guich_ControlHot) -(guich_CORTCold + guich_ControlCold)),3)`) or the hormone (_L.
-delicata_: Control learning slope - CORT learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`; _L.
-guichenoti_: Control learning slope - CORT learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`).
-Finally, there were not significant differences when we compared the estimated slopes between species (_L.
+delicata_ (Control-Cold - CORT-Cold = `r format_dec(mean(deli_ControlCold - deli_CORTCold), 3)`, p- value = `r format_dec(pmcmc(deli_ControlCold - deli_CORTCold), 3)`; Control-Hot - CORT-Hot = `r format_dec(mean(deli_ControlHot - deli_CORTHot), 3)`, p- value = `r format_dec(pmcmc(deli_ControlHot - deli_CORTHot), 3)`; Control-Hot - Control-Cold = `r format_dec(mean(deli_ControlHot - deli_ControlCold), 3)`, p-value = `r format_p(pmcmc(deli_ControlHot - deli_ControlCold), 3)`; CORT-Hot - CORT-Cold = `r format_dec(mean(deli_CORTHot - deli_CORTCold), 3)`, p-value = `r format_p(pmcmc(deli_CORTHot - deli_CORTCold), 3)`) (see @fig-results) or _L.
+guichenoti_ (Control-Cold - CORT-Cold = `r format_dec(mean(guich_ControlCold - guich_CORTCold), 3)`, p- value = `r format_dec(pmcmc(guich_ControlCold - guich_CORTCold), 3)`; Control-Hot - CORT-Hot = `r format_dec(mean(guich_ControlHot - guich_CORTHot), 3)`, p- value = `r format_dec(pmcmc(guich_ControlHot - guich_CORTHot), 3)`; Control-Hot - Control-Cold = `r format_dec(mean(guich_ControlHot - guich_ControlCold), 3)`, p-value = `r format_p(pmcmc(guich_ControlHot - guich_ControlCold), 3)`; CORT-Hot - CORT-Cold = `r format_dec(mean(guich_CORTHot - guich_CORTCold), 3)`, p-value = `r format_p(pmcmc(guich_CORTHot - guich_CORTCold), 3)`) (see @fig-results).
+ We compared each factor (hormone and incubation temperature) separately by pooling together the observations for all the individuals from the same hormone treatment or the same incubation temperature.
+In this regard, we did not find any significant effect of the hormone treatment (_L.
+delicata_: Control learning slope - CORT learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`; _L.
+guichenoti_: Control learning slope - CORT learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`) or the incubation temperature (_L.
+delicata_: Hot learning slope - Cold learning slope = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`; _L.
+guichenoti_: Hot learning slope - Cold learning slope = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) -(guich_CORTCold + guich_ControlCold)),3)`) in either species.
+ Finally, when all individuals from all the treatments were pooled together and species were compared, there were not significant differences in the estimated slopes (_L.
 delicata_ - _L.
-guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`).
+guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`, p-value = `r format_p(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`).
 
@@
 intervals_2 <- paste(interval_025_2, interval_975_2, sep = " , ")
-pvalue_2 <- format_dec(sapply(estimates_2, pmcmc), 4)
+pvalue_2 <- format_p(sapply(estimates_2, pmcmc), 4)
 #

### 2024-02-23 R/func.r

@@ -120,7 +120,20 @@ pmcmc <- function(x, null = 0, twotail = TRUE, dir){
 #' @param n The number of decimals
 format_dec <- function(x, n) {
   z <- sprintf(paste0("%.",n,"f"), x)
-  return(as.numeric(z))
+  return(z)
+}
+####################
+####################
+# Function to format numbers with 2 decimal places
+#' @title format_dec
+#' @param x The object
+#' @param n The number of decimals
+format_p <- function(x, n) {
+  z <- sprintf(paste0("%.",n,"f"), x)
+  tmp <- ifelse(as.numeric(z) <= 0.001, "< 0.001",
+         ifelse(as.numeric(z) <= 0.05 & as.numeric(z) > 0.001, "< 0.05",
+                as.character(z)))
+  return(tmp)
 }
 ####################
 ####################

### 2024-02-26 ms.qmd
Updates

@@
 Moreover, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017], an aspect considered essential in successful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
-Here, we studied the interactive contribution of prenatal temperature and CORT on behavioural flexibility in two species that exhibit distinct outcomes in their roles as invasive species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+Here, we studied the interactive effects of prenatal temperature and CORT on behavioural flexibility in two species with distinct histories of invasiveness, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_).
-These two species are closely related and share similar life history traits [@chapple_know_2011; @chapple_biology_2014], but only _L.
-delicata_ has successfully colonised different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI].
-Some studies have shown differences in personality traits between these two species that can be related to higher behavioural flexibility in _L.
-delicata_, and are likely key to its invasive success [@chapple_know_2011; @chapple2012can; @bezzina2014does].
-However, differences between species in behavioural flexibility and how this trait is affected by the prenatal environment remain unknown.
-To investigate these effects, we first manipulated CORT levels and incubation temperature in eggs from both species, then subjected the juveniles to a reversal learning task to measure behavioural flexibility [@brown2010behavioral; @szabo2020can].
+_L.
+delicata_ has been succesful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI], but the same is not true of _L.
+guichenoti_ despite the two species having similar life-histories and overlapping distributions [@chapple_know_2011; @chapple_biology_2014].
+Personality has been shown to be different between these two species [@chapple_know_2011; @chapple2012can; @bezzina2014does], which could be related to general cognitive differences that are important for invasion success.
+Additionally, early environments are known to affect suites of morphological and behavioural traits differently in each species [**REFS**], but the interactive role of maternal CORT and early temperatures have not yet been explored.
+Differences in the relative impact that early environments have on behavioural flexibility may help explain differing invasion success between the two species.
 We predicted that _L.
-delicata_ would, on average, perform more proficiently in the task than _L.
+delicata_ would, on average, perform more proficiently in the task compared to _L.
 guichenoti_.
-We also predicted that prenatal CORT and temperature would affect the behavioural flexibility of both species and that _L.
-guichenoti_ would be more impacted by the prenatal treatments than _L.
+We also anticipated prenatal CORT and temperature to affect the behavioural flexibility of both species, and that _L.
+guichenoti_ would be more impacted by the prenatal environment than _L.
 delicata_.
-**The rationale behind this prediction is that behavioural flexibility is expected to be preserved through generations in invassive species, and as such, less impacted by early environment.** Further, we predicted those incubated at higher temperatures to perform better in the reversal task because high prenatal temperatures often improve performance in cognitive tasks in ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-Conversely, we predicted that prenatal CORT would impair learning as shown in other species [@lemaire_prenatal_2000; @zhu_prenatal_2004; @lui2017chronic].
-Finally, we expected an interaction between both treatments, with high temperatures mitigating the negative effects of prenatal CORT on the performance of the lizards in the task.
-This may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004]; and second, the elevated metabolic rate associated with higher temperatures accelerates the metabolism of CORT, resulting in embryos being exposed to CORT for a shorter time.
 
@@
                    levels = c("CORT-Cold", "Control-Cold", "CORT-Hot","Control-Hot")))
+# Estimate total sample size per species and number of observations (this will allow to include this data in the first column of the table)
+n_deli <- n_list$delicata_CORT_Cold+n_list$delicata_Control_Cold+n_list$delicata_CORT_Hot+n_list$delicata_Control_Hot
+ob_deli <- sum(clean_df$species == "delicata", na.rm = TRUE)
+n_guich <- n_list$guichenoti_CORT_Cold+n_list$guichenoti_Control_Cold+n_list$guichenoti_CORT_Hot+n_list$guichenoti_Control_Hot
+ob_guich <- sum(clean_df$species == "guichenoti", na.rm = TRUE)
 # Merge both dfs, put sample size together with the treatment, and organize the new df to make it look like the table
@@
                       `p-value` = "p-value") %>%
-    italic(j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
+    italic(i= c(1, 5), j = 1, italic = TRUE, part = "body") %>% # To have names of species in italics
     flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
+    flextable::compose(i = 2, j = 1, value = as_paragraph(sprintf("N = %d", n_deli)), part = "body") %>% # To write the delicata sample size
+    flextable::compose(i = 6, j = 1, value = as_paragraph(sprintf("N = %d", n_guich)), part = "body") %>% # To write the guichenoti sample size
+    flextable::compose(i = 3, j = 1, value = as_paragraph(sprintf("Obs = %d", ob_deli)), part = "body") %>% # To write the delicata total observations
+    flextable::compose(i = 7, j = 1, value = as_paragraph(sprintf("Obs = %d", ob_guich)), part = "body") %>% # To write the guichenoti total observations
     hline(i = 4, j = c(1:5), part = "body") %>% # To make some horizontal lines

### 2024-02-26 .vdoc.r

@@ -1,0 +1,461 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of early environment manipulation and learning tasks. Stages 1-3 indicate the different phases of the habituation phase. In the associative and reversal tasks, white lids show the ramps where the food reward was not accessible."
+
+knitr::include_graphics("./Others/BEHFLEX_FIG_1.svg")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleandata
+# Obtain the main df using "./R/1_data_process.R"
+source(here("R", "1_data_process.R"))
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(k in 1:length(hormone)){
+    for(l in 1:length(temperature)){
+      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
+      }
+    }
+  }
+#
+#
+#
+#
+#
+#| label: models
+# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
+source(here("R", "func.R"))
+# Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
+## A) L. delicata
[…]

### 2024-02-26 ms.qmd
Updates

@@
                    levels = c("CORT-Cold", "Control-Cold", "CORT-Hot","Control-Hot")))
+# Estimate total sample size per species and number of observations (this will allow to include this data in the first column of the table)
+n_deli_2 <- n_list_2$delicata_CORT_Cold+n_list_2$delicata_Control_Cold+n_list_2$delicata_CORT_Hot+n_list_2$delicata_Control_Hot
+ob_deli_2 <- sum(clean_df_2$species == "delicata", na.rm = TRUE)
+n_guich_2 <- n_list_2$guichenoti_CORT_Cold+n_list_2$guichenoti_Control_Cold+n_list_2$guichenoti_CORT_Hot+n_list_2$guichenoti_Control_Hot
+ob_guich_2 <- sum(clean_df_2$species == "guichenoti", na.rm = TRUE)
 # Merge both dfs, put sample size together with the treatment, and organize the new df to make it look like the table
@@
                       `p-value` = "p-value") %>%
-    italic(j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
+    italic(i = c(1,5), j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
     flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
+    flextable::compose(i = 2, j = 1, value = as_paragraph(sprintf("N = %d", n_deli_2)), part = "body") %>% # To write the delicata sample size
+    flextable::compose(i = 6, j = 1, value = as_paragraph(sprintf("N = %d", n_guich_2)), part = "body") %>% # To write the guichenoti sample size
+    flextable::compose(i = 3, j = 1, value = as_paragraph(sprintf("Obs = %d", ob_deli_2)), part = "body") %>% # To write the delicata total observations
+    flextable::compose(i = 7, j = 1, value = as_paragraph(sprintf("Obs = %d", ob_guich_2)), part = "body") %>% # To write the guichenoti total observations
     hline(i = 4, j = c(1:5), part = "body") %>% # To make some horizontal lines

### 2024-02-26 .vdoc.r

@@ -425,6 +425,11 @@ n_df_2 <- as.data.frame(do.call(rbind, n_list_2)) %>%
                   labels = c(delicata = "L. delicata", guichenoti = "L. guichenoti")),
         Treatment = factor(Treatment,
                    levels = c("CORT-Cold", "Control-Cold", "CORT-Hot","Control-Hot")))
+# Estimate total sample size per species and number of observations (this will allow to include this data in the first column of the table)
+n_deli_2 <- n_list_2$delicata_CORT_Cold+n_list_2$delicata_Control_Cold+n_list_2$delicata_CORT_Hot+n_list_2$delicata_Control_Hot
+ob_deli_2 <- sum(clean_df_2$species == "delicata", na.rm = TRUE)
+n_guich_2 <- n_list_2$guichenoti_CORT_Cold+n_list_2$guichenoti_Control_Cold+n_list_2$guichenoti_CORT_Hot+n_list_2$guichenoti_Control_Hot
+ob_guich_2 <- sum(clean_df_2$species == "guichenoti", na.rm = TRUE)
 # Merge both dfs, put sample size together with the treatment, and organize the new df to make it look like the table
 new_table_df_2 <- merge(table_df_2, n_df_2) %>%
   rename('p-value' = 'PValue', '95% CI' = 'CI') %>% #Change the names of the columns for the table
@@ -451,8 +456,12 @@ real_table_2 <- flextable(new_table_df_2) %>%
     set_header_labels(Mean = "Mean",
                       `95% CI` = "95% CI",
                       `p-value` = "p-value") %>%
-    italic(j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
+    italic(i = c(1,5), j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
     flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
+    flextable::compose(i = 2, j = 1, value = as_paragraph(sprintf("N = %d", n_deli_2)), part = "body") %>% # To write the delicata sample size
+    flextable::compose(i = 6, j = 1, value = as_paragraph(sprintf("N = %d", n_guich_2)), part = "body") %>% # To write the guichenoti sample size
+    flextable::compose(i = 3, j = 1, value = as_paragraph(sprintf("Obs = %d", ob_deli_2)), part = "body") %>% # To write the delicata total observations
[…]

### 2024-02-28 ms.qmd
Updates

@@
  We found that the learning slopes for all treatments and species were higher from zero (@tbl-data), but we did not find any difference between treatments or species in the learning rate (@fig-results).
+For _L.
+delicata_, we did not find any significant effects of the hormone (Control - CORT = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`).
+ For _L.
+guichenoti_, we did not find any significant effects of the hormone (Control - CORT = `r format_dec(mean((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`).
+Finally, when all individuals from all the treatments were pooled together and species were compared, there were not significant differences in the estimated slopes (_L.
+delicata_ - _L.
+guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`, p-value = `r format_p(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`).
+
 There were not significant differences between treatments in _L.

### 2024-02-29 ms.qmd
Updates

--- 2024-02-26 ms.qmd
@@
 #| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot)
 ```
@@
 #### Quantifying Behavioural Flexibility  
-Briefly, the learning test was divided in three main phases: a habituation phase where lizards had to learn to eat a frozen-thawed cricket from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm).
+Briefly, the learning test was divided in three main phases: a habituation phase where lizards had to learn to eat a frozen-thawed cricket from white 3D-printed polylactic acid (PLA) ramps (9 L x 4 W x 5 H cm).
 The habituation phase lasted 38 days.
@@
 
- We found that the learning slopes for all treatments and species were higher from zero (@tbl-data), but we did not find any difference between treatments or species in the learning rate (@fig-results).
-There were not significant differences between treatments in _L.
-delicata_ (Control-Cold - CORT-Cold = `r format_dec(mean(deli_ControlCold - deli_CORTCold), 3)`, p- value = `r format_dec(pmcmc(deli_ControlCold - deli_CORTCold), 3)`; Control-Hot - CORT-Hot = `r format_dec(mean(deli_ControlHot - deli_CORTHot), 3)`, p- value = `r format_dec(pmcmc(deli_ControlHot - deli_CORTHot), 3)`; Control-Hot - Control-Cold = `r format_dec(mean(deli_ControlHot - deli_ControlCold), 3)`, p-value = `r format_p(pmcmc(deli_ControlHot - deli_ControlCold), 3)`; CORT-Hot - CORT-Cold = `r format_dec(mean(deli_CORTHot - deli_CORTCold), 3)`, p-value = `r format_p(pmcmc(deli_CORTHot - deli_CORTCold), 3)`) (see @fig-results) or _L.
-guichenoti_ (Control-Cold - CORT-Cold = `r format_dec(mean(guich_ControlCold - guich_CORTCold), 3)`, p- value = `r format_dec(pmcmc(guich_ControlCold - guich_CORTCold), 3)`; Control-Hot - CORT-Hot = `r format_dec(mean(guich_ControlHot - guich_CORTHot), 3)`, p- value = `r format_dec(pmcmc(guich_ControlHot - guich_CORTHot), 3)`; Control-Hot - Control-Cold = `r format_dec(mean(guich_ControlHot - guich_ControlCold), 3)`, p-value = `r format_p(pmcmc(guich_ControlHot - guich_ControlCold), 3)`; CORT-Hot - CORT-Cold = `r format_dec(mean(guich_CORTHot - guich_CORTCold), 3)`, p-value = `r format_p(pmcmc(guich_CORTHot - guich_CORTCold), 3)`) (see @fig-results).
- We compared each factor (hormone and incubation temperature) separately by pooling together the observations for all the individuals from the same hormone treatment or the same incubation temperature.
-In this regard, we did not find any significant effect of the hormone treatment (_L.
-delicata_: Control learning slope - CORT learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`; _L.
-guichenoti_: Control learning slope - CORT learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`) or the incubation temperature (_L.
-delicata_: Hot learning slope - Cold learning slope = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`; _L.
-guichenoti_: Hot learning slope - Cold learning slope = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) -(guich_CORTCold + guich_ControlCold)),3)`) in either species.
- Finally, when all individuals from all the treatments were pooled together and species were compared, there were not significant differences in the estimated slopes (_L.
-delicata_ - _L.
-guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`, p-value = `r format_p(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`).
+We found that the learning slopes for all treatments and species were higher from zero (@tbl-data), but we did not find any difference between treatments or species in the learning rate.  
+For _L.
+delicata_, we did not find any significant effects of the hormone (Control - CORT = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`) (see @fig-deli).
 
-```{r, fig-results}
-#| label: fig-results
-#| fig.cap: "Predicted probability of choosing the correct feeder first over trials.
+```{r, fig-deli}
+#| label: fig-deli
+#| fig.cap: "Results for L.
+delicata.
+A) Predicted probability of choosing the correct feeder first over trials.
 The lines represent the mean predicted probability of choosing the correct feeder first, and the shaded areas represent the standard deviation of the mean; both obtained by using the slope and intercept estimates from the posterior distributions.
+The different colours represent the different treatments.
+B) Distribution of the estimates of the slopes per each treatment.
+The x-axis represents the estimates of the slopes, and the y-axis represents the density of the estimates.
 The different colours represent the different treatments."
 source(here("R", "func.R"))
-# First step, create the dfs for all models
-## 1) L. delicata
-df_deli <- df_fig(as.data.frame(deli), "L. delicata")
-## 2) L. guichenoti
-df_guich <- df_fig(as.data.frame(guich), "L. guichenoti")
+# Create the dfs for the probability plot A) (df_prob)
 #
-# Second step, merge the df into a big Fig_df
-Fig_df <- rbind(df_deli, df_guich) %>%
+df_deliA <- df_fig(as.data.frame(deli), "L. delicata") %>%
   mutate(Trial = gsub("X", "", Trial)) %>%
@@
     ) %>%
+    select(-Species) %>%
 data.frame()
-write.csv(Fig_df, file= "./output/Checking/Fig_df.csv")
-# Make the plot
-figure_results <- plotting(Fig_df)
-ggsave("./output/figures/figure_results.png", plot=figure_results, width = 18, height = 20, units = "cm", dpi = 3000)
-knitr::include_graphics("./output/figures/figure_results.png")
+#
+# Create the df for the violin plots in plot B) (df_violin)
+deliB_list <- list(
+  'CORT-Cold' = deli_CORTCold,
+  'Control-Cold' = deli_ControlCold,
+  'CORT-Hot' = deli_CORTHot,
+  'Control-Hot' = deli_ControlHot)
+df_deliB1 <- data.frame(
+  Value = unlist(deliB_list),
+  Treatment = factor(rep(names(deliB_list), each = length(deli_CORTCold)))
+)
+#
+# Create the df for the points and bars in plot B) (df_points)
+df_deliB2 <- df_deliB1 %>%
+  group_by(Treatment) %>%
+  summarize(
+    Mean = mean(Value),
+    SE = (sd(Value)/sqrt(length(Value))),
+    SD = sd(Value)
+  ) %>%
+  ungroup() %>%
+  mutate(
+    Treatment = factor(Treatment,
+                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot"))
+  ) %>%
+  data.frame()
+# Make plot
+fig_deli <- plotting(df_prob = df_deliA, df_violin = df_deliB1, df_points = df_deliB2)
+ggsave("./output/figures/fig_deli.png", plot=fig_deli, width = 20, height = 10, units = "cm", dpi = 3000)
+knitr::include_graphics("./output/figures/fig_deli.png")
 ```
+
+For _L.
+guichenoti_, we did not find any significant effects of the hormone (Control - CORT = `r format_dec(mean((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) (@fig-guich).
+
+```{r, fig-guich}
+#| label: fig-guich
+#| fig.cap: "Results for L.
+guichenoti.
+A) Predicted probability of choosing the correct feeder first over trials.
+The lines represent the mean predicted probability of choosing the correct feeder first, and the shaded areas represent the standard deviation of the mean; both obtained by using the slope and intercept estimates from the posterior distributions.
+The different colours represent the different treatments.
+B) Distribution of the estimates of the slopes per each treatment.
+The x-axis represents the estimates of the slopes, and the y-axis represents the density of the estimates.
+The different colours represent the different treatments."
+source(here("R", "func.R"))
+# Create the dfs for the probability plot A) (df_prob)
+#
+df_guichA <- df_fig(as.data.frame(guich), "L. guichenoti") %>%
+  mutate(Trial = gsub("X", "", Trial)) %>%
+  mutate(Trial = as.numeric(Trial)) %>%
+  group_by(Trial, Treatment, Species) %>%
+  summarize(
+    Mean_Predicted_prob = mean(Value),
+    SE_Predicted_prob = sd(Value)
+    ) %>%
+  ungroup() %>%
+  mutate(
+    Treatment = factor(Treatment,
+                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
+    ) %>%
+    select(-Species) %>%
+data.frame()
+#
+# Create the df for the violin plots in plot B) (df_violin)
+guichB_list <- list(
+  'CORT-Cold' = guich_CORTCold,
+  'Control-Cold' = guich_ControlCold,
+  'CORT-Hot' = guich_CORTHot,
+  'Control-Hot' = guich_ControlHot)
+df_guichB1 <- data.frame(
+  Value = unlist(guichB_list),
+  Treatment = factor(rep(names(guichB_list), each = length(guich_CORTCold)))
+)
+#
+# Create the df for the points and bars in plot B) (df_points)
+df_guichB2 <- df_guichB1 %>%
+  group_by(Treatment) %>%
+  summarize(
+    Mean = mean(Value),
+    SE = (sd(Value)/sqrt(length(Value))),
+    SD = sd(Value)
+  ) %>%
+  ungroup() %>%
+  mutate(
+    Treatment = factor(Treatment,
+                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot"))
+  ) %>%
+  data.frame()
+# Make plot
+fig_guich <- plotting(df_prob = df_guichA, df_violin = df_guichB1, df_points = df_guichB2)
+ggsave("./output/figures/fig_guich.png", plot=fig_guich, width = 20, height = 10, units = "cm", dpi = 3000)
+knitr::include_graphics("./output/figures/fig_guich.png")
+```
+
+Finally, when all individuals from all the treatments were pooled together and species were compared, there were not significant differences in the estimated slopes (_L.
+delicata_ - _L.
+guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`, p-value = `r format_p(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`).
 

### 2024-02-29 .vdoc.r

@@ -1,470 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: fig-Methods
-#| fig.cap: "Experimental design of early environment manipulation and learning tasks. Stages 1-3 indicate the different phases of the habituation phase. In the associative and reversal tasks, white lids show the ramps where the food reward was not accessible."
-
-knitr::include_graphics("./Others/BEHFLEX_FIG_1.svg")
-
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: cleandata
-# Obtain the main df using "./R/1_data_process.R"
-source(here("R", "1_data_process.R"))
-#
-#
-#
-#| label: sampleSize
-# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
-source(here("R", "func.R"))
-#
-specie <- c("delicata", "guichenoti")
-hormone <- c("CORT", "Control")
-temperature <- c("Cold", "Hot")
-#
-n_list <- list()
-#
-for(i in 1:length(specie)){
-  for(k in 1:length(hormone)){
-    for(l in 1:length(temperature)){
-      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
-      }
-    }
-  }
-#
-#
-#
-#
-#
-#| label: models
-# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
-source(here("R", "func.R"))
-# Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
-## A) L. delicata
[…]

### 2024-02-29 R/func.r

@@ -183,27 +183,57 @@ df_fig <- function(df, specie){
 }
 ####################
 ####################
-# Function to create the plot
+# Function to create the prob_plot
 #' @title plotting
-#' @param df to select the df
-plotting <- function(df){
-  plot <- ggplot(df, aes(x = Trial, y = Mean_Predicted_prob, color = Treatment)) +
+#' @param df_prob to select the df for probability (plot A)
+#' @param df_violin to select the df for the violin plot (plot B)
+#' @param df_points to select the df for the points and geom_bars (plot B)
+plotting <- function(df_prob, df_violin, df_points){
+  # First part of the plot (A), the probabilities of choosing right over trial
+  plotA <- ggplot(df_prob, aes(x = Trial, y = Mean_Predicted_prob, color = Treatment)) +
   geom_line(linewidth = 1) +
-  scale_color_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="cyan", "CORT-Hot"="black", "Control-Hot"="#616161")) +
+  scale_color_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="cyan", "CORT-Hot"="black", "Control-Hot"="#a2a2a2")) +
   geom_ribbon(aes(ymin = Mean_Predicted_prob - SE_Predicted_prob, ymax = Mean_Predicted_prob + SE_Predicted_prob, fill = Treatment), color = NA, alpha = 0.075) + 
-  scale_fill_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="cyan", "CORT-Hot"="black", "Control-Hot"="#616161")) +
+  scale_fill_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="cyan", "CORT-Hot"="black", "Control-Hot"="#a2a2a2")) +
   theme_classic() +
-  facet_wrap(Species ~ ., scale = "free_x", ncol= 1, strip.position = "right") +
-  theme(strip.placement = "outside") +
-  theme(strip.background = element_blank()) +
   labs(y = "Predicted probability of correct choice", x = "Trial") +
   theme(plot.margin = margin(5.5, 5.5, 5.5, 5.5, "mm")) +
   theme(
     axis.title = element_text(size = 15, family = "Times"),
     axis.text = element_text(size = 10, family = "Times"),
+    legend.position = "none"
+  ) 
+  #
+  # Second part of the plot (B), the slope estimates of each treatment
[…]

### 2024-02-29 R/func.r
Updates

@@ -199,7 +199,7 @@ plotting <- function(df_prob, df_violin, df_points){
   labs(y = "Predicted probability of correct choice", x = "Trial") +
   theme(plot.margin = margin(5.5, 5.5, 5.5, 5.5, "mm")) +
   theme(
-    axis.title = element_text(size = 15, family = "Times"),
+    axis.title = element_text(size = 12, family = "Times"),
     axis.text = element_text(size = 10, family = "Times"),
     legend.position = "none"
   ) 

### 2024-02-29 ms.qmd
Updates

@@
 For _L.
-delicata_, we did not find any significant effects of the hormone (Control - CORT = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`) (see @fig-deli).
+delicata_, we did not find any significant effects of the hormone (Control - CORT = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`, p-value = `r format_p(pmcmc((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`) (see @fig-deli).
 
@@
 The x-axis represents the estimates of the slopes, and the y-axis represents the density of the estimates.
-The different colours represent the different treatments."
+The different colours represent the different treatments.
+Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
 source(here("R", "func.R"))
@@
 For _L.
-guichenoti_, we did not find any significant effects of the hormone (Control - CORT = `r format_dec(mean((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) (@fig-guich).
+guichenoti_, we did not find any significant effects of the hormone (Control - CORT = `r format_dec(mean((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`, p-value = `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) (@fig-guich).
 

### 2024-03-01 ms.qmd
Updates

@@
 Behavioural flexibility describes the ability of individuals to adjust behaviour adaptively in response to internal or external changes in the environment [@brown2010behavioral].
-It comprises a suite of behavioural aspects like problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral]; and it is predicted to be crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can].
-Generally, species with greater behavioural flexibility are more likely to survive and establish in new habitats because behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can].
+It comprises a suite of behavioural aspects like problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral]; all cognitive abilities predicted to be crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can].
+Species with greater behavioural flexibility are expected to be more likely to survive and establish in new habitats because behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can].
 For instance, in closely related bird species successful invaders show a higher frequency of foraging innovations [@sol2000behavioural].
@@
 We performed the analyses for each species separately.
-We fitted a total of two different Bayesian multilevel models using the brm function from the _brms_ package [@burkner2017brms] using the R extension (version 2.8.2) [@R] for Visual Studio Code.
-We run four parallel MCMC chains of 3000 iterations for each model, with a warmup period of 1000 iterations.
-We used Choice - whether the individual chose correct (1) or not (0) - as the response variable, and trial, hormone (CORT versus Control), incubation temperature (Cold versus Hot), and their interaction as fixed factors.
+We fitted two different Bayesian multilevel models using the brm function from the _brms_ package [@burkner2017brms] using in R extension (version 2.8.2) [@R].
+We ran four parallel MCMC chains of 3000 iterations for each model, with a warmup period of 1000 iterations.
+We modelled correct choices [correct (1) or not (0)] as the response variable, and trial, hormone (CORT versus Control), incubation temperature (Cold versus Hot), and their interaction as fixed factors.
 We included a random intercept and slope (trial) for each lizard in our models.
 We used the posterior distributions of parameters from these models to test for differences in learning rate between treatments and species.
-Learning slopes were obtained using the estimates of the variable trial per each level of the hormone-temperature interaction (Treatments); values greater than zero were considered as evidence of learning, while those less or equal to zero were not.
-We used the pmcmc method to test whether those slopes or the comparisons between treatments (e.g.
-slope for CORT-Cold lizards minus CORT-Hot lizards) or species differed from zero (two-tailed tests).
-We considered statistical significance if p-value < 0.05.
+Learning slopes were obtained using the ‘trial’ estimates and its interaction with hormone and temperature treatments.
+Slope estimates greater than zero were considered as evidence of learning, while those less or equal to zero were not.
+We calculated the probability that slopes or contrasts between slopes differed from zero (pmcmc) using the posterior distributions.
+We considered statistical significance if p~mcmc~  < 0.05.
 
@@
 Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
-All p-values were obtained using pmcmc and tested the hypothesis that the mean equals zero.
-In bold, those values that are significant (p-value <0.05)"
+All pmcmc tested the hypothesis that the mean equals zero.
+In bold, those values that are significant (pmcmc <0.05)"
 source(here("R", "func.R"))
@@
 treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
-values <- c("Mean", "95% CI", "p-value")
-# Building the vectors for estimated means, co.intervals(95%), and p-values for the slopes obtained from posteriors.
-p-values are obtained using pmcmc function (see func.R), assuming a two-tailed test that testes the hypothesis that the value (slopes in this case) is 0.
+values <- c("Mean", "95% CI", "pmcmc")
+# Building the vectors for estimated means, co.intervals(95%), and pmcmc for the slopes obtained from posteriors, assuming a two-tailed test that testes the hypothesis that the value (slopes in this case) is 0.
 #First get estimates for both tasks
@@
 #
-# Then get the mean, co.intervals(95%), and p-values
+# Then get the mean, co.intervals(95%), and pmcmc
 mean <- format_dec(sapply(estimates, mean), 3)
@@
 intervals <- paste(interval_025, interval_975, sep = " , ")
-pvalue <- format_p(sapply(estimates, pmcmc), 4)
+pmcmc <- format_p(sapply(estimates, pmcmc), 4)
 #
@@
   CI = rep(intervals, each = 1),
-  PValue = rep(pvalue, each = 1)
+  pmcmc = rep(pmcmc, each = 1)
 )
@@
 new_table_df <- merge(table_df, n_df) %>%
-  rename('p-value' = 'PValue', '95% CI' = 'CI') %>% #Change the names of the columns for the table
-  select(Specie, Treatment, Mean, `95% CI`, `p-value`, n) %>% #To order the columns in the way I want for the table
+  rename('pmcmc' = 'pmcmc', '95% CI' = 'CI') %>% #Change the names of the columns for the table
+  select(Specie, Treatment, Mean, `95% CI`, `pmcmc`, n) %>% #To order the columns in the way I want for the table
   mutate(Specie = factor(Specie,
@@
 real_table <- flextable(new_table_df) %>%
-    bold(~ `p-value` < 0.05, ~ `p-value` + Mean + `95% CI`) %>%
+    bold(~ `pmcmc` < 0.05, ~ `pmcmc` + Mean + `95% CI`) %>%
     set_table_properties(width = 1) %>%
@@
                       `95% CI` = "95% CI",
-                      `p-value` = "p-value") %>%
+                      `pmcmc` = "pmcmc") %>%
     italic(i= c(1, 5), j = 1, italic = TRUE, part = "body") %>% # To have names of species in italics
@@
 
-We found that the learning slopes for all treatments and species were higher from zero (@tbl-data), but we did not find any difference between treatments or species in the learning rate.  
+Both species learnt across all treatments  (?@tbl-data), but we did not find any difference between treatments or species in the rate of learning.
 For _L.
-delicata_, we did not find any significant effects of the hormone (Control - CORT = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`, p-value = `r format_p(pmcmc((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`) (see @fig-deli).
+delicata_, hormone treatment (Control - CORT = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-deli).
+We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`, p~mcmc~ = `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L.
+guichenoti_ (see @fig-guich).
 
@@
 
-For _L.
-guichenoti_, we did not find any significant effects of the hormone (Control - CORT = `r format_dec(mean((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`, p-value = `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) (@fig-guich).
-
 ```{r, fig-guich}
@@
 
-Finally, when all individuals from all the treatments were pooled together and species were compared, there were not significant differences in the estimated slopes (_L.
+Finally, when all individuals from all the treatments were pooled together and species were compared, there were not significant differences in the estimated slopes (Mean learning slope _L.
+delicata_ = `r format_dec(mean(deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot), 3)`, 95% CI = [`r format_dec(quantile(mean(deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot), 0.025), 3)`, `r format_dec(quantile(mean(deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot), 0.975), 3)`]; Mean learning slope _L.
+guichenoti_ = `r format_dec(mean(guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot), 3)`, 95% CI = [`r format_dec(quantile(mean(guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot), 0.025), 3)`, `r format_dec(quantile(mean(guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot), 0.975), 3)`]; _L.
 delicata_ - _L.
-guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`, p-value = `r format_p(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`).
+guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`).
 
@@
 treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
-values <- c("Mean", "95% CI", "p-value")
-# Building the vectors for estimated means, co.intervals(95%), and p-values for the slopes obtained from posteriors.
-p-values are obtained using pmcmc function (see func.R), assuming a two-tailed test that testes the hypothesis that the value (slopes in this case) is 0.
+values <- c("Mean", "95% CI", "pmcmc")
+# Building the vectors for estimated means, co.intervals(95%), and pmcmcm for the slopes obtained from posteriors assuming a two-tailed test that testes the hypothesis that the value (slopes in this case) is 0.
 #First get estimates for both tasks
@@
 #
-# Then get the mean, co.intervals(95%), and p-values
+# Then get the mean, co.intervals(95%), and pmcmc
 mean_2 <- format_dec(sapply(estimates_2, mean), 3)
@@
 intervals_2 <- paste(interval_025_2, interval_975_2, sep = " , ")
-pvalue_2 <- format_p(sapply(estimates_2, pmcmc), 4)
+pmcmc_2 <- format_p(sapply(estimates_2, pmcmc), 4)
 #
@@
   CI = rep(intervals_2, each = 1),
-  PValue = rep(pvalue_2, each = 1)
+  pmcmc = rep(pmcmc_2, each = 1)
 )
@@
 new_table_df_2 <- merge(table_df_2, n_df_2) %>%
-  rename('p-value' = 'PValue', '95% CI' = 'CI') %>% #Change the names of the columns for the table
-  select(Specie, Treatment, Mean, `95% CI`, `p-value`, n) %>% #To order the columns in the way I want for the table
+  rename('pmcmc' = 'pmcmc', '95% CI' = 'CI') %>% #Change the names of the columns for the table
+  select(Specie, Treatment, Mean, `95% CI`, `pmcmc`, n) %>% #To order the columns in the way I want for the table
   mutate(Specie = factor(Specie,
@@
 real_table_2 <- flextable(new_table_df_2) %>%
-    bold(~ `p-value` < 0.05, ~ `p-value` + Mean + `95% CI`) %>%
+    bold(~ `pmcmc` < 0.05, ~ `pmcmc` + Mean + `95% CI`) %>%
     set_table_properties(width = 1) %>%
@@
                       `95% CI` = "95% CI",
-                      `p-value` = "p-value") %>%
+                      `pmcmc` = "pmcmc") %>%
     italic(i = c(1,5), j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics

### 2024-03-01 R/func.r

@@ -91,7 +91,7 @@ return(new_df)
 }
 ####################
 ####################
-# Estimate p-values using pmcm
+# Estimate pmcm
 #' @title pMCMC Function
 #' @param x The vector for the posterior distribution. Note that this will test the null hypothesis that the parameter of interest is significantly different from 0. 
 #' @param null A numeric value decsribing what the null hypothesis should be

### 2024-03-01 ms.qmd
Updates

@@
 #| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot)
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
 ```
@@
 
-```{r, tbl-data, results='asis'}
-#| label: tbl-data
-#| tbl-cap: "Estimates of Reversal learning slope for all the different treatments per each task, species, and group.
-Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
-All pmcmc tested the hypothesis that the mean equals zero.
-In bold, those values that are significant (pmcmc <0.05)"
-source(here("R", "func.R"))
-#
-############################## CREATING BIG DF FOR TABLE ##############################
-# Building the vectors for titles of rows and columns
-specie <- c("L. delicata", "L. guichenoti")
-treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
-values <- c("Mean", "95% CI", "pmcmc")
-# Building the vectors for estimated means, co.intervals(95%), and pmcmc for the slopes obtained from posteriors, assuming a two-tailed test that testes the hypothesis that the value (slopes in this case) is 0.
-#First get estimates for both tasks
-estimates <- list(
-  deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot, 
-  guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot
-)
-#
-# Then get the mean, co.intervals(95%), and pmcmc
-mean <- format_dec(sapply(estimates, mean), 3)
-interval_025 <- format_dec(sapply(estimates, function(x) quantile(x,0.025)), 3)
-interval_975 <- format_dec(sapply(estimates, function(x) quantile(x,0.975)), 3)
-intervals <- paste(interval_025, interval_975, sep = " , ")
-pmcmc <- format_p(sapply(estimates, pmcmc), 4)
-#
-# Building the df
-table_df <- data.frame(
-  Specie = rep(specie, each = length(treatments)),
-  Treatment = rep(rep(treatments, each = 1), times = length(specie)),
-  Mean = rep(mean, each = 1),
-  CI = rep(intervals, each = 1),
-  pmcmc = rep(pmcmc, each = 1)
-)
-#
-write.csv(table_df, file= "./output/Checking/df.csv")
-#
-############################## ADDING SAMPLE SIZE TO DF FOR TABLE ##############################
-# Make n_list into a df
-n_df <- as.data.frame(do.call(rbind, n_list)) %>%
-  rename("n" = V1) %>%
-  rownames_to_column("model") %>%
-  separate(model, into = c("Specie", "cort", "temp"), sep = "_") %>%
-  unite("Treatment", c("cort", "temp"), sep = "-") %>%
-  mutate(Specie = factor(Specie,
-                  labels = c(delicata = "L. delicata", guichenoti = "L. guichenoti")),
-        Treatment = factor(Treatment,
-                   levels = c("CORT-Cold", "Control-Cold", "CORT-Hot","Control-Hot")))
-# Estimate total sample size per species and number of observations (this will allow to include this data in the first column of the table)
-n_deli <- n_list$delicata_CORT_Cold+n_list$delicata_Control_Cold+n_list$delicata_CORT_Hot+n_list$delicata_Control_Hot
-ob_deli <- sum(clean_df$species == "delicata", na.rm = TRUE)
-n_guich <- n_list$guichenoti_CORT_Cold+n_list$guichenoti_Control_Cold+n_list$guichenoti_CORT_Hot+n_list$guichenoti_Control_Hot
-ob_guich <- sum(clean_df$species == "guichenoti", na.rm = TRUE)
-# Merge both dfs, put sample size together with the treatment, and organize the new df to make it look like the table
-new_table_df <- merge(table_df, n_df) %>%
-  rename('pmcmc' = 'pmcmc', '95% CI' = 'CI') %>% #Change the names of the columns for the table
-  select(Specie, Treatment, Mean, `95% CI`, `pmcmc`, n) %>% #To order the columns in the way I want for the table
-  mutate(Specie = factor(Specie,
-                  levels = c("L. delicata", "L. guichenoti")),
-        Treatment = factor(Treatment, 
-                  levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")))%>%
-  arrange(Specie, Treatment) %>% # To arrange the rows the way I want
-  unite("Treatment", c("Treatment", "n"), sep = " (n = ") %>%
-  mutate(Treatment = paste0(Treatment, ")"))
-write.csv(new_table_df, file= "./output/Checking/new_table_data.csv")
-#
-############################## MAKING THE TABLE ##############################
-## Table format
-set_flextable_defaults(
- font.family = "Times New Roman",
- fint.size = 10)
-# Split the table_data df by task
-real_table <- flextable(new_table_df) %>%
-    bold(~ `pmcmc` < 0.05, ~ `pmcmc` + Mean + `95% CI`) %>%
-    set_table_properties(width = 1) %>%
-    align(align="center", part="all") %>% 
-    set_header_labels(Mean = "Mean",
-                      `95% CI` = "95% CI",
-                      `pmcmc` = "pmcmc") %>%
-    italic(i= c(1, 5), j = 1, italic = TRUE, part = "body") %>% # To have names of species in italics
-    flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
-    flextable::compose(i = 2, j = 1, value = as_paragraph(sprintf("N = %d", n_deli)), part = "body") %>% # To write the delicata sample size
-    flextable::compose(i = 6, j = 1, value = as_paragraph(sprintf("N = %d", n_guich)), part = "body") %>% # To write the guichenoti sample size
-    flextable::compose(i = 3, j = 1, value = as_paragraph(sprintf("Obs = %d", ob_deli)), part = "body") %>% # To write the delicata total observations
-    flextable::compose(i = 7, j = 1, value = as_paragraph(sprintf("Obs = %d", ob_guich)), part = "body") %>% # To write the guichenoti total observations
-    hline(i = 4, j = c(1:5), part = "body") %>% # To make some horizontal lines
-    autofit() 
-knitr::knit_print(real_table)
-```
+Both species learnt across all treatments (@fig-results B, D), but we did not find any difference between treatments or species in the rate of learning.
+For _L.
+delicata_, hormone treatment (Control - CORT = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B).
+We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`, p~mcmc~ = `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L.
+guichenoti_ (see @fig-results C, D).
 
-Both species learnt across all treatments  (?@tbl-data), but we did not find any difference between treatments or species in the rate of learning.
-For _L.
-delicata_, hormone treatment (Control - CORT = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-deli).
-We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`, p~mcmc~ = `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L.
-guichenoti_ (see @fig-guich).
-
-```{r, fig-deli}
-#| label: fig-deli
+```{r, fig-results}
+#| label: fig-results
 #| fig.cap: "Results for L.
-delicata.
-A) Predicted probability of choosing the correct feeder first over trials.
+delicata (A,B) and L.
+guichenoti (C, D).
+A, C) Predicted probability of choosing the correct feeder first over trials.
 The lines represent the mean predicted probability of choosing the correct feeder first, and the shaded areas represent the standard deviation of the mean; both obtained by using the slope and intercept estimates from the posterior distributions.
 The different colours represent the different treatments.
-B) Distribution of the estimates of the slopes per each treatment.
+B, D) Distribution of the estimates of the slopes per each treatment.
 The x-axis represents the estimates of the slopes, and the y-axis represents the density of the estimates.
@@
 source(here("R", "func.R"))
-# Create the dfs for the probability plot A) (df_prob)
-#
-df_deliA <- df_fig(as.data.frame(deli), "L. delicata") %>%
-  mutate(Trial = gsub("X", "", Trial)) %>%
-  mutate(Trial = as.numeric(Trial)) %>%
-  group_by(Trial, Treatment, Species) %>%
-  summarize(
-    Mean_Predicted_prob = mean(Value),
-    SE_Predicted_prob = sd(Value)
-    ) %>%
-  ungroup() %>%
-  mutate(
-    Treatment = factor(Treatment,
-                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
-    ) %>%
-    select(-Species) %>%
-data.frame()
+# Create the dfs for the probability plot A and C) (df_prob)
+# L. delicata
+df_deliprob <- df_plotAC("deli")
+# L. guichenoti
+df_guichprob <- df_plotAC("guich")
 #
 # Create the df for the violin plots in plot B) (df_violin)
-deliB_list <- list(
-  'CORT-Cold' = deli_CORTCold,
-  'Control-Cold' = deli_ControlCold,
-  'CORT-Hot' = deli_CORTHot,
-  'Control-Hot' = deli_ControlHot)
-df_deliB1 <- data.frame(
-  Value = unlist(deliB_list),
-  Treatment = factor(rep(names(deliB_list), each = length(deli_CORTCold)))
-)
+# L. delicata
+df_deliV <- df_plotBD1("deli")
+# L. guichenoti
+df_guichV <- df_plotBD1("guich")
 #
 # Create the df for the points and bars in plot B) (df_points)
-df_deliB2 <- df_deliB1 %>%
-  group_by(Treatment) %>%
-  summarize(
-    Mean = mean(Value),
-    SE = (sd(Value)/sqrt(length(Value))),
-    SD = sd(Value)
-  ) %>%
-  ungroup() %>%
-  mutate(
-    Treatment = factor(Treatment,
-                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot"))
-  ) %>%
-  data.frame()
-# Make plot
-fig_deli <- plotting(df_prob = df_deliA, df_violin = df_deliB1, df_points = df_deliB2)
-ggsave("./output/figures/fig_deli.png", plot=fig_deli, width = 20, height = 10, units = "cm", dpi = 3000)
+# L. delicata
+df_deliP <- df_plotBD2("deli")
+# L. guichenoti
+df_guichP <- df_plotBD2("guich")
+#
+#
+# Make plots deli and guich
+source(here("R", "func.R"))
+fig_deli <- plotting(sp = "deli", df_prob = df_deliprob, df_violin = df_deliV, df_points = df_deliP)
+fig_guich <- plotting(sp = "guich", df_prob = df_guichprob, df_violin = df_guichV, df_points = df_guichP)
+# Combine plots of both species into the final figure
+fig_results <- plot_grid(fig_deli, fig_guich, ncol = 1)
+ggsave("./output/figures/fig_results.png", plot=fig_results, width = 25, height = 18, units = "cm", dpi = 600)
 knitr::include_graphics("./output/figures/fig_deli.png")
-```
-
-```{r, fig-guich}
-#| label: fig-guich
-#| fig.cap: "Results for L.
-guichenoti.
-A) Predicted probability of choosing the correct feeder first over trials.
-The lines represent the mean predicted probability of choosing the correct feeder first, and the shaded areas represent the standard deviation of the mean; both obtained by using the slope and intercept estimates from the posterior distributions.
-The different colours represent the different treatments.
-B) Distribution of the estimates of the slopes per each treatment.
-The x-axis represents the estimates of the slopes, and the y-axis represents the density of the estimates.
-The different colours represent the different treatments.
-Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
-source(here("R", "func.R"))
-# Create the dfs for the probability plot A) (df_prob)
-#
-df_guichA <- df_fig(as.data.frame(guich), "L. guichenoti") %>%
-  mutate(Trial = gsub("X", "", Trial)) %>%
-  mutate(Trial = as.numeric(Trial)) %>%
-  group_by(Trial, Treatment, Species) %>%
-  summarize(
-    Mean_Predicted_prob = mean(Value),
-    SE_Predicted_prob = sd(Value)
-    ) %>%
-  ungroup() %>%
-  mutate(
-    Treatment = factor(Treatment,
-                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
-    ) %>%
-    select(-Species) %>%
-data.frame()
-#
-# Create the df for the violin plots in plot B) (df_violin)
-guichB_list <- list(
-  'CORT-Cold' = guich_CORTCold,
-  'Control-Cold' = guich_ControlCold,
-  'CORT-Hot' = guich_CORTHot,
-  'Control-Hot' = guich_ControlHot)
-df_guichB1 <- data.frame(
-  Value = unlist(guichB_list),
-  Treatment = factor(rep(names(guichB_list), each = length(guich_CORTCold)))
-)
-#
-# Create the df for the points and bars in plot B) (df_points)
-df_guichB2 <- df_guichB1 %>%
-  group_by(Treatment) %>%
-  summarize(
-    Mean = mean(Value),
-    SE = (sd(Value)/sqrt(length(Value))),
-    SD = sd(Value)
-  ) %>%
-  ungroup() %>%
-  mutate(
-    Treatment = factor(Treatment,
-                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot"))
-  ) %>%
-  data.frame()
-# Make plot
-fig_guich <- plotting(df_prob = df_guichA, df_violin = df_guichB1, df_points = df_guichB2)
-ggsave("./output/figures/fig_guich.png", plot=fig_guich, width = 20, height = 10, units = "cm", dpi = 3000)
-knitr::include_graphics("./output/figures/fig_guich.png")
 ```
@@
 
-#### Results employing only those individuals that passed a learning criterion of 80% correct choices in the last 10 trials of the associative task
+#### Slopes estimates per treatment and species for the original database
+```{r, tbl-data, results='asis'}
+#| label: tbl-data
+#| tbl-cap: "Estimates of Reversal learning slope for all the different treatments per each task, species, and group.
+Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
+All pmcmc tested the hypothesis that the mean equals zero.
+In bold, those values that are significant (pmcmc <0.05)"
+source(here("R", "func.R"))
+#
+############################## CREATING BIG DF FOR TABLE ##############################
+# Building the vectors for titles of rows and columns
+specie <- c("L. delicata", "L. guichenoti")
+treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
+values <- c("Mean", "95% CI", "pmcmc")
+# Building the vectors for estimated means, co.intervals(95%), and pmcmc for the slopes obtained from posteriors, assuming a two-tailed test that testes the hypothesis that the value (slopes in this case) is 0.
+#First get estimates for both tasks
+estimates <- list(
+  deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot, 
+  guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot
+)
+#
+# Then get the mean, co.intervals(95%), and pmcmc
+mean <- format_dec(sapply(estimates, mean), 3)
+interval_025 <- format_dec(sapply(estimates, function(x) quantile(x,0.025)), 3)
+interval_975 <- format_dec(sapply(estimates, function(x) quantile(x,0.975)), 3)
+intervals <- paste(interval_025, interval_975, sep = " , ")
+Pmcmc <- format_p(sapply(estimates, pmcmc), 4)
+#
+# Building the df
+table_df <- data.frame(
+  Specie = rep(specie, each = length(treatments)),
+  Treatment = rep(rep(treatments, each = 1), times = length(specie)),
+  Mean = rep(mean, each = 1),
+  CI = rep(intervals, each = 1),
+  Pmcmc = rep(Pmcmc, each = 1)
+)
+#
+write.csv(table_df, file= "./output/Checking/df.csv")
+#
+############################## ADDING SAMPLE SIZE TO DF FOR TABLE ##############################
+# Make n_list into a df
+n_df <- as.data.frame(do.call(rbind, n_list)) %>%
+  rename("n" = V1) %>%
+  rownames_to_column("model") %>%
+  separate(model, into = c("Specie", "cort", "temp"), sep = "_") %>%
+  unite("Treatment", c("cort", "temp"), sep = "-") %>%
+  mutate(Specie = factor(Specie,
+                  labels = c(delicata = "L. delicata", guichenoti = "L. guichenoti")),
+        Treatment = factor(Treatment,
+                   levels = c("CORT-Cold", "Control-Cold", "CORT-Hot","Control-Hot")))
+# Estimate total sample size per species and number of observations (this will allow to include this data in the first column of the table)
+n_deli <- n_list$delicata_CORT_Cold+n_list$delicata_Control_Cold+n_list$delicata_CORT_Hot+n_list$delicata_Control_Hot
+ob_deli <- sum(clean_df$species == "delicata", na.rm = TRUE)
+n_guich <- n_list$guichenoti_CORT_Cold+n_list$guichenoti_Control_Cold+n_list$guichenoti_CORT_Hot+n_list$guichenoti_Control_Hot
+ob_guich <- sum(clean_df$species == "guichenoti", na.rm = TRUE)
+# Merge both dfs, put sample size together with the treatment, and organize the new df to make it look like the table
+new_table_df <- merge(table_df, n_df) %>%
+  rename('pmcmc' = 'Pmcmc', '95% CI' = 'CI') %>% #Change the names of the columns for the table
+  select(Specie, Treatment, Mean, `95% CI`, `pmcmc`, n) %>% #To order the columns in the way I want for the table
+  mutate(Specie = factor(Specie,
+                  levels = c("L. delicata", "L. guichenoti")),
+        Treatment = factor(Treatment, 
+                  levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")))%>%
+  arrange(Specie, Treatment) %>% # To arrange the rows the way I want
+  unite("Treatment", c("Treatment", "n"), sep = " (n = ") %>%
+  mutate(Treatment = paste0(Treatment, ")"))
+write.csv(new_table_df, file= "./output/Checking/new_table_data.csv")
+#
+############################## MAKING THE TABLE ##############################
+## Table format
+set_flextable_defaults(
+ font.family = "Times New Roman",
+ fint.size = 10)
+# Split the table_data df by task
+real_table <- flextable(new_table_df) %>%
+    bold(~ `pmcmc` < 0.05, ~ `pmcmc` + Mean + `95% CI`) %>%
+    set_table_properties(width = 1) %>%
+    align(align="center", part="all") %>% 
+    set_header_labels(Mean = "Mean",
+                      `95% CI` = "95% CI",
+                      `pmcmc` = "pmcmc") %>%
+    italic(i= c(1, 5), j = 1, italic = TRUE, part = "body") %>% # To have names of species in italics
+    flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
+    flextable::compose(i = 2, j = 1, value = as_paragraph(sprintf("N = %d", n_deli)), part = "body") %>% # To write the delicata sample size
+    flextable::compose(i = 6, j = 1, value = as_paragraph(sprintf("N = %d", n_guich)), part = "body") %>% # To write the guichenoti sample size
+    flextable::compose(i = 3, j = 1, value = as_paragraph(sprintf("Obs = %d", ob_deli)), part = "body") %>% # To write the delicata total observations
+    flextable::compose(i = 7, j = 1, value = as_paragraph(sprintf("Obs = %d", ob_guich)), part = "body") %>% # To write the guichenoti total observations
+    hline(i = 4, j = c(1:5), part = "body") %>% # To make some horizontal lines
+    autofit() 
+real_table
+```
+
+#### Slopes estimates per treatment and species employing only those individuals that passed a learning criterion of 80% correct choices in the last 10 trials of the associative task
 
@@
 intervals_2 <- paste(interval_025_2, interval_975_2, sep = " , ")
-pmcmc_2 <- format_p(sapply(estimates_2, pmcmc), 4)
+Pmcmc_2 <- format_p(sapply(estimates_2, pmcmc), 4)
 #
@@
   CI = rep(intervals_2, each = 1),
-  pmcmc = rep(pmcmc_2, each = 1)
+  Pmcmc = rep(Pmcmc_2, each = 1)
 )
@@
 new_table_df_2 <- merge(table_df_2, n_df_2) %>%
-  rename('pmcmc' = 'pmcmc', '95% CI' = 'CI') %>% #Change the names of the columns for the table
+  rename('pmcmc' = 'Pmcmc', '95% CI' = 'CI') %>% #Change the names of the columns for the table
   select(Specie, Treatment, Mean, `95% CI`, `pmcmc`, n) %>% #To order the columns in the way I want for the table

### 2024-03-01 .vdoc.r

@@ -1,0 +1,472 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of early environment manipulation and learning tasks. Stages 1-3 indicate the different phases of the habituation phase. In the associative and reversal tasks, white lids show the ramps where the food reward was not accessible."
+
+knitr::include_graphics("./Others/BEHFLEX_FIG_1.svg")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleandata
+# Obtain the main df using "./R/1_data_process.R"
+source(here("R", "1_data_process.R"))
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(k in 1:length(hormone)){
+    for(l in 1:length(temperature)){
+      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
+      }
+    }
+  }
+#
+#
+#
+#
+#
+#| label: models
+# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
+source(here("R", "func.R"))
+# Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
[…]

### 2024-03-01 R/func.r

@@ -137,11 +137,19 @@ format_p <- function(x, n) {
 }
 ####################
 ####################
-# Function to create each df for the figure
-#' @title df_fig
-#' @param df to select the df
-#' @param specie to add data of the specie
-df_fig <- function(df, specie){
+# Function to create each df for the probability figure (plots A, C Fig-results)
+#' @title df_plotAC
+#' @param sp to select the df, levels are deli or guich
+df_plotAC <- function(sp){
+  if (sp == "deli"){
+      df <- as.data.frame(deli)
+    } else {
+      if(sp == "guich"){
+        df <- as.data.frame(guich)
+      } else {
+        stop("Species not valid")
+      }
+    }
   # Create a vector with treatments
   treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
   # Create new matrix and new dfs
@@ -177,24 +185,125 @@ df_fig <- function(df, specie){
     treat_df$Treatment <- t
     fig_df <- rbind(fig_df, treat_df)
   }
-  # Add species and group information
-  fig_df$Species <- specie
+  # Transform the database for better use
+  fig_df <- fig_df %>%
+  mutate(Trial = gsub("X", "", Trial)) %>%
+  mutate(Trial = as.numeric(Trial)) %>%
+  group_by(Trial, Treatment) %>%
+  summarize(
+    Mean_Predicted_prob = mean(Value),
+    SE_Predicted_prob = sd(Value)
+    ) %>%
+  ungroup() %>%
+  mutate(
+    Treatment = factor(Treatment,
+                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
+    ) %>%
+data.frame()
   return(fig_df)
 }
 ####################
 ####################
-# Function to create the prob_plot
+# Function to create each df for the slopes figure (part of plots B, D Fig-results)
+#' @title df_plotBD1
+#' @param sp to select the df, levels are deli or guich
+df_plotBD1 <- function(sp){
+  if (sp == "deli"){
+      lst <- list('CORT-Cold' = deli_CORTCold,
+                  'Control-Cold' = deli_ControlCold,
+                  'CORT-Hot' = deli_CORTHot,
+                  'Control-Hot' = deli_ControlHot)
+      df_plotBD <- data.frame(Value = unlist(lst),
[…]

### 2024-03-04 ms.qmd
Updates

@@
 Slope estimates greater than zero were considered as evidence of learning, while those less or equal to zero were not.
-We calculated the probability that slopes or contrasts between slopes differed from zero (pmcmc) using the posterior distributions.
+We calculated the probability that slopes or contrasts between slopes differed from zero (p~mcmc~) using the posterior distributions.
 We considered statistical significance if p~mcmc~  < 0.05.
@@
 
-```{r, resultsRev}
-# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task doing the same thing we did in the chunk above.
+```{r, results}
+#| label: results
+# Rename some of the posteriors and make means and sd for the posteriors.
 ## 1) L. delicata
@@
 guich_ControlHot <- (guich$'b_trial_reversal:cortControl:tempHot' + guich$b_trial_reversal + guich$'b_trial_reversal:cortControl' + guich$'b_trial_reversal:tempHot')
+```
+
+```{r, coeficients}
+#| label: coeficients
+# Getting the Cohen's d coeficients of the (below) between treatments and species comparisons using the formula: 
+# d =(mean1 - mean2) / sqrt((sd1^2 + sd2^2)/2)
+# For the estimations of the confidence intervals we used Cohen's standard error based on the formula: se = 1 / sqrt(n1-3 + n2-3)
+# And critical value:
+critical_value <- qnorm((1 + 0.95) / 2)
+## A) L. delicata
+#### A.1.- CORT
+mean_deliControl <- mean(c(deli_ControlCold, deli_ControlHot))
+sd_deliControl <- sd(c(deli_ControlCold, deli_ControlHot))
+mean_deliCORT <- mean(c(deli_CORTCold, deli_CORTHot))
+sd_deliCORT <- sd(c(deli_CORTCold, deli_CORTHot))
+#
+deli_CORTd <- format_dec((mean_deliControl - mean_deliCORT) / sqrt((sd_deliControl^2 + sd_deliCORT^2)/2), 3)
+#
+standard_error <- 1 / sqrt((n_list$delicata_Control_Cold + n_list$delicata_Control_Hot)- 3 + (n_list$delicata_CORT_Cold + n_list$delicata_CORT_Hot) - 3)
+
+#
+#### A.2.- Temperature
+mean_deliCold <- mean(c(deli_ControlCold, deli_CORTCold))
+sd_deliCold <- sd(c(deli_ControlCold, deli_CORTCold))
+mean_deliHot <- mean(c(deli_CORTHot, deli_ControlHot))
+sd_deliHot <- sd(c(deli_CORTHot, deli_ControlHot))
+#
+deli_Tempd <- format_dec((mean_deliHot - mean_deliCold) / sqrt((sd_deliHot^2 + sd_deliCold^2)/2), 3)
+#
+#### A.3.- Interaction
+
+#
+## B) L. guichenoti
+#### B.1.- CORT
+mean_guichControl <- mean(c(guich_ControlCold, guich_ControlHot))
+sd_guichControl <- sd(c(guich_ControlCold, guich_ControlHot))
+mean_guichCORT <- mean(c(guich_CORTCold, guich_CORTHot))
+sd_guichCORT <- sd(c(guich_CORTCold, guich_CORTHot))
+#
+guich_CORTd <- format_dec((mean_guichControl - mean_guichCORT) / sqrt((sd_guichControl^2 + sd_guichCORT^2)/2), 3)
+#
+#### B.2.- Temperature
+mean_guichCold <- mean(c(guich_ControlCold, guich_CORTCold))
+sd_guichCold <- sd(c(guich_ControlCold, guich_CORTCold))
+mean_guichHot <- mean(c(guich_CORTHot, guich_ControlHot))
+sd_guichHot <- sd(c(guich_CORTHot, guich_ControlHot))
+#
+guich_Tempd <- format_dec((mean_guichHot - mean_guichCold) / sqrt((sd_guichHot^2 + sd_guichCold^2)/2), 3)
+#
+#### B.3.- Interaction
+
 ```

### 2024-03-04 .vdoc.r

@@ -94,7 +94,8 @@ write.csv(guich, file= "./output/Checking/guich.csv")
 #
 #
 #
-# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task doing the same thing we did in the chunk above.
+#| label: results
+# Rename some of the posteriors and make means and sd for the posteriors.
 ## 1) L. delicata
 deli_CORTCold <- deli$b_trial_reversal
 deli_ControlCold <- (deli$'b_trial_reversal:cortControl' + deli$b_trial_reversal)
@@ -105,6 +106,58 @@ guich_CORTCold <- guich$b_trial_reversal
 guich_ControlCold <- (guich$'b_trial_reversal:cortControl' + guich$b_trial_reversal)
 guich_CORTHot <- (guich$'b_trial_reversal:tempHot' + guich$b_trial_reversal)
 guich_ControlHot <- (guich$'b_trial_reversal:cortControl:tempHot' + guich$b_trial_reversal + guich$'b_trial_reversal:cortControl' + guich$'b_trial_reversal:tempHot')
+#
+#
+#
+#
+#| label: coeficients
+# Getting the Cohen's d coeficients of the (below) between treatments and species comparisons using the formula: 
+# d =(mean1 - mean2) / sqrt((sd1^2 + sd2^2)/2)
+# For the estimations of the confidence intervals we used Cohen's standard error based on the formula: se = 1 / sqrt(n1-3 + n2-3)
+# And critical value:
+critical_value <- qnorm((1 + 0.95) / 2)
+## A) L. delicata
+#### A.1.- CORT
+mean_deliControl <- mean(c(deli_ControlCold, deli_ControlHot))
+sd_deliControl <- sd(c(deli_ControlCold, deli_ControlHot))
+mean_deliCORT <- mean(c(deli_CORTCold, deli_CORTHot))
+sd_deliCORT <- sd(c(deli_CORTCold, deli_CORTHot))
+#
+deli_CORTd <- format_dec((mean_deliControl - mean_deliCORT) / sqrt((sd_deliControl^2 + sd_deliCORT^2)/2), 3)
+#
[…]

### 2024-03-04 R/func.r

@@ -301,9 +301,9 @@ plotting <- function(sp, df_prob, df_violin, df_points){
   # First part of the plot (A, C), the probabilities of choosing right over trial
   plot1 <- ggplot(df_prob, aes(x = Trial, y = Mean_Predicted_prob, color = Treatment)) +
   geom_line(linewidth = 1) +
-  scale_color_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="#68bde1", "CORT-Hot"="#b52201", "Control-Hot"="#f38778")) +
+  scale_color_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="#68bde1", "CORT-Hot"="#b50101", "Control-Hot"="#fa927d")) +
   geom_ribbon(aes(ymin = Mean_Predicted_prob - SE_Predicted_prob, ymax = Mean_Predicted_prob + SE_Predicted_prob, fill = Treatment), color = NA, alpha = 0.075) + 
-  scale_fill_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="#68bde1", "CORT-Hot"="#b52201", "Control-Hot"="#f38778")) +
+  scale_fill_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="#68bde1", "CORT-Hot"="#b50101", "Control-Hot"="#fa927d")) +
   theme_classic() +
   labs(y = "Predicted probability of correct choice", x = "Trial") +
   theme(plot.margin = margin(5.5, 5.5, 5.5, 5.5, "mm")) +
@@ -316,7 +316,7 @@ plotting <- function(sp, df_prob, df_violin, df_points){
   # Second part of the plot (B, D), the slope estimates of each treatment
   plot2 <- ggplot(df_violin, aes(x = Treatment, y = Value, fill = Treatment)) +
   geom_flat_violin(alpha = 0.5) +
-  scale_fill_manual(values = c("#f38778", "#b52201", "#68bde1", "darkblue")) +
+  scale_fill_manual(values = c("#fa927d", "#b50101", "#68bde1", "darkblue")) +
   geom_point(data = df_points, aes(y = Mean, x = Treatment), position = position_dodge(width = 0.75), color = "black", fill = "black", size = 3) +
   geom_segment(data = df_points, aes(y = Mean - SD, yend = Mean + SD, x = Treatment, xend = Treatment), size = 1.5, color = "black") +
   geom_hline(yintercept = 0, linetype = "dashed", color = "black") +

### 2024-03-04 ms.qmd
Updates

--- 2024-03-01 ms.qmd
@@
 
+```{r, coeficients}
+#| label: coeficients
+# Getting the Cohen's d coeficients of the (below) between treatments and species comparisons using the formula: 
+# d =(mean1 - mean2) / sqrt((sd1^2 + sd2^2)/2)
+# For the estimations of the confidence intervals we used Cohen's standard error based on the formula: se = 1 / sqrt(n1-3 + n2-3)
+# And critical value:
+critical_value <- qnorm((1 + 0.95) / 2)
+## A) L. delicata
+#### A.1.- CORT
+mean_deliControl <- mean(c(deli_ControlCold, deli_ControlHot))
+sd_deliControl <- sd(c(deli_ControlCold, deli_ControlHot))
+mean_deliCORT <- mean(c(deli_CORTCold, deli_CORTHot))
+sd_deliCORT <- sd(c(deli_CORTCold, deli_CORTHot))
+#
+deli_CORTd <- format_dec((mean_deliControl - mean_deliCORT) / sqrt((sd_deliControl^2 + sd_deliCORT^2)/2), 3)
+#
+#### A.2.- Temperature
+mean_deliCold <- mean(c(deli_ControlCold, deli_CORTCold))
+sd_deliCold <- sd(c(deli_ControlCold, deli_CORTCold))
+mean_deliHot <- mean(c(deli_ControlHot, deli_CORTHot))
+sd_deliHot <- sd(c(deli_ControlHot, deli_CORTHot))
+#
+deli_Tempd <- format_dec((mean_deliHot - mean_deliCold) / sqrt((sd_deliHot^2 + sd_deliCold^2)/2), 3)
+#
+#### A.3.- Interaction
+
+#
+## B) L. guichenoti
+#### B.1.- CORT
+mean_guichControl <- mean(c(guich_ControlCold, guich_ControlHot))
+sd_guichControl <- sd(c(guich_ControlCold, guich_ControlHot))
+mean_guichCORT <- mean(c(guich_CORTCold, guich_CORTHot))
+sd_guichCORT <- sd(c(guich_CORTCold, guich_CORTHot))
+#
+guich_CORTd <- format_dec((mean_guichControl - mean_guichCORT) / sqrt((sd_guichControl^2 + sd_guichCORT^2)/2), 3)
+#
+#### B.2.- Temperature
+mean_guichCold <- mean(c(guich_ControlCold, guich_CORTCold))
+sd_guichCold <- sd(c(guich_ControlCold, guich_CORTCold))
+mean_guichHot <- mean(c(guich_ControlHot, guich_CORTHot))
+sd_guichHot <- sd(c(guich_ControlHot, guich_CORTHot))
+#
+guich_Tempd <- format_dec((mean_guichHot - mean_guichCold) / sqrt((sd_guichHot^2 + sd_guichCold^2)/2), 3)
+#
+#### B.3.- Interaction
+
+```
+
 Both species learnt across all treatments (@fig-results B, D), but we did not find any difference between treatments or species in the rate of learning.
 For _L.
-delicata_, hormone treatment (Control - CORT = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B).
+delicata_, hormone treatment (Control - CORT = `r format_dec(mean(deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B).
 We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`, p~mcmc~ = `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L.
@@
 ggsave("./output/figures/fig_results.png", plot=fig_results, width = 25, height = 18, units = "cm", dpi = 600)
-knitr::include_graphics("./output/figures/fig_deli.png")
+knitr::include_graphics("./output/figures/fig_results.png")
 ```

### 2024-03-04 .vdoc.r

@@ -109,7 +109,6 @@ guich_ControlHot <- (guich$'b_trial_reversal:cortControl:tempHot' + guich$b_tria
 #
 #
 #
-#
 #| label: coeficients
 # Getting the Cohen's d coeficients of the (below) between treatments and species comparisons using the formula: 
 # d =(mean1 - mean2) / sqrt((sd1^2 + sd2^2)/2)
@@ -125,14 +124,11 @@ sd_deliCORT <- sd(c(deli_CORTCold, deli_CORTHot))
 #
 deli_CORTd <- format_dec((mean_deliControl - mean_deliCORT) / sqrt((sd_deliControl^2 + sd_deliCORT^2)/2), 3)
 #
-standard_error <- 1 / sqrt((n_list$delicata_Control_Cold + n_list$delicata_Control_Hot)- 3 + (n_list$delicata_CORT_Cold + n_list$delicata_CORT_Hot) - 3)
-
-#
 #### A.2.- Temperature
 mean_deliCold <- mean(c(deli_ControlCold, deli_CORTCold))
 sd_deliCold <- sd(c(deli_ControlCold, deli_CORTCold))
-mean_deliHot <- mean(c(deli_CORTHot, deli_ControlHot))
-sd_deliHot <- sd(c(deli_CORTHot, deli_ControlHot))
+mean_deliHot <- mean(c(deli_ControlHot, deli_CORTHot))
+sd_deliHot <- sd(c(deli_ControlHot, deli_CORTHot))
 #
 deli_Tempd <- format_dec((mean_deliHot - mean_deliCold) / sqrt((sd_deliHot^2 + sd_deliCold^2)/2), 3)
 #
@@ -151,12 +147,17 @@ guich_CORTd <- format_dec((mean_guichControl - mean_guichCORT) / sqrt((sd_guichC
 #### B.2.- Temperature
 mean_guichCold <- mean(c(guich_ControlCold, guich_CORTCold))
 sd_guichCold <- sd(c(guich_ControlCold, guich_CORTCold))
-mean_guichHot <- mean(c(guich_CORTHot, guich_ControlHot))
-sd_guichHot <- sd(c(guich_CORTHot, guich_ControlHot))
+mean_guichHot <- mean(c(guich_ControlHot, guich_CORTHot))
+sd_guichHot <- sd(c(guich_ControlHot, guich_CORTHot))
 #
[…]

### 2024-03-04 ms.qmd
Update ms.qmd

@@
 
-```{r, coeficients}
+```{r, coefficients}
 #| label: coeficients

### 2024-03-08 ms.qmd
Updates

--- 2024-03-04 ms.qmd
@@
 
-```{r, coeficients}
-#| label: coeficients
-# Getting the Cohen's d coeficients of the (below) between treatments and species comparisons using the formula: 
-# d =(mean1 - mean2) / sqrt((sd1^2 + sd2^2)/2)
-# For the estimations of the confidence intervals we used Cohen's standard error based on the formula: se = 1 / sqrt(n1-3 + n2-3)
-# And critical value:
-critical_value <- qnorm((1 + 0.95) / 2)
-## A) L. delicata
-#### A.1.- CORT
-mean_deliControl <- mean(c(deli_ControlCold, deli_ControlHot))
-sd_deliControl <- sd(c(deli_ControlCold, deli_ControlHot))
-mean_deliCORT <- mean(c(deli_CORTCold, deli_CORTHot))
-sd_deliCORT <- sd(c(deli_CORTCold, deli_CORTHot))
-#
-deli_CORTd <- format_dec((mean_deliControl - mean_deliCORT) / sqrt((sd_deliControl^2 + sd_deliCORT^2)/2), 3)
-#
-#### A.2.- Temperature
-mean_deliCold <- mean(c(deli_ControlCold, deli_CORTCold))
-sd_deliCold <- sd(c(deli_ControlCold, deli_CORTCold))
-mean_deliHot <- mean(c(deli_ControlHot, deli_CORTHot))
-sd_deliHot <- sd(c(deli_ControlHot, deli_CORTHot))
-#
-deli_Tempd <- format_dec((mean_deliHot - mean_deliCold) / sqrt((sd_deliHot^2 + sd_deliCold^2)/2), 3)
-#
-#### A.3.- Interaction
-
-#
-## B) L. guichenoti
-#### B.1.- CORT
-mean_guichControl <- mean(c(guich_ControlCold, guich_ControlHot))
-sd_guichControl <- sd(c(guich_ControlCold, guich_ControlHot))
-mean_guichCORT <- mean(c(guich_CORTCold, guich_CORTHot))
-sd_guichCORT <- sd(c(guich_CORTCold, guich_CORTHot))
-#
-guich_CORTd <- format_dec((mean_guichControl - mean_guichCORT) / sqrt((sd_guichControl^2 + sd_guichCORT^2)/2), 3)
-#
-#### B.2.- Temperature
-mean_guichCold <- mean(c(guich_ControlCold, guich_CORTCold))
-sd_guichCold <- sd(c(guich_ControlCold, guich_CORTCold))
-mean_guichHot <- mean(c(guich_ControlHot, guich_CORTHot))
-sd_guichHot <- sd(c(guich_ControlHot, guich_CORTHot))
-#
-guich_Tempd <- format_dec((mean_guichHot - mean_guichCold) / sqrt((sd_guichHot^2 + sd_guichCold^2)/2), 3)
-#
-#### B.3.- Interaction
-
-```
-
 Both species learnt across all treatments (@fig-results B, D), but we did not find any difference between treatments or species in the rate of learning.
 For _L.
-delicata_, hormone treatment (Control - CORT = `r format_dec(mean(deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B).
-We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`, p~mcmc~ = `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L.
-guichenoti_ (see @fig-results C, D).
+delicata_, hormone treatment (Control - CORT = `r format_dec(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold + deli_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc(c(deli_ControlCold, deli_ControlHot) - c(deli_CORTCold, deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc(c(deli_CORTHot, deli_ControlHot) - c(deli_CORTCold, deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(deli_ControlHot - deli_CORTHot) - mean(deli_ControlCold - deli_CORTCold), 3)`, p~mcmc~ = `r format_p(pmcmc(c(deli_ControlHot, deli_CORTHot) - c(deli_ControlCold, deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B).
+We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc(c(guich_ControlCold, guich_ControlHot) - c(guich_CORTCold, guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc(c(guich_CORTHot, guich_ControlHot) - c(guich_CORTCold, guich_ControlCold)),3)`), **or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(guich_ControlHot - guich_CORTHot) - mean(guich_ControlCold - guich_CORTCold), 3)`, p~mcmc~ = `r format_p(pmcmc(mean(guich_ControlHot - guich_CORTHot) - mean(guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L.
+guichenoti_ (see @fig-results C, D).**
 
@@
 Finally, when all individuals from all the treatments were pooled together and species were compared, there were not significant differences in the estimated slopes (Mean learning slope _L.
-delicata_ = `r format_dec(mean(deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot), 3)`, 95% CI = [`r format_dec(quantile(mean(deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot), 0.025), 3)`, `r format_dec(quantile(mean(deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot), 0.975), 3)`]; Mean learning slope _L.
-guichenoti_ = `r format_dec(mean(guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot), 3)`, 95% CI = [`r format_dec(quantile(mean(guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot), 0.025), 3)`, `r format_dec(quantile(mean(guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot), 0.975), 3)`]; _L.
+delicata_ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot), 0.025), 3)`, `r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot), 0.975), 3)`]; Mean learning slope _L.
+guichenoti_ = `r format_dec(mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot), 0.025), 3)`, `r format_dec(quantile(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot), 0.975), 3)`]; _L.
 delicata_ - _L.
-guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`).
+guichenoti_ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, p~mcmc~ = `r format_p(pmcmc(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot) - c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`).
 

### 2024-03-15 ms.qmd
Updates

@@
 Behavioural flexibility describes the ability of individuals to adjust behaviour adaptively in response to internal or external changes in the environment [@brown2010behavioral].
-It comprises a suite of behavioural aspects like problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral]; all cognitive abilities predicted to be crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can].
+It comprises a suite of behavioural aspects like problem-solving and innovation [@brown2010behavioral], that are predicted to be crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can].
 Species with greater behavioural flexibility are expected to be more likely to survive and establish in new habitats because behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can].

### 2024-03-15 ms.qmd
Updates

@@
 Behavioural flexibility describes the ability of individuals to adjust behaviour adaptively in response to internal or external changes in the environment [@brown2010behavioral].
-It comprises a suite of behavioural aspects like problem-solving and innovation [@brown2010behavioral], that are predicted to be crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can].
+It comprises a suite of behavioural aspects like problem-solving and innovation [@brown2010behavioral] predicted to be crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can].
 Species with greater behavioural flexibility are expected to be more likely to survive and establish in new habitats because behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can].
@@
 However, the brain is also sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004] creating uncertainty about how environmental insults faced by early invaders might impact behavioural flexibility and thus the probability of invasion success.
-**BETTER LINK**In this scenario, prenatal glucocorticoids (GCs) and the thermal environment can be salient factors in the study of behavioural flexibility within invasion biology.
-GCs are the main group of hormones related to animals’ response towards alterations in homeostasis [@sapolsky_how_2000] that may become relevant when facing new environments and their new thermal conditions [@Crino_2023].
-In addition, there is evidence that developmental GCs and thermal environment can impact cognition in different taxa [@jonson1976effect; @zhu_prenatal_2004; @amiel_hotter_2012; @lui2017chronic].
-For instance, young Sprague-Dawley rats treated with corticosterone (CORT) - the principal GC in rodents, birds, and reptiles [@Crino_2023] - performed worse than controls in a reversal learning task [@lui2017chronic], while cold incubation temperatures in the eastern three-lined skink resulted in significant impairments with associative and reversal learning [@clark_colour_2014].
-Moreover, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017], an aspect considered essential in successful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
-Here, we studied the interactive effects of prenatal temperature and CORT on behavioural flexibility in two species with distinct histories of invasiveness, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+New environments faced by invasive populations introduce organisms to a plethora of unfamiliar conditions that can entail alterations in homeostasis.
+This disruption triggers a suite of physiological and behavioural responses that are mediated by glucocorticoids (GCs), the "stress"-related hormones [@sapolsky_how_2000].
+These GCs can be transmitted to the offspring and  influence its phenotype through transgenerational effects [@Crino_2023].
+At the same time, other aspects of the environment, such as temperature, can impact the offspring phenotype through direct effects [@noble_developmental_2018].
+As such, GCs and  temperature are predicted to interact to influence the offspring's phenotype.
+In this sense, both factors are known to affect similar aspects of brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017] and also cognitive abilities such as reversal learning [@clark_colour_2014; @lui2017chronic].
+However, the interactive repercussions of prenatal GCs and temperature on behavioural flexibility have not been explored.
+Here, we studied the effects of prenatal temperature and CORT, the main GC in reptiles [@Crino_2023], on behavioural flexibility in two species with distinct histories of invasiveness, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_).
@@
 Personality has been shown to be different between these two species [@chapple_know_2011; @chapple2012can; @bezzina2014does], which could be related to general cognitive differences that are important for invasion success.
-Additionally, early environments are known to affect suites of morphological and behavioural traits differently in each species [**REFS**], but the interactive role of maternal CORT and early temperatures have not yet been explored.
+Additionally, early environments are known to affect suites of morphological and behavioural traits differently in each species [@carrasco2023maternal; @kar2023heritability], but the interactive role of maternal CORT and early temperatures have not yet been explored.
 Differences in the relative impact that early environments have on behavioural flexibility may help explain differing invasion success between the two species.
@@
 delicata_, hormone treatment (Control - CORT = `r format_dec(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold + deli_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc(c(deli_ControlCold, deli_ControlHot) - c(deli_CORTCold, deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc(c(deli_CORTHot, deli_ControlHot) - c(deli_CORTCold, deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(deli_ControlHot - deli_CORTHot) - mean(deli_ControlCold - deli_CORTCold), 3)`, p~mcmc~ = `r format_p(pmcmc(c(deli_ControlHot, deli_CORTHot) - c(deli_ControlCold, deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B).
-We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc(c(guich_ControlCold, guich_ControlHot) - c(guich_CORTCold, guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc(c(guich_CORTHot, guich_ControlHot) - c(guich_CORTCold, guich_ControlCold)),3)`), **or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(guich_ControlHot - guich_CORTHot) - mean(guich_ControlCold - guich_CORTCold), 3)`, p~mcmc~ = `r format_p(pmcmc(mean(guich_ControlHot - guich_CORTHot) - mean(guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L.
-guichenoti_ (see @fig-results C, D).**
+We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc(c(guich_ControlCold, guich_ControlHot) - c(guich_CORTCold, guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc(c(guich_CORTHot, guich_ControlHot) - c(guich_CORTCold, guich_ControlCold)),3)`), **or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(guich_ControlHot - guich_CORTHot) - mean(guich_ControlCold - guich_CORTCold), 3)`, p~mcmc~  `r format_p(pmcmc(mean(guich_ControlHot - guich_CORTHot) - mean(guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L.
+guichenoti_ (see @fig-results C, D).
+(Control-Hot - CORT-Hot = `r format_dec(mean(guich_ControlHot) - mean(guich_CORTHot),3)`; p~mcmc~ = `r format_dec(pmcmc(guich_ControlHot - guich_CORTHot),3)`) or (Control-Cold - CORT-Cold = `r format_dec(mean(guich_ControlCold) - mean(guich_CORTCold),3)`; p~mcmc~ = `r format_dec(pmcmc(guich_ControlCold - guich_CORTCold),3)`)**
 

### 2024-03-15 ms.qmd

@@
 ---
+title: "Early environmental conditions do not impact behavioural flexibility in an invasive and non-invasive lizard species"
+format:
   docx: 
@@
 
+Pablo Recio-Santiago^1^,$\ddagger$ , Dalton L. Leibold^1^, Ondi Crino ^1,2^, Kris Wild^1,3^, Daniel W.A. Noble^1^
+
+^1^ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2601, Australia &NewLine;
+^2^ Flinder's University, Adelaide, SA 5001, Australia &NewLine;
+^3^ Melbourne University, Melbourne, VIC 3000, Australia &NewLine;
+$\ddagger$ Corresponding author: pablo.reciosantiago@anu.edu.au &NewLine;
+
+## Abstract
+
 ## Introduction
 Behavioural flexibility describes the ability of individuals to adjust behaviour adaptively in response to internal or external changes in the environment [@brown2010behavioral].
-It comprises a suite of behavioural aspects like problem-solving and innovation [@brown2010behavioral] predicted to be crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can].
+It comprises a suite of behaviours, including problem-solving and innovation [@brown2010behavioral], that are predicted to be crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can].
 Species with greater behavioural flexibility are expected to be more likely to survive and establish in new habitats because behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can].
 For instance, in closely related bird species successful invaders show a higher frequency of foraging innovations [@sol2000behavioural].
-According to the 'adaptive flexibility hypothesis', behavioural flexibility is most relevant during introduction, establishment, and spread of an invasive population [@wright2010behavioral; @chapple2012can; @szabo2020can].
+According to the 'adaptive flexibility hypothesis', behavioural flexibility is most relevant during introduction, establishment, and the spread of an invasive population [@wright2010behavioral; @chapple2012can; @szabo2020can].
 In mammals, birds, reptiles and amphibians, relative brain size has been shown to be a good predictor of behavioural flexibility and invasive success [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
 However, the brain is also sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004] creating uncertainty about how environmental insults faced by early invaders might impact behavioural flexibility and thus the probability of invasion success.
-New environments faced by invasive populations introduce organisms to a plethora of unfamiliar conditions that can entail alterations in homeostasis.
-This disruption triggers a suite of physiological and behavioural responses that are mediated by glucocorticoids (GCs), the "stress"-related hormones [@sapolsky_how_2000].
-These GCs can be transmitted to the offspring and  influence its phenotype through transgenerational effects [@Crino_2023].
-At the same time, other aspects of the environment, such as temperature, can impact the offspring phenotype through direct effects [@noble_developmental_2018].
-As such, GCs and  temperature are predicted to interact to influence the offspring's phenotype.
-In this sense, both factors are known to affect similar aspects of brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017] and also cognitive abilities such as reversal learning [@clark_colour_2014; @lui2017chronic].
-However, the interactive repercussions of prenatal GCs and temperature on behavioural flexibility have not been explored.
-Here, we studied the effects of prenatal temperature and CORT, the main GC in reptiles [@Crino_2023], on behavioural flexibility in two species with distinct histories of invasiveness, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+
+New environments faced by invasive populations introduce organisms to a plethora of unfamiliar, and potentially stressful, situatons.
+Sensory systems detect and transmit environmental signals to instigate adaptive physiological and behavioural adjustments – responses  that are mediated by glucocorticoids (GCs) [@sapolsky_how_2000].
+Glucocorticoids can be transmitted to offspring and influence their phenotype and development through transgenerational effects [@Crino_2023].
+In addition to novel enviroments experienced by parents, offspring also experience potentially stressful environmental conditions that can interact with or amplify parental effects.
+Temperature, in particular, is likely to deviate in invasive populations compared to source populations having a direct effect on offspring phenotype with long-lasting consequences [@noble_developmental_2018].
+As such, GCs and temperature are predicted to interact to influence the offspring phenotype with particuarly potent effects on brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017] and cognition [@clark_colour_2014; @lui2017chronic].
+While the importance of behavioural flexibility is recognised as being important for invasion success, we know little about how novel environmental stressors, such as GCs and temperature, impact behavioural flexibility.
+Such knowledge is crucial for understanding the potential for invasive populations to adapt to new environments and the potential for invasion success.
+
+Here, we studied the effects of prenatal temperature and the glucocorticoid, corticosterone (CORT) (the main GC in reptiles) [@Crino_2023], on behavioural flexibility in two species with distinct histories of invasion success, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_).
@@
 Lizards were tested once daily between 11 to 12 am when they were most active.
+
 In associative and reversal tasks we used three different ramps that were identical in size and shape to the ones for the habituation phase.
@@
 In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
+
 We recorded whether the animal chose the correct ramp first or not.
@@
 delicata_ [@chapple_know_2011].
+
 Our early environment manipulation did not affect the lizards' performance in the task.
@@
 These hypotheses are not mutually exclusive and could be tested in future experiments using multiple doses of prenatal CORT treatment, assessing learning using multiple cognitive tasks, and by measuring the neurophysiological effects on different brain nuclei.
+
 In conclusion, our results indicate that lizards performed the reversal learning task, a measure of behavioural flexibility, at similar rates, with no discernible differences between treatments or species.
@@
 Room temperatures are set to 22-24 Celsius, and warm side of enclosures is usually at 32 Celsius.
+
 *Eggs collection and incubation* -- Between mid-October 2022 to the end of February 2023, we provided females with a place to lay the eggs by means of small boxes (12.5 L x 8.3 W x 5 H cm) with moist vermiculite inside, that were placed in one extreme of the communal enclosures (see above).
@@
 The cups were covered with cling wrap to retain moisture and left in LATWIT 2X5D-R1160 incubators at two different temperatures (see CORT and Temperature manipulation below) until hatching.
+
 *Hatchlings* -- Eggs in the incubator were checked three times a week for hatchlings.
@@
 All care otherwise follows similar protocols to adults (see above).
+
 Two weeks before we started the training phase (see below), lizards were moved to the experimental arena for acclimatation.
@@
 This test was done once a day for 40 days.
+
 We performed the full experiment between the 6^th^ of March until the 26^th^ of June 2023, between 11 to 12 am, when the lizards were active.
@@
 #### Checking the models plots
+
 ```{r, residuals}
@@
 Model formula for the reversal task is:
+
 Choice  ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
+
 Plots for the different models of the associative task:  
@@
 #### Slopes estimates per treatment and species for the original database
+
 ```{r, tbl-data, results='asis'}

### 2024-03-16 ms.qmd
Updates

@@
 For _L.
-delicata_, hormone treatment (Control - CORT = `r format_dec(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold + deli_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc(c(deli_ControlCold, deli_ControlHot) - c(deli_CORTCold, deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc(c(deli_CORTHot, deli_ControlHot) - c(deli_CORTCold, deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(deli_ControlHot - deli_CORTHot) - mean(deli_ControlCold - deli_CORTCold), 3)`, p~mcmc~ = `r format_p(pmcmc(c(deli_ControlHot, deli_CORTHot) - c(deli_ControlCold, deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B).
-We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc(c(guich_ControlCold, guich_ControlHot) - c(guich_CORTCold, guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc(c(guich_CORTHot, guich_ControlHot) - c(guich_CORTCold, guich_ControlCold)),3)`), **or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(guich_ControlHot - guich_CORTHot) - mean(guich_ControlCold - guich_CORTCold), 3)`, p~mcmc~  `r format_p(pmcmc(mean(guich_ControlHot - guich_CORTHot) - mean(guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L.
-guichenoti_ (see @fig-results C, D).
-(Control-Hot - CORT-Hot = `r format_dec(mean(guich_ControlHot) - mean(guich_CORTHot),3)`; p~mcmc~ = `r format_dec(pmcmc(guich_ControlHot - guich_CORTHot),3)`) or (Control-Cold - CORT-Cold = `r format_dec(mean(guich_ControlCold) - mean(guich_CORTCold),3)`; p~mcmc~ = `r format_dec(pmcmc(guich_ControlCold - guich_CORTCold),3)`)**
+delicata_, hormone treatment (Control - CORT = `r format_dec(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold + deli_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold, deli_CORTHot))), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold))),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold))), 3)`) did not affect learning (see @fig-results A, B).
+We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot))), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold))),3)`), on learning in _L.
+guichenoti_ (see @fig-results C, D), but we found a significant interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec((mean(guich_ControlHot) - mean(guich_CORTHot)) - (mean(guich_ControlCold) - mean(guich_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((mean(guich_ControlHot) - mean(guich_CORTHot)) - (mean(guich_ControlCold) - mean(guich_CORTCold))), 3)`).
+However, when the  (Control-Hot - CORT-Hot = `r format_dec(mean(guich_ControlHot) - mean(guich_CORTHot),3)`; p~mcmc~ `r format_p(pmcmc(mean(guich_ControlHot) - mean(guich_CORTHot)),3)`) or (Control-Cold - CORT-Cold = `r format_dec(mean(guich_ControlCold) - mean(guich_CORTCold),3)`; p~mcmc~ `r format_p(pmcmc(mean(guich_ControlCold) - mean(guich_CORTCold)),3)`).
 
@@
 delicata_ - _L.
-guichenoti_ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, p~mcmc~ = `r format_p(pmcmc(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot) - c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`).
+guichenoti_ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot))), 3)`).
 

### 2024-03-16 R/func.r

@@ -132,7 +132,7 @@ format_p <- function(x, n) {
   z <- sprintf(paste0("%.",n,"f"), x)
   tmp <- ifelse(as.numeric(z) <= 0.001, "< 0.001",
          ifelse(as.numeric(z) <= 0.05 & as.numeric(z) > 0.001, "< 0.05",
-                as.character(z)))
+                paste0("=", as.character(z))))
   return(tmp)
 }
 ####################

### 2024-03-16 ms.qmd
Updates

@@
 However, our final sample size was 81 due to natural mortality (n = 11), failure to complete the training stage (n = 1), or if the number of failed tasks (see above) was higher than 15 (n = 3).
-Final sample sizes per treatment and species are listed in @tbl-data.
+Final sample sizes per treatment and species are listed in @fig-results.
 
@@
 For _L.
-delicata_, hormone treatment (Control - CORT = `r format_dec(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold + deli_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold, deli_CORTHot))), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold))),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold))), 3)`) did not affect learning (see @fig-results A, B).
+delicata_, hormone treatment (Mean learning slope in Control = `r format_dec(mean(c(deli_ControlHot, deli_ControlCold)), 3)`, 95% CI = [`r format_dec(quantile(c(deli_ControlHot, deli_ControlCold), 0.025),3)` , `r format_dec(quantile(c(deli_ControlHot, deli_ControlCold), 0.975),3)`] mean learning slope in CORT = `r format_dec(mean(c(deli_CORTHot, deli_CORTCold)),3)`, 95% CI = [`r format_dec(quantile(c(deli_CORTHot, deli_CORTCold), 0.025), 3)` , `r format_dec(quantile(c(deli_CORTHot, deli_CORTCold), 0.975), 3)`], Control - CORT = `r format_dec(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold, deli_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold, deli_CORTHot))), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold))),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold))), 3)`) did not affect learning (see @fig-results A, B).
 We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot))), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold))),3)`), on learning in _L.
@@
 
-Finally, when all individuals from all the treatments were pooled together and species were compared, there were not significant differences in the estimated slopes (Mean learning slope _L.
-delicata_ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot), 0.025), 3)`, `r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot), 0.975), 3)`]; Mean learning slope _L.
+Finally, when all individuals from all the treatments were pooled together and species were compared, there were not significant differences in the estimated slopes (mean of learning slope in _L.
+delicata_ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot), 0.025), 3)`, `r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot), 0.975), 3)`]; mean learning of slope in _L.
 guichenoti_ = `r format_dec(mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot), 0.025), 3)`, `r format_dec(quantile(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot), 0.975), 3)`]; _L.

### 2024-03-16 ms.qmd
Updates

@@
 #| fig.cap: "Experimental design of early environment manipulation and learning tasks.
-Stages 1-3 indicate the different phases of the habituation phase.
-In the associative and reversal tasks, white lids show the ramps where the food reward was not accessible."
+On top, the early environment manipulation for both species.
+Center, the habituation phase with the respective three different stages.
+On the bottom, the associative and reversal tasks; white lids show the ramps where the food reward was not accessible."
 
@@
 For _L.
-delicata_, hormone treatment (Mean learning slope in Control = `r format_dec(mean(c(deli_ControlHot, deli_ControlCold)), 3)`, 95% CI = [`r format_dec(quantile(c(deli_ControlHot, deli_ControlCold), 0.025),3)` , `r format_dec(quantile(c(deli_ControlHot, deli_ControlCold), 0.975),3)`] mean learning slope in CORT = `r format_dec(mean(c(deli_CORTHot, deli_CORTCold)),3)`, 95% CI = [`r format_dec(quantile(c(deli_CORTHot, deli_CORTCold), 0.025), 3)` , `r format_dec(quantile(c(deli_CORTHot, deli_CORTCold), 0.975), 3)`], Control - CORT = `r format_dec(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold, deli_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold, deli_CORTHot))), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold))),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold))), 3)`) did not affect learning (see @fig-results A, B).
-We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot))), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold))),3)`), on learning in _L.
-guichenoti_ (see @fig-results C, D), but we found a significant interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec((mean(guich_ControlHot) - mean(guich_CORTHot)) - (mean(guich_ControlCold) - mean(guich_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((mean(guich_ControlHot) - mean(guich_CORTHot)) - (mean(guich_ControlCold) - mean(guich_CORTCold))), 3)`).
-However, when the  (Control-Hot - CORT-Hot = `r format_dec(mean(guich_ControlHot) - mean(guich_CORTHot),3)`; p~mcmc~ `r format_p(pmcmc(mean(guich_ControlHot) - mean(guich_CORTHot)),3)`) or (Control-Cold - CORT-Cold = `r format_dec(mean(guich_ControlCold) - mean(guich_CORTCold),3)`; p~mcmc~ `r format_p(pmcmc(mean(guich_ControlCold) - mean(guich_CORTCold)),3)`).
+delicata_, hormone treatment (Control - CORT = `r format_dec(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold, deli_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(deli_ControlCold, deli_ControlHot) - c(deli_CORTCold, deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(c(deli_CORTHot, deli_ControlHot) - c(deli_CORTCold, deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((deli_ControlHot - deli_CORTHot) - (deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B).
+We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(guich_ControlCold, guich_ControlHot) - c(guich_CORTCold, guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(c(guich_CORTHot, guich_ControlHot) - c(guich_CORTCold, guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec((mean(guich_ControlHot) - mean(guich_CORTHot)) - (mean(guich_ControlCold) - mean(guich_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L.
+guichenoti_ (see @fig-results C, D).
 
@@
 delicata_ - _L.
-guichenoti_ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot))), 3)`).
+guichenoti_ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot) - c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`).
 

### 2024-03-16 R/func.r

@@ -132,7 +132,7 @@ format_p <- function(x, n) {
   z <- sprintf(paste0("%.",n,"f"), x)
   tmp <- ifelse(as.numeric(z) <= 0.001, "< 0.001",
          ifelse(as.numeric(z) <= 0.05 & as.numeric(z) > 0.001, "< 0.05",
-                paste0("=", as.character(z))))
+                paste0("= ", as.character(z))))
   return(tmp)
 }
 ####################

### 2024-03-16 ms.qmd
Updates

@@
 
-Pablo Recio-Santiago^1^,$\ddagger$ , Dalton L. Leibold^1^, Ondi Crino ^1,2^, Kris Wild^1,3^, Daniel W.A. Noble^1^
+Pablo Recio-Santiago^1^,$\ddagger$ , Dalton C. Leibold^1^, Ondi Crino ^1,2^, Kris Wild^1,3^, Chris Friesen^4^, Basile Mauclaire^1,5^, Amelia Peardon ^1^, Daniel W.A. Noble^1^
 
-^1^ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2601, Australia &NewLine;
-^2^ Flinder's University, Adelaide, SA 5001, Australia &NewLine;
-^3^ Melbourne University, Melbourne, VIC 3000, Australia &NewLine;
-$\ddagger$ Corresponding author: pablo.reciosantiago@anu.edu.au &NewLine;
+^1^ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2601, Australia  
+^2^ Flinder's University, Adelaide, SA 5001, Australia  
+^3^ Melbourne University, Melbourne, VIC 3000, Australia  
+^4^ University of Wollongong, Wollongong, NSW 2500, Australia  
+^5^ Université de Lille, Lille 59000, France  
+$\ddagger$ Corresponding author: pablo.reciosantiago@anu.edu.au
 
 ## Abstract
+Behavioural flexibility is crucial for species adapting to new environments, specially during invasion events.
+However, the early environment experienced can profoundly impact animals' ability to behave flexibly.
+Aspects like parents' transmitted hormones or temperature are predicted to interact to shape behavioural flexibility.
+But, given the advantages associated to behaving flexibly during the invasion process, behavioural flexibility in invasive species is expected to be less susceptible to the impacts of early environment.
+Here, we investigated the interactive effects of prenatal corticosterone (CORT) and temperature on behavioural flexibility in two lizard species, _Lampropholis delicata_ and _L.
+guichenoti_, with distinct invasion success.
+We manipulated prenatal CORT levels and incubation temperature in a 2x2 factorial design, and then assessed behavioural flexibility through a reversal learning task.
+Contrary to our expectations, we found no significant differences in the reversal learning rate between treatments or species.
+Our results suggest that prenatal temperature and CORT may not influence reversal learning in these species and that other factors in _L.
+delicata_ biology may be more influential in invasion success than behavioural flexibility alone.
 
@@
 
-knitr::include_graphics("./Others/BEHFLEX_FIG_1.svg")
+knitr::include_graphics("./Others/BEHFLEX_FIG_1")
 
@@
 Nevertheless, it remains possible that the effects of the early environment are task-dependent, and future studies should explore performance across different cognitive tasks and the effects of both treatments on brain function.
+
+## Ethics  
+Experiments complied with Australian law and were approved by the Australian National University Animal Experimentation Ethics Committee (A2022_33).
+
+## Data accessibility  
+All data, data description, and R code are availabe in public repository https://github.com/Pablo-Recio/CORT_Temp_Behavioural_flexibility
+
+## Declaration of AI use
+We declare Chat GPT was used for questions related to coding and data analyses.
+All other parts of the manuscript were written by the authors and those parts were AI was used were checked and modified accordingly by the authors.
+
+## Authors' contributions
+P.R.: conceptualization, methodology, data collection, data curation, formal analysis, writing—original draft, writing—review and editing; D.C.L.: data collection, writing—review and editing; O.C.: conceptualization, methodology, writing—review and editing; K.W.: conceptualization, writing—review and editing; C.F.: conceptualization, methodology, writing—review and editing; B.M: data collection, writing—review and editing; A.P.: data collection, writing—review and editing; D.N.: conceptualization, methodology, funding acquisition, project administration, resources, supervision, writing—review and editing.
+All authors gave final approval for publication and agreed to be held accountable for the work performed therein.
+
+## Conflict of interest declaration  
+We declare we have no competing interests.
+
+## Funding
+This work was supported by a National Australian University fellowship (P.R.), the Australian Research Council (grant no. DP210101152) to D.N., and the ACT Herpetological Association grant to P.R.
+
+## Acknowledgements
+and two anonymous reviewers for their valuable feedback on the manuscript.
 

### 2024-03-16 ms.qmd
Updates

@@
 
-knitr::include_graphics("./Others/BEHFLEX_FIG_1")
+knitr::include_graphics("./Others/BEHFLEX_FIG_1.png")
 
@@
 
-#### Slopes estimates per treatment and species for the original database
-
 ```{r, tbl-data, results='asis'}
@@
 
-#### Slopes estimates per treatment and species employing only those individuals that passed a learning criterion of 80% correct choices in the last 10 trials of the associative task
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
 

### 2024-03-16 .vdoc.r

@@ -1,0 +1,519 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of early environment manipulation and learning tasks. On top, the early environment manipulation for both species. Center, the habituation phase with the respective three different stages. On the bottom, the associative and reversal tasks; white lids show the ramps where the food reward was not accessible."
+
+knitr::include_graphics("./Others/BEHFLEX_FIG_1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleandata
+# Obtain the main df using "./R/1_data_process.R"
+source(here("R", "1_data_process.R"))
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(k in 1:length(hormone)){
+    for(l in 1:length(temperature)){
+      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
+      }
+    }
+  }
+#
+#
+#
+#
+#
+#| label: models
[…]

### 2024-03-16 ms.qmd
Updates

@@
 ## Acknowledgements
-and two anonymous reviewers for their valuable feedback on the manuscript.
+We thank the help and assistance of our lab technicians Benjamin Durant and Michelle Stephens for taking care of the lizards.
+We are also grateful to ACTHA for the grant for the 3D printed feeders, and we also thank ANU MakerSpace, where we design and built the prototypes of the 3D printed feeders.
+Finally, we wish to acknowledge the anonymous reviewers for their valuable feedback on the manuscript.
 

### 2024-03-26 ms.qmd
Updates

@@
 
-Pablo Recio-Santiago^1^,$\ddagger$ , Dalton C. Leibold^1^, Ondi Crino ^1,2^, Kris Wild^1,3^, Chris Friesen^4^, Basile Mauclaire^1,5^, Amelia Peardon ^1^, Daniel W.A. Noble^1^
+Pablo Recio-Santiago^1^,$\ddagger$ , Dalton C. Leibold^1^, Ondi Crino ^1,2^, Kristoffer H. Wild^1,3^, Chris Friesen^4^, Basile Mauclaire^1,5^, Amelia Peardon ^1^, Daniel W.A. Noble^1^
 
@@
 However, the early environment experienced can profoundly impact animals' ability to behave flexibly.
-Aspects like parents' transmitted hormones or temperature are predicted to interact to shape behavioural flexibility.
-But, given the advantages associated to behaving flexibly during the invasion process, behavioural flexibility in invasive species is expected to be less susceptible to the impacts of early environment.
-Here, we investigated the interactive effects of prenatal corticosterone (CORT) and temperature on behavioural flexibility in two lizard species, _Lampropholis delicata_ and _L.
-guichenoti_, with distinct invasion success.
+Aspects like developmental environments and parental investment are predicted to interact to shape behavioural plasticity.
+However, given the advantages associated to behaving flexibly during the invasion process, behavioural flexibility in invasive species is expected to be less susceptible to the impacts of early environment.
+Here, we investigated the interactive effects of prenatal corticosterone (CORT) and temperature on behavioural plasticity in two lizard species, _Lampropholis delicata_ and _L.
+guichenoti_, with distinct histories of invasion.
 We manipulated prenatal CORT levels and incubation temperature in a 2x2 factorial design, and then assessed behavioural flexibility through a reversal learning task.
 Contrary to our expectations, we found no significant differences in the reversal learning rate between treatments or species.
-Our results suggest that prenatal temperature and CORT may not influence reversal learning in these species and that other factors in _L.
+We argue that prenatal temperature and CORT may not influence reversal learning in these species, which suggests that other aspects of _L.
 delicata_ biology may be more influential in invasion success than behavioural flexibility alone.
@@
 
-New environments faced by invasive populations introduce organisms to a plethora of unfamiliar, and potentially stressful, situatons.
+Novel environments faced by invasive populations introduce organisms to a plethora of unfamiliar and potentially stressful situatons.
 Sensory systems detect and transmit environmental signals to instigate adaptive physiological and behavioural adjustments – responses  that are mediated by glucocorticoids (GCs) [@sapolsky_how_2000].
 Glucocorticoids can be transmitted to offspring and influence their phenotype and development through transgenerational effects [@Crino_2023].
-In addition to novel enviroments experienced by parents, offspring also experience potentially stressful environmental conditions that can interact with or amplify parental effects.
-Temperature, in particular, is likely to deviate in invasive populations compared to source populations having a direct effect on offspring phenotype with long-lasting consequences [@noble_developmental_2018].
-As such, GCs and temperature are predicted to interact to influence the offspring phenotype with particuarly potent effects on brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017] and cognition [@clark_colour_2014; @lui2017chronic].
-While the importance of behavioural flexibility is recognised as being important for invasion success, we know little about how novel environmental stressors, such as GCs and temperature, impact behavioural flexibility.
+In addition to novel environments experienced by parents, offspring also experience potentially stressful environmental conditions that can interact with or amplify parental effects.
+Temperature, in particular, is likely to deviate in invasive populations compared to source populations, which have a direct effect on offspring phenotypes and long-lasting consequences [@noble_developmental_2018].
+As such, GCs and temperature are predicted to interact to influence the offspring phenotype with particularly potent effects on brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017] and cognition [@clark_colour_2014; @lui2017chronic].
+While behavioural flexibility is recognised as an important behavioural phenotype for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can], we know little about how novel environmental stressors, such as GCs or temperature, impact behavioural flexibility.
 Such knowledge is crucial for understanding the potential for invasive populations to adapt to new environments and the potential for invasion success.
@@
 guichenoti_).
-_L.
-delicata_ has been succesful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI], but the same is not true of _L.
+_Lampropholis delicata_ has been successful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI], but the same is not true of _L.
 guichenoti_ despite the two species having similar life-histories and overlapping distributions [@chapple_know_2011; @chapple_biology_2014].
 Personality has been shown to be different between these two species [@chapple_know_2011; @chapple2012can; @bezzina2014does], which could be related to general cognitive differences that are important for invasion success.
-Additionally, early environments are known to affect suites of morphological and behavioural traits differently in each species [@carrasco2023maternal; @kar2023heritability], but the interactive role of maternal CORT and early temperatures have not yet been explored.
-Differences in the relative impact that early environments have on behavioural flexibility may help explain differing invasion success between the two species.
-We predicted that _L.
-delicata_ would, on average, perform more proficiently in the task compared to _L.
+Additionally, early environments are known to affect suites of morphological and behavioural traits differently in each species [@carrasco2023maternal; @kar2023heritability], but the interactive role of maternal CORT and early temperatures has not yet been explored.
+Differences in the relative impact of early environments on behavioural flexibility may help explain differing invasion success between the two species.
+We predict that _L.
+delicata_, on average, will perform more proficiently in the task compared to _L.
 guichenoti_.
-We also anticipated prenatal CORT and temperature to affect the behavioural flexibility of both species, and that _L.
-guichenoti_ would be more impacted by the prenatal environment than _L.
+We also anticipate prenatal CORT and temperature to affect the behavioural flexibility of both species, and that _L.
+guichenoti_ will be more impacted by the prenatal environment than _L.
 delicata_.
@@
 #| fig.cap: "Experimental design of early environment manipulation and learning tasks.
-On top, the early environment manipulation for both species.
-Center, the habituation phase with the respective three different stages.
-On the bottom, the associative and reversal tasks; white lids show the ramps where the food reward was not accessible."
+Panel A represents the early environment manipulation for both species.
+Panel B shows the habituation phase with the respective three different stages.
+And panel C represents the associative and reversal tasks; white lids show the ramps where the food reward was not accessible."
 
@@
 guichenoti (C, D).
-A, C) Predicted probability of choosing the correct feeder first over trials.
-The lines represent the mean predicted probability of choosing the correct feeder first, and the shaded areas represent the standard deviation of the mean; both obtained by using the slope and intercept estimates from the posterior distributions.
-The different colours represent the different treatments.
-B, D) Distribution of the estimates of the slopes per each treatment.
-The x-axis represents the estimates of the slopes, and the y-axis represents the density of the estimates.
-The different colours represent the different treatments.
+Panels A and C show the predicted probability of choosing the correct feeder first over trials.
+The lines represent the mean predicted probability of choosing the correct feeder first on each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions.
+The different colours indicate the different treatments.
+Panels B and D show the distribution of the estimates of slopes per each treatment.
+The x-axis represents the slope estimate, and in the y-axis are the density of the estimates.
+The different colours indicate the different treatments.
 Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
@@
 
-The study embarked on unravelling the interactive effects of prenatal temperature and GCs on behavioural flexibility in two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+The study aimed to determine the interactive effects of prenatal temperature and GCs on behavioural flexibility in two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_).
 Despite sharing life history traits, only _L.
-delicata_ has proven successful in colonising various global regions, and we hypothesised this may be related to higher behavioural flexibility.
+delicata_ has proven successful in colonising various global regions [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI], and we predicted this may relate to higher behavioural flexibility.
 Furthermore, we expected behavioural flexibility in this species to be less susceptible to the effect of early environment since this trait can be adaptive in several stages of invasion involving more than one generation.
@@
 We found that, on average, all the lizards from the four treatments and the two species learned the reversal task - indicated by estimated slopes that are significantly different from zero - and that they learn, on average, at the same rate.
-Furthermore, these results were consistent when only those individuals that performed better in the previous associative task were included (see Supplementary material).
+Furthermore, these results were consistent when only those individuals who performed better in the previous associative task were included (see Supplementary material).
+
 Previous studies have shown that _L.
@@
 guichenoti_, which can be advantageous during colonisation [@chapple_know_2011].
-However, Bezzina et al.
-[@bezzina2014does] found no differences in learning between the two skinks in an associative learning task.
+However, Bezzina _et al._ [@bezzina2014does] found no differences in learning between the two skinks in an associative learning task.
 Our results align with the latter study and suggest that behavioural flexibility does not differ between these species.
@@
 However, our results show no significant differences between treatments in both species.
-Our outcome contrasts with previous studies that show impairments of high GCs levels in different types of learning tests [@lemaire_prenatal_2000; @zhu_prenatal_2004;  @farrell_developmental_2016], but they are consistent with other experiments where GCs increased or did not impact learning abilities [@szuran_water_1994; @bebus_associative_2016].
+In contrast to previous studies that show high GCs levels impaired performance in different types of learning tests [@lemaire_prenatal_2000; @zhu_prenatal_2004;  @farrell_developmental_2016], we did not find any effect of CORT on the speed at which lizards learn.
+Our results are, however, consistent with other experiments where GCs did not impact learning abilities [@szuran_water_1994; @bebus_associative_2016].
 More striking is the absence of an effect of incubation temperature since most of the studies in reptiles reported better performance when incubated at higher temperatures in different associative learning and motor tasks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-Furthermore, those studies that reported cold-incubated lizards learn faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temperatures far beyond the natural range in the hot treatment.
+Furthermore, those studies that reported cold-incubated lizards learn faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temperatures far beyond the natural range in their hot treatments.
 In some systems, exposure to CORT during development has hormetic effects on  learning and neural structures [@du_dynamic_2009; @mcewen_brain_2012].
@@
 However, it is possible that prenatal CORT treatment affects tissues differently.
-Conversely, it is likely that the effects of the early environment may vary depending on the cognitive task, as evidenced by studies showing variations in the impact of prenatal GCs and temperature on different brain regions [@coomber_independent_1997; @sakata_neural_2000; @lemaire_prenatal_2000].
-These hypotheses are not mutually exclusive and could be tested in future experiments using multiple doses of prenatal CORT treatment, assessing learning using multiple cognitive tasks, and by measuring the neurophysiological effects on different brain nuclei.
+Conversely, the effects of the early environment may likely vary depending on the cognitive task, as evidenced by studies showing variations in the impact of prenatal GCs and temperature on different brain regions [@coomber_independent_1997; @sakata_neural_2000; @lemaire_prenatal_2000].
+These hypotheses are not mutually exclusive and could be tested in future experiments using multiple doses of prenatal CORT treatment, assessing learning using multiple cognitive tasks, and measuring the neurophysiological effects on different brain nuclei.
 

### 2024-03-31 ms.qmd
Update ms.qmd

@@
 
-Pablo Recio-Santiago^1^,$\ddagger$ , Dalton C. Leibold^1^, Ondi Crino ^1,2^, Kristoffer H. Wild^1,3^, Chris Friesen^4^, Basile Mauclaire^1,5^, Amelia Peardon ^1^, Daniel W.A. Noble^1^
+Pablo Recio-Santiago^1^,$\ddagger$ , Dalton C. Leibold^1^, Ondi Crino ^1,2^, Kristoffer H. Wild^1,3^, Chris Friesen^4^, Basile Mauclaire^1,5^, Amelia Y. Peardon ^1^, Daniel W.A. Noble^1^
 
@@
 In mammals, birds, reptiles and amphibians, relative brain size has been shown to be a good predictor of behavioural flexibility and invasive success [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
-However, the brain is also sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004] creating uncertainty about how environmental insults faced by early invaders might impact behavioural flexibility and thus the probability of invasion success.
+However, the brain is also sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004], creating uncertainty about how environmental insults faced by early invaders might impact behavioural flexibility and thus the probability of invasion success.
 
-Novel environments faced by invasive populations introduce organisms to a plethora of unfamiliar and potentially stressful situatons.
+Novel environments faced by invasive populations introduce organisms to a plethora of unfamiliar and potentially stressful situations.
 Sensory systems detect and transmit environmental signals to instigate adaptive physiological and behavioural adjustments – responses  that are mediated by glucocorticoids (GCs) [@sapolsky_how_2000].
@@
 In addition to novel environments experienced by parents, offspring also experience potentially stressful environmental conditions that can interact with or amplify parental effects.
-Temperature, in particular, is likely to deviate in invasive populations compared to source populations, which have a direct effect on offspring phenotypes and long-lasting consequences [@noble_developmental_2018].
+Temperature, in particular, is likely to deviate in invasive populations compared to source populations, having a direct effect on offspring phenotypes with long-lasting consequences [@noble_developmental_2018].
 As such, GCs and temperature are predicted to interact to influence the offspring phenotype with particularly potent effects on brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017] and cognition [@clark_colour_2014; @lui2017chronic].
@@
 The associative learning task lasted 35 days.
-Finally, to quantify behavioural flexibility, we reversed the previously trained colour (red or blue) so that they needed to learn to associate the food with the opposite colour (@fig-Methods Reversal task).
+Finally, to quantify behavioural flexibility, we reversed the previously trained colour (red or blue) so that the lizards needed to learn to associate the food with the opposite colour (@fig-Methods Reversal task).
 The reversal learning task lasted a total of 40 days.
-Lizards were tested once daily between 11 to 12 am when they were most active.
+Lizards were tested once daily between 11 am to 12 pm when they were most active.
 
-In associative and reversal tasks we used three different ramps that were identical in size and shape to the ones for the habituation phase.
+In associative and reversal tasks we used three different ramps that were identical in size and shape to the ones used in the habituation phase.
 The colours of the ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
@@
 We considered that a choice was made if the head of the lizard was inside the well of one of the ramps.
-We considered a trial failed if there was no choice in one hour of recording and those trials.
+We considered a trial failed if there was no choice in one hour of recording and those trials were scored as NA.
 Here, we analysed the data of the reversal task as a measure of behavioural flexibility [@brown2010behavioral].
@@
 We performed the analyses for each species separately.
-We fitted two different Bayesian multilevel models using the brm function from the _brms_ package [@burkner2017brms] using in R extension (version 2.8.2) [@R].
+We fitted two different Bayesian multilevel models using the brm function from the _brms_ package [@burkner2017brms] using an R extension (version 2.8.2) [@R].
 We ran four parallel MCMC chains of 3000 iterations for each model, with a warmup period of 1000 iterations.
@@
 
-The study aimed to determine the interactive effects of prenatal temperature and GCs on behavioural flexibility in two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+This study aimed to determine the interactive effects of prenatal temperature and GCs on behavioural flexibility in two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_).
-Despite sharing life history traits, only _L.
+Despite sharing life-history traits, only _L.
 delicata_ has proven successful in colonising various global regions [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI], and we predicted this may relate to higher behavioural flexibility.
@@
 We declare Chat GPT was used for questions related to coding and data analyses.
-All other parts of the manuscript were written by the authors and those parts were AI was used were checked and modified accordingly by the authors.
+All other parts of the manuscript were written by the authors and those parts where AI was used were checked and modified accordingly by the authors.
 
 ## Authors' contributions
-P.R.: conceptualization, methodology, data collection, data curation, formal analysis, writing—original draft, writing—review and editing; D.C.L.: data collection, writing—review and editing; O.C.: conceptualization, methodology, writing—review and editing; K.W.: conceptualization, writing—review and editing; C.F.: conceptualization, methodology, writing—review and editing; B.M: data collection, writing—review and editing; A.P.: data collection, writing—review and editing; D.N.: conceptualization, methodology, funding acquisition, project administration, resources, supervision, writing—review and editing.
+P.R.: conceptualization, methodology, data collection, data curation, formal analysis, writing—original draft, writing—review and editing; D.C.L.: data collection, writing—review and editing; O.C.: conceptualization, methodology, writing—review and editing; K.H.W.: conceptualization, writing—review and editing; C.F.: conceptualization, methodology, writing—review and editing; B.M: data collection, writing—review and editing; A.Y.P.: data collection, writing—review and editing; D.N.: conceptualization, methodology, funding acquisition, project administration, resources, supervision, writing—review and editing.
 All authors gave final approval for publication and agreed to be held accountable for the work performed therein.
@@
 We thank the help and assistance of our lab technicians Benjamin Durant and Michelle Stephens for taking care of the lizards.
-We are also grateful to ACTHA for the grant for the 3D printed feeders, and we also thank ANU MakerSpace, where we design and built the prototypes of the 3D printed feeders.
+We are also grateful to ACTHA for the grant for the 3D printed feeders, and we also thank ANU MakerSpace, where we designed and built the prototypes of the 3D printed feeders.
 Finally, we wish to acknowledge the anonymous reviewers for their valuable feedback on the manuscript.

### 2024-03-31 .vdoc.r
Updates

@@ -1,519 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: fig-Methods
-#| fig.cap: "Experimental design of early environment manipulation and learning tasks. On top, the early environment manipulation for both species. Center, the habituation phase with the respective three different stages. On the bottom, the associative and reversal tasks; white lids show the ramps where the food reward was not accessible."
-
-knitr::include_graphics("./Others/BEHFLEX_FIG_1.png")
-
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: cleandata
-# Obtain the main df using "./R/1_data_process.R"
-source(here("R", "1_data_process.R"))
-#
-#
-#
-#| label: sampleSize
-# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
-source(here("R", "func.R"))
-#
-specie <- c("delicata", "guichenoti")
-hormone <- c("CORT", "Control")
-temperature <- c("Cold", "Hot")
-#
-n_list <- list()
-#
-for(i in 1:length(specie)){
-  for(k in 1:length(hormone)){
-    for(l in 1:length(temperature)){
-      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
-      }
-    }
-  }
-#
-#
-#
-#
-#
-#| label: models
[…]

### 2024-04-02 ms.qmd
Update ms.qmd

@@
 
-Pablo Recio-Santiago^1^,$\ddagger$ , Dalton C. Leibold^1^, Ondi Crino ^1,2^, Kristoffer H. Wild^1,3^, Chris Friesen^4^, Basile Mauclaire^1,5^, Amelia Y. Peardon ^1^, Daniel W.A. Noble^1^
+Pablo Recio-Santiago^1^,$\ddagger$ , Dalton C. Leibold^1^, Ondi L. Crino ^1,2^, Kristoffer H. Wild^1,3^, Chris Friesen^4^, Basile Mauclaire^1,5^, Amelia Y. Peardon ^1^, Daniel W.A. Noble^1^
 
 ^1^ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2601, Australia  
-^2^ Flinder's University, Adelaide, SA 5001, Australia  
+^2^ Flinder's University, College of Science and Engineering, Bedford Park, SA 5042, Australia  
 ^3^ Melbourne University, Melbourne, VIC 3000, Australia  
@@
 ## Abstract
-Behavioural flexibility is crucial for species adapting to new environments, specially during invasion events.
-However, the early environment experienced can profoundly impact animals' ability to behave flexibly.
-Aspects like developmental environments and parental investment are predicted to interact to shape behavioural plasticity.
-However, given the advantages associated to behaving flexibly during the invasion process, behavioural flexibility in invasive species is expected to be less susceptible to the impacts of early environment.
-Here, we investigated the interactive effects of prenatal corticosterone (CORT) and temperature on behavioural plasticity in two lizard species, _Lampropholis delicata_ and _L.
+Behavioural flexibility is crucial for animals adapting to and colonizing new environments.
+However, novel environmental conditions experienced during early development can profoundly impact behavioural flexibility making it unclear how invasive populations establish in new locations.
+Given the advantages associated with behaving flexibly during the invasion process we predict that behavioural flexibility in invasive species should be less susceptible to the impacts of early environmental conditions.
+Here, we investigated the interactive effects of prenatal corticosterone (CORT) and temperature on behavioural flexibility in two lizard species, _Lampropholis delicata_ and _L.
 guichenoti_, with distinct histories of invasion.
@@
 Contrary to our expectations, we found no significant differences in the reversal learning rate between treatments or species.
-We argue that prenatal temperature and CORT may not influence reversal learning in these species, which suggests that other aspects of _L.
-delicata_ biology may be more influential in invasion success than behavioural flexibility alone.
+Behavioural flexibility appears to be robust to prenatal temperature and CORT which may be one reason why _L.
+delicata_ has been so successful as an invasive species.
+However, the lack of difference in reversal learning between _L.
+delicata_ and _L.
+guichenoti_ suggests that other processes are likely more influential in invasion success than behavioural flexibility itself.
 
@@
 Species with greater behavioural flexibility are expected to be more likely to survive and establish in new habitats because behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can].
-For instance, in closely related bird species successful invaders show a higher frequency of foraging innovations [@sol2000behavioural].
+For instance, bird species that are successful invaders have a higher frequency of foraging innovations compared to closely related species without a history of invasions [@sol2000behavioural].
 According to the 'adaptive flexibility hypothesis', behavioural flexibility is most relevant during introduction, establishment, and the spread of an invasive population [@wright2010behavioral; @chapple2012can; @szabo2020can].
 In mammals, birds, reptiles and amphibians, relative brain size has been shown to be a good predictor of behavioural flexibility and invasive success [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
-However, the brain is also sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004], creating uncertainty about how environmental insults faced by early invaders might impact behavioural flexibility and thus the probability of invasion success.
+However, the brain is also sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004], creating uncertainty about how environmental conditions faced by early invaders might impact behavioural flexibility and thus the probability of invasion success.
 
@@
 ## Authors' contributions
-P.R.: conceptualization, methodology, data collection, data curation, formal analysis, writing—original draft, writing—review and editing; D.C.L.: data collection, writing—review and editing; O.C.: conceptualization, methodology, writing—review and editing; K.H.W.: conceptualization, writing—review and editing; C.F.: conceptualization, methodology, writing—review and editing; B.M: data collection, writing—review and editing; A.Y.P.: data collection, writing—review and editing; D.N.: conceptualization, methodology, funding acquisition, project administration, resources, supervision, writing—review and editing.
+P.R.: conceptualization, methodology, data collection, data curation, formal analysis, writing—original draft, writing—review and editing; D.C.L.: data collection, writing—review and editing; O.C.: conceptualization, methodology, writing—review and editing; K.H.W.: conceptualization, writing—review and editing; C.F.: conceptualization, methodology, funding acquisition,writing—review and editing; B.M: data collection, writing—review and editing; A.Y.P.: data collection, writing—review and editing; D.N.: conceptualization, methodology, funding acquisition, project administration, resources, supervision, writing—review and editing.
 All authors gave final approval for publication and agreed to be held accountable for the work performed therein.
@@
 ## Funding
-This work was supported by a National Australian University fellowship (P.R.), the Australian Research Council (grant no. DP210101152) to D.N., and the ACT Herpetological Association grant to P.R.
+This work was supported by a National Australian University fellowship (P.R.), the Australian Research Council (grant no.
+DP210101152) to D.N.
+and C.F., and the ACT Herpetological Association grant to P.R.
 

### 2024-04-03 ms.qmd
Updates

@@
 Our results are, however, consistent with other experiments where GCs did not impact learning abilities [@szuran_water_1994; @bebus_associative_2016].
+In some systems, exposure to CORT during development has hormetic effects on learning and neural structures [@du_dynamic_2009; @mcewen_brain_2012].
+For example, in Sprague–Dawley rats, exposure to high doses of CORT, but not low doses, reduced density of immature neurons and cell proliferation and in the dentate gyrus [@DOSEneurobrummelte2010chronic].
+The CORT treatment employed here is known to impact other aspects such as growth or mortality in these species (unpublished data), but the effect of the same dose can differ between tissues (@lemaire_prenatal_2000).
 More striking is the absence of an effect of incubation temperature since most of the studies in reptiles reported better performance when incubated at higher temperatures in different associative learning and motor tasks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
 Furthermore, those studies that reported cold-incubated lizards learn faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temperatures far beyond the natural range in their hot treatments.
-In some systems, exposure to CORT during development has hormetic effects on  learning and neural structures [@du_dynamic_2009; @mcewen_brain_2012].
-For example, in Sprague–Dawley rats, exposure to high doses of CORT, but not low doses, reduced density of immature neurons and cell proliferation and in the dentate gyrus [@DOSEneurobrummelte2010chronic].
-We know that prenatal CORT treatment affects other traits in both species of lizards used in this experiment (unpublished data).
-However, it is possible that prenatal CORT treatment affects tissues differently.
+We know that our prenatal treatments affect other traits in both species of lizards used in this experiment (unpublished data).
+However, it is possible that those treatments affect tissues differently.
+An alternative hypothesis is that the effects of the prenatal treatments are age-dependent [see @frisone2002social], but our subjucts were tested before maturity (see Supplementary material).
 Conversely, the effects of the early environment may likely vary depending on the cognitive task, as evidenced by studies showing variations in the impact of prenatal GCs and temperature on different brain regions [@coomber_independent_1997; @sakata_neural_2000; @lemaire_prenatal_2000].
-These hypotheses are not mutually exclusive and could be tested in future experiments using multiple doses of prenatal CORT treatment, assessing learning using multiple cognitive tasks, and measuring the neurophysiological effects on different brain nuclei.
+These hypotheses are not mutually exclusive and could be tested in future experiments using multiple doses of prenatal CORT treatment, assessing learning using multiple cognitive tasks and at different ages, and measuring the neurophysiological effects on different brain nuclei.
 
@@
 ```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+In the figure, the distribution of age per treatment and species:
+
+```{r, age} 
+#| label: age
+# Plotting the distribution of the age of the lizards by treatment and species
+# Load the data
+data_age <- read.csv(here("data/Learning.csv"))
+# Plot the distribution of the age of the lizards by treatment and species
+img_deli <- readPNG("./Others/Deli.png")
+plot_age_deli <- data_age %>%
+  filter(species == "delicata") %>%
+  mutate(trt = factor(trt, 
+          levels = c("A_23", "B_23", "A_28", "B_28"), 
+          labels = c("Control-Cold", "CORT-Cold", "Control-Hot", "CORT-Hot"))) %>%
+  ggplot(aes(x = age.start, color = trt)) +
+  geom_density(linewidth = 1.5) +
+  scale_color_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="#68bde1", "CORT-Hot"="#b50101", "Control-Hot"="#fa927d")) +  
+  labs(title = "L. delicata", x = "Age (days)", color = "Treatments") +
+  theme_classic() +
+  theme(plot.margin = margin(5.5, 5.5, 5.5, 5.5, "mm"),
+    plot.title = element_text(size = 14, family = "Times", face = "italic"),
+    axis.text.y = element_blank(),   # Remove y-axis labels
+    axis.title = element_text(size = 12, family = "Times"),
+    axis.text = element_text(size = 10, family = "Times"),
+    legend.position = "right",
+    legend.title = element_text(size = 12, family = "Times"),
+    legend.text = element_text(size = 11, family = "Times")
+    ) +
+  annotation_custom(rasterGrob(img_deli), xmin = 0.73, xmax = 0.98, ymin = 0.73, ymax = 0.98)
+#
+img_guich <- readPNG("./Others/Guich.png")
+plot_age_guich <- data_age %>%
+  filter(species == "guichenoti") %>%
+  mutate(trt = factor(trt, 
+          levels = c("A_23", "B_23", "A_28", "B_28"), 
+          labels = c("Control-Cold", "CORT-Cold", "Control-Hot", "CORT-Hot"))) %>%
+  ggplot(aes(x = age.start, color = trt)) +
+  geom_density(linewidth = 1.5) +
+  scale_color_manual(values = c("CORT-Cold"="darkblue", "Control-Cold"="#68bde1", "CORT-Hot"="#b50101", "Control-Hot"="#fa927d")) +  
+  labs(title = "L. guichenoti", x = "Age (days)", color = "Treatments") +
+  theme_classic() +
+  theme(plot.margin = margin(5.5, 5.5, 5.5, 5.5, "mm"),
+    plot.title = element_text(size = 14, family = "Times", face = "italic"),
+    axis.text.y = element_blank(),   # Remove y-axis labels
+    axis.title = element_text(size = 12, family = "Times"),
+    axis.text = element_text(size = 10, family = "Times"),
+    legend.position = "right",
+    legend.title = element_text(size = 12, family = "Times"),
+    legend.text = element_text(size = 11, family = "Times")
+    ) +
+  annotation_custom(rasterGrob(img_guich), xmin = 0.73, xmax = 0.98, ymin = 0.73, ymax = 0.98)
+#
+plot_age <- plot_grid(plot_age_deli, plot_age_guich, ncol = 1)
+ggsave("./output/figures/plot_age.png", plot=plot_age, width = 25, height = 18, units = "cm", dpi = 600)
+knitr::include_graphics("./output/figures/plot_age.png")

### 2024-04-04 ms.qmd
Updates

@@
 
+Checking the effect of age on the learning rate in the associative task.
+
+Model formula: 
+Choice ~ age.start + trial_associative*cort*temp + (1 + trial_associative|lizard_id)
+
+```{r, modelsage}
+#| label: modelsage
+# Fitting the models for L. delicata and L. guichenoti including age as a covariate
+#
+refit2 = TRUE
+formula <- FC_reversal ~ age.start + trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
+species <- c("delicata", "guichenoti")
+#
+models <- list() # Create an empty list to store the models
+for(s in species){
+  # Subset the data for the species
+  data_species <- clean_df %>%
+    filter(species == s)
+  # Define model file name
+  model_file <- paste0("output/models/model_age_", s, ".rds")
+# Fit the model only if it has not been fit yet (if refit2 = TRUE)
+  if(refit2){
+    # Fit the model
+    model <- brm(formula,
+                data = data_species,
+                family = bernoulli(link = "logit"),
+                chains = 4, cores = 4, iter = 3000, warmup = 1000, control = list(adapt_delta = 0.99))
+    # Write the model to a file
+    saveRDS(model, file = model_file)
+  } else {
+      # Read the model from a file
+      model <- readRDS(file = model_file)
+  }
+  # Save the model to the list
+  models[[s]] <- model
+}
+model_age_deli <- models[["delicata"]]
+model_age_guich <- models[["guichenoti"]]
+```
+
+Results for L_delicata:
+` r summary(model_age_deli)`
+
+Results for L_guichenoti:
+` r summary(model_age_guich)`
+
 In the figure, the distribution of age per treatment and species:
-
 ```{r, age} 

### 2024-04-04 .vdoc.r

@@ -1,0 +1,630 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of early environment manipulation and learning tasks. Panel A represents the early environment manipulation for both species. Panel B shows the habituation phase with the respective three different stages. And panel C represents the associative and reversal tasks; white lids show the ramps where the food reward was not accessible."
+
+knitr::include_graphics("./Others/BEHFLEX_FIG_1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleandata
+# Obtain the main df using "./R/1_data_process.R"
+source(here("R", "1_data_process.R"))
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(k in 1:length(hormone)){
+    for(l in 1:length(temperature)){
+      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
+      }
+    }
+  }
+#
+#
+#
+#
+#
+#| label: models
[…]

### 2024-04-04 ms.qmd
Updates

@@
 However, it is possible that those treatments affect tissues differently.
-An alternative hypothesis is that the effects of the prenatal treatments are age-dependent [see @frisone2002social], but our subjucts were tested before maturity (see Supplementary material).
+An alternative hypothesis is that the effects of the prenatal treatments are age-dependent [see @frisone2002social].
+Here, the lizards' age at the beginning of the experiment ranged from 41 to 148 days old in _L.
+delicata_ and 48 to 132 in _L.
+guichenoti_, and when this variable was included in the models, we did no find any significant effect of age (see Supplementary material).
+However, the treatments may have consequences at earlier or later stages of life that are not being captured in our experiment.
 Conversely, the effects of the early environment may likely vary depending on the cognitive task, as evidenced by studies showing variations in the impact of prenatal GCs and temperature on different brain regions [@coomber_independent_1997; @sakata_neural_2000; @lemaire_prenatal_2000].
@@
 #
-refit2 = TRUE
+refit2 = FALSE
 formula <- FC_reversal ~ age.start + trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
@@
 
-Results for L_delicata:
+Results for _L. delicata_:
 ` r summary(model_age_deli)`
 
-Results for L_guichenoti:
+Results for _L. guichenoti_:
 ` r summary(model_age_guich)`

### 2024-04-04 .vdoc.r

@@ -1,630 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: fig-Methods
-#| fig.cap: "Experimental design of early environment manipulation and learning tasks. Panel A represents the early environment manipulation for both species. Panel B shows the habituation phase with the respective three different stages. And panel C represents the associative and reversal tasks; white lids show the ramps where the food reward was not accessible."
-
-knitr::include_graphics("./Others/BEHFLEX_FIG_1.png")
-
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: cleandata
-# Obtain the main df using "./R/1_data_process.R"
-source(here("R", "1_data_process.R"))
-#
-#
-#
-#| label: sampleSize
-# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
-source(here("R", "func.R"))
-#
-specie <- c("delicata", "guichenoti")
-hormone <- c("CORT", "Control")
-temperature <- c("Cold", "Hot")
-#
-n_list <- list()
-#
-for(i in 1:length(specie)){
-  for(k in 1:length(hormone)){
-    for(l in 1:length(temperature)){
-      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
-      }
-    }
-  }
-#
-#
-#
-#
-#
-#| label: models
[…]

### 2024-04-05 ms.qmd
Updates

@@
 We know that our prenatal treatments affect other traits in both species of lizards used in this experiment (unpublished data).
-However, it is possible that those treatments affect tissues differently.
+However, it is possible that the treatments affected tissues differently.
 An alternative hypothesis is that the effects of the prenatal treatments are age-dependent [see @frisone2002social].
@@
 Conversely, the effects of the early environment may likely vary depending on the cognitive task, as evidenced by studies showing variations in the impact of prenatal GCs and temperature on different brain regions [@coomber_independent_1997; @sakata_neural_2000; @lemaire_prenatal_2000].
-These hypotheses are not mutually exclusive and could be tested in future experiments using multiple doses of prenatal CORT treatment, assessing learning using multiple cognitive tasks and at different ages, and measuring the neurophysiological effects on different brain nuclei.
+In addition, prenatal GCs can have programmatic effects on HPA axis sensitivity [@crino_corticosterone_2014], potentially impacting the lizards' sensitivity to stressors.
+This altered stress response may influence learning dynamics through hormetic effects of CORT [@du_dynamic_2009], particularly in stressful contexts; although such effects were not likely observable in our experimental design.
+These hypotheses are not mutually exclusive and could be tested in future experiments using multiple doses of prenatal CORT treatment, assessing learning using multiple cognitive tasks and at different ages, testing the effect of stress during the learning process, and measuring the neurophysiological effects on different brain nuclei.
 
@@
 Model formula: 
-Choice ~ age.start + trial_associative*cort*temp + (1 + trial_associative|lizard_id)
+Choice ~ age.start + trial_associative * cort * temp + (1 + trial_associative|lizard_id)
 
@@
 Results for _L. delicata_:
-` r summary(model_age_deli)`
+```{r, tbl-agedeli, results='asis'}
+#| label: tbl-agedeli
+deli_age_res <- summary(model_age_deli)
+
+```
 
@@
 
-In the figure, the distribution of age per treatment and species:
-```{r, age} 
-#| label: age
+```{r, fig-age} 
+#| label: fig-age
+#| fig.cap: "Distribution of the age of the lizards by treatment and species"
 # Plotting the distribution of the age of the lizards by treatment and species
@@
 knitr::include_graphics("./output/figures/plot_age.png")
+```

### 2024-04-06 ms.qmd
Final updates

@@
 Conversely, the effects of the early environment may likely vary depending on the cognitive task, as evidenced by studies showing variations in the impact of prenatal GCs and temperature on different brain regions [@coomber_independent_1997; @sakata_neural_2000; @lemaire_prenatal_2000].
-In addition, prenatal GCs can have programmatic effects on HPA axis sensitivity [@crino_corticosterone_2014], potentially impacting the lizards' sensitivity to stressors.
-This altered stress response may influence learning dynamics through hormetic effects of CORT [@du_dynamic_2009], particularly in stressful contexts; although such effects were not likely observable in our experimental design.
+In addition, prenatal GCs can have programmatic effects on HPA axis sensitivity, potentially impacting the lizards' sensitivity to stressors [@crino_corticosterone_2014].
+This altered stress response may influence learning dynamics through hormetic effects of CORT [@du_dynamic_2009], particularly in stressful contexts [@taborsky2021towards]; although such effects were not likely observable in our experimental design.
 These hypotheses are not mutually exclusive and could be tested in future experiments using multiple doses of prenatal CORT treatment, assessing learning using multiple cognitive tasks and at different ages, testing the effect of stress during the learning process, and measuring the neurophysiological effects on different brain nuclei.
@@
 #| tbl-cap: "Estimates of Reversal learning slope for all the different treatments per each task, species, and group.
+Here we included only those individuals who made the right choice in 8 out of the last 10 trials in the previous associative task.
 Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
@@
 Results for _L. delicata_:
-```{r, tbl-agedeli, results='asis'}
+```{r, tbl-agedeli, results='asis', out.widht = "26cm"}
 #| label: tbl-agedeli
+#| tbl-cap: "Summary model_age_deli"
 deli_age_res <- summary(model_age_deli)
+# Extract fixed effects names and their corresponding estimates, CIs, etc.
+fixed_effects <- deli_age_res$fixed %>%
+  mutate_all(~ format_dec(., 2))
+Predictors <- rownames(fixed_effects)
+deli_age_tbl_df <- cbind(Predictors, fixed_effects)
+# Convert the fixed effects data frame to a flextable
+flextable(deli_age_tbl_df) %>%
+  set_table_properties(., width = 1) %>%
+  fontsize(size = 10, part = "all")
+```
 
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
 ```
@@
 Results for _L. guichenoti_:
-` r summary(model_age_guich)`
+```{r, tbl-ageguich, results='asis'}
+#| label: tbl-ageguich
+#| tbl-cap: "Summary model_age_guich"
+guich_age_res <- summary(model_age_guich)
+# Extract fixed effects names and their corresponding estimates, CIs, etc.
+fixed_effects <- guich_age_res$fixed %>%
+  mutate_all(~ format_dec(., 2))
+Predictors <- rownames(fixed_effects)
+guich_age_tbl_df <- cbind(Predictors, fixed_effects)
+# Convert the fixed effects data frame to a flextable
+flextable(guich_age_tbl_df)%>%
+  set_table_properties(., width = 1) %>%
+  fontsize(size = 10, part = "all")
+```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
 

### 2024-04-06 R/func.r

@@ -114,7 +114,7 @@ pmcmc <- function(x, null = 0, twotail = TRUE, dir){
 }
 ####################
 ####################
-# Function to format numbers with 2 decimal places
+# Function to format numbers with n decimal places
 #' @title format_dec
 #' @param x The object
 #' @param n The number of decimals
@@ -124,8 +124,8 @@ format_dec <- function(x, n) {
 }
 ####################
 ####################
-# Function to format numbers with 2 decimal places
-#' @title format_dec
+# Function to format p_values with n decimal places
+#' @title format_p
 #' @param x The object
 #' @param n The number of decimals
 format_p <- function(x, n) {

### 2024-04-08 ms.qmd
Updates

@@
 #
+data_age <- clean_df %>%
+  mutate(age.start = as.numeric(age.start)-mean(as.numeric(age.start)))
 refit2 = FALSE
@@
   # Subset the data for the species
-  data_species <- clean_df %>%
+  data_species <- data_age %>%
     filter(species == s)
@@
 # Load the data
-data_age <- read.csv(here("data/Learning.csv"))
+data_age <- clean_df
 # Plot the distribution of the age of the lizards by treatment and species

### 2024-05-17 ms.qmd
Updates

@@
     bibliography: "./bib/refs.bib"
-    csl: "./bib/biology-letters.csl"
+    csl: "./bib/animal-behaviour.csl"
     reference-doc: "./bib/tmpl.docx"
@@
 
-Pablo Recio-Santiago^1^,$\ddagger$ , Dalton C. Leibold^1^, Ondi L. Crino ^1,2^, Kristoffer H. Wild^1,3^, Chris Friesen^4^, Basile Mauclaire^1,5^, Amelia Y. Peardon ^1^, Daniel W.A. Noble^1^
+Pablo Recio^1^,$\ddagger$ , Dalton C. Leibold^1^, Ondi L. Crino ^1,2^, Kristoffer H. Wild^1,3^, Chris Friesen^4^, Basile Mauclaire^1,5^, Amelia Y. Peardon ^1^, Daniel W.A. Noble^1^
 
@@
 In addition to novel environments experienced by parents, offspring also experience potentially stressful environmental conditions that can interact with or amplify parental effects.
-Temperature, in particular, is likely to deviate in invasive populations compared to source populations, having a direct effect on offspring phenotypes with long-lasting consequences [@noble_developmental_2018].
+Temperature, in particular, is likely to deviate in invasive populations compared to source populations, with direct effect on offspring phenotypes with long-lasting consequences in ectotherms [@noble_developmental_2018].
 As such, GCs and temperature are predicted to interact to influence the offspring phenotype with particularly potent effects on brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017] and cognition [@clark_colour_2014; @lui2017chronic].
@@
 guichenoti_ despite the two species having similar life-histories and overlapping distributions [@chapple_know_2011; @chapple_biology_2014].
-Personality has been shown to be different between these two species [@chapple_know_2011; @chapple2012can; @bezzina2014does], which could be related to general cognitive differences that are important for invasion success.
+Personality has been shown to be different between these two species [@chapple_know_2011; @chapple2012can; @bezzina2014does], which could be related to general cognitive differences like learning (**REF**) that are important for invasion success.
 Additionally, early environments are known to affect suites of morphological and behavioural traits differently in each species [@carrasco2023maternal; @kar2023heritability], but the interactive role of maternal CORT and early temperatures has not yet been explored.
@@
 delicata_.
+More specifically, we predicted cold incubation temperatures and CORT treatment to impair behavioural flexibility (**REFs**), and that the combination of both treatments would have the most detrimental effect on behavioural flexibility.
 
@@
 
+#### Methods details
+
+###### Husbandry  
+*Breeding colony* -- We tested juveniles originating from a breeding colony established in the lab since 2019.
+There is a total of 270 and 180 adults of *L.
+delicata* and *L.
+guichenoti* respectively, housed in big containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure.
+Enclosures are provided with non-stick matting, shelter, and several small water dishes.
+Water is given daily, and they are fed approx.
+40 mid-size crickets (*Acheta domestica*) per enclosure three days a week.
+Crickets are dusted with calcium weekly and multivitamin and calcium biweekly.
+To ensure a temperature gradient, we employ a heat chord and a heat lamp following a 12 h light:12 h dark cycle.
+Room temperatures are set to 22-24 Celsius, and warm side of enclosures is usually at 32 Celsius.
+
+*Eggs collection and incubation* -- Between mid-October 2022 to the end of February 2023, we provided females with a place to lay the eggs by means of small boxes (12.5 L x 8.3 W x 5 H cm) with moist vermiculite inside, that were placed in one extreme of the communal enclosures (see above).
+We checked for the presence of eggs in the boxes three days a week.
+After collection, we measured length and width of eggs with a digital caliper to the nearest 0.1 mm and weighed them with a (OHAUS, Model spx123) digital scale ± 0.001g error, and we recorded the clutch and egg identities.
+Then eggs were treated with CORT or vehicle (see CORT and Temperature manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite).
+The cups were covered with cling wrap to retain moisture and left in LATWIT 2X5D-R1160 incubators at two different temperatures (see CORT and Temperature manipulation below) until hatching.
+
+*Hatchlings* -- Eggs in the incubator were checked three times a week for hatchlings.
+After hatchling, we measured juveniles' SVL and Tail Length (TL) with a ruler to the nearest mm and weighed them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
+We then placed hatchlings in individual enclosures (18.7L x 13.2W x 6.3H cm) and provided them with non-stick matting and a small water dish.
+During this period, they were sprayed water every day and received 3-6 small *A.
+domestica* crickets three times a week.
+All care otherwise follows similar protocols to adults (see above).
+
+Two weeks before we started the training phase (see below), lizards were moved to the experimental arena for acclimatation.
+The arenas were individual medium size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the extremes and a water dish on the other.
+These new enclosures were placed in two rooms in 7 different racks associated to 7 different CCTV systems (device model DVR-HP210475) that allowed us to record their behaviour during the experiment (see details below).
+The number of lizards per species and treatment in each rack was counterbalanced to control for any effect of the room or the position of the lizard in the rack.
+During acclimatation and throughout the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin (see protocol below), and water was supplied *ad libitum*.
+We provided a temperature gradient by means of a heat cord and heat lamps in a 12 h light: 12 h dark cycle.
+The temperature of both rooms was set to between 22-24 Celsius.
+
 #### Manipulating Early Thermal and CORT Environments
-To manipulate early thermal environment and CORT, we collected eggs of _L.
-delicata_ and _L.
-guichenoti_ from a lab breeding colony that was established from a Sydney population in 2019.
-The Sydney population is thought to be the source population for invasive populations established on Lord Howe Island [@chapple2016origin].
-Eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (CORT treatment) or the same volume of the vehicle (Control) and were then incubated at different temperatures (Cold – 23ºC ± 3ºC or Hot – 30ºC ± 3ºC) until hatching in a fully factorial design.
-For full details of breeding colony and husbandry see Supplementary Material.
+
+To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (Cold -- 23ºC ± 3ºC or Hot -- 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
+We first allocated eggs to one of two different treatments: in the CORT treatment, eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (vehicle) at a final (10 pg CORT/mL) concentration; in the Control treatment eggs received an equal volume of the vehicle.
+CORT concentration employed in the CORT treatment represents 2 standard deviations above the mean natural concentration obtained in eggs from both species (non-published data).
+Then, eggs were incubated in one of the two previously mentioned temperature regimes (Cold or Hot) until hatching.
+This temperatures represent the upper and lower limit of the natural incubation temperatures [**REF**].
+The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.
 
 #### Quantifying Behavioural Flexibility  
-Briefly, the learning test was divided in three main phases: a habituation phase where lizards had to learn to eat a frozen-thawed cricket from white 3D-printed polylactic acid (PLA) ramps (9 L x 4 W x 5 H cm).
-The habituation phase lasted 38 days.
-This was followed by a colour association task where lizards had to associate the food reward with one of two colours (red or blue) (@fig-Methods Associative task).
-The associative learning task lasted 35 days.
-Finally, to quantify behavioural flexibility, we reversed the previously trained colour (red or blue) so that the lizards needed to learn to associate the food with the opposite colour (@fig-Methods Reversal task).
-The reversal learning task lasted a total of 40 days.
-Lizards were tested once daily between 11 am to 12 pm when they were most active.
+Briefly, the learning test was divided in three main phases: a habituation phase where lizards had to learn to eat a frozen-thawed cricket from white 3D-printed polylactic acid (PLA) ramps (9 L x 4 W x 5 H cm); a colour association task where lizards had to associate the food reward with one of two colours (red or blue) (@fig-Methods Associative task); and finally, to quantify behavioural flexibility, we reversed the previously trained colour (red or blue) so that the lizards needed to learn to associate the food with the opposite colour (@fig-Methods Reversal task).
 
-In associative and reversal tasks we used three different ramps that were identical in size and shape to the ones used in the habituation phase.
-The colours of the ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
-To avoid the influence of chemical cues, we placed the food reward in all three ramps, but in two of them the cricket was covered by immovable small lids with holes on the top.
-To control for potential colour biases, we assigned one group of lizards within each treatment to associate food in the blue ramp followed by the red ramp in the reversal, while in the other group the order was reversed.
+The habituation phase was divided into three stages: in the first stage, the reward, a small, frozen cricket (*A.
+domestica*) was placed in an opaque petri dish (3D x 1.6H cm) (@fig-Methods Habituation phase, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods Habituation phase, Stage 2); and in the third stage, the cricket was left inside a well (3D x 1.75H cm) on top of the ramp (Fig.
+@fig-Methods Habituation phase, Stage 3).
+Trials in every stage lasted one hour, begining when the feeding block (petri dish, ramp, or both) was placed inside the enclosure and finishing when we took the feeding block away.
+We recorded whether the cricket had been consumed or not and we considered a stage as completed if the lizards ate the crickets in at least 5 out of 6 trials.
+This phase lasted 38 days, and only in one case we decided not to use the lizard in the next phases because it did not pass the aqcuisition criterium.
+
+In the colour association (Associative task in Fig.
+@fig-Methods) and reversal task (Reversal task in @fig-Methods B), we used three ramps that were identical in shape and size but differ in the colour.
+The colours of these ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
+However, to control for potential colour biases, we assigned one group of lizards within each treatment to associate food in the blue ramp followed by the red ramp in the reversal, while in the other group the order was reversed.
+As in the last stage of the habituation phase, we placed the cricket inside the wells of the ramps, but then two of them were covered with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp.
+The food reward was placed in all three ramps to avoid lizards using prey chemical cues, that were released in the closed wells through a series of small holes on the top of the lids.
 In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
+Lizards were tested in the association task once a day for 35 days and once a day for 40 days in teh reversal.
 
+The full experiment was performed between the 6^th^ of March until the 26^th^ of June 2023.
+Tests were made between 11 to 12 am, when the lizards were active.
+Trials in the learning phases (colour associative task and reversal tasks) were recorded with different CCTV systems always using the same camera per individual.
 We recorded whether the animal chose the correct ramp first or not.
@@
 We included a random intercept and slope (trial) for each lizard in our models.
+We also incorporated the clutch identity as a random factor.
 We used the posterior distributions of parameters from these models to test for differences in learning rate between treatments and species.
@@
 source(here("R", "func.R"))
-# Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
+# Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id) + (1|clutch)
 ## A) L. delicata
@@
 # Suplementary Material
-
-#### Methods details
-
-###### Husbandry  
-*Breeding colony* -- We tested juveniles originating from a breeding colony established in the lab since 2019.
-There is a total of 270 and 180 adults of *L.
-delicata* and *L.
-guichenoti* respectively, housed in big containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure.
-Enclosures are provided with non-stick matting, shelter, and several small water dishes.
-Water is given daily, and they are fed approx.
-40 mid-size crickets (*Acheta domestica*) per enclosure three days a week.
-Crickets are dusted with calcium weekly and multivitamin and calcium biweekly.
-To ensure a temperature gradient, we employ a heat chord and a heat lamp following a 12 h light:12 h dark cycle.
-Room temperatures are set to 22-24 Celsius, and warm side of enclosures is usually at 32 Celsius.
-
-*Eggs collection and incubation* -- Between mid-October 2022 to the end of February 2023, we provided females with a place to lay the eggs by means of small boxes (12.5 L x 8.3 W x 5 H cm) with moist vermiculite inside, that were placed in one extreme of the communal enclosures (see above).
-We checked for the presence of eggs in the boxes three days a week.
-After collection, we measured length and width of eggs with a digital caliper to the nearest 0.1 mm and weighed them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
-Then eggs were treated with CORT or vehicle (see CORT and Temperature manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite).
-The cups were covered with cling wrap to retain moisture and left in LATWIT 2X5D-R1160 incubators at two different temperatures (see CORT and Temperature manipulation below) until hatching.
-
-*Hatchlings* -- Eggs in the incubator were checked three times a week for hatchlings.
-After hatchling, we measured juveniles' SVL and Tail Length (TL) with a ruler to the nearest mm and weighed them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
-We then placed hatchlings in individual enclosures (18.7L x 13.2W x 6.3H cm) and provided them with non-stick matting and a small water dish.
-During this period, they were sprayed water every day and received 3-6 small *A.
-domestica* crickets three times a week.
-All care otherwise follows similar protocols to adults (see above).
-
-Two weeks before we started the training phase (see below), lizards were moved to the experimental arena for acclimatation.
-The arenas were individual medium size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the extremes and a water dish on the other.
-These new enclosures were placed in two rooms in 7 different racks associated to 7 different CCTV systems (device model DVR-HP210475) that allowed us to record their behaviour during the experiment (see details below).
-The number of lizards per species and treatment in each rack was counterbalanced to control for any effect of the room or the position of the lizard in the rack.
-During acclimatation and throughout the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin (see protocol below), and water was supplied *ad libitum*.
-We provided a temperature gradient by means of a heat cord and heat lamps in a 12 h light: 12 h dark cycle.
-The temperature of both rooms was set to between 22-24 Celsius.
-
-###### CORT and Temperature manipulation  
-To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (Cold -- 23ºC ± 3ºC or Hot -- 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
-We first allocated eggs to one of two different treatments: CORT treatment, where eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (vehicle) at a final (10 pg CORT/mL) concentration (CORT treatment); and a Control treatment, where eggs received an equal volume of the vehicle.
-CORT concentration employed in the CORT treatment represents 2 standard deviations above the mean natural concentration obtained in eggs from both species (non-published data).
-Then, eggs were incubated in one of the two previously mentioned temperature regimes (Cold or Hot) until hatching.
-The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.
-
-###### Learning task
-The habituation phase was divided into three stages: in the first stage, the reward, a small, frozen cricket (*A.
-domestica*) was placed in an opaque petri dish (3D x 1.6H cm) (@fig-Methods B, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods B, Stage 2); and in the third stage, the cricket was left inside a well (3D x 1.75H cm) on top of the ramp (Fig.
-@fig-Methods B, Stage 3).
-Trials in every stage lasted one hour, begining when the feeding block (petri dish, ramp, or both) was placed inside the enclosure and finished when we took the feeding block away.
-We recorded whether the cricket had been consumed or not and we considered a stage as completed if the lizards ate the crickets in at least 5 out of 6 trials.
-This phase lasted 38 days, and only in one case we decided not to use the lizard in the next phases because its behaviour was not consistent.
-In the associative phase, we used three ramps that were identical in shape and size but differ in the colour (Associative task in Fig.
-@fig-Methods B).
-As in the last stage of the habituation phase, we placed the cricket inside the wells of the ramps, but then two of them were covered with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp.
-The food reward was placed in all three wells to avoid lizards using prey chemical cues, that were released in the closed wells through a series of small holes on the top of the lids.
-The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
-However, we decided to split the lizards in two groups to control for potential colour preference that could bias our results.
-One group of lizards was assigned the blue ramp as the correct choice (i.e., the ramp with the non-covered frozen cricket) in the associative task and the red ramp in the reversal, while the other group was assigned red as correct for the associative and blue for the reversal.
-In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
-Lizards were tested in this task once a day for 35 days.
-After the colour association phase, we performed a choice reversal task (Reversal task in @fig-Methods B).
-Here, the attainability of prey was indicated by a different colour from the reversal, requiring the lizards to form a novel association between the new colour and the food reward.
-This test was done once a day for 40 days.
-
-We performed the full experiment between the 6^th^ of March until the 26^th^ of June 2023, between 11 to 12 am, when the lizards were active.
-Trials in the learning phases (colour associative task and reversal tasks) were recorded with different CCTV systems always using the same camera per individual.
-Videos were analysed manually using a standard video player (IINA) by PR, who recorded whether the first choice made by each subject was the correct feeder or not.
-We considered a choice was made if the head of the lizard was inside the well of one of the ramps.
-We considered a trial failed if there was no choice in one hour of recording and those trials were considered as 'non data' in the analyses.
-We excluded from our analyses those individuals with more than 15 trials failed (i.e.
-they did not make a choice), and we considered the first trial to be the first one where the individual made a choice.
-We also considered individuals to be reinforced if the cricket was eaten after the test independently of whether their initial choice was correct or not.
-
-```{r, results='asis', echo=FALSE}
-cat("\\newpage")
-```
 
@@
 Model formula: 
-Choice ~ age.start + trial_associative * cort * temp + (1 + trial_associative|lizard_id)
+Choice ~ age.start + trial_associative * cort * temp + (1 + trial_associative|lizard_id) + (1|clutch)
 
@@
 refit2 = FALSE
-formula <- FC_reversal ~ age.start + trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
+formula <- FC_reversal ~ age.start + trial_reversal*cort*temp + (1 + trial_reversal|lizard_id) + (1|clutch)
 species <- c("delicata", "guichenoti")

### 2024-05-17 .vdoc.r

@@ -1,0 +1,665 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of early environment manipulation and learning tasks. Panel A represents the early environment manipulation for both species. Panel B shows the habituation phase with the respective three different stages. And panel C represents the associative and reversal tasks; white lids show the ramps where the food reward was not accessible."
+
+knitr::include_graphics("./Others/BEHFLEX_FIG_1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleandata
+# Obtain the main df using "./R/1_data_process.R"
+source(here("R", "1_data_process.R"))
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(k in 1:length(hormone)){
+    for(l in 1:length(temperature)){
+      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
+      }
+    }
+  }
+#
+#
+#
+#
+#
+#| label: models
[…]

### 2024-05-17 R/func.r

@@ -32,7 +32,7 @@ sample <- function(df, sp, corti, therm){
 #' @param refit To choose whether to refit the models (TRUE, default) or use the ones already made (FALSE)
 #' @return Raw posteriors of fitted brm model for each treatment, species, and group (df)
 fit_m <- function(df, sp, com, refit = TRUE) {
-  formula <- (FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)) 
+  formula <- (FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id) + (1|clutch)) 
   #Specify species
     if (sp == "deli"){
       sp_data <- df %>%

### 2024-05-17 .vdoc.r
Updates

@@ -74,13 +74,6 @@ pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4,
 #
 #
 #
-#
-#
-#
-#
-#
-#
-#
 #| label: fig-Methods
 #| fig.cap: "Experimental design of early environment manipulation and learning tasks. Panel A represents the early environment manipulation for both species. Panel B shows the habituation phase with the respective three different stages. And panel C represents the associative and reversal tasks; white lids show the ramps where the food reward was not accessible."
 
@@ -128,10 +121,10 @@ for(i in 1:length(specie)){
 source(here("R", "func.R"))
 # Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id) + (1|clutch)
 ## A) L. delicata
-deli <- fit_m(clean_df, "deli", "complete",  refit = FALSE)
+deli <- fit_m(clean_df, "deli", "complete",  refit = TRUE)
 write.csv(deli, file= "./output/Checking/deli.csv")
 ## B) L. guichenoti
-guich <- fit_m(clean_df, "guich", "complete", refit = FALSE)
+guich <- fit_m(clean_df, "guich", "complete", refit = TRUE)
 write.csv(guich, file= "./output/Checking/guich.csv")
 #
 #
@@ -410,10 +403,10 @@ for(i in 1:length(specie)){
 source(here("R", "func.R"))
 # Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id) + (1|clutch)
 ## A) L. delicata
-deli_2 <- fit_m(clean_df_2, "deli", "suppl", refit = TRUE)
+deli_2 <- fit_m(clean_df_2, "deli", "suppl", refit = FALSE)
 write.csv(deli_2, file= "./output/Checking/deli.csv")
 ## B) L. guichenoti
-guich_2 <- fit_m(clean_df_2, "guich", "suppl", refit = TRUE)
+guich_2 <- fit_m(clean_df_2, "guich", "suppl", refit = FALSE)
 write.csv(guich_2, file= "./output/Checking/guich.csv")
 #
 #

### 2024-05-17 .vdoc.r
Updates

@@ -1,658 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: fig-Methods
-#| fig.cap: "Experimental design of early environment manipulation and learning tasks. Panel A represents the early environment manipulation for both species. Panel B shows the habituation phase with the respective three different stages. And panel C represents the associative and reversal tasks; white lids show the ramps where the food reward was not accessible."
-
-knitr::include_graphics("./Others/BEHFLEX_FIG_1.png")
-
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: cleandata
-# Obtain the main df using "./R/1_data_process.R"
-source(here("R", "1_data_process.R"))
-#
-#
-#
-#| label: sampleSize
-# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
-source(here("R", "func.R"))
-#
-specie <- c("delicata", "guichenoti")
-hormone <- c("CORT", "Control")
-temperature <- c("Cold", "Hot")
-#
-n_list <- list()
-#
-for(i in 1:length(specie)){
-  for(k in 1:length(hormone)){
-    for(l in 1:length(temperature)){
-      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
-      }
-    }
-  }
-#
-#
-#
-#
-#
-#| label: models
[…]

### 2024-05-20 ms.qmd
Updates

@@
 ## Introduction
-Behavioural flexibility describes the ability of individuals to adjust behaviour adaptively in response to internal or external changes in the environment [@brown2010behavioral].
-It comprises a suite of behaviours, including problem-solving and innovation [@brown2010behavioral], that are predicted to be crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can].
-Species with greater behavioural flexibility are expected to be more likely to survive and establish in new habitats because behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can].
-For instance, bird species that are successful invaders have a higher frequency of foraging innovations compared to closely related species without a history of invasions [@sol2000behavioural].
-According to the 'adaptive flexibility hypothesis', behavioural flexibility is most relevant during introduction, establishment, and the spread of an invasive population [@wright2010behavioral; @chapple2012can; @szabo2020can].
-In mammals, birds, reptiles and amphibians, relative brain size has been shown to be a good predictor of behavioural flexibility and invasive success [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
-However, the brain is also sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004], creating uncertainty about how environmental conditions faced by early invaders might impact behavioural flexibility and thus the probability of invasion success.
+Behavioural flexibility describes the ability of individuals to adjust behaviour adaptively in response to changes in the internal or external environment [@brown2010behavioral].
+It comprises a suite of behaviours, including problem-solving or innovation [@brown2010behavioral], that can be beneficial for adapting to novel circumstances [@szabo2020can; @szulkin2020urban].
+Species with greater behavioural flexibility are expected to be more resilient to environmental changes because behaving flexibly is predicted to be crucial for exploiting new resources and facing new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can; @szulkin2020urban].
+For example, shifting hydration activity to day hours instead of hydrating during the night alone, allows cane toads to survive in semi-arid regions of Australia [@webb2014behavioural]; and succesful colonisation of new environments by birds is related to higher frequency of foraging innovations [@sol2000behavioural].
+Although there is limited understanding of the physiological mechanisms involved in animals' ability to behave flexibly, relative brain size has been shown to be a good predictor of behavioural flexibility in mammals, birds, reptiles and amphibians [@sol2000behavioural; @sol2008brain; @amiel_smart_2011].
+This suggests that behavioural flexibility is likely to be underpinned by neural mechanisms, and that alterations in these mechanisms may impact animals' ability to respond to novel situations.
+In this sense, the brain is considered especially sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004], creating uncertainty about how the conditions faced during early life stages might impact behavioural flexibility.
 
-Novel environments faced by invasive populations introduce organisms to a plethora of unfamiliar and potentially stressful situations.
-Sensory systems detect and transmit environmental signals to instigate adaptive physiological and behavioural adjustments – responses  that are mediated by glucocorticoids (GCs) [@sapolsky_how_2000].
+The conditions in which the organisms develop can be altered by the circumstances faced by the parents.
+**For example** .
+Under stressful situations, animal's sensory systems detect and transmit environmental signals to instigate adaptive physiological and behavioural adjustments – responses that are mediated by glucocorticoids (GCs) [@sapolsky_how_2000].
 Glucocorticoids can be transmitted to offspring and influence their phenotype and development through transgenerational effects [@Crino_2023].
-In addition to novel environments experienced by parents, offspring also experience potentially stressful environmental conditions that can interact with or amplify parental effects.
-Temperature, in particular, is likely to deviate in invasive populations compared to source populations, with direct effect on offspring phenotypes with long-lasting consequences in ectotherms [@noble_developmental_2018].
-As such, GCs and temperature are predicted to interact to influence the offspring phenotype with particularly potent effects on brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017] and cognition [@clark_colour_2014; @lui2017chronic].
-While behavioural flexibility is recognised as an important behavioural phenotype for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can], we know little about how novel environmental stressors, such as GCs or temperature, impact behavioural flexibility.
-Such knowledge is crucial for understanding the potential for invasive populations to adapt to new environments and the potential for invasion success.
+In addition to the environments experienced by parents, offspring also experience potentially stressful environmental conditions that can interact with or amplify parental effects.
+For instance, coping stress style is related to nest-site selection in eider ducks [@seltmann2014boldness], and snapping turtles select nest micro-habitats 2ºC colder in areas with high degree of human disturbance [@kolbe2002impact].
+This way, parental effects like transmitted GCs, are predicted to interact with other environmental factors like temperature to influence the offspring phenotype.
+Furthermore, both GCs and temperature are expected to exert potent effects on brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017] and cognition [@clark_colour_2014; @lui2017chronic].
+[**EXAMPLE Gcs and beh flexibility + EXAMPLE temp and beh flexibility**].
+Although behaving flexibly is essential for coping with environmental changes, little is known about how developmental GCs and temperature impact behavioural flexibility.
 
-Here, we studied the effects of prenatal temperature and the glucocorticoid, corticosterone (CORT) (the main GC in reptiles) [@Crino_2023], on behavioural flexibility in two species with distinct histories of invasion success, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+Here, we studied the effects of prenatal temperature and corticosterone (CORT) (the main GC in reptiles) [@Crino_2023], on behavioural flexibility in two species of reptiles, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_).
@@
 guichenoti_ despite the two species having similar life-histories and overlapping distributions [@chapple_know_2011; @chapple_biology_2014].
-Personality has been shown to be different between these two species [@chapple_know_2011; @chapple2012can; @bezzina2014does], which could be related to general cognitive differences like learning (**REF**) that are important for invasion success.
-Additionally, early environments are known to affect suites of morphological and behavioural traits differently in each species [@carrasco2023maternal; @kar2023heritability], but the interactive role of maternal CORT and early temperatures has not yet been explored.
+[**IMPORTANCE OF BEHAVIOURAL FLEXIBILITY ON INVASION SUCCESS**] Additionally, early environments are known to affect suites of morphological and behavioural traits differently in each species [@carrasco2023maternal; @kar2023heritability], but the interactive role of maternal CORT and early temperatures has not yet been explored.
 Differences in the relative impact of early environments on behavioural flexibility may help explain differing invasion success between the two species.
-We predict that _L.
+[**How can environment affect differently based on invassive success??**].
+In this regard, we predict that _L.
 delicata_, on average, will perform more proficiently in the task compared to _L.
@@
 delicata_.
-More specifically, we predicted cold incubation temperatures and CORT treatment to impair behavioural flexibility (**REFs**), and that the combination of both treatments would have the most detrimental effect on behavioural flexibility.
+More specifically, we predict cold incubation temperatures and CORT treatment to impair behavioural flexibility (**REFs**), and that the combination of both treatments to have the most detrimental effect on behavioural flexibility.
 
@@
 
-#### Methods details
-
-###### Husbandry  
+#### Husbandry  
 *Breeding colony* -- We tested juveniles originating from a breeding colony established in the lab since 2019.
@@
 However, to control for potential colour biases, we assigned one group of lizards within each treatment to associate food in the blue ramp followed by the red ramp in the reversal, while in the other group the order was reversed.
-As in the last stage of the habituation phase, we placed the cricket inside the wells of the ramps, but then two of them were covered with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp.
+As in the last stage of the habituation phase, we placed the cricket inside the wells of the ramps, but then two of them were covered with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in one ramp.
 The food reward was placed in all three ramps to avoid lizards using prey chemical cues, that were released in the closed wells through a series of small holes on the top of the lids.
 In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
-Lizards were tested in the association task once a day for 35 days and once a day for 40 days in teh reversal.
+Lizards were tested in the association task once a day for 35 days and once a day for 40 days in the reversal.
 
@@
 We considered statistical significance if p~mcmc~  < 0.05.
+
+#### Ethical note
+We collected subjects from a breeding colony kept in the lab since 2019.
+Both the breeding animals and the ones used in this experiment were provided humane laboratory housing, with thermorregulation opportunity, light and humidity conditions (see above for details).
+Lizards in the colony received food *ad libitum* while the subjects in the experiment were feed one cricket daily during the experiment.
+All lizards were handled minimally to avoid stress.
+Experimental procedures and laboratory housing complied with Australian law and were approved by the Australian National University Animal Experimentation Ethics Committee (A2022_33).
+Upon completion of experimental trials, lizards were kept in their enclosure for until they were euthanized following standard humane procedures.
 
@@
 guichenoti_).
-Despite sharing life-history traits, only _L.
-delicata_ has proven successful in colonising various global regions [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI], and we predicted this may relate to higher behavioural flexibility.
-Furthermore, we expected behavioural flexibility in this species to be less susceptible to the effect of early environment since this trait can be adaptive in several stages of invasion involving more than one generation.
-Nevertheless, we did not find significant differences between treatments or species when we compared their performance in a reversal task.
-We found that, on average, all the lizards from the four treatments and the two species learned the reversal task - indicated by estimated slopes that are significantly different from zero - and that they learn, on average, at the same rate.
-Furthermore, these results were consistent when only those individuals who performed better in the previous associative task were included (see Supplementary material).
-
-Previous studies have shown that _L.
-delicata_ more readily explores novel environments than _L.
-guichenoti_, which can be advantageous during colonisation [@chapple_know_2011].
-However, Bezzina _et al._ [@bezzina2014does] found no differences in learning between the two skinks in an associative learning task.
-Our results align with the latter study and suggest that behavioural flexibility does not differ between these species.
-In addition, we did not find any effect of the treatments on either species.
-Both results contrast our original predictions and may indicate that other aspects of their biology are more relevant for _L.
-delicata_'s success as invaders than behavioural flexibility.
-For instance, the mentioned differences in exploratory behaviour can be the key factor explaining why _L.
-delicata_ and not _L.
-guichenoti_ is better at colonising new areas, since exploring more can also enhance the ability to effectively locate novel resources in _L.
-delicata_ [@chapple_know_2011].
 
@@
 
+Despite sharing life-history traits, only _L.
+delicata_ has proven successful in colonising various global regions [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI], and we predicted this may relate to higher behavioural flexibility.
+Furthermore, we expected behavioural flexibility in this species to be less susceptible to the effect of early environment since this trait can be adaptive in several stages of invasion involving more than one generation.
+Nevertheless, we did not find significant differences between treatments or species when we compared their performance in a reversal task.
+We found that, on average, all the lizards from the four treatments and the two species learned the reversal task - indicated by estimated slopes that are significantly different from zero - and that they learn, on average, at the same rate.
+Furthermore, these results were consistent when only those individuals who performed better in the previous associative task were included (see Supplementary material).
+
+Previous studies have shown that _L.
+delicata_ more readily explores novel environments than _L.
+guichenoti_, which can be advantageous during colonisation [@chapple_know_2011].
+However, Bezzina _et al._ [@bezzina2014does] found no differences in learning between the two skinks in an associative learning task.
+Our results align with the latter study and suggest that behavioural flexibility does not differ between these species.
+In addition, we did not find any effect of the treatments on either species.
+Both results contrast our original predictions and may indicate that other aspects of their biology are more relevant for _L.
+delicata_'s success as invaders than behavioural flexibility.
+For instance, the mentioned differences in exploratory behaviour can be the key factor explaining why _L.
+delicata_ and not _L.
+guichenoti_ is better at colonising new areas, since exploring more can also enhance the ability to effectively locate novel resources in _L.
+delicata_ [@chapple_know_2011].
+
 In conclusion, our results indicate that lizards performed the reversal learning task, a measure of behavioural flexibility, at similar rates, with no discernible differences between treatments or species.
@@
 Nevertheless, it remains possible that the effects of the early environment are task-dependent, and future studies should explore performance across different cognitive tasks and the effects of both treatments on brain function.
-
-## Ethics  
-Experiments complied with Australian law and were approved by the Australian National University Animal Experimentation Ethics Committee (A2022_33).
 

### 2024-05-22 ms.qmd
Updates

@@
 Species with greater behavioural flexibility are expected to be more resilient to environmental changes because behaving flexibly is predicted to be crucial for exploiting new resources and facing new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can; @szulkin2020urban].
-For example, shifting hydration activity to day hours instead of hydrating during the night alone, allows cane toads to survive in semi-arid regions of Australia [@webb2014behavioural]; and succesful colonisation of new environments by birds is related to higher frequency of foraging innovations [@sol2000behavioural].
+For example, survival of cane toads in semi-arid regions of Australia depend on adjusting their hydration activities to include daytime hours, rather than relying solely on nighttime [@webb2014behavioural]; while succesful colonisation of new environments by birds is related to higher frequency of foraging innovations [@sol2000behavioural].
 Although there is limited understanding of the physiological mechanisms involved in animals' ability to behave flexibly, relative brain size has been shown to be a good predictor of behavioural flexibility in mammals, birds, reptiles and amphibians [@sol2000behavioural; @sol2008brain; @amiel_smart_2011].
-This suggests that behavioural flexibility is likely to be underpinned by neural mechanisms, and that alterations in these mechanisms may impact animals' ability to respond to novel situations.
-In this sense, the brain is considered especially sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004], creating uncertainty about how the conditions faced during early life stages might impact behavioural flexibility.
+This suggests that behavioural flexibility is likely to be underpinned by complex neural mechanisms, and that alterations in these mechanisms may impact animals' ability to respond to novel situations.
+In this sense, the brain is considered especially sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004], creating uncertainty about how the conditions faced during early life might impact behavioural flexibility.
 
 The conditions in which the organisms develop can be altered by the circumstances faced by the parents.
-**For example** .
+For instance, exposing threespine sticklebacks females to a model predator while yolking eggs affected offspring tedency to use social cues [@feng2015effect].
 Under stressful situations, animal's sensory systems detect and transmit environmental signals to instigate adaptive physiological and behavioural adjustments – responses that are mediated by glucocorticoids (GCs) [@sapolsky_how_2000].
@@
 In addition to the environments experienced by parents, offspring also experience potentially stressful environmental conditions that can interact with or amplify parental effects.
-For instance, coping stress style is related to nest-site selection in eider ducks [@seltmann2014boldness], and snapping turtles select nest micro-habitats 2ºC colder in areas with high degree of human disturbance [@kolbe2002impact].
-This way, parental effects like transmitted GCs, are predicted to interact with other environmental factors like temperature to influence the offspring phenotype.
-Furthermore, both GCs and temperature are expected to exert potent effects on brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017] and cognition [@clark_colour_2014; @lui2017chronic].
-[**EXAMPLE Gcs and beh flexibility + EXAMPLE temp and beh flexibility**].
-Although behaving flexibly is essential for coping with environmental changes, little is known about how developmental GCs and temperature impact behavioural flexibility.
+For example, human disturbance alters snapping turtles' nest-site choice, ultimately impacting the temperature at which eggs are incubated [@kolbe2002impact].
+This way, parental effects like transmitted GCs, are predicted to interact with other factors from the early environment to influence the offspring phenotype.
+Both GCs and temperature are known to exert potent effects on brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017] and cognition [@clark_colour_2014; @lui2017chronic], but little is known about how their ineraction could affect behavioural flexibility.
+Since behaving flexibly is essential for facing novel circumstances, studying the interactive effect of early environment on behavioural flexibility is crucial if we aim to understand animals' capability to adapt to environmental changes.
 
@@
 guichenoti_).
-_Lampropholis delicata_ has been successful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI], but the same is not true of _L.
-guichenoti_ despite the two species having similar life-histories and overlapping distributions [@chapple_know_2011; @chapple_biology_2014].
-[**IMPORTANCE OF BEHAVIOURAL FLEXIBILITY ON INVASION SUCCESS**] Additionally, early environments are known to affect suites of morphological and behavioural traits differently in each species [@carrasco2023maternal; @kar2023heritability], but the interactive role of maternal CORT and early temperatures has not yet been explored.
-Differences in the relative impact of early environments on behavioural flexibility may help explain differing invasion success between the two species.
-[**How can environment affect differently based on invassive success??**].
-In this regard, we predict that _L.
+Both species have similar life-histories and overlapping distributions [@chapple_know_2011; @chapple_biology_2014], but only _Lampropholis delicata_ has been successful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI].
+The differences in invassion success between both skinks may be driven by disparities in behavioural flexibility, a prominent quality in other invassive species [@sol2000behavioural; @sol2008brain; @wright2010behavioral; @amiel_smart_2011; @chapple2012can].
+However, the relative impact of early environments on behavioural flexibility remains unexplored.
+Early environment affects suites of morphological and behavioural traits differently in each species [@carrasco2023maternal; @kar2023heritability], but we are uncertain about the interactive role of maternal CORT and early temperatures on behavioural flexibility.
+We stigate here the effect of early environment on behavioural flexibility in both species by manipulating CORT and incubation temperature and then subjecting hatchlings to a reversal learning task.
+Since invassive species are expected to behave more flexibly [@sol2000behavioural; @sol2008brain; @wright2010behavioral; @amiel_smart_2011; @chapple2012can], we predict that _L.
 delicata_, on average, will perform more proficiently in the task compared to _L.
 guichenoti_.
-We also anticipate prenatal CORT and temperature to affect the behavioural flexibility of both species, and that _L.
+Furthermore, given that behavioural flexibility can be advantageous during different stages of invasion  [@wright2010behavioral; @chapple2012can; @szabo2020can], and that these phases can involve more than one generation, we anticipate that _L.
 guichenoti_ will be more impacted by the prenatal environment than _L.
 delicata_.
-More specifically, we predict cold incubation temperatures and CORT treatment to impair behavioural flexibility (**REFs**), and that the combination of both treatments to have the most detrimental effect on behavioural flexibility.
+Finally, we predic that both cold incubation temperatures and CORT treatment will impair behavioural flexibility [@clark_colour_2014; @lui2017chronic], and that the combination of both treatments to have the most detrimental effect on behavioural flexibility.
 
@@
 To ensure a temperature gradient, we employ a heat chord and a heat lamp following a 12 h light:12 h dark cycle.
-Room temperatures are set to 22-24 Celsius, and warm side of enclosures is usually at 32 Celsius.
+Room temperatures are set to 22-24ºC, and warm side of enclosures is usually at 32ºC.
 
@@
 
-Two weeks before we started the training phase (see below), lizards were moved to the experimental arena for acclimatation.
+Two weeks before starting the training phase (see below), lizards were moved to the experimental arena for acclimatation.
 The arenas were individual medium size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the extremes and a water dish on the other.
@@
 We provided a temperature gradient by means of a heat cord and heat lamps in a 12 h light: 12 h dark cycle.
-The temperature of both rooms was set to between 22-24 Celsius.
+The temperature of both rooms was set to between 22-24ºC.
 
@@
 To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (Cold -- 23ºC ± 3ºC or Hot -- 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
-We first allocated eggs to one of two different treatments: in the CORT treatment, eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (vehicle) at a final (10 pg CORT/mL) concentration; in the Control treatment eggs received an equal volume of the vehicle.
+We first allocated eggs onto one of two different treatments: in the CORT treatment, eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (vehicle) at a final (10 pg CORT/mL) concentration; in the Control treatment eggs received an equal volume of the vehicle.
 CORT concentration employed in the CORT treatment represents 2 standard deviations above the mean natural concentration obtained in eggs from both species (non-published data).
 Then, eggs were incubated in one of the two previously mentioned temperature regimes (Cold or Hot) until hatching.
-This temperatures represent the upper and lower limit of the natural incubation temperatures [**REF**].
+This temperatures represent the upper and lower limit of the natural incubation temperatures [@qualls2000post; @cheetham2011embryonic].
 The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.

### 2024-05-24 ms.qmd
Updates

@@
 ## Abstract
-Behavioural flexibility is crucial for animals adapting to and colonizing new environments.
-However, novel environmental conditions experienced during early development can profoundly impact behavioural flexibility making it unclear how invasive populations establish in new locations.
-Given the advantages associated with behaving flexibly during the invasion process we predict that behavioural flexibility in invasive species should be less susceptible to the impacts of early environmental conditions.
+Behavioural flexibility is crucial for animals adapting to environmental changes.
+However, the conditions experienced during early development can profoundly impact behavioural flexibility making it unclear how populations will respond to novel circumstances.
+Stressful situations faced by the parents can have a direct impact on animals' cognition through the transmission of glucocorticoids - stress-related hormones.
+At the same time, stressful conditions can influence parental behaviour during nesting and, in consequence the developmental conditions such as temperature.
 Here, we investigated the interactive effects of prenatal corticosterone (CORT) and temperature on behavioural flexibility in two lizard species, _Lampropholis delicata_ and _L.
-guichenoti_, with distinct histories of invasion.
+guichenoti_.
 We manipulated prenatal CORT levels and incubation temperature in a 2x2 factorial design, and then assessed behavioural flexibility through a reversal learning task.
+We hypothesized prenatal CORT and cold temperatures to impair with lizards' performance in the reversal task.
+Also, given _L.
+delicata_ success as an invassive species, we expected this species to behave more flexible and be less affected by the incubation conditions.
 Contrary to our expectations, we found no significant differences in the reversal learning rate between treatments or species.
-Behavioural flexibility appears to be robust to prenatal temperature and CORT which may be one reason why _L.
-delicata_ has been so successful as an invasive species.
-However, the lack of difference in reversal learning between _L.
+Behavioural flexibility appears to be robust to prenatal temperature and CORT in both species.
+Furthermore, the lack of difference in reversal learning between _L.
 delicata_ and _L.
@@
 The conditions in which the organisms develop can be altered by the circumstances faced by the parents.
-For instance, exposing threespine sticklebacks females to a model predator while yolking eggs affected offspring tedency to use social cues [@feng2015effect].
+For instance, exposing threespine sticklebacks females to a model predator while yolking eggs, affected offspring tedency to use social cues [@feng2015effect].
 Under stressful situations, animal's sensory systems detect and transmit environmental signals to instigate adaptive physiological and behavioural adjustments – responses that are mediated by glucocorticoids (GCs) [@sapolsky_how_2000].
@@
 For example, human disturbance alters snapping turtles' nest-site choice, ultimately impacting the temperature at which eggs are incubated [@kolbe2002impact].
-This way, parental effects like transmitted GCs, are predicted to interact with other factors from the early environment to influence the offspring phenotype.
-Both GCs and temperature are known to exert potent effects on brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017] and cognition [@clark_colour_2014; @lui2017chronic], but little is known about how their ineraction could affect behavioural flexibility.
+Because animals' responses to abrupt changes in temperature are mediated by GCs [@Crino_2023], and this response can affect animals' decision-making while nesting, GCs transmission and early therma environment are predicted to interact to shape offspring phenotype.
+In this sense, both GCs and temperature are known to exert potent effects on brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017] and cognition [@clark_colour_2014; @lui2017chronic], but little is known about how their ineraction could affect behavioural flexibility.
 Since behaving flexibly is essential for facing novel circumstances, studying the interactive effect of early environment on behavioural flexibility is crucial if we aim to understand animals' capability to adapt to environmental changes.
@@
 guichenoti_).
+We expected incubation conditions to influence behavioural flexibility in both species; and we also predicted that _L.
+delicata_ would be more flexible than _L.
+guichenoti_ and less affected by the early environment.
+Nevertheless, we did not find significant differences between treatments or species when we compared their performance in a reversal task.
+Our results show that, on average, all the lizards from the four treatments and the two species learned the reversal task - indicated by estimated slopes that are significantly different from zero - and that they learn, on average, at the same rate.
+Furthermore, these results were consistent when only those individuals who performed better in the previous associative task were included (see Supplementary material).
 
@@
 Our results are, however, consistent with other experiments where GCs did not impact learning abilities [@szuran_water_1994; @bebus_associative_2016].
-In some systems, exposure to CORT during development has hormetic effects on learning and neural structures [@du_dynamic_2009; @mcewen_brain_2012].
+More striking is the absence of an effect of incubation temperature since most of the studies reported better performance in different associative learning and motor tasks when reptiles were incubated at higher temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+Furthermore, those studies that reported cold-incubated lizards to learn faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temperatures far beyond the natural range in their hot treatments.
+Our results suggest that behavioural flexibility, measured here as lizards' ability to solve a reversal learning task, is robust to prenatal CORT and temperature in both species of skinks.
+One potential limitation of our study is whether the dose we applied onto eggs increased CORT levels enough to impact lizards, as exposure to CORT during development has hormetic effects on learning and neural structures [@du_dynamic_2009; @mcewen_brain_2012].
 For example, in Sprague–Dawley rats, exposure to high doses of CORT, but not low doses, reduced density of immature neurons and cell proliferation and in the dentate gyrus [@DOSEneurobrummelte2010chronic].
-The CORT treatment employed here is known to impact other aspects such as growth or mortality in these species (unpublished data), but the effect of the same dose can differ between tissues (@lemaire_prenatal_2000).
-More striking is the absence of an effect of incubation temperature since most of the studies in reptiles reported better performance when incubated at higher temperatures in different associative learning and motor tasks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-Furthermore, those studies that reported cold-incubated lizards learn faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temperatures far beyond the natural range in their hot treatments.
-We know that our prenatal treatments affect other traits in both species of lizards used in this experiment (unpublished data).
-However, it is possible that the treatments affected tissues differently.
-An alternative hypothesis is that the effects of the prenatal treatments are age-dependent [see @frisone2002social].
+We find this possibility unlikely since in a previous experiment, we observed that a similar dose affected other traits such as growth and mortality in _L.
+delicata_ (unpublished data), but that is a scenario that cannot be dismissed.
+Furthermore, the effect of the same dose can differ between tissues (@lemaire_prenatal_2000), affecting mortality and growth, but nor mortality.
+Another alternative hypothesis is that the effects of the prenatal treatments are age-dependent [see @frisone2002social].
 Here, the lizards' age at the beginning of the experiment ranged from 41 to 148 days old in _L.
@@
 Furthermore, we expected behavioural flexibility in this species to be less susceptible to the effect of early environment since this trait can be adaptive in several stages of invasion involving more than one generation.
-Nevertheless, we did not find significant differences between treatments or species when we compared their performance in a reversal task.
-We found that, on average, all the lizards from the four treatments and the two species learned the reversal task - indicated by estimated slopes that are significantly different from zero - and that they learn, on average, at the same rate.
-Furthermore, these results were consistent when only those individuals who performed better in the previous associative task were included (see Supplementary material).
-
+Nevertheless, we did not find differences in reversal learning between _L.
+delicata_ and _L.
+guichenoti_, and in both species, behavioural flexibility seems robust to the influence of prenatal conditions.
 Previous studies have shown that _L.
@@
 In conclusion, our results indicate that lizards performed the reversal learning task, a measure of behavioural flexibility, at similar rates, with no discernible differences between treatments or species.
-These findings contrast our initial predictions and suggest that other aspects of _L.
-delicata_ biology may be more influential for their success as invaders than behavioural flexibility alone.
-The present study also indicates that prenatal CORT and temperature do not affect learning abilities in these species.
-Nevertheless, it remains possible that the effects of the early environment are task-dependent, and future studies should explore performance across different cognitive tasks and the effects of both treatments on brain function.
+These findings contrast our initial predictions and suggest that behavioural flexibility in both species is robust against conditions during early stages of development.
+Furthermore, our results indicate that other aspects of the biology of _L.
+delicata_ may be more influential for their success as invaders than behavioural flexibility alone.
+Nevertheless, it remains possible that the effects of the prenatal CORT and temperature on cognition depend on other aspects like the age at which animals are tested or the cognitive task employed; and future studies should explore performance across different cognitive tasks and the effects of both treatments on brain function.
 
@@
 
-Results for _L. delicata_:
+Results for _L. delicata_ when the model included the age:
 ```{r, tbl-agedeli, results='asis', out.widht = "26cm"}
@@
 
-Results for _L. guichenoti_:
+Results for _L. guichenoti_ when the model included the age:
 ```{r, tbl-ageguich, results='asis'}

### 2024-05-24 .vdoc.r

@@ -1,0 +1,654 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of early environment manipulation and learning tasks. Panel A represents the early environment manipulation for both species. Panel B shows the habituation phase with the respective three different stages. And panel C represents the associative and reversal tasks; white lids show the ramps where the food reward was not accessible."
+
+knitr::include_graphics("./Others/BEHFLEX_FIG_1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleandata
+# Obtain the main df using "./R/1_data_process.R"
+source(here("R", "1_data_process.R"))
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(k in 1:length(hormone)){
+    for(l in 1:length(temperature)){
+      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
+      }
+    }
+  }
+#
+#
+#
+#
+#
+#| label: models
[…]

### 2024-05-29 ms.qmd
updates manuscript

@@
 ## Abstract
-Behavioural flexibility is crucial for animals adapting to environmental changes.
+Behavioural flexibility is expected to be crucial for animals adapting to environmental changes.
 However, the conditions experienced during early development can profoundly impact behavioural flexibility making it unclear how populations will respond to novel circumstances.
-Stressful situations faced by the parents can have a direct impact on animals' cognition through the transmission of glucocorticoids - stress-related hormones.
-At the same time, stressful conditions can influence parental behaviour during nesting and, in consequence the developmental conditions such as temperature.
+Stressful situations faced by the parents can have a direct impact on animals' cognition through the transmission of glucocorticoids - stress-related hormones that affect offspring cognition.
+At the same time, stressful conditions can influence parental behaviour during nesting and consequently the thermal developmental conditions they experience.
 Here, we investigated the interactive effects of prenatal corticosterone (CORT) and temperature on behavioural flexibility in two lizard species, _Lampropholis delicata_ and _L.
@@
 We hypothesized prenatal CORT and cold temperatures to impair with lizards' performance in the reversal task.
-Also, given _L.
-delicata_ success as an invassive species, we expected this species to behave more flexible and be less affected by the incubation conditions.
-Contrary to our expectations, we found no significant differences in the reversal learning rate between treatments or species.
-Behavioural flexibility appears to be robust to prenatal temperature and CORT in both species.
-Furthermore, the lack of difference in reversal learning between _L.
+Given _L.
+delicata_'s success as an invassive species, we expected this species to behave more flexibly and be less affected by early environmental conditions.
+Contrary to our expectations, behavioural flexibility appears to be robust to prenatal temperature and CORT in both species.
+The lack of difference in reversal learning between _L.
 delicata_ and _L.
-guichenoti_ suggests that other processes are likely more influential in invasion success than behavioural flexibility itself.
+guichenoti_ suggests that novel environments are unlikely to influence flexible behavioural learning and that behavioural flexibility itself is unlikely to explain differences in invasion success between these species.
 
@@
 This suggests that behavioural flexibility is likely to be underpinned by complex neural mechanisms, and that alterations in these mechanisms may impact animals' ability to respond to novel situations.
-In this sense, the brain is considered especially sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004], creating uncertainty about how the conditions faced during early life might impact behavioural flexibility.
+The brain is considered especially sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004], creating uncertainty about how the conditions faced during early life might impact behavioural flexibility.
 
-The conditions in which the organisms develop can be altered by the circumstances faced by the parents.
-For instance, exposing threespine sticklebacks females to a model predator while yolking eggs, affected offspring tedency to use social cues [@feng2015effect].
+The conditions in which organisms develop can be altered by the circumstances faced by their parents.
+For instance, exposing threespine sticklebacks females to a model predator during ovulation, affected their offspring's tedency to use social cues [@feng2015effect].
 Under stressful situations, animal's sensory systems detect and transmit environmental signals to instigate adaptive physiological and behavioural adjustments – responses that are mediated by glucocorticoids (GCs) [@sapolsky_how_2000].
@@
 Because animals' responses to abrupt changes in temperature are mediated by GCs [@Crino_2023], and this response can affect animals' decision-making while nesting, GCs transmission and early therma environment are predicted to interact to shape offspring phenotype.
-In this sense, both GCs and temperature are known to exert potent effects on brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017] and cognition [@clark_colour_2014; @lui2017chronic], but little is known about how their ineraction could affect behavioural flexibility.
-Since behaving flexibly is essential for facing novel circumstances, studying the interactive effect of early environment on behavioural flexibility is crucial if we aim to understand animals' capability to adapt to environmental changes.
+Both GCs and temperature are known to exert potent effects on brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017] and cognition [@clark_colour_2014; @lui2017chronic], but little is known about how they may interact to affect behavioural flexibility.
+Since behaving flexibly is essential for facing novel environments, studying the interactive effect of early environment on behavioural flexibility is crucial if we aim to understand animals' capability to adapt to environmental changes.
 
@@
 Both species have similar life-histories and overlapping distributions [@chapple_know_2011; @chapple_biology_2014], but only _Lampropholis delicata_ has been successful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI].
-The differences in invassion success between both skinks may be driven by disparities in behavioural flexibility, a prominent quality in other invassive species [@sol2000behavioural; @sol2008brain; @wright2010behavioral; @amiel_smart_2011; @chapple2012can].
+The differences in invassion success between both skinks may be driven by disparities in behavioural flexibility - a prediction supperted in other invasive species [@sol2000behavioural; @sol2008brain; @wright2010behavioral; @amiel_smart_2011; @chapple2012can].
 However, the relative impact of early environments on behavioural flexibility remains unexplored.
-Early environment affects suites of morphological and behavioural traits differently in each species [@carrasco2023maternal; @kar2023heritability], but we are uncertain about the interactive role of maternal CORT and early temperatures on behavioural flexibility.
-We stigate here the effect of early environment on behavioural flexibility in both species by manipulating CORT and incubation temperature and then subjecting hatchlings to a reversal learning task.
-Since invassive species are expected to behave more flexibly [@sol2000behavioural; @sol2008brain; @wright2010behavioral; @amiel_smart_2011; @chapple2012can], we predict that _L.
+Early environments are known to affect suites of morphological and behavioural traits differently in each species [@carrasco2023maternal; @kar2023heritability], but we are uncertain about the interactive role of maternal CORT and early temperatures on behavioural flexibility.
+We manipulated CORT and incubation temperature in both species and then subjected hatchlings to a reversal learning task.
+We predicted that both cold incubation temperatures and CORT treatment will impair behavioural flexibility [@clark_colour_2014; @lui2017chronic], and the combination of both treatments to have the most detrimental effect on behavioural flexibility.
+Since invassive species are expected to behave more flexibly [@sol2000behavioural; @sol2008brain; @wright2010behavioral; @amiel_smart_2011; @chapple2012can], we predicted that _L.
 delicata_, on average, will perform more proficiently in the task compared to _L.
-guichenoti_.
-Furthermore, given that behavioural flexibility can be advantageous during different stages of invasion  [@wright2010behavioral; @chapple2012can; @szabo2020can], and that these phases can involve more than one generation, we anticipate that _L.
-guichenoti_ will be more impacted by the prenatal environment than _L.
-delicata_.
-Finally, we predic that both cold incubation temperatures and CORT treatment will impair behavioural flexibility [@clark_colour_2014; @lui2017chronic], and that the combination of both treatments to have the most detrimental effect on behavioural flexibility.
+guichenoti_ and that behavioural flexibility in _L.
+delicata_ will be more robust to early environmental conditions.
 
@@
 *Breeding colony* -- We tested juveniles originating from a breeding colony established in the lab since 2019.
-There is a total of 270 and 180 adults of *L.
+A total of 270 and 180 adults of *L.
 delicata* and *L.
-guichenoti* respectively, housed in big containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure.
-Enclosures are provided with non-stick matting, shelter, and several small water dishes.
-Water is given daily, and they are fed approx.
+guichenoti*, respectively, were established in containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure.
+Enclosures had non-stick matting, a shelter, and several small water dishes.
+Water was given daily, and they were fed approx.
 40 mid-size crickets (*Acheta domestica*) per enclosure three days a week.
-Crickets are dusted with calcium weekly and multivitamin and calcium biweekly.
-To ensure a temperature gradient, we employ a heat chord and a heat lamp following a 12 h light:12 h dark cycle.
-Room temperatures are set to 22-24ºC, and warm side of enclosures is usually at 32ºC.
+Crickets were dusted with calcium weekly and multivitamin and calcium biweekly.
+Using a heat chord and a heat lamp we created a temperature gradient and kept lights on a 12 h light:12 h dark cycle.
+UVA/UVB lighting was also provided.
+Room temperatures were set to 22-24ºC, and warm side of enclosures reached 32ºC.
 
-*Eggs collection and incubation* -- Between mid-October 2022 to the end of February 2023, we provided females with a place to lay the eggs by means of small boxes (12.5 L x 8.3 W x 5 H cm) with moist vermiculite inside, that were placed in one extreme of the communal enclosures (see above).
+*Eggs collection and incubation* -- Between mid-October 2022 to the end of February 2023, we provided females with a place to lay eggs by means of small boxes (12.5 L x 8.3 W x 5 H cm) with moist vermiculite inside that were placed in one extreme of the communal enclosures (see above).
 We checked for the presence of eggs in the boxes three days a week.
-After collection, we measured length and width of eggs with a digital caliper to the nearest 0.1 mm and weighed them with a (OHAUS, Model spx123) digital scale ± 0.001g error, and we recorded the clutch and egg identities.
-Then eggs were treated with CORT or vehicle (see CORT and Temperature manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite).
+After collection, we measured the length and width of eggs with a digital caliper to the nearest 0.1 mm and weighed them with a digital scale ± 0.001g error (OHAUS, Model spx123).
+We also recorded the clutch and egg identities.
+Eggs were then treated with CORT or vehicle (see CORT and Temperature manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite).
 The cups were covered with cling wrap to retain moisture and left in LATWIT 2X5D-R1160 incubators at two different temperatures (see CORT and Temperature manipulation below) until hatching.
 
-*Hatchlings* -- Eggs in the incubator were checked three times a week for hatchlings.
-After hatchling, we measured juveniles' SVL and Tail Length (TL) with a ruler to the nearest mm and weighed them with a (OHAUS, Model spx123) digital scale ± 0.001g error.
+Hatchlings – Eggs in the incubator were checked three times a week for hatchlings.
+After hatchling, we measured juveniles’ SVL and Tail Length (TL) with a ruler to the nearest mm and weighed them with a digital scale ± 0.001g error.
 We then placed hatchlings in individual enclosures (18.7L x 13.2W x 6.3H cm) and provided them with non-stick matting and a small water dish.
-During this period, they were sprayed water every day and received 3-6 small *A.
-domestica* crickets three times a week.
-All care otherwise follows similar protocols to adults (see above).
-
-Two weeks before starting the training phase (see below), lizards were moved to the experimental arena for acclimatation.
-The arenas were individual medium size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the extremes and a water dish on the other.
-These new enclosures were placed in two rooms in 7 different racks associated to 7 different CCTV systems (device model DVR-HP210475) that allowed us to record their behaviour during the experiment (see details below).
+During this period, they were sprayed with water every day and received 3-6 small A.
+domestica crickets three times a week.
+All care otherwise followed similar protocols to adults (see above).
+Two weeks before starting the training phase (see below), lizards were moved to an experimental arena for acclimatation.
+The arenas were individual medium size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the side and a water dish on the other.
+These new enclosures were placed in two rooms across 7 different racks associated to 7 different CCTV systems (device model DVR-HP210475) that allowed us to record their behaviour during the experiment (see details below).
 The number of lizards per species and treatment in each rack was counterbalanced to control for any effect of the room or the position of the lizard in the rack.
-During acclimatation and throughout the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin (see protocol below), and water was supplied *ad libitum*.
+During acclimatation and throughout the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin (see protocol below), and water was supplied ad libitum.
 We provided a temperature gradient by means of a heat cord and heat lamps in a 12 h light: 12 h dark cycle.
@@
 To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (Cold -- 23ºC ± 3ºC or Hot -- 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
-We first allocated eggs onto one of two different treatments: in the CORT treatment, eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (vehicle) at a final (10 pg CORT/mL) concentration; in the Control treatment eggs received an equal volume of the vehicle.
+We first allocated eggs into one of two different treatments: in the CORT treatment, eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (vehicle) at a final concentration of 10 pg CORT/mL; in the Control treatment eggs received an equal volume of the vehicle.
 CORT concentration employed in the CORT treatment represents 2 standard deviations above the mean natural concentration obtained in eggs from both species (non-published data).
-Then, eggs were incubated in one of the two previously mentioned temperature regimes (Cold or Hot) until hatching.
-This temperatures represent the upper and lower limit of the natural incubation temperatures [@qualls2000post; @cheetham2011embryonic].
+Eggs were then incubated in one of the two previously mentioned temperature regimes (Cold or Hot) until hatching.
+These temperatures represent the upper and lower limit of the natural incubation temperatures [@qualls2000post; @cheetham2011embryonic].
 The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.
@@
 #### Quantifying Behavioural Flexibility  
-Briefly, the learning test was divided in three main phases: a habituation phase where lizards had to learn to eat a frozen-thawed cricket from white 3D-printed polylactic acid (PLA) ramps (9 L x 4 W x 5 H cm); a colour association task where lizards had to associate the food reward with one of two colours (red or blue) (@fig-Methods Associative task); and finally, to quantify behavioural flexibility, we reversed the previously trained colour (red or blue) so that the lizards needed to learn to associate the food with the opposite colour (@fig-Methods Reversal task).
+The learning test was divided in three main phases: a habituation phase where lizards had to learn to eat a frozen-thawed cricket from white 3D-printed polylactic acid (PLA) ramps (9 L x 4 W x 5 H cm); a colour association task where lizards had to associate the food reward with one of two colours (red or blue) (@fig-Methods Associative task); and finally, to quantify behavioural flexibility, we reversed the previously trained colour (red or blue) so that the lizards needed to learn to associate the food with the opposite colour (@fig-Methods Reversal task).
 
@@
 We recorded whether the cricket had been consumed or not and we considered a stage as completed if the lizards ate the crickets in at least 5 out of 6 trials.
-This phase lasted 38 days, and only in one case we decided not to use the lizard in the next phases because it did not pass the aqcuisition criterium.
+This phase lasted 38 days, and only in one case a lizard did not progress to the next phases because it did not pass the aqcuisition criteria.
 
 In the colour association (Associative task in Fig.
-@fig-Methods) and reversal task (Reversal task in @fig-Methods B), we used three ramps that were identical in shape and size but differ in the colour.
+@fig-Methods) and reversal task (Reversal task in @fig-Methods B), we used three ramps that were identical in shape and size but different in the colour.
 The colours of these ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
@@
 As in the last stage of the habituation phase, we placed the cricket inside the wells of the ramps, but then two of them were covered with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in one ramp.
-The food reward was placed in all three ramps to avoid lizards using prey chemical cues, that were released in the closed wells through a series of small holes on the top of the lids.
+The food reward was placed in all three ramps to avoid lizards using prey chemical cues that were released in the closed wells through a series of small holes on the top of the lids.
 In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
@@
 We considered that a choice was made if the head of the lizard was inside the well of one of the ramps.
-We considered a trial failed if there was no choice in one hour of recording and those trials were scored as NA.
+We considered a trial failed if there was no choice in one hour of recording.
+Those trials were scored as NA.
 Here, we analysed the data of the reversal task as a measure of behavioural flexibility [@brown2010behavioral].
@@
 We also incorporated the clutch identity as a random factor.
+Learning can also be age-dependent (see @noble_age-dependent_2014), and given that lizards incubated at different temperatures hatch at different times we explored the effects of age on learning.
+Indeed, lizards’ age at the beginning of the experiment ranged from 41 to 148 days old in _L.
+delicata_ and 48 to 132 in _L.
+guichenoti_.
+However, when this variable was included in the models we did not find any significant effect of age (see Supplementary material).
+As such, we present models without age as a fixed effect.
 We used the posterior distributions of parameters from these models to test for differences in learning rate between treatments and species.
@@
 We collected subjects from a breeding colony kept in the lab since 2019.
-Both the breeding animals and the ones used in this experiment were provided humane laboratory housing, with thermorregulation opportunity, light and humidity conditions (see above for details).
-Lizards in the colony received food *ad libitum* while the subjects in the experiment were feed one cricket daily during the experiment.
+Both the breeding animals and the ones used in this experiment were provided humane laboratory housing, with thermoregulatory opportunities, light (UV and heat) and moderate levels of humidity (see above for details).
+Lizards in the colony received food ad libitum while the subjects in the experiment were feed one cricket daily during the experiment.
 All lizards were handled minimally to avoid stress.
 Experimental procedures and laboratory housing complied with Australian law and were approved by the Australian National University Animal Experimentation Ethics Committee (A2022_33).
-Upon completion of experimental trials, lizards were kept in their enclosure for until they were euthanized following standard humane procedures.
+Upon completion of experimental trials, lizards were kept in their enclosure until they were humanely euthanized following approved procedures.
 
@@
 
-Originally, we started with 96 lizards, 48 per species and 12 per treatment per species.
-However, our final sample size was 81 due to natural mortality (n = 11), failure to complete the training stage (n = 1), or if the number of failed tasks (see above) was higher than 15 (n = 3).
-Final sample sizes per treatment and species are listed in @fig-results.
+We started with 96 lizards, 48 per species and 12 per treatment per species.
+However, our final sample size was 81 due to natural mortality (n = 11), failure to complete the training stage (n = 1), or because the number of failed tasks (see above) was higher than 15 (n = 3).
+The final sample sizes per treatment and species are listed in @fig-results.
 
@@
 
-This study aimed to determine the interactive effects of prenatal temperature and GCs on behavioural flexibility in two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
+This study aimed to determine whether prenatal temperature and GCs impact behavioural flexibility in two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L.
 guichenoti_).
@@
 Nevertheless, we did not find significant differences between treatments or species when we compared their performance in a reversal task.
-Our results show that, on average, all the lizards from the four treatments and the two species learned the reversal task - indicated by estimated slopes that are significantly different from zero - and that they learn, on average, at the same rate.
+Our results show that, on average, all the lizards from the four treatments and the two species learnt the reversal task - indicated by estimated slopes that are significantly different from zero - and that they learn, on average, at the same rate.
 Furthermore, these results were consistent when only those individuals who performed better in the previous associative task were included (see Supplementary material).
 
-Our early environment manipulation did not affect the lizards' performance in the task.
-We predicted that prenatal CORT treatment would decrease reversal learning abilities and that high temperatures would minimise these effects.
-However, our results show no significant differences between treatments in both species.
-In contrast to previous studies that show high GCs levels impaired performance in different types of learning tests [@lemaire_prenatal_2000; @zhu_prenatal_2004;  @farrell_developmental_2016], we did not find any effect of CORT on the speed at which lizards learn.
+Behavioural flexbility appears to be robust to early exposure to maternal GCs in both _L.
+delicata_ and _L.
+guichenoti_.
+We predicted that prenatal CORT treatment would decrease reversal learning abilities.
+As such, our results contrast to previous studies that show high GCs levels impaired performance in different types of learning tests [@lemaire_prenatal_2000; @zhu_prenatal_2004;  @farrell_developmental_2016].
 Our results are, however, consistent with other experiments where GCs did not impact learning abilities [@szuran_water_1994; @bebus_associative_2016].
-More striking is the absence of an effect of incubation temperature since most of the studies reported better performance in different associative learning and motor tasks when reptiles were incubated at higher temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+One possible reason for why GCs did not affect learning in our study may be because GCs can have hormetic effects on brain structure and learning.
+For example, in Sprague–Dawley rats, exposure to high doses of CORT, but not low doses, reduced the density of immature neurons and cell proliferation in the dentate gyrus [@DOSEneurobrummelte2010chronic].
+It is possible such dose-dependent effects exist and our concentrations failed to elicit changes to the brain that would result in impaired behavioural flexibility.
+We find this possibility unlikely since, in a previous experiment, we observed that a similar dose affected a multitude of other traits including growth and mortality in _L.
+delicata_ (unpublished data).
+Nonetheless, we cannot dismiss this possibility because dose effects can differ between tissues [@lemaire_prenatal_2000].
+Conversely, the effects of GCs early in development may vary depending on the cognitive task, as evidenced by studies showing variations in the impact of prenatal GCs on different brain regions [@lemaire_prenatal_2000].
+Prenatal GCs can have programmatic effects on HPA axis sensitivity, potentially impacting the lizards’ sensitivity to stressors [@crino_corticosterone_2014].
+This altered stress response may influence learning dynamics through hormetic effects of CORT [@du_dynamic_2009], particularly in stressful contexts of which our experiment was not [@taborsky2021towards].
+These hypotheses are not mutually exclusive and could be tested in future experiments using multiple doses of prenatal CORT treatment, assessing learning using multiple cognitive tasks and testing the effect of stressors during the learning process.
+
+More striking is the absence of an effect of incubation temperature on learning and behavioural flexibility because most studies have reported better performance in different associative learning and motor tasks when incubated at higher temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
 Furthermore, those studies that reported cold-incubated lizards to learn faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temperatures far beyond the natural range in their hot treatments.
-Our results suggest that behavioural flexibility, measured here as lizards' ability to solve a reversal learning task, is robust to prenatal CORT and temperature in both species of skinks.
-One potential limitation of our study is whether the dose we applied onto eggs increased CORT levels enough to impact lizards, as exposure to CORT during development has hormetic effects on learning and neural structures [@du_dynamic_2009; @mcewen_brain_2012].
-For example, in Sprague–Dawley rats, exposure to high doses of CORT, but not low doses, reduced density of immature neurons and cell proliferation and in the dentate gyrus [@DOSEneurobrummelte2010chronic].
-We find this possibility unlikely since in a previous experiment, we observed that a similar dose affected other traits such as growth and mortality in _L.
-delicata_ (unpublished data), but that is a scenario that cannot be dismissed.
-Furthermore, the effect of the same dose can differ between tissues (@lemaire_prenatal_2000), affecting mortality and growth, but nor mortality.
-Another alternative hypothesis is that the effects of the prenatal treatments are age-dependent [see @frisone2002social].
-Here, the lizards' age at the beginning of the experiment ranged from 41 to 148 days old in _L.
-delicata_ and 48 to 132 in _L.
-guichenoti_, and when this variable was included in the models, we did no find any significant effect of age (see Supplementary material).
-However, the treatments may have consequences at earlier or later stages of life that are not being captured in our experiment.
-Conversely, the effects of the early environment may likely vary depending on the cognitive task, as evidenced by studies showing variations in the impact of prenatal GCs and temperature on different brain regions [@coomber_independent_1997; @sakata_neural_2000; @lemaire_prenatal_2000].
-In addition, prenatal GCs can have programmatic effects on HPA axis sensitivity, potentially impacting the lizards' sensitivity to stressors [@crino_corticosterone_2014].
-This altered stress response may influence learning dynamics through hormetic effects of CORT [@du_dynamic_2009], particularly in stressful contexts [@taborsky2021towards]; although such effects were not likely observable in our experimental design.
-These hypotheses are not mutually exclusive and could be tested in future experiments using multiple doses of prenatal CORT treatment, assessing learning using multiple cognitive tasks and at different ages, testing the effect of stress during the learning process, and measuring the neurophysiological effects on different brain nuclei.
+Our results suggest that behavioural flexibility is robust to temperature in both species of skinks, at least in our study.
+**ADD**
 
@@
 Furthermore, we expected behavioural flexibility in this species to be less susceptible to the effect of early environment since this trait can be adaptive in several stages of invasion involving more than one generation.
-Nevertheless, we did not find differences in reversal learning between _L.
+While it will be important to explore replicate invasion events (both successful and unsuccessful) such information is seldom available.
+Nonetheless, there is precedence in the literature to expect differences between these two species [**REFS**].
+Regardless, while we did not find differences in reversal learning between _L.
 delicata_ and _L.
-guichenoti_, and in both species, behavioural flexibility seems robust to the influence of prenatal conditions.
-Previous studies have shown that _L.
+guichenoti_, previous studies have shown that _L.
 delicata_ more readily explores novel environments than _L.
@@
 However, Bezzina _et al._ [@bezzina2014does] found no differences in learning between the two skinks in an associative learning task.
-Our results align with the latter study and suggest that behavioural flexibility does not differ between these species.
-In addition, we did not find any effect of the treatments on either species.
-Both results contrast our original predictions and may indicate that other aspects of their biology are more relevant for _L.
-delicata_'s success as invaders than behavioural flexibility.
-For instance, the mentioned differences in exploratory behaviour can be the key factor explaining why _L.
+Our results align with the latter study and suggest that behavioural flexibility does not differ between these species either.
+Our results along with others' [@bezzina2014does] suggest that other aspects of their biology are more relevant for _L.
+delicata_'s success as invaders than learning and behavioural flexibility.
+Differences in exploratory behaviour is likely to be the key factor explaining why _L.
 delicata_ and not _L.
-guichenoti_ is better at colonising new areas, since exploring more can also enhance the ability to effectively locate novel resources in _L.
-delicata_ [@chapple_know_2011].
+guichenoti_ is better at colonising new areas [@chapple_know_2011].
 
 In conclusion, our results indicate that lizards performed the reversal learning task, a measure of behavioural flexibility, at similar rates, with no discernible differences between treatments or species.
-These findings contrast our initial predictions and suggest that behavioural flexibility in both species is robust against conditions during early stages of development.
+These findings contrast with our initial predictions and suggest that behavioural flexibility in both species is robust to insults (at least for temperature and GCs) during early stages of development.
 Furthermore, our results indicate that other aspects of the biology of _L.
 delicata_ may be more influential for their success as invaders than behavioural flexibility alone.
-Nevertheless, it remains possible that the effects of the prenatal CORT and temperature on cognition depend on other aspects like the age at which animals are tested or the cognitive task employed; and future studies should explore performance across different cognitive tasks and the effects of both treatments on brain function.
+Nevertheless, it remains **possible that the effects of the prenatal CORT and temperature on cognition depend on other aspects like the age at which animals are tested or the cognitive task employed; and future studies should explore performance across different cognitive tasks and the effects of both treatments on brain function.**
 
 ## Data accessibility  
-All data, data description, and R code are availabe in public repository https://github.com/Pablo-Recio/CORT_Temp_Behavioural_flexibility
+All data, data description, and R code are available in public repository https://github.com/Pablo-Recio/CORT_Temp_Behavioural_flexibility
 
@@
 ## Authors' contributions
-P.R.: conceptualization, methodology, data collection, data curation, formal analysis, writing—original draft, writing—review and editing; D.C.L.: data collection, writing—review and editing; O.C.: conceptualization, methodology, writing—review and editing; K.H.W.: conceptualization, writing—review and editing; C.F.: conceptualization, methodology, funding acquisition,writing—review and editing; B.M: data collection, writing—review and editing; A.Y.P.: data collection, writing—review and editing; D.N.: conceptualization, methodology, funding acquisition, project administration, resources, supervision, writing—review and editing.
+P.R.: conceptualization, methodology, data collection, data curation, formal analysis, writing—original draft, writing—review and editing; D.C.L.: data collection, writing—review and editing; O.C.: conceptualization, methodology, writing—review and editing; K.H.W.: conceptualization, writing—review and editing; C.F.: conceptualization, methodology, funding acquisition, writing—review and editing; B.M: data collection, writing—review and editing; A.Y.P.: data collection, writing—review and editing; D.N.: conceptualization, methodology, funding acquisition, project administration, resources, supervision, writing—review and editing.
 All authors gave final approval for publication and agreed to be held accountable for the work performed therein.

### 2024-05-30 ms.qmd
Updates

@@
 This altered stress response may influence learning dynamics through hormetic effects of CORT [@du_dynamic_2009], particularly in stressful contexts of which our experiment was not [@taborsky2021towards].
-These hypotheses are not mutually exclusive and could be tested in future experiments using multiple doses of prenatal CORT treatment, assessing learning using multiple cognitive tasks and testing the effect of stressors during the learning process.
+These hypotheses are not mutually exclusive and could be tested in future experiments using multiple doses of prenatal CORT treatment, assessing learning using multiple cognitive tasks, and testing the effect of stressors during the learning process.
 
@@
 Our results suggest that behavioural flexibility is robust to temperature in both species of skinks, at least in our study.
-**ADD**
+It could be arguable whether the differences in our incubation temperatures were extreme enough to elicit significant differences in learning performance.
+However, the mean difference between the temperatures used in our experiment  were similar to those in previous studies [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+In lizards, disparities in learning caused by the early thermal environment are associated to changes in neural density [@amiel_effects_2017], however, several studies have shown that the effects of temperature on brain structure and physiology are region dependent [@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017].
+It is possible that the temperatures used in our experiment did not affect the brain regions involved in coding reversal learning.
+Future studies should explore the effects of thermal environment on brain structure and function in these species to understand the mechanisms underlying the effects of temperature on learning.
+Furthermore, testing learning across different cognitive tasks could provide a more comprehensive understanding of the influence of temperature on cognition.
+In our analyses, sex was not included as a factor because the lizads employed were not considered sexually mature, and because previous studies did not find any differences on learning [@szabo2019sex], or on the effects of temperature on learning [@amiel_hotter_2012; @clark_colour_2014].
+However, some studies evidence interactive effects of incubation temperature and sex on brain physiology in other species of reptiles [@coomber_independent_1997; @sakata_neural_2000].
+In addition, the species employed by @amiel_hotter_2012, @amiel_egg_2014, and @clark_colour_2014, is known to sex-reverse - some individuals can have female chromosomes but male phenotypes - under cold temperatures [@dissanayake2021effects]; which was not accounted for in these experiments [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+As such, a potential temperature-sex interaction could be impacting our results, and future studies should explore the interactive effects of sex and incubation temperature on cognitive performance.
 
@@
 While it will be important to explore replicate invasion events (both successful and unsuccessful) such information is seldom available.
-Nonetheless, there is precedence in the literature to expect differences between these two species [**REFS**].
+Nonetheless, there is precedence in the literature to expect differences between these two species [@chapple_know_2011; @chapple2013biosecurity].
 Regardless, while we did not find differences in reversal learning between _L.
@@
 guichenoti_, which can be advantageous during colonisation [@chapple_know_2011].
-However, Bezzina _et al._ [@bezzina2014does] found no differences in learning between the two skinks in an associative learning task.
+However, @bezzina2014does found no differences in learning between the two skinks in an associative learning task.
 Our results align with the latter study and suggest that behavioural flexibility does not differ between these species either.
@@
 delicata_ may be more influential for their success as invaders than behavioural flexibility alone.
-Nevertheless, it remains **possible that the effects of the prenatal CORT and temperature on cognition depend on other aspects like the age at which animals are tested or the cognitive task employed; and future studies should explore performance across different cognitive tasks and the effects of both treatments on brain function.**
+Nevertheless, future studies should investigate the potential influence of prenatal CORT and temperature on cognition, considering other factors such as the type of cognitive task.
+It is also imperative to explore the effects of these treatments on brain function comprehensively.
+Additionally, further research is essential to determine which aspects of _L.
+delicata_’s biology contribute more significantly to their success as invaders than behavioral flexibility alone.
+Investigating these areas will provide a better understanding of the cognitive and biological mechanisms underlying the adaptability and invasive potential of both species.
 

### 2024-05-30 .vdoc.r

@@ -1,654 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: fig-Methods
-#| fig.cap: "Experimental design of early environment manipulation and learning tasks. Panel A represents the early environment manipulation for both species. Panel B shows the habituation phase with the respective three different stages. And panel C represents the associative and reversal tasks; white lids show the ramps where the food reward was not accessible."
-
-knitr::include_graphics("./Others/BEHFLEX_FIG_1.png")
-
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: cleandata
-# Obtain the main df using "./R/1_data_process.R"
-source(here("R", "1_data_process.R"))
-#
-#
-#
-#| label: sampleSize
-# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
-source(here("R", "func.R"))
-#
-specie <- c("delicata", "guichenoti")
-hormone <- c("CORT", "Control")
-temperature <- c("Cold", "Hot")
-#
-n_list <- list()
-#
-for(i in 1:length(specie)){
-  for(k in 1:length(hormone)){
-    for(l in 1:length(temperature)){
-      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
-      }
-    }
-  }
-#
-#
-#
-#
-#
-#| label: models
[…]

### 2024-05-30 ms.qmd
Updates

@@
 guichenoti_).
-We expected incubation conditions to influence behavioural flexibility in both species; and we also predicted that _L.
+We expected early environment to influence behavioural flexibility in both species.
+We also predicted that _L.
 delicata_ would be more flexible than _L.
@@
 
-More striking is the absence of an effect of incubation temperature on learning and behavioural flexibility because most studies have reported better performance in different associative learning and motor tasks when incubated at higher temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-Furthermore, those studies that reported cold-incubated lizards to learn faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temperatures far beyond the natural range in their hot treatments.
-Our results suggest that behavioural flexibility is robust to temperature in both species of skinks, at least in our study.
-It could be arguable whether the differences in our incubation temperatures were extreme enough to elicit significant differences in learning performance.
-However, the mean difference between the temperatures used in our experiment  were similar to those in previous studies [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-In lizards, disparities in learning caused by the early thermal environment are associated to changes in neural density [@amiel_effects_2017], however, several studies have shown that the effects of temperature on brain structure and physiology are region dependent [@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017].
+More striking is the absence of an effect of incubation temperature on behavioural flexibility because most studies have reported better performance in different associative learning and motor tasks when incubated at higher temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+Studies that have reported cold-incubated lizards to learning faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temperatures far beyond the natural range in their hot treatments and it is unclear how such conditions relate to wild environments.
+Our results suggest that behavioural flexibility is robust to temperature in both species of skinks - at least in this study.
+It could be argued that the differences in our incubation temperatures were not extreme enough to elicit significant differences in learning performance.
+However, the mean difference between the temperatures used in our experiment  were similar to those in previous studies [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014], and are aligned with natural variation at the extremes of incubation conditions in the wild [@qualls2000post; @cheetham2011embryonic].
+In lizards, impacts on learning from early thermal environments are associated with changes in neural density [@amiel_effects_2017].
+However, several studies have shown that the effects of temperature on brain structure and physiology are region dependent [@coomber_independent_1997; @sakata_neural_2000; @amiel_effects_2017].
 It is possible that the temperatures used in our experiment did not affect the brain regions involved in coding reversal learning.
@@
 Furthermore, testing learning across different cognitive tasks could provide a more comprehensive understanding of the influence of temperature on cognition.
-In our analyses, sex was not included as a factor because the lizads employed were not considered sexually mature, and because previous studies did not find any differences on learning [@szabo2019sex], or on the effects of temperature on learning [@amiel_hotter_2012; @clark_colour_2014].
-However, some studies evidence interactive effects of incubation temperature and sex on brain physiology in other species of reptiles [@coomber_independent_1997; @sakata_neural_2000].
-In addition, the species employed by @amiel_hotter_2012, @amiel_egg_2014, and @clark_colour_2014, is known to sex-reverse - some individuals can have female chromosomes but male phenotypes - under cold temperatures [@dissanayake2021effects]; which was not accounted for in these experiments [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-As such, a potential temperature-sex interaction could be impacting our results, and future studies should explore the interactive effects of sex and incubation temperature on cognitive performance.
+In our analyses, sex was not included as a factor because lizads were not considered sexually mature, and because previous studies have found weak evidence for sex-dependent learning in many cognitive domains [@szabo2019sex].
+Indeed, the impacts of temperature on learning was not sex-depedent for the Eastern three-lined skink (_Bassiana dupeyerri_) [@amiel_hotter_2012; @clark_colour_2014].
+However, some studies find evidence for interactive effects of incubation temperature and sex on brain physiology in other species of reptiles [@coomber_independent_1997; @sakata_neural_2000].
+In addition, _B.
+dupeyerri_ are known to sex-reverse - some individuals can have female chromosomes but male phenotypes - under cold temperatures [@dissanayake2021effects].
+Such effects were not easily accounted for in these experiments making it challenging to understand if sex or temperature were the major drivers of learning differences [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
+Future studies should explore the possible interactive effects of sex and incubation temperature on cognitive performance.
+However, such studies will be challenging given the large sample sizes required to execute these studies rigorously.
 
@@
 
+Table 1.
+Estimates of Reversal learning slope for all the different treatments per each task, species, and group.
+Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
+All pmcmc tested the hypothesis that the mean equals zero.
+In bold, those values that are significant (pmcmc <0.05)
 ```{r, tbl-data, results='asis'}
@@
 
+Table 2.
+Estimates of Reversal learning slope for all the different treatments per each task, species, and group.
+Here we included only those individuals who made the right choice in 8 out of the last 10 trials in the previous associative task.
+Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
+All pmcmc tested the hypothesis that the mean equals zero.
+In bold, those values that are significant (pmcmc <0.05)
+
 ```{r, tbl-data_2}
@@
 
-Results for _L. delicata_ when the model included the age:
+Table 3. Results for _L. delicata_ when the model included the age:
 ```{r, tbl-agedeli, results='asis', out.widht = "26cm"}
@@
 
-Results for _L. guichenoti_ when the model included the age:
+Table 4. Results for _L. guichenoti_ when the model included the age:
 ```{r, tbl-ageguich, results='asis'}

### 2024-05-30 .vdoc.r

@@ -1,0 +1,657 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of early environment manipulation and learning tasks. Panel A represents the early environment manipulation for both species. Panel B shows the habituation phase with the respective three different stages. And panel C represents the associative and reversal tasks; white lids show the ramps where the food reward was not accessible."
+
+knitr::include_graphics("./Others/BEHFLEX_FIG_1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleandata
+# Obtain the main df using "./R/1_data_process.R"
+source(here("R", "1_data_process.R"))
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(k in 1:length(hormone)){
+    for(l in 1:length(temperature)){
+      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
+      }
+    }
+  }
+#
+#
+#
+#
+#
+#| label: models
[…]

### 2024-06-05 ms.qmd
updates

@@
 Experimental procedures and laboratory housing complied with Australian law and were approved by the Australian National University Animal Experimentation Ethics Committee (A2022_33).
-Upon completion of experimental trials, lizards were kept in their enclosure until they were humanely euthanized following approved procedures.
+Animals born in captivity cannot be re-released into the wild as string biosafety protocols across the states prohibit this.
+It is also not possible to rehome such a large number of animals for experiments.
+Therefore, upon completion of experimental trials, lizards were kept in their enclosure until they were humanely euthanized following approved procedures.
+To euthanise animals, we use an injection of sodium pentobarbital (i.e., Lethabarb) (diluted 1:4 ringers solution) at
+60-100mg/kg, injected intrapleuroperitoneally.
+We monitored the animals to ensure there was no irritation from the agent as indicated by distressed animals.
+Gently pinching the toes was used to confirm the absence of a response before the animal was disposed of.
 
@@
 ## Data accessibility  
-All data, data description, and R code are available in public repository https://github.com/Pablo-Recio/CORT_Temp_Behavioural_flexibility
+All data, data description, and R code are available in public repository [https://github.com/Pablo-Recio/CORT_Temp_Behavioural_flexibility](https://github.com/Pablo-Recio/CORT_Temp_Behavioural_flexibility).
 

### 2024-08-30 ms.qmd
Updates

@@
 
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
 ## Abstract
@@
 However, the conditions experienced during early development can profoundly impact behavioural flexibility making it unclear how populations will respond to novel circumstances.
-Stressful situations faced by the parents can have a direct impact on animals' cognition through the transmission of glucocorticoids - stress-related hormones that affect offspring cognition.
-At the same time, stressful conditions can influence parental behaviour during nesting and consequently the thermal developmental conditions they experience.
+Stressful situations faced by the parents can have a direct impact on offspring cognition through the transmission of glucocorticoids - stress-related hormones that affect offspring cognition.
+At the same time, stressful conditions can influence parental behaviour during nesting and consequently the thermal developmental conditions offspring experience.
 Here, we investigated the interactive effects of prenatal corticosterone (CORT) and temperature on behavioural flexibility in two lizard species, _Lampropholis delicata_ and _L.
@@
 Species with greater behavioural flexibility are expected to be more resilient to environmental changes because behaving flexibly is predicted to be crucial for exploiting new resources and facing new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can; @szulkin2020urban].
-For example, survival of cane toads in semi-arid regions of Australia depend on adjusting their hydration activities to include daytime hours, rather than relying solely on nighttime [@webb2014behavioural]; while succesful colonisation of new environments by birds is related to higher frequency of foraging innovations [@sol2000behavioural].
+For example, successful colonisation of new environments by birds is related to higher frequency of foraging innovations [@sol2000behavioural].
 Although there is limited understanding of the physiological mechanisms involved in animals' ability to behave flexibly, relative brain size has been shown to be a good predictor of behavioural flexibility in mammals, birds, reptiles and amphibians [@sol2000behavioural; @sol2008brain; @amiel_smart_2011].
@@
 The conditions in which organisms develop can be altered by the circumstances faced by their parents.
-For instance, exposing threespine sticklebacks females to a model predator during ovulation, affected their offspring's tedency to use social cues [@feng2015effect].
+For instance, exposing three-spined stickleback (_Gasterosteus aculeatus_) females to a model predator during ovulation, affected their offspring's tedency to use social cues [@feng2015effect].
 Under stressful situations, animal's sensory systems detect and transmit environmental signals to instigate adaptive physiological and behavioural adjustments – responses that are mediated by glucocorticoids (GCs) [@sapolsky_how_2000].
@@
 For example, human disturbance alters snapping turtles' nest-site choice, ultimately impacting the temperature at which eggs are incubated [@kolbe2002impact].
-Because animals' responses to abrupt changes in temperature are mediated by GCs [@Crino_2023], and this response can affect animals' decision-making while nesting, GCs transmission and early therma environment are predicted to interact to shape offspring phenotype.
+Animals’ responses to abrupt temperature changes are mediated by GCs [@Crino_2023], which can influence animals’ decision-making while nesting [@kolbe2002impact].
+As a result, GCs transmission and early thermal environment are expected to interact and shape offspring traits.
 Both GCs and temperature are known to exert potent effects on brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017] and cognition [@clark_colour_2014; @lui2017chronic], but little is known about how they may interact to affect behavioural flexibility.
@@
 Both species have similar life-histories and overlapping distributions [@chapple_know_2011; @chapple_biology_2014], but only _Lampropholis delicata_ has been successful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI].
-The differences in invassion success between both skinks may be driven by disparities in behavioural flexibility - a prediction supperted in other invasive species [@sol2000behavioural; @sol2008brain; @wright2010behavioral; @amiel_smart_2011; @chapple2012can].
+Previous studies exploring behavioral differences between the two species have found _L.
+delicata_ to be more exploratory than _L.
+guichenoti_ [@chapple_know_2011], but no differences in learning were observed between the skinks in an associative learning task [@bezzina2014does].
+Disparities in behavioural flexibility may be driving the differences in invasion success between both skinks, a prediction supported in other invasive species [@sol2000behavioural; @sol2008brain; @wright2010behavioral; @amiel_smart_2011; @chapple2012can].
 However, the relative impact of early environments on behavioural flexibility remains unexplored.
-Early environments are known to affect suites of morphological and behavioural traits differently in each species [@carrasco2023maternal; @kar2023heritability], but we are uncertain about the interactive role of maternal CORT and early temperatures on behavioural flexibility.
+Early environments are known to affect suites of morphological and behavioural traits differently in each species [@carrasco2023maternal; @kar2023heritability], but uncertainty still exists about the interactive role of maternal CORT and early temperatures on behavioural flexibility.
 We manipulated CORT and incubation temperature in both species and then subjected hatchlings to a reversal learning task.
+Reversal learning, in particular, is a widely employed tool to measure behavioral flexibility [@gapp2014early; @hurtubise2017effects], as it assesses an individual's ability to alter a learned behavior in response to environmental changes, providing researchers with a clear indicator of their ability to adjust to new conditions [@brown2010behavioral].
+
 We predicted that both cold incubation temperatures and CORT treatment will impair behavioural flexibility [@clark_colour_2014; @lui2017chronic], and the combination of both treatments to have the most detrimental effect on behavioural flexibility.
@@
 UVA/UVB lighting was also provided.
-Room temperatures were set to 22-24ºC, and warm side of enclosures reached 32ºC.
+Room temperatures were set to 22-24ºC, and the warm side of enclosures reached 32ºC.
 
-*Eggs collection and incubation* -- Between mid-October 2022 to the end of February 2023, we provided females with a place to lay eggs by means of small boxes (12.5 L x 8.3 W x 5 H cm) with moist vermiculite inside that were placed in one extreme of the communal enclosures (see above).
+*Eggs collection and incubation* -- Between mid-October 2022 to the end of February 2023, we provided females with a place to lay eggs by means of small boxes (12.5 L x 8.3 W x 5 H cm) with moist vermiculite inside that were placed on one side of the communal enclosures (see above).
 We checked for the presence of eggs in the boxes three days a week.
 After collection, we measured the length and width of eggs with a digital caliper to the nearest 0.1 mm and weighed them with a digital scale ± 0.001g error (OHAUS, Model spx123).
-We also recorded the clutch and egg identities.
+We also assigned identities to the clutch and each egg.
 Eggs were then treated with CORT or vehicle (see CORT and Temperature manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite).
@@
 
-Hatchlings – Eggs in the incubator were checked three times a week for hatchlings.
+*Hatchlings* – Eggs in the incubator were checked three times a week for hatchlings.
 After hatchling, we measured juveniles’ SVL and Tail Length (TL) with a ruler to the nearest mm and weighed them with a digital scale ± 0.001g error.
-We then placed hatchlings in individual enclosures (18.7L x 13.2W x 6.3H cm) and provided them with non-stick matting and a small water dish.
-During this period, they were sprayed with water every day and received 3-6 small A.
-domestica crickets three times a week.
+We then placed hatchlings in individual enclosures (18.7L x 13.2W x 6.3H cm) and provided them with non-stick matting, a shelter, and a small water dish.
+During this period, they were sprayed with water every day and received 3-6 small _A.
+domestica_ crickets three times a week.
 All care otherwise followed similar protocols to adults (see above).
-Two weeks before starting the training phase (see below), lizards were moved to an experimental arena for acclimatation.
+Two weeks before starting the training phase (see below), lizards were moved to an experimental arena for acclimatisation.
 The arenas were individual medium size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the side and a water dish on the other.
-These new enclosures were placed in two rooms across 7 different racks associated to 7 different CCTV systems (device model DVR-HP210475) that allowed us to record their behaviour during the experiment (see details below).
-The number of lizards per species and treatment in each rack was counterbalanced to control for any effect of the room or the position of the lizard in the rack.
-During acclimatation and throughout the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin (see protocol below), and water was supplied ad libitum.
+These new enclosures were placed in two rooms across 7 different racks that were monitored by 7 different CCTV systems (device model DVR-HP210475) that allowed us to record their behaviour during the experiment (see details below).
+Conditions in these rooms where identical to the main room, but the number of lizards per species and treatment in each rack was counterbalanced to control for any potential effect of the room or the position of the lizard on the rack.
+During acclimatisation and throughout the experiment, lizards were fed with only one cricket per day dusted with calcium and multivitamin (see protocol below), and water was supplied _ad libitum_.
 We provided a temperature gradient by means of a heat cord and heat lamps in a 12 h light: 12 h dark cycle.
@@
 
-To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (Cold -- 23ºC ± 3ºC or Hot -- 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
+To empirically test the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (Cold -- 23ºC ± 3ºC or Hot -- 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
 We first allocated eggs into one of two different treatments: in the CORT treatment, eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (vehicle) at a final concentration of 10 pg CORT/mL; in the Control treatment eggs received an equal volume of the vehicle.
 CORT concentration employed in the CORT treatment represents 2 standard deviations above the mean natural concentration obtained in eggs from both species (non-published data).
-Eggs were then incubated in one of the two previously mentioned temperature regimes (Cold or Hot) until hatching.
+Doses were determined by referencing published yolk corticosterone concentrations in other oviparous species [@lovern2008effects ; @hanover2019corticosterone] and our own unpublished data.
+After the hormone treatment, were then incubated in one of the two previously mentioned temperature regimes (Cold or Hot) until hatching.
 These temperatures represent the upper and lower limit of the natural incubation temperatures [@qualls2000post; @cheetham2011embryonic].
@@
 However, to control for potential colour biases, we assigned one group of lizards within each treatment to associate food in the blue ramp followed by the red ramp in the reversal, while in the other group the order was reversed.
-As in the last stage of the habituation phase, we placed the cricket inside the wells of the ramps, but then two of them were covered with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in one ramp.
-The food reward was placed in all three ramps to avoid lizards using prey chemical cues that were released in the closed wells through a series of small holes on the top of the lids.
+As in the last stage of the habituation phase, we placed the cricket inside the wells of the ramps, but then two of them were covered with 3D-printed lids (3D x 0.5H cm) so prey was only accessible on one ramp.
+The food reward was placed on all three ramps to avoid lizards using prey chemical cues that were released in the closed wells through a series of small holes on the top of the lids.
 In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association.
@@
 We ran four parallel MCMC chains of 3000 iterations for each model, with a warmup period of 1000 iterations.
-We modelled correct choices [correct (1) or not (0)] as the response variable, and trial, hormone (CORT versus Control), incubation temperature (Cold versus Hot), and their interaction as fixed factors.
+We modelled correct choices [correct (1) or not (0)] as the response variable, and trial, hormone (CORT versus Control), incubation temperature (Cold versus Hot), and the three-way interaction between trial, hormone, and temperature.
+The error structure was modeled using a Bernoulli distribution with a logit link function (family = Bernoulli(link = 'logit')).
 We included a random intercept and slope (trial) for each lizard in our models.
 We also incorporated the clutch identity as a random factor.
+_L.
+delicata_ lays one clutch per year, while _L.
+guichenoti_ lays two [@chapple_know_2011; @chapple_biology_2014].
+Since eggs were collected during half of the breeding season, clutches likely come from different mothers.
+By including clutch as a random factor, maternal condition should be accounted for in our analyses.
+Additionally, differential paternity may be captured by including both clutch and lizard identity in the model.
 Learning can also be age-dependent (see @noble_age-dependent_2014), and given that lizards incubated at different temperatures hatch at different times we explored the effects of age on learning.
@@
 Experimental procedures and laboratory housing complied with Australian law and were approved by the Australian National University Animal Experimentation Ethics Committee (A2022_33).
-Animals born in captivity cannot be re-released into the wild as string biosafety protocols across the states prohibit this.
-It is also not possible to rehome such a large number of animals for experiments.
+Animals born in captivity cannot be re-released into the wild as stringent biosafety protocols across the states prohibit this.
+It is also not possible to rehome such a large number of animals.
 Therefore, upon completion of experimental trials, lizards were kept in their enclosure until they were humanely euthanized following approved procedures.
-To euthanise animals, we use an injection of sodium pentobarbital (i.e., Lethabarb) (diluted 1:4 ringers solution) at
-60-100mg/kg, injected intrapleuroperitoneally.
+To euthanise animals, we use an injection of sodium pentobarbital (i.e., Lethabarb) (diluted 1:4 ringers solution) at 60-100mg/kg, injected intrapleuroperitoneally.
 We monitored the animals to ensure there was no irritation from the agent as indicated by distressed animals.
 Gently pinching the toes was used to confirm the absence of a response before the animal was disposed of.
+Crickets were maintained in big communal enclosures in the same room where the big colony is, and at the same temperature and light conditions.
+They were provided vegetables and water ad libitum, and they were given several egg carton shelters to refuge.
+All lizards were fed alive crickets except during the experiment, when we used crickets frozen at -21 ºC for 24 hours.
 
@@
 
-Both species learnt across all treatments (@fig-results B, D), but we did not find any difference between treatments or species in the rate of learning.
+Both species learnt across all treatments (@fig-results B, D), but we did not find any difference between treatments or species in the rate of learning (mean slopes per treatment for both species provided in Table 2 in Supplementary Material).
 For _L.
-delicata_, hormone treatment (Control - CORT = `r format_dec(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold, deli_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(deli_ControlCold, deli_ControlHot) - c(deli_CORTCold, deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(c(deli_CORTHot, deli_ControlHot) - c(deli_CORTCold, deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((deli_ControlHot - deli_CORTHot) - (deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B).
+delicata_, hormone treatment (slopes contrast: Control - CORT = `r format_dec(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold, deli_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(deli_ControlCold, deli_ControlHot) - c(deli_CORTCold, deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(c(deli_CORTHot, deli_ControlHot) - c(deli_CORTCold, deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((deli_ControlHot - deli_CORTHot) - (deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B).
 We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(guich_ControlCold, guich_ControlHot) - c(guich_CORTCold, guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(c(guich_CORTHot, guich_ControlHot) - c(guich_CORTCold, guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec((mean(guich_ControlHot) - mean(guich_CORTHot)) - (mean(guich_ControlCold) - mean(guich_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L.
@@
 guichenoti_ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot) - c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`).
+Figures for both species with the raw data were included in the Supplementary Material.
 
@@
 guichenoti_).
-We expected early environment to influence behavioural flexibility in both species.
+We expected the early environment to influence behavioural flexibility in both species.
 We also predicted that _L.
 delicata_ would be more flexible than _L.
-guichenoti_ and less affected by the early environment.
+guichenoti_ and less affected by prenatal conditions.
 Nevertheless, we did not find significant differences between treatments or species when we compared their performance in a reversal task.
@@
 We predicted that prenatal CORT treatment would decrease reversal learning abilities.
-As such, our results contrast to previous studies that show high GCs levels impaired performance in different types of learning tests [@lemaire_prenatal_2000; @zhu_prenatal_2004;  @farrell_developmental_2016].
+As such, our results contrast with previous studies that show high GCs levels impaired performance in different types of learning tests [@lemaire_prenatal_2000; @zhu_prenatal_2004;  @farrell_developmental_2016].
 Our results are, however, consistent with other experiments where GCs did not impact learning abilities [@szuran_water_1994; @bebus_associative_2016].
@@
 For example, in Sprague–Dawley rats, exposure to high doses of CORT, but not low doses, reduced the density of immature neurons and cell proliferation in the dentate gyrus [@DOSEneurobrummelte2010chronic].
-It is possible such dose-dependent effects exist and our concentrations failed to elicit changes to the brain that would result in impaired behavioural flexibility.
-We find this possibility unlikely since, in a previous experiment, we observed that a similar dose affected a multitude of other traits including growth and mortality in _L.
-delicata_ (unpublished data).
+It is possible such dose-dependent effects exist and our concentrations failed to elicit changes in the brain that would result in impaired behavioural flexibility.
+We find this possibility unlikely since, in a previous experiment, we observed that a similar dose affected a multitude of other traits including growth and baseline CORT levels in _L.
+delicata_ [@crino2024eggs].
 Nonetheless, we cannot dismiss this possibility because dose effects can differ between tissues [@lemaire_prenatal_2000].
@@
 It is possible that the temperatures used in our experiment did not affect the brain regions involved in coding reversal learning.
-Future studies should explore the effects of thermal environment on brain structure and function in these species to understand the mechanisms underlying the effects of temperature on learning.
+Future studies should explore the effects of the thermal environment on brain structure and function in these species to understand the mechanisms underlying the effects of temperature on learning.
 Furthermore, testing learning across different cognitive tasks could provide a more comprehensive understanding of the influence of temperature on cognition.
@@
 In addition, _B.
-dupeyerri_ are known to sex-reverse - some individuals can have female chromosomes but male phenotypes - under cold temperatures [@dissanayake2021effects].
+dupeyerri_ are known to sex-reverse - some individuals can have female chromosomes but male phenotypes - under cold incubation temperatures [@dissanayake2021effects].
 Such effects were not easily accounted for in these experiments making it challenging to understand if sex or temperature were the major drivers of learning differences [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-Future studies should explore the possible interactive effects of sex and incubation temperature on cognitive performance.
+Further research should focus on the possible interactive effects of sex and incubation temperature on cognitive performance.
 However, such studies will be challenging given the large sample sizes required to execute these studies rigorously.
@@
 
-#### Checking the models plots
-
-```{r, residuals}
-# Chunk for calling all the models and making the residuals
-## L. delicata
-mod_deli <- readRDS(here("output/models/delicomplete.rds"))
-resid_deli <- residuals(mod_deli)
-## L. guichenoti
-mod_guich <- readRDS(here("output/models/guichcomplete.rds"))
-resid_guich <- residuals(mod_guich)
-```
-
-Model formula for the reversal task is:
-
-Choice  ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
-
-Plots for the different models of the associative task:  
-1.- _L. delicata_    
-```{r , plotmod_drr, out.width="70%", fig.align="center"}
-bayes_R2(mod_deli)
-plot(mod_deli)
-```
-
-```{r, results='asis', echo=FALSE}
-cat("\\newpage")
-```
-
-2.- _L. guichenoti_  
-```{r , plotmod_grr, out.width="70%", fig.align="center"}
-bayes_R2(mod_guich)
-plot(mod_guich)
-```
-
-```{r, results='asis', echo=FALSE}
-cat("\\newpage")
-```
-
 Table 1.
-Estimates of Reversal learning slope for all the different treatments per each task, species, and group.
+Estimates of Reversal learning slope for all the different treatments per each task, specie, and group.
 Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
 All pmcmc tested the hypothesis that the mean equals zero.
-In bold, those values that are significant (pmcmc <0.05)
+In bold, those values that are significant (pmcmc <0.05).
 ```{r, tbl-data, results='asis'}
@@
 
+Figures with raw data
+
+```{r, fig_rawdata}
+#| label: fig_rawdata
+#| fig.cap: "Raw data for the reversal tasks for both species. Lines represent the mean proportion of correct choices per trial for each treatment."
+#
+# Load the data
+data_raw <- clean_df %>%
+  mutate(trt = factor(trt, 
+          levels = c("A_23", "B_23", "A_28", "B_28"), 
+          labels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
+        species = factor(species,
+          levels = c("delicata", "guichenoti"),
+          labels = c("italic('L. delicata')", "italic('L. guichenoti')"))) %>%
+data.frame()
+#
+# Plot the raw data for the reversal tasks for both species
+plot_raw <- ggplot(data_raw, aes(x = trial_reversal, y = FC_reversal, color = trt, fill = trt)) +
+  geom_smooth(method = "loess", linewidth = 1, alpha = 0.1) +
+  scale_color_manual(values = c("darkblue", "#68bde1", "#b50101", "#fa927d")) +
+  scale_fill_manual(values = c("darkblue", "#68bde1", "#b50101", "#fa927d")) +
+  facet_wrap(~species, nrow = 1, labeller = label_parsed) +
+  labs(x = "Trial", y = "Proportion of correct choices", color = "Treatments", fill = "Treatments") +
+  theme_classic()
+#
+# Save the plot
+ggsave("./output/figures/plot_raw.png", plot=plot_raw, width = 25, height = 18, units = "cm", dpi = 600)
+knitr::include_graphics("./output/figures/plot_raw.png")
+```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+Table 3.
+Number of individuals per treatment and species that reached a learning criterium of 5 consecutive correct choices (n lizards), and the average of trials taken (Trial) together with the standard deviation (sd).
+```{r, tbl-standard_crit, results='asis', out.widht = "26cm"}
+#| label: standard_crit
+#| tbl-cap: "Number of individuals per treatment and species that reached a learning criterium of 5 consecutive correct choices (n lizards), and the average of trials taken (Trial) together with the standard deviation (sd)."
+#
+source(here("R", "func.R"))
+# Load the data
+scrit_df <- clean_df %>%
+  group_by(lizard_id,species, trt) %>%
+  mutate(
+    run_id = cumsum(lag(FC_reversal, default = 0) == 0 & FC_reversal == 1),
+    run_length = ave(FC_reversal , run_id, FUN = cumsum) * FC_reversal 
+  ) %>%
+  filter(run_length >= 5) %>%
+  group_by(lizard_id, species, trt) %>%
+  slice_min(trial_reversal) %>%  # Get the first trial when the criterion was met
+  summarize(
+    species = first(species),
+    trt = first(trt),
+    trial_crit = min(trial_reversal),
+    .groups = "drop") %>%
+  mutate(trt = factor(trt, 
+          levels = c("A_23", "B_23", "A_28", "B_28"), 
+          labels = c("Control-Cold", "CORT-Cold", "Control-Hot", "CORT-Hot")),
+        species = factor(species,
+          levels = c("delicata", "guichenoti"),
+          labels = c("L. delicata", "L. guichenoti")))%>%
+  group_by(species, trt) %>%
+  summarize(
+    n = n(),
+    mean_trial = format_dec(mean(trial_crit),2),
+    des_trial = format_dec(sd(trial_crit),2),
+    .groups = "drop") %>%
+data.frame()
+#
+# Create the table
+crit_tbl <- flextable(scrit_df) %>%
+  set_table_properties(width = 1) %>%
+  align(align = "center", part = "all") %>%
+  fontsize(size = 10, part = "all") %>%
+  set_header_labels(species = "Specie",
+                    trt = "Treatment",
+                    n = "n lizards",
+                    mean_trial = "Mean",
+                    des_trial = "sd") %>%
+    italic(i = c(1,5), j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
+    flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
+    hline(i = 4, j = c(1:5), part = "body") %>% # To make some horizontal lines
+    autofit()
+crit_tbl
+```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
 Checking the effect of age on the learning rate in the associative task.
@@
 
-Table 3. Results for _L. delicata_ when the model included the age:
+Table 4. Results for _L. delicata_ when the model included the age:
 ```{r, tbl-agedeli, results='asis', out.widht = "26cm"}
@@
 
-Table 4. Results for _L. guichenoti_ when the model included the age:
+Table 5. Results for _L. guichenoti_ when the model included the age:
 ```{r, tbl-ageguich, results='asis'}
@@
 ```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+#### Checking the main models plots
+
+```{r, residuals}
+# Chunk for calling all the models and making the residuals
+## L. delicata
+mod_deli <- readRDS(here("output/models/delicomplete.rds"))
+resid_deli <- residuals(mod_deli)
+## L. guichenoti
+mod_guich <- readRDS(here("output/models/guichcomplete.rds"))
+resid_guich <- residuals(mod_guich)
+```
+
+Model formula for the reversal task is:
+
+Choice  ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
+
+Plots for the different models of the associative task:  
+1.- _L. delicata_    
+```{r , plotmod_drr, out.width="70%", fig.align="center"}
+bayes_R2(mod_deli)
+plot(mod_deli)
+```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+2.- _L. guichenoti_  
+```{r , plotmod_grr, out.width="70%", fig.align="center"}
+bayes_R2(mod_guich)
+plot(mod_guich)
+```

### 2024-08-30 .vdoc.r

@@ -69,11 +69,14 @@ pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4,
 #
 #
 #
+#
+#
 #| label: fig-Methods
 #| fig.cap: "Experimental design of early environment manipulation and learning tasks. Panel A represents the early environment manipulation for both species. Panel B shows the habituation phase with the respective three different stages. And panel C represents the associative and reversal tasks; white lids show the ramps where the food reward was not accessible."
 
 knitr::include_graphics("./Others/BEHFLEX_FIG_1.png")
 
+#
 #
 #
 #
@@ -218,42 +221,6 @@ cat("\\newpage")
 #
 #
 #
-#
-#
-#
-#
-# Chunk for calling all the models and making the residuals
-## L. delicata
-mod_deli <- readRDS(here("output/models/delicomplete.rds"))
-resid_deli <- residuals(mod_deli)
-## L. guichenoti
-mod_guich <- readRDS(here("output/models/guichcomplete.rds"))
-resid_guich <- residuals(mod_guich)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-bayes_R2(mod_deli)
-plot(mod_deli)
-#
-#
-#
-cat("\\newpage")
-#
-#
-#
-#
-bayes_R2(mod_guich)
-plot(mod_guich)
-#
-#
-#
-cat("\\newpage")
 #
 #
 #
@@ -518,6 +485,96 @@ cat("\\newpage")
 #
 #
 #
+#| label: fig_rawdata
+#| fig.cap: "Raw data for the reversal tasks for both species. Lines represent the mean proportion of correct choices per trial for each treatment."
+#
+# Load the data
+data_raw <- clean_df %>%
+  mutate(trt = factor(trt, 
+          levels = c("A_23", "B_23", "A_28", "B_28"), 
+          labels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
+        species = factor(species,
+          levels = c("delicata", "guichenoti"),
+          labels = c("italic('L. delicata')", "italic('L. guichenoti')"))) %>%
+data.frame()
+#
+# Plot the raw data for the reversal tasks for both species
+plot_raw <- ggplot(data_raw, aes(x = trial_reversal, y = FC_reversal, color = trt, fill = trt)) +
+  geom_smooth(method = "loess", linewidth = 1, alpha = 0.1) +
[…]

### 2024-08-30 ms.qmd
Updates

@@
 
+#### Estimates of reversal learning slopes for all the different treatments per each task, specie, and group.
 Table 1.
@@
 
-Figures with raw data
+#### Figures with raw data
 
@@
 
+#### Results using a standard learning criterion of 5 consecutive correct choices  
 Table 3.
@@
 
-Checking the effect of age on the learning rate in the associative task.
+#### Checking the main models plots
+
+```{r, residuals}
+# Chunk for calling all the models and making the residuals
+## L. delicata
+mod_deli <- readRDS(here("output/models/delicomplete.rds"))
+resid_deli <- residuals(mod_deli)
+## L. guichenoti
+mod_guich <- readRDS(here("output/models/guichcomplete.rds"))
+resid_guich <- residuals(mod_guich)
+```
+
+Model formula for the reversal task is:
+
+Choice  ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
+
+Plots for the different models of the reversal task:  
+1.- _L. delicata_    
+```{r , plotmod_drr, out.width="70%", fig.align="center"}
+bayes_R2(mod_deli)
+plot(mod_deli)
+```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+2.- _L. guichenoti_  
+```{r , plotmod_grr, out.width="70%", fig.align="center"}
+bayes_R2(mod_guich)
+plot(mod_guich)
+```
+
+```{r, results='asis', echo=FALSE}
+cat("\\newpage")
+```
+
+#### Checking the effect of age on the learning rate in the associative task.
 
@@
 ```
-
-```{r, results='asis', echo=FALSE}
-cat("\\newpage")
-```
-
-#### Checking the main models plots
-
-```{r, residuals}
-# Chunk for calling all the models and making the residuals
-## L. delicata
-mod_deli <- readRDS(here("output/models/delicomplete.rds"))
-resid_deli <- residuals(mod_deli)
-## L. guichenoti
-mod_guich <- readRDS(here("output/models/guichcomplete.rds"))
-resid_guich <- residuals(mod_guich)
-```
-
-Model formula for the reversal task is:
-
-Choice  ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
-
-Plots for the different models of the associative task:  
-1.- _L. delicata_    
-```{r , plotmod_drr, out.width="70%", fig.align="center"}
-bayes_R2(mod_deli)
-plot(mod_deli)
-```
-
-```{r, results='asis', echo=FALSE}
-cat("\\newpage")
-```
-
-2.- _L. guichenoti_  
-```{r , plotmod_grr, out.width="70%", fig.align="center"}
-bayes_R2(mod_guich)
-plot(mod_guich)
-```

### 2024-08-30 .vdoc.r
Updates

@@ -1,752 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: setup
-pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: fig-Methods
-#| fig.cap: "Experimental design of early environment manipulation and learning tasks. Panel A represents the early environment manipulation for both species. Panel B shows the habituation phase with the respective three different stages. And panel C represents the associative and reversal tasks; white lids show the ramps where the food reward was not accessible."
-
-knitr::include_graphics("./Others/BEHFLEX_FIG_1.png")
-
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#| label: cleandata
-# Obtain the main df using "./R/1_data_process.R"
-source(here("R", "1_data_process.R"))
-#
-#
-#
-#| label: sampleSize
-# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
-source(here("R", "func.R"))
-#
-specie <- c("delicata", "guichenoti")
-hormone <- c("CORT", "Control")
-temperature <- c("Cold", "Hot")
-#
-n_list <- list()
-#
-for(i in 1:length(specie)){
-  for(k in 1:length(hormone)){
-    for(l in 1:length(temperature)){
-      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
-      }
-    }
-  }
-#
-#
-#
-#
-#
-#| label: models
[…]

### 2024-08-31 ms.qmd
Updates

@@
 All pmcmc tested the hypothesis that the mean equals zero.
-In bold, those values that are significant (pmcmc <0.05).
+In bold, those values that are significant (p~mcmc~ <0.05).
 ```{r, tbl-data, results='asis'}
@@
 #| label: fig_rawdata
-#| fig.cap: "Raw data for the reversal tasks for both species. Lines represent the mean proportion of correct choices per trial for each treatment."
+#| fig.cap: "Probability of choosing correctly over trials for each of the treatments and species.
+The dots represent the proportion of individuals per trial that chose correctly while the lines show the mean predicted probability of choosing correctly, estimated using the posteriors of our model."
 #
@@
 data_raw <- clean_df %>%
+  group_by(species, trt, trial_reversal) %>%
+  summarize(prop_correct = mean(FC_reversal, na.rm = TRUE)) %>%
   mutate(trt = factor(trt, 
@@
           labels = c("italic('L. delicata')", "italic('L. guichenoti')"))) %>%
+  rename(Trial = trial_reversal,
+         Treatment = trt) %>%
 data.frame()
 #
-# Plot the raw data for the reversal tasks for both species
-plot_raw <- ggplot(data_raw, aes(x = trial_reversal, y = FC_reversal, color = trt, fill = trt)) +
-  geom_smooth(method = "loess", linewidth = 1, alpha = 0.1) +
+# Get the df for the predicted prob
+df_deliprob$species <- "italic('L. delicata')"
+df_guichprob$species <- "italic('L. guichenoti')"
+df_combined <- rbind(df_deliprob, df_guichprob)
+df_all <- full_join(df_combined, data_raw, by = c("Trial", "Treatment", "species"))
+# Plot the raw data for the reversal tasks for both species with the predicted prob
+plot_raw <- ggplot(data = df_all, aes(x = Trial, y = Mean_Predicted_prob, color = Treatment, fill = Treatment)) +
+  geom_smooth(linewidth = 1) +
+  geom_point(data = df_all, aes(x = Trial, y = prop_correct, color = Treatment, fill = Treatment)) +
   scale_color_manual(values = c("darkblue", "#68bde1", "#b50101", "#fa927d")) +
   scale_fill_manual(values = c("darkblue", "#68bde1", "#b50101", "#fa927d")) +
-  facet_wrap(~species, nrow = 1, labeller = label_parsed) +
+  facet_grid(species ~ Treatment, labeller = label_parsed, switch = "y") +
   labs(x = "Trial", y = "Proportion of correct choices", color = "Treatments", fill = "Treatments") +

### 2024-09-02 ms.qmd
Updates

@@
 We manipulated CORT and incubation temperature in both species and then subjected hatchlings to a reversal learning task.
-Reversal learning, in particular, is a widely employed tool to measure behavioral flexibility [@gapp2014early; @hurtubise2017effects], as it assesses an individual's ability to alter a learned behavior in response to environmental changes, providing researchers with a clear indicator of their ability to adjust to new conditions [@brown2010behavioral].
+Reversal learning, in particular, is a widely employed tool to measure behavioural flexibility [@gapp2014early; @hurtubise2017effects], as it assesses an individual's ability to reverse a previously learned behaviour providing researchers with a clear indicator of their ability to adjust to new conditions [@brown2010behavioral].
 
@@
 We first allocated eggs into one of two different treatments: in the CORT treatment, eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (vehicle) at a final concentration of 10 pg CORT/mL; in the Control treatment eggs received an equal volume of the vehicle.
-CORT concentration employed in the CORT treatment represents 2 standard deviations above the mean natural concentration obtained in eggs from both species (non-published data).
-Doses were determined by referencing published yolk corticosterone concentrations in other oviparous species [@lovern2008effects ; @hanover2019corticosterone] and our own unpublished data.
+This method has been validated before in _L.
+delicata_ [@crino2024eggs], increasing CORT concentration in egg approximately 2 standard deviations above the mean natural concentration.
 After the hormone treatment, were then incubated in one of the two previously mentioned temperature regimes (Cold or Hot) until hatching.
@@
 We ran four parallel MCMC chains of 3000 iterations for each model, with a warmup period of 1000 iterations.
-We modelled correct choices [correct (1) or not (0)] as the response variable, and trial, hormone (CORT versus Control), incubation temperature (Cold versus Hot), and the three-way interaction between trial, hormone, and temperature.
-The error structure was modeled using a Bernoulli distribution with a logit link function (family = Bernoulli(link = 'logit')).
+We modelled correct choices [correct (1) or not (0)] as the response variable, and trial, hormone (CORT versus Control), incubation temperature (Cold versus Hot), along with the three-way interaction between trial, hormone, and temperature.
+If early environments impact learning then we would predict that the rate of learning (i.e., trial slope) varies by treatment as captured by the interactions.
+The error structure was modelled using a Bernoulli distribution with a logit link function (family = Bernoulli(link = 'logit')).
 We included a random intercept and slope (trial) for each lizard in our models.
@@
 Since eggs were collected during half of the breeding season, clutches likely come from different mothers.
-By including clutch as a random factor, maternal condition should be accounted for in our analyses.
-Additionally, differential paternity may be captured by including both clutch and lizard identity in the model.
-Learning can also be age-dependent (see @noble_age-dependent_2014), and given that lizards incubated at different temperatures hatch at different times we explored the effects of age on learning.
+Additionally, previous research has shown that clutches are generally sired by a single male, but sperm storage can occur [@kar2023heritability].
+Given our partial split-clutch design, and the fact that maternal effects are expected to be stronger than paternal effects in these species, including the clutch as a random factor would account for the effects of parental condition.
+Learning can also be age-dependent [see @noble_age-dependent_2014], and given that lizards incubated at different temperatures hatch at different times we explored the effects of age on learning.
 Indeed, lizards’ age at the beginning of the experiment ranged from 41 to 148 days old in _L.
@@
 Slope estimates greater than zero were considered as evidence of learning, while those less or equal to zero were not.
-We calculated the probability that slopes or contrasts between slopes differed from zero (p~mcmc~) using the posterior distributions.
-We considered statistical significance if p~mcmc~ < 0.05.
+p~mcmc~ test the hypothesis that slopes and slopes contrasts are zero.
+We considered statistical significance if pmcmc < 0.05.
 
@@
 Gently pinching the toes was used to confirm the absence of a response before the animal was disposed of.
-Crickets were maintained in big communal enclosures in the same room where the big colony is, and at the same temperature and light conditions.
+Crickets were maintained in big communal enclosures (68.5 L x 49 W x 39 H cm) in the same room where the big colony is, and at the same temperature and light conditions.
 They were provided vegetables and water ad libitum, and they were given several egg carton shelters to refuge.
@@
 For _L.
-delicata_, hormone treatment (slopes contrast: Control - CORT = `r format_dec(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold, deli_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(deli_ControlCold, deli_ControlHot) - c(deli_CORTCold, deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(c(deli_CORTHot, deli_ControlHot) - c(deli_CORTCold, deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((deli_ControlHot - deli_CORTHot) - (deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B).
-We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(guich_ControlCold, guich_ControlHot) - c(guich_CORTCold, guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(c(guich_CORTHot, guich_ControlHot) - c(guich_CORTCold, guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec((mean(guich_ControlHot) - mean(guich_CORTHot)) - (mean(guich_ControlCold) - mean(guich_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L.
+delicata_, hormone treatment (β~Control~ - β~CORT~ = `r format_dec(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold, deli_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(deli_ControlCold, deli_ControlHot) - c(deli_CORTCold, deli_CORTHot)), 3)`), incubation temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(c(deli_CORTHot, deli_ControlHot) - c(deli_CORTCold, deli_ControlCold)),3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((deli_ControlHot - deli_CORTHot) - (deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B).
+We similarly found no significant effects of  hormone (β~Control~ - β~CORT~ = `r format_dec(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(guich_ControlCold, guich_ControlHot) - c(guich_CORTCold, guich_CORTHot)), 3)`), incubation temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(c(guich_CORTHot, guich_ControlHot) - c(guich_CORTCold, guich_ControlCold)),3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec((mean(guich_ControlHot) - mean(guich_CORTHot)) - (mean(guich_ControlCold) - mean(guich_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L.
 guichenoti_ (see @fig-results C, D).
@@
 delicata_ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot), 0.025), 3)`, `r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot), 0.975), 3)`]; mean learning of slope in _L.
-guichenoti_ = `r format_dec(mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot), 0.025), 3)`, `r format_dec(quantile(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot), 0.975), 3)`]; _L.
-delicata_ - _L.
-guichenoti_ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot) - c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`).
+guichenoti_ = `r format_dec(mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot), 0.025), 3)`, `r format_dec(quantile(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot), 0.975), 3)`]; β~_L.
+delicata_~ - β~_L.
+guichenoti_~ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot) - c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`).
 Figures for both species with the raw data were included in the Supplementary Material.
@@
 Table 3.
-Number of individuals per treatment and species that reached a learning criterium of 5 consecutive correct choices (n lizards), and the average of trials taken (Trial) together with the standard deviation (sd).
+Number of individuals per treatment and species that reached a learning criterion of 5 consecutive correct choices (n lizards), and the average of trials taken (Trial) together with the standard deviation (sd).
 ```{r, tbl-standard_crit, results='asis', out.widht = "26cm"}
 #| label: standard_crit
-#| tbl-cap: "Number of individuals per treatment and species that reached a learning criterium of 5 consecutive correct choices (n lizards), and the average of trials taken (Trial) together with the standard deviation (sd)."
+#| tbl-cap: "Number of individuals per treatment and species that reached a learning criterion of 5 consecutive correct choices (n lizards), and the average of trials taken (Trial) together with the standard deviation (sd)."
 #

### 2024-09-02 ms.qmd
Updates

@@
 We manipulated prenatal CORT levels and incubation temperature in a 2x2 factorial design, and then assessed behavioural flexibility through a reversal learning task.
-We hypothesized prenatal CORT and cold temperatures to impair with lizards' performance in the reversal task.
+We hypothesized prenatal CORT and cold temperatures would impair performance in the reversal task.
 Given _L.
-delicata_'s success as an invassive species, we expected this species to behave more flexibly and be less affected by early environmental conditions.
+delicata_'s success as an invasive species, we expected this species to behave more flexibly and be less affected by early environmental conditions.
 Contrary to our expectations, behavioural flexibility appears to be robust to prenatal temperature and CORT in both species.
@@
 This suggests that behavioural flexibility is likely to be underpinned by complex neural mechanisms, and that alterations in these mechanisms may impact animals' ability to respond to novel situations.
-The brain is considered especially sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004], creating uncertainty about how the conditions faced during early life might impact behavioural flexibility.
+The brain is considered especially sensitive to environmental change during the early stages of development [@zhu_prenatal_2004], creating uncertainty about how the conditions faced during early life might impact behavioural flexibility.
 
 The conditions in which organisms develop can be altered by the circumstances faced by their parents.
-For instance, exposing three-spined stickleback (_Gasterosteus aculeatus_) females to a model predator during ovulation, affected their offspring's tedency to use social cues [@feng2015effect].
-Under stressful situations, animal's sensory systems detect and transmit environmental signals to instigate adaptive physiological and behavioural adjustments – responses that are mediated by glucocorticoids (GCs) [@sapolsky_how_2000].
+For instance, exposing three-spined stickleback (_Gasterosteus aculeatus_) females to a model predator during ovulation, affected their offspring's tendency to use social cues [@feng2015effect].
+Under stressful situations, animal sensory systems detect and transmit environmental signals to instigate adaptive physiological and behavioural adjustments – responses that are mediated by glucocorticoids (GCs) [@sapolsky_how_2000].
 Glucocorticoids can be transmitted to offspring and influence their phenotype and development through transgenerational effects [@Crino_2023].
@@
 Both GCs and temperature are known to exert potent effects on brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017] and cognition [@clark_colour_2014; @lui2017chronic], but little is known about how they may interact to affect behavioural flexibility.
-Since behaving flexibly is essential for facing novel environments, studying the interactive effect of early environment on behavioural flexibility is crucial if we aim to understand animals' capability to adapt to environmental changes.
+Since behaving flexibly is essential for dealing with novel environments, understanding how early developmental environments collectively impact cognition is crucial for predicting the consequences of environmental change.
 
@@
 Both species have similar life-histories and overlapping distributions [@chapple_know_2011; @chapple_biology_2014], but only _Lampropholis delicata_ has been successful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI].
-Previous studies exploring behavioral differences between the two species have found _L.
+Previous studies exploring behavioural differences between the two species have found _L.
 delicata_ to be more exploratory than _L.
@@
 However, the relative impact of early environments on behavioural flexibility remains unexplored.
-Early environments are known to affect suites of morphological and behavioural traits differently in each species [@carrasco2023maternal; @kar2023heritability], but uncertainty still exists about the interactive role of maternal CORT and early temperatures on behavioural flexibility.
+Early environments are known to affect suites of morphological and behavioural traits differently in each species [@carrasco2023maternal; @kar2023heritability].
 We manipulated CORT and incubation temperature in both species and then subjected hatchlings to a reversal learning task.
-Reversal learning, in particular, is a widely employed tool to measure behavioural flexibility [@gapp2014early; @hurtubise2017effects], as it assesses an individual's ability to reverse a previously learned behaviour providing researchers with a clear indicator of their ability to adjust to new conditions [@brown2010behavioral].
+Reversal learning is a widely employed tool to measure behavioural flexibility [@gapp2014early; @hurtubise2017effects], as it assesses an individual's ability to reverse a previously learnt behaviour providing researchers with a clear indicator of their ability to adjust to new conditions [@brown2010behavioral].
 
 We predicted that both cold incubation temperatures and CORT treatment will impair behavioural flexibility [@clark_colour_2014; @lui2017chronic], and the combination of both treatments to have the most detrimental effect on behavioural flexibility.
-Since invassive species are expected to behave more flexibly [@sol2000behavioural; @sol2008brain; @wright2010behavioral; @amiel_smart_2011; @chapple2012can], we predicted that _L.
+Since invasive species are expected to behave more flexibly [@sol2000behavioural; @sol2008brain; @wright2010behavioral; @amiel_smart_2011; @chapple2012can], we predicted that _L.
 delicata_, on average, will perform more proficiently in the task compared to _L.
@@
 This method has been validated before in _L.
-delicata_ [@crino2024eggs], increasing CORT concentration in egg approximately 2 standard deviations above the mean natural concentration.
+delicata_ [@crino2024eggs], increasing CORT concentration in eggs by approximately 2 standard deviations above the mean natural concentration.
 After the hormone treatment, were then incubated in one of the two previously mentioned temperature regimes (Cold or Hot) until hatching.
@@
 Additionally, previous research has shown that clutches are generally sired by a single male, but sperm storage can occur [@kar2023heritability].
-Given our partial split-clutch design, and the fact that maternal effects are expected to be stronger than paternal effects in these species, including the clutch as a random factor would account for the effects of parental condition.
+Given our partial split-clutch design, and the fact that maternal effects are expected to be stronger than paternal effects in these species, including the clutch as a random factor should account for the effects of parental condition.
 Learning can also be age-dependent [see @noble_age-dependent_2014], and given that lizards incubated at different temperatures hatch at different times we explored the effects of age on learning.
@@
 Slope estimates greater than zero were considered as evidence of learning, while those less or equal to zero were not.
-p~mcmc~ test the hypothesis that slopes and slopes contrasts are zero.
-We considered statistical significance if pmcmc < 0.05.
+p~mcmc~ test the hypothesis that slopes and slopes contrasts are different from zero.
+We considered an effect statistically significant if pmcmc < 0.05.
 
@@
 
-Both species learnt across all treatments (@fig-results B, D), but we did not find any difference between treatments or species in the rate of learning (mean slopes per treatment for both species provided in Table 2 in Supplementary Material).
+Both species learnt across all treatments (@fig-results B, D), but we did not find any difference between treatments or species in the rate of learning [mean slopes (denoted as β throughout) per treatment for both species provided in Table 2 in Supplementary Material].
 For _L.
@@
 
-Behavioural flexbility appears to be robust to early exposure to maternal GCs in both _L.
+Behavioural flexibility appears to be robust to early exposure to maternal GCs in both _L.
 delicata_ and _L.
@@
 More striking is the absence of an effect of incubation temperature on behavioural flexibility because most studies have reported better performance in different associative learning and motor tasks when incubated at higher temperatures [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014].
-Studies that have reported cold-incubated lizards to learning faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temperatures far beyond the natural range in their hot treatments and it is unclear how such conditions relate to wild environments.
-Our results suggest that behavioural flexibility is robust to temperature in both species of skinks - at least in this study.
+However, studies that have reported cold-incubated lizards to learning faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temperatures far beyond the natural range in their hot treatments.
+As such, it is unclear how such conditions relate to wild environments.
+Our results suggest that behavioural flexibility is robust to temperature in both species of skinks at least in this study.
 It could be argued that the differences in our incubation temperatures were not extreme enough to elicit significant differences in learning performance.
@@
 
-Despite sharing life-history traits, only _L.
-delicata_ has proven successful in colonising various global regions [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI], and we predicted this may relate to higher behavioural flexibility.
-Furthermore, we expected behavioural flexibility in this species to be less susceptible to the effect of early environment since this trait can be adaptive in several stages of invasion involving more than one generation.
+Despite sharing life-history traits, only L.
+delicata has proven successful in colonising various regions globally [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI], and we predicted this may relate to higher behavioural flexibility.
+Furthermore, we expected behavioural flexibility in _L.
+delicata_ to be less susceptible to the effect of early environment since this trait can be adaptive in several stages of invasion involving more than one generation.
+Regardless, we did not find differences in reversal learning between _L.
+delicata_ and _L.
+guichenoti_ as expected.
+@bezzina2014does also found no differences in learning between the two skinks in an associative learning task.
+Our results align with the latter study and suggest that behavioural flexibility does not differ between these species either.
 While it will be important to explore replicate invasion events (both successful and unsuccessful) such information is seldom available.
 Nonetheless, there is precedence in the literature to expect differences between these two species [@chapple_know_2011; @chapple2013biosecurity].
-Regardless, while we did not find differences in reversal learning between _L.
-delicata_ and _L.
-guichenoti_, previous studies have shown that _L.
+For example, previous studies have shown that _L.
 delicata_ more readily explores novel environments than _L.
 guichenoti_, which can be advantageous during colonisation [@chapple_know_2011].
-However, @bezzina2014does found no differences in learning between the two skinks in an associative learning task.
-Our results align with the latter study and suggest that behavioural flexibility does not differ between these species either.
-Our results along with others' [@bezzina2014does] suggest that other aspects of their biology are more relevant for _L.
-delicata_'s success as invaders than learning and behavioural flexibility.
+Our results along with others’ [@bezzina2014does] suggest that other aspects of their biology are more relevant for _L.
+delicata_’s success as invaders than learning and behavioural flexibility.
 Differences in exploratory behaviour is likely to be the key factor explaining why _L.

### 2024-09-02 ms.qmd
Updates

@@
 ## Abstract
-Behavioural flexibility is expected to be crucial for animals adapting to environmental changes.
+Behavioural flexibility, the ability to adjust behaviour adaptively in response to internal or external changes, is expected to be crucial for animals adapting to environmental fluctuations.
 However, the conditions experienced during early development can profoundly impact behavioural flexibility making it unclear how populations will respond to novel circumstances.
@@
 At the same time, stressful conditions can influence parental behaviour during nesting and consequently the thermal developmental conditions offspring experience.
-Here, we investigated the interactive effects of prenatal corticosterone (CORT) and temperature on behavioural flexibility in two lizard species, _Lampropholis delicata_ and _L.
-guichenoti_.
+Here, we investigated the interactive effects of prenatal corticosterone (CORT) and temperature on behavioural flexibility in two lizard species, Lampropholis delicata and L.
+guichenoti.
 We manipulated prenatal CORT levels and incubation temperature in a 2x2 factorial design, and then assessed behavioural flexibility through a reversal learning task.
 We hypothesized prenatal CORT and cold temperatures would impair performance in the reversal task.
-Given _L.
-delicata_'s success as an invasive species, we expected this species to behave more flexibly and be less affected by early environmental conditions.
+Given L.
+delicata’s success as an invasive species, we expected this species to behave more flexibly and be less affected by early environmental conditions.
 Contrary to our expectations, behavioural flexibility appears to be robust to prenatal temperature and CORT in both species.
-The lack of difference in reversal learning between _L.
-delicata_ and _L.
-guichenoti_ suggests that novel environments are unlikely to influence flexible behavioural learning and that behavioural flexibility itself is unlikely to explain differences in invasion success between these species.
+The lack of difference in reversal learning between L.
+delicata and L.
+guichenoti suggests that novel environments are unlikely to influence flexible behavioural learning and that behavioural flexibility itself is unlikely to explain differences in invasion success between these species.
 

### 2024-10-31 ms.qmd
Updates

--- 2024-09-02 ms.qmd
@@
 Given _L.
-delicata_'s success as an invasive species, we expected this species to behave more flexibly and be less affected by early environmental conditions.
+delicata_’s success as an invasive species, we expected this species to behave more flexibly and be less affected by early environmental conditions.
 Contrary to our expectations, behavioural flexibility appears to be robust to prenatal temperature and CORT in both species.
@@
 *Breeding colony* -- We tested juveniles originating from a breeding colony established in the lab since 2019.
-A total of 270 and 180 adults of *L.
-delicata* and *L.
-guichenoti*, respectively, were established in containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure.
+A total of 270 and 180 adults of _L.
+delicata_ and _L.
+guichenoti_, respectively, were established in containers (41.5 L x 30.5 W x 21 H cm) with six lizards (2 males and 4 females) per enclosure.
 Enclosures had non-stick matting, a shelter, and several small water dishes.
 Water was given daily, and they were fed approx.
-40 mid-size crickets (*Acheta domestica*) per enclosure three days a week.
+40 mid-size crickets (_Acheta domestica_) per enclosure three days a week.
 Crickets were dusted with calcium weekly and multivitamin and calcium biweekly.
@@
 We checked for the presence of eggs in the boxes three days a week.
-After collection, we measured the length and width of eggs with a digital caliper to the nearest 0.1 mm and weighed them with a digital scale ± 0.001g error (OHAUS, Model spx123).
-We also assigned identities to the clutch and each egg.
+After collection, we measured the length and width of eggs with a digital caliper to the nearest 0.1 mm and weighed them with a digital scale ± 0.001 g error (OHAUS, Model spx123).
+We also assigned a unique number to the clutch and each egg.
 Eggs were then treated with CORT or vehicle (see CORT and Temperature manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite).
@@
 *Hatchlings* – Eggs in the incubator were checked three times a week for hatchlings.
-After hatchling, we measured juveniles’ SVL and Tail Length (TL) with a ruler to the nearest mm and weighed them with a digital scale ± 0.001g error.
+After hatchling, we measured juveniles’ SVL and Tail Length (TL) with a ruler to the nearest mm and weighed them with a digital scale ± 0.001 g error.
 We then placed hatchlings in individual enclosures (18.7L x 13.2W x 6.3H cm) and provided them with non-stick matting, a shelter, and a small water dish.
@@
 Two weeks before starting the training phase (see below), lizards were moved to an experimental arena for acclimatisation.
-The arenas were individual medium size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the side and a water dish on the other.
+The arenas were individual medium size (41 L x 29.7 W x 22 H cm) plastic containers with a shelter (9 L x 6 W x 1.5 H cm) on one of the sides and a water dish on the other.
 These new enclosures were placed in two rooms across 7 different racks that were monitored by 7 different CCTV systems (device model DVR-HP210475) that allowed us to record their behaviour during the experiment (see details below).
@@
 We provided a temperature gradient by means of a heat cord and heat lamps in a 12 h light: 12 h dark cycle.
-The temperature of both rooms was set to between 22-24ºC.
+The temperature of both rooms was set to between 22-24 ºC.
 
@@
 
-To empirically test the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (Cold -- 23ºC ± 3ºC or Hot -- 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A).
+To empirically test the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (Cold -- 23 ºC ± 3 ºC or Hot -- 30 ºC ± 3 ºC) in a 2x2 factorial design (@fig-Methods A).
 We first allocated eggs into one of two different treatments: in the CORT treatment, eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (vehicle) at a final concentration of 10 pg CORT/mL; in the Control treatment eggs received an equal volume of the vehicle.
@@
 delicata_ [@crino2024eggs], increasing CORT concentration in eggs by approximately 2 standard deviations above the mean natural concentration.
-After the hormone treatment, were then incubated in one of the two previously mentioned temperature regimes (Cold or Hot) until hatching.
+After the hormone treatment, eggs were incubated in one of the two previously mentioned temperature regimes (Cold or Hot) until hatching.
 These temperatures represent the upper and lower limit of the natural incubation temperatures [@qualls2000post; @cheetham2011embryonic].
-The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.
+
+We counterbalanced the number of eggs assigned to each hormone and temperature treatment using a partial split-clutch design.
+We assigned at least one egg per clutch to each treatment, and the remaining eggs were randomly assigned to one of the treatments.
+When the eggs per clutch was less than four eggs, we assigned each egg randomly to one of the treatments.
+The final total number of clutches per species is included in Results.
 
@@
 The habituation phase was divided into three stages: in the first stage, the reward, a small, frozen cricket (*A.
-domestica*) was placed in an opaque petri dish (3D x 1.6H cm) (@fig-Methods Habituation phase, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods Habituation phase, Stage 2); and in the third stage, the cricket was left inside a well (3D x 1.75H cm) on top of the ramp (Fig.
+domestica*) was placed in an opaque petri dish (3 D x 1.6 H cm) (@fig-Methods Habituation phase, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods Habituation phase, Stage 2); and in the third stage, the cricket was left inside a well (3D x 1.75H cm) on top of the ramp (Fig.
 @fig-Methods Habituation phase, Stage 3).
-Trials in every stage lasted one hour, begining when the feeding block (petri dish, ramp, or both) was placed inside the enclosure and finishing when we took the feeding block away.
+Trials in every stage lasted one hour, beginning when the feeding block (petri dish, ramp, or both) was placed inside the enclosure and finishing when we took the feeding block away.
 We recorded whether the cricket had been consumed or not and we considered a stage as completed if the lizards ate the crickets in at least 5 out of 6 trials.
@@
 
-In the colour association (Associative task in Fig.
-@fig-Methods) and reversal task (Reversal task in @fig-Methods B), we used three ramps that were identical in shape and size but different in the colour.
+In the colour association (Associative task in @fig-Methods) and reversal task (Reversal task in @fig-Methods B), we used three ramps that were identical in shape and size but different in the colour.
 The colours of these ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision].
 However, to control for potential colour biases, we assigned one group of lizards within each treatment to associate food in the blue ramp followed by the red ramp in the reversal, while in the other group the order was reversed.
-As in the last stage of the habituation phase, we placed the cricket inside the wells of the ramps, but then two of them were covered with 3D-printed lids (3D x 0.5H cm) so prey was only accessible on one ramp.
+As in the last stage of the habituation phase, we placed the cricket inside the wells of the ramps, but then two of them were covered with 3D-printed lids (3 D x 0.5 H cm) so prey was only accessible on one ramp.
 The food reward was placed on all three ramps to avoid lizards using prey chemical cues that were released in the closed wells through a series of small holes on the top of the lids.
@@
 Additionally, previous research has shown that clutches are generally sired by a single male, but sperm storage can occur [@kar2023heritability].
-Given our partial split-clutch design, and the fact that maternal effects are expected to be stronger than paternal effects in these species, including the clutch as a random factor should account for the effects of parental condition.
+Given our partial split-clutch design, and the fact that maternal effects are expected to be stronger than paternal effects in these species, including the clutch as a random factor should account for the effects of parental identity.
+
 Learning can also be age-dependent [see @noble_age-dependent_2014], and given that lizards incubated at different temperatures hatch at different times we explored the effects of age on learning.
@@
 guichenoti_.
-However, when this variable was included in the models we did not find any significant effect of age (see Supplementary material).
+However, when this variable was included in the models we did not find any significant effect of age (see Supplementary Material).
 As such, we present models without age as a fixed effect.
+
 We used the posterior distributions of parameters from these models to test for differences in learning rate between treatments and species.
@@
 p~mcmc~ test the hypothesis that slopes and slopes contrasts are different from zero.
-We considered an effect statistically significant if pmcmc < 0.05.
+We considered an effect statistically significant if p~mcmc~ < 0.05.
 
@@
 Both the breeding animals and the ones used in this experiment were provided humane laboratory housing, with thermoregulatory opportunities, light (UV and heat) and moderate levels of humidity (see above for details).
-Lizards in the colony received food ad libitum while the subjects in the experiment were feed one cricket daily during the experiment.
+Lizards in the colony received food _ad libitum_ while the subjects in the experiment were fed one cricket daily during the experiment.
 All lizards were handled minimally to avoid stress.
@@
 
+```{r, countclutches}
+#| label: countclutches
+# Count the number of clutches per species
+## L. delicata
+deli_clutches <- clean_df %>% filter(species == "delicata") %>% distinct(clutch) %>% nrow()
+## L. guichenoti
+guich_clutches <- clean_df %>% filter(species == "guichenoti") %>% distinct(clutch) %>% nrow()
+```
+
 We started with 96 lizards, 48 per species and 12 per treatment per species.
@@
 The final sample sizes per treatment and species are listed in @fig-results.
+These animals came from a total of `r deli_clutches` clutches in _L.
+delicata_ and `r guich_clutches` in _L.
+guichenoti_.
 
@@
 
-Both species learnt across all treatments (@fig-results B, D), but we did not find any difference between treatments or species in the rate of learning [mean slopes (denoted as β throughout) per treatment for both species provided in Table 2 in Supplementary Material].
+Both species learnt across all treatments (@fig-results B, D), but we did not find any difference between treatments or species in the rate of learning [mean slopes (denoted as β throughout) per treatment for both species provided in Table 1 in Supplementary Material].
 For _L.
-delicata_, hormone treatment (β~Control~ - β~CORT~ = `r format_dec(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold, deli_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(deli_ControlCold, deli_ControlHot) - c(deli_CORTCold, deli_CORTHot)), 3)`), incubation temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(c(deli_CORTHot, deli_ControlHot) - c(deli_CORTCold, deli_ControlCold)),3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((deli_ControlHot - deli_CORTHot) - (deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B).
-We similarly found no significant effects of  hormone (β~Control~ - β~CORT~ = `r format_dec(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(guich_ControlCold, guich_ControlHot) - c(guich_CORTCold, guich_CORTHot)), 3)`), incubation temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(c(guich_CORTHot, guich_ControlHot) - c(guich_CORTCold, guich_ControlCold)),3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec((mean(guich_ControlHot) - mean(guich_CORTHot)) - (mean(guich_ControlCold) - mean(guich_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L.
+delicata_, hormone treatment (β~Control~ - β~CORT~ = `r format_dec(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold, deli_CORTHot)), 3)`, 95% CI = [`r format_dec(quantile(c(deli_ControlCold, deli_ControlHot) - c(deli_CORTCold, deli_CORTHot), 0.025), 3)`, `r format_dec(quantile(c(deli_ControlCold, deli_ControlHot) - c(deli_CORTCold, deli_CORTHot), 0.975), 3)`], p~mcmc~ `r format_p(pmcmc(c(deli_ControlCold, deli_ControlHot) - c(deli_CORTCold, deli_CORTHot)), 3)`), incubation temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold)),3)`, 95% CI = [`r format_dec(quantile(c(deli_CORTHot, deli_ControlHot) - c(deli_CORTCold, deli_ControlCold), 0.025), 3)`, `r format_dec(quantile(c(deli_CORTHot, deli_ControlHot) - c(deli_CORTCold, deli_ControlCold), 0.975), 3)`], p~mcmc~ `r format_p(pmcmc(c(deli_CORTHot, deli_ControlHot) - c(deli_CORTCold, deli_ControlCold)),3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold)), 3)`, 95%CI = [`r format_dec(quantile((deli_ControlHot - deli_CORTHot) - (deli_ControlCold - deli_CORTCold), 0.025), 3)`, `r format_dec(quantile((deli_ControlHot - deli_CORTHot) - (deli_ControlCold - deli_CORTCold), 0.975), 3)`], p~mcmc~ `r format_p(pmcmc((deli_ControlHot - deli_CORTHot) - (deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B).
+We similarly found no significant effects of  hormone (β~Control~ - β~CORT~ = `r format_dec(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot)), 3)`, 95% CI = [`r format_dec(quantile(c(guich_ControlCold, guich_ControlHot) - c(guich_CORTCold, guich_CORTHot), 0.025), 3)`, `r format_dec(quantile(c(guich_ControlCold, guich_ControlHot) - c(guich_CORTCold, guich_CORTHot), 0.975), 3)`], p~mcmc~ `r format_p(pmcmc(c(guich_ControlCold, guich_ControlHot) - c(guich_CORTCold, guich_CORTHot)), 3)`), incubation temperature (β~Hot~ - β~Cold~ = `r format_dec(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold)),3)`, 95% CI = [`r format_dec(quantile(c(guich_CORTHot, guich_ControlHot) - c(guich_CORTCold, guich_ControlCold), 0.025), 3)`, `r format_dec(quantile(c(guich_CORTHot, guich_ControlHot) - c(guich_CORTCold, guich_ControlCold), 0.975), 3)`], p~mcmc~ `r format_p(pmcmc(c(guich_CORTHot, guich_ControlHot) - c(guich_CORTCold, guich_ControlCold)),3)`), or the interaction ([(β~Control-Hot~ - β~CORT-Hot~) - (β~Control-Cold~ - β~CORT-Cold~)] = `r format_dec((mean(guich_ControlHot) - mean(guich_CORTHot)) - (mean(guich_ControlCold) - mean(guich_CORTCold)), 3)`, 95%CI = [`r format_dec(quantile((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold), 0.025), 3)`, `r format_dec(quantile((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold), 0.975), 3)`], p~mcmc~ `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L.
 guichenoti_ (see @fig-results C, D).
@@
 #| fig.cap: "Results for L.
-delicata (A,B) and L.
-guichenoti (C, D).
-Panels A and C show the predicted probability of choosing the correct feeder first over trials.
+delicata [(a), (b)] and L.
+guichenoti [(c), (d)].
+Panels (a) and (c) show the predicted probability of choosing the correct feeder first over trials.
 The lines represent the mean predicted probability of choosing the correct feeder first on each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions.
 The different colours indicate the different treatments.
-Panels B and D show the distribution of the estimates of slopes per each treatment.
+Panels (b) and (d) show the distribution of the estimates of slopes per each treatment.
 The x-axis represents the slope estimate, and in the y-axis are the density of the estimates.
@@
 
-Finally, when all individuals from all the treatments were pooled together and species were compared, there were not significant differences in the estimated slopes (mean of learning slope in _L.
+Finally, when all individuals from all the treatments were pooled together and species were compared, there were no significant differences in the estimated slopes (mean of learning slope in _L.
 delicata_ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot), 0.025), 3)`, `r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot), 0.975), 3)`]; mean learning of slope in _L.
@@
 delicata_~ - β~_L.
-guichenoti_~ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot) - c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`).
+guichenoti_~ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot) - c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot), 0.025), 3)`, `r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot) - c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot), 0.975), 3)`], p~mcmc~ `r format_p(pmcmc(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot) - c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`).
 Figures for both species with the raw data were included in the Supplementary Material.
@@
 Furthermore, testing learning across different cognitive tasks could provide a more comprehensive understanding of the influence of temperature on cognition.
-In our analyses, sex was not included as a factor because lizads were not considered sexually mature, and because previous studies have found weak evidence for sex-dependent learning in many cognitive domains [@szabo2019sex].
+In our analyses, sex was not included as a factor because lizards were not considered sexually mature, and because previous studies have found weak evidence for sex-dependent learning in many cognitive domains [@szabo2019sex].
 Indeed, the impacts of temperature on learning was not sex-depedent for the Eastern three-lined skink (_Bassiana dupeyerri_) [@amiel_hotter_2012; @clark_colour_2014].
@@
 
-Despite sharing life-history traits, only L.
-delicata has proven successful in colonising various regions globally [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI], and we predicted this may relate to higher behavioural flexibility.
+Despite sharing life-history traits, only _L.
+delicata_ has proven successful in colonising various regions globally [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI], and we predicted this may relate to higher behavioural flexibility.
 Furthermore, we expected behavioural flexibility in _L.
@@
 delicata_’s success as invaders than learning and behavioural flexibility.
-Differences in exploratory behaviour is likely to be the key factor explaining why _L.
+Differences in exploratory behaviour are likely to be the key factor explaining why _L.
 delicata_ and not _L.
@@
 
+```{r, percentmeans}
+#| label: percentmeans
+# Getting the average percentual differences between means for each predictor (temp, CORT, and interaction)
+## L. delicata
+dif_mean_CORT_deli <- mean(c(deli_CORTHot, deli_CORTCold) / c(deli_ControlHot, deli_ControlCold)) * 100
+dif_mean_temp_deli <- mean(c(deli_CORTHot, deli_ControlHot) / c(deli_CORTCold, deli_ControlCold)) * 100
+## L. guichenoti
+dif_mean_CORT_guich <- mean(c(guich_CORTHot, guich_CORTCold) / c(guich_ControlHot, guich_ControlCold)) * 100
+dif_mean_temp_guich <- mean(c(guich_CORTHot, guich_ControlHot) / c(guich_CORTCold, guich_ControlCold)) * 100
+```
+
+We acknowledge that sample size may be limiting our ability to detect the small effect sizes in our experiment given the uncertainty around slope contrasts between treatments (see 95% CI of contrasts in results).
+We analysed the behaviour of 81 individuals coming from a total of `r deli_clutches` unique clutches in _L.
+delicata_ and `r guich_clutches` in _L.
+guichenoti_, yet it is challenging to do more animals than this given the logistical constraints associated with running such detailed cognitive trials.
+However, it is noteworthy that our effect sizes are very small and likely of little biological significance.
+For example, slopes of CORT-treated animals is `r format_dec(dif_mean_CORT_deli, 3)`% the slope of Controls in _L.
+delicata_ and `r format_dec(dif_mean_CORT_guich, 3)`% in _L.
+guichenoti_, while the slope in hot-incubated lizards is `r format_dec(dif_mean_temp_deli, 3)`% the slope of those incubated at cold temperatures in _L.
+delicata_ and `r format_dec(dif_mean_temp_guich, 3)`% in _L.
+guichenoti_.
+
 In conclusion, our results indicate that lizards performed the reversal learning task, a measure of behavioural flexibility, at similar rates, with no discernible differences between treatments or species.
-These findings contrast with our initial predictions and suggest that behavioural flexibility in both species is robust to insults (at least for temperature and GCs) during early stages of development.
+These findings contrast with our initial predictions and suggest that behavioural flexibility in both species is robust to insults (at least from temperature and GCs) during early stages of development.
 Furthermore, our results indicate that other aspects of the biology of _L.
@@
 #### Estimates of reversal learning slopes for all the different treatments per each task, specie, and group.
-Table 1.
-Estimates of Reversal learning slope for all the different treatments per each task, specie, and group.
-Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
-All pmcmc tested the hypothesis that the mean equals zero.
-In bold, those values that are significant (p~mcmc~ <0.05).
+Table 1. Estimates of Reversal learning slope for all the different treatments per each task, specie, and group.
 ```{r, tbl-data, results='asis'}
@@
 
+Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
+All pmcmc tested the hypothesis that the mean equals zero.
+In bold, those values that are significant (p~mcmc~ <0.05).
+
 ```{r, results='asis', echo=FALSE}
@@
 
-Table 2.
-Estimates of Reversal learning slope for all the different treatments per each task, species, and group.
-Here we included only those individuals who made the right choice in 8 out of the last 10 trials in the previous associative task.
-Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
-All pmcmc tested the hypothesis that the mean equals zero.
-In bold, those values that are significant (pmcmc <0.05)
+Table 2. Estimates of Reversal learning slope for all the different treatments per each task, species, and group.
 
@@
 ```
+
+Here we included only those individuals who made the right choice in 8 out of the last 10 trials in the previous associative task.
+Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean.
+All pmcmc tested the hypothesis that the mean equals zero.
+In bold, those values that are significant (pmcmc <0.05).
 

### 2024-10-31 R/func.r

@@ -284,13 +284,15 @@ df_plotBD2 <- function(sp){
 plotting <- function(sp, df_prob, df_violin, df_points){
   # Specify labels depending on species and relevel the factor treatment for the legend
   if(sp == "deli"){
-    lab <- c("A", "B")
+    lab1 <- "(a)"
+    lab2 <- "(b)"
     df_violin$Treatment <- factor(df_violin$Treatment,
       levels = c("Control-Hot (n =  12 )", "CORT-Hot (n =  12 )", "Control-Cold (n = 12 )", "CORT-Cold (n = 11 )"))
     img <- readPNG("./Others/Deli.png")
     note <- paste("L. delicata")
   } else if (sp == "guich"){
-    lab <- c("C", "D")
+    lab1 <- "(c)"
+    lab2 <- "(d)"
     df_violin$Treatment <- factor(df_violin$Treatment,
       levels = c("Control-Hot (n =  10 )", "CORT-Hot (n =  10 )", "Control-Cold (n = 7 )", "CORT-Cold (n = 10 )"))
     img <- readPNG("./Others/Guich.png")
@@ -311,7 +313,8 @@ plotting <- function(sp, df_prob, df_violin, df_points){
     axis.title = element_text(size = 12, family = "Times"),
     axis.text = element_text(size = 10, family = "Times"),
     legend.position = "none"
-  ) 
+  ) + 
+  annotate("text", x = 2, y = 0.88, label = lab1, size = 5.5, hjust = 0.5, vjust = 1)
   #
   # Second part of the plot (B, D), the slope estimates of each treatment
   plot2 <- ggplot(df_violin, aes(x = Treatment, y = Value, fill = Treatment)) +
@@ -320,7 +323,7 @@ plotting <- function(sp, df_prob, df_violin, df_points){
   geom_point(data = df_points, aes(y = Mean, x = Treatment), position = position_dodge(width = 0.75), color = "black", fill = "black", size = 3) +
   geom_segment(data = df_points, aes(y = Mean - SD, yend = Mean + SD, x = Treatment, xend = Treatment), size = 1.5, color = "black") +
   geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
-  ylim(-0.015, max(df_violin$Value)) +
+  ylim(-0.025, max(df_violin$Value)) +
   coord_flip() +
   theme_classic() +
   labs(y = "Slope estimates", x = "Treatments") +
[…]

### 2024-11-09 ms.qmd
Updates

@@
   }
+
+a <- n_list$delicata_CORT_Cold + n_list$delicata_CORT_Hot + n_list$delicata_Control_Cold + n_list$delicata_Control_Hot + n_list$guichenoti_CORT_Cold + n_list$guichenoti_CORT_Hot + n_list$guichenoti_Control_Cold + n_list$guichenoti_Control_Hot
+
+n_list_2 <- list()
+#
+b <- unique(data$lizard_id)
 ```
@@
 We started with 96 lizards, 48 per species and 12 per treatment per species.
-However, our final sample size was 81 due to natural mortality (n = 11), failure to complete the training stage (n = 1), or because the number of failed tasks (see above) was higher than 15 (n = 3).
+However, our final sample size was 84 due to natural mortality (n = 11), failure to complete the training stage (n = 1), or because the number of failed tasks (see above) was higher than 15 (n = 0).
 The final sample sizes per treatment and species are listed in @fig-results.
@@
 
-```{r, fig_rawdata}
-#| label: fig_rawdata
+```{r, fig-rawdata}
+#| label: fig-rawdata
 #| fig.cap: "Probability of choosing correctly over trials for each of the treatments and species.

### 2024-11-09 .vdoc.r

@@ -1,0 +1,805 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: setup
+pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+cat("\\newpage")
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: fig-Methods
+#| fig.cap: "Experimental design of early environment manipulation and learning tasks. Panel A represents the early environment manipulation for both species. Panel B shows the habituation phase with the respective three different stages. And panel C represents the associative and reversal tasks; white lids show the ramps where the food reward was not accessible."
+
+knitr::include_graphics("./Others/BEHFLEX_FIG_1.png")
+
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#| label: cleandata
+# Obtain the main df using "./R/1_data_process.R"
+source(here("R", "1_data_process.R"))
+#
+#
+#
+#| label: sampleSize
+# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
+source(here("R", "func.R"))
+#
+specie <- c("delicata", "guichenoti")
+hormone <- c("CORT", "Control")
+temperature <- c("Cold", "Hot")
+#
+n_list <- list()
+#
+for(i in 1:length(specie)){
+  for(k in 1:length(hormone)){
+    for(l in 1:length(temperature)){
+      n_list[[paste(specie[i], hormone[k], temperature[l], sep = "_")]] <- sample(clean_df, specie[i], hormone[k], temperature[l])
+      }
+    }
+  }
+
[…]

### 2024-11-09 ms.qmd
Update ms.qmd

@@
 We started with 96 lizards, 48 per species and 12 per treatment per species.
-However, our final sample size was 84 due to natural mortality (n = 11), failure to complete the training stage (n = 1), or because the number of failed tasks (see above) was higher than 15 (n = 0).
+However, our final sample size was 81 due to natural mortality (n = 11), failure to complete the training stage (n = 1), or because the number of failed tasks (see above) was higher than 15 (n = 3).
 The final sample sizes per treatment and species are listed in @fig-results.

### 2024-11-27 ms.qmd
Updates

@@
 We started with 96 lizards, 48 per species and 12 per treatment per species.
-However, our final sample size was 81 due to natural mortality (n = 11), failure to complete the training stage (n = 1), or because the number of failed tasks (see above) was higher than 15 (n = 3).
+However, our final sample size was 84 due to natural mortality (n = 11) or failure to complete the training stage (n = 1).
 The final sample sizes per treatment and species are listed in @fig-results.

### 2025-01-12 ms.qmd
updates

@@
 ^1^ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2601, Australia  
-^2^ Flinder's University, College of Science and Engineering, Bedford Park, SA 5042, Australia  
-^3^ Melbourne University, Melbourne, VIC 3000, Australia  
-^4^ University of Wollongong, Wollongong, NSW 2500, Australia  
+^2^ College of Science and Engineering, Flinders University, Bedford Park, SA 5001, Australia  
+^3^ School of BioSciences, The University of Melbourne, Melbourne, VIC 3000, Australia  
+^4^ School of Science, University of Wollongong, Wollongong, NSW 2500, Australia  
 ^5^ Université de Lille, Lille 59000, France  
@@
 guichenoti_).
-Both species have similar life-histories and overlapping distributions [@chapple_know_2011; @chapple_biology_2014], but only _Lampropholis delicata_ has been successful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI].
+Both species have similar life-histories and overlapping distributions [@chapple_know_2011; @chapple2015deliinvLHI], but only _Lampropholis delicata_ has been successful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI].
 Previous studies exploring behavioural differences between the two species have found _L.
@@
 delicata_ lays one clutch per year, while _L.
-guichenoti_ lays two [@chapple_know_2011; @chapple_biology_2014].
+guichenoti_ lays two [@chapple_know_2011; @chapple2015deliinvLHI].
 Since eggs were collected during half of the breeding season, clutches likely come from different mothers.
@@
 # Save the plot
-ggsave("./output/figures/plot_raw.png", plot=plot_raw, width = 25, height = 18, units = "cm", dpi = 600)
-knitr::include_graphics("./output/figures/plot_raw.png")
+ggsave("./output/Figs_supplementary/Figure_S1.png", plot=plot_raw, width = 25, height = 18, units = "cm", dpi = 600)
+knitr::include_graphics("./output/Figs_supplementary/Figure_S1.png")
 ```
@@
 bayes_R2(mod_deli)
-plot(mod_deli)
+plot_mod_deli_list <- plot(mod_deli)
+#
+plot_mod_deli_1 <- plot_mod_deli_list[[1]]
+plot_mod_deli_2 <- plot_mod_deli_list[[2]]
+plot_mod_deli_3 <- plot_mod_deli_list[[3]]
+#
+plot_mod_deli <- plot_grid(plot_mod_deli_1, plot_mod_deli_2, plot_mod_deli_3, ncol = 1)
+ggsave("./output/Figs_supplementary/Figure_S2.png", plot=plot_mod_deli, width = 20, height = 35, units = "cm", dpi = 600, bg = "white")
+knitr::include_graphics("./output/Figs_supplementary/Figure_S2.png")
 ```
@@
 bayes_R2(mod_guich)
-plot(mod_guich)
+plot_mod_guich_list <- plot(mod_guich)
+#
+plot_mod_guich_1 <- plot_mod_guich_list[[1]]
+plot_mod_guich_2 <- plot_mod_guich_list[[2]]
+plot_mod_guich_3 <- plot_mod_guich_list[[3]]
+#
+plot_mod_guich <- plot_grid(plot_mod_guich_1, plot_mod_guich_2, plot_mod_guich_3, ncol = 1)
+ggsave("./output/Figs_supplementary/Figure_S3.png", plot=plot_mod_guich, width = 20, height = 35, units = "cm", dpi = 600, bg = "white")
+knitr::include_graphics("./output/Figs_supplementary/Figure_S3.png")
 ```
@@
 plot_age <- plot_grid(plot_age_deli, plot_age_guich, ncol = 1)
-ggsave("./output/figures/plot_age.png", plot=plot_age, width = 25, height = 18, units = "cm", dpi = 600)
-knitr::include_graphics("./output/figures/plot_age.png")
-```
+ggsave("./output/Figs_supplementary/Figure_S4.png", plot=plot_age, width = 25, height = 18, units = "cm", dpi = 600)
+knitr::include_graphics("./output/Figs_supplementary/Figure_S4.png")
+```
